### 2021-11-29 Algebraic geometry/submission.tex
Created basic files

\documentclass{scrartcl}

\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[ngerman]{babel}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{listings}
\usepackage[style=english]{csquotes}
\usepackage[language=english, backend=biber, style=alphabetic, sorting=nyt]{biblatex}

\addbibresource{bibliography.bib}

\title{Miniproject - Algebraic Geometry}
\author{Simon Pohmann}
\date{}

\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\I}{\mathbb{I}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\divides}{\ | \ }
\newcommand\restr[2]{{
    \left.\kern-\nulldelimiterspace
    #1
    \vphantom{\big|}
    \right|_{#2}
}}

\begin{document}
\maketitle

\printbibliography
\end{document}

### 2021-11-29 Analytic number theory/submission.tex
Created basic files
Added ANT to the right file and extended it somewhat

--- 2021-11-29 Algebraic geometry/submission.tex
@@
 \usepackage{listings}
+\usepackage{amsthm}
 \usepackage[style=english]{csquotes}
@@
 
-\title{Miniproject - Algebraic Geometry}
+\title{Miniproject - Analytic Number Theory}
 \author{Simon Pohmann}
@@
 
+\newcommand{\primes}{\mathbb{P}}
 \newcommand{\R}{\mathbb{R}}
@@
 \newcommand{\C}{\mathbb{C}}
-\newcommand{\I}{\mathbb{I}}
-\newcommand{\V}{\mathbb{V}}
 \newcommand{\divides}{\ | \ }
+\newcommand{\units}{\times}
+\newcommand{\sgn}{\mathrm{sgn}}
 \newcommand\restr[2]{{
@@
 
+\newtheorem{definition}{Definition}
+\newtheorem{lemma}[definition]{Lemma}
+\newtheorem{proposition}[definition]{Proposition}
+\newtheorem{example}[definition]{Example}
+
 \begin{document}
@@
 
+We use the convention that $\N = \{ n \in \Z \ | \ n \geq 0 \}$.
+
+\section{Part 1}
+
+For convenience, we include the definition of a Dirichlet character from the task description first.
+\begin{definition}
+    Let $q \geq 2$, then a \emph{Dirichlet character (mod $q$)} is a function $\chi: \N \to \C$ such that
+    \begin{itemize}
+        \item $\chi$ is completely multiplicative, so $\chi(a)\chi(b) = \chi(ab)$
+        \item $\chi$ is periodic modulo $q$, so $\chi(n + q) = \chi(n)$
+        \item $\chi(n) \neq 0$ if and only if $n \perp q$
+    \end{itemize}
+\end{definition}
+First, we will give another characterization of Dirichlet characters.
+\begin{lemma}[Characterization of Dirichlet characters]
+    \label{prop:characterization_dirichlet_character}
+    We have a one-to-one correspondence between Dirichlet characters mod $q$ and group homomorphisms $(\Z/q\Z)^\units \to \C^\units$ via
+    \begin{align*}
+        \{ \chi: (\Z/q\Z)^\units \to \C^\units \ | \ \chi \ \text{group hom} \} &\to \{ \chi: \N \to \C \ | \ \chi \ \text{Dirichlet character mod $q$} \} \\
+        \chi &\mapsto \tilde{\chi} := \left( \N \to \C, \ n \mapsto \begin{cases}
+            \chi([n]_q) & \text{if $n \perp q$} \\
+            0 & \text{otherwise}
+        \end{cases} \right)
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    First of all, we show that the map is well-defined. Let $\chi: (\Z/q\Z)^\units \to \C^\units$ be a (multiplicative) group homomorphism, and we show that $\tilde{\chi}$ is a Dirichlet character.
+
+    Note that property (ii) and (iii) directly follow from the definition, as $\tilde{\chi}(n)$ only depends on the value of $n \mod q$.
+    So consider some $a, b \in \N$.
+    If both $a \perp q$ and $b \perp q$ then
+    \begin{equation*}
+        \tilde{\chi}(a)\tilde{\chi}(b) = \chi([a])\chi([b]) = \chi([ab]) = \tilde{\chi}(ab)
+    \end{equation*}
+    as also $ab \perp q$.
+
+    On the other hand, if $a \not\perp q$ or $b \not\perp q$ have $\chi(a) = 0$ resp. $\chi(b) = 0$.
+    We also have in this case that $ab \not\perp q$ and so
+    \begin{equation*}
+        \chi(a)\chi(b) = 0 = \chi(ab)
+    \end{equation*}
+    Now it is left to show that the correspondence is a bijection.
+    Clearly, if $\chi \neq \xi$ then $\chi(x) \neq \xi(x)$ for some $x \in (\Z/q\Z)^\units$ and so $\tilde{\chi}(n) \neq \tilde{\xi}(n)$ for some representative $n \in \N$ of $x$.
+
+    To show surjectivity, consider some Dirichlet character $f: \N \to \C$ and construct a group homomorphism $\chi: (\Z/q\Z)^\units \to \C^\units$. 
+    For each $x \in (\Z/q\Z)^\units$, there is a representative $n \in \N$ of $x$ and as $f(n)$ does not depend on the choice of $n$, we may define $\chi(x) := f(n)$.
+    Note that as $x \in (\Z/q\Z)^\units$, we find $n \perp q$ and so $f(n) \neq 0$, i.e. $f(n) \in \C^*$.
+    Then clearly for $a, b \in (\Z/q\Z)^*$ with representatives $n, m \in \N$ have
+    \begin{equation*}
+        \chi(ab) = f(nm) = f(n)f(m) = \chi(a)\chi(b)
+    \end{equation*}
+    So $\chi$ is a well-defined group homomorphism and we obviously have $\tilde{\chi} = f$.
+\end{proof}
+\begin{example}[Part 1 (i)]
+    \label{ex:nontrivial_dirichlet_character_mod_4}
+    The function
+    \begin{equation*}
+        f: \N \to \C, \quad n \mapsto \begin{cases}
+            0 & \text{if $n \equiv 0, 2 \mod 4$} \\
+            1 & \text{if $n \equiv 1 \mod 4$} \\
+            -1 & \text{if $n \equiv 3 \mod 4$}
+        \end{cases}
+    \end{equation*}
+    is a Dirichlet character.
+\end{example}
+\begin{proof}
+    This follows directly from Lemma~\ref{prop:characterization_dirichlet_character}, as $f = \tilde{\chi}$ for the group homomorphism
+    \begin{equation*}
+        \chi: (\Z/4\Z)^\units = \{ 1, 3 \} \to \C^*, \quad 1 \mapsto 1, \ 3 \mapsto -1
+    \end{equation*}
+    (this is a group homomorphism, as $3^2 = 9 \equiv 1 \mod 4$)
+\end{proof}
+Now we want to define Dirichlet series of Dirichlet characters.
+\begin{proposition}
+    For a Dirichlet character $\chi: \N \to \C$ and some $\epsilon > 0$, the series
+    \begin{equation*}
+        L(s, f) := \sum_{n \geq 1} f(n) n^{-s}
+    \end{equation*}
+    converges uniformly on $\Re(s) \geq 1 + \epsilon$.
+    We will call it the Dirichlet series of $\chi$.
+\end{proposition}
+\begin{proof}
+    By Lemma~\ref{prop:characterization_dirichlet_character}, we know that $\chi$ corresponds to a group homomorphism $\chi': (\Z/q\Z)^\units \to \C^\units$ such that $\chi(\N) = \chi((\Z/q\Z)^*) \cup \{ 0 \} \subseteq \C$ is a finite subset of $\C$.
+    Hence, there is $C > 0$ with $|\chi(n)| \leq C$ for all $n \in \N$, and it follows that
+    \begin{equation*}
+        \sum_{1 \leq n \leq X} \left| f(n) n^{-s} \right| \leq \sum_{1 \leq n \leq X} C \left| n^{-s} \right| \leq C \sum_{1 \leq n \leq X} n^{-1 - \epsilon}
+    \end{equation*}
+    which is finite.
+\end{proof}
+\begin{proposition}[Part 1 (ii)]
+    \label{prop:dirichlet_series_at_one}
+    Let $\chi: (\Z/q\Z)^\units \to \C^\units$ be a group homomorphism. Then for the associated Dirichlet character $\tilde{\chi}$ we have that
+    \begin{equation*}
+        \lim_{s \to 1^+} L(s, \tilde{\chi}) \ \text{exists} \ \Leftrightarrow \ \sum_{x \in (\Z/q\Z)^\units} \chi(x) = 0
+    \end{equation*}
+    In this case, have that
+    \begin{equation*}
+        \lim_{s \to 1^+} L(s, \tilde{\chi}) = \sum_{n \geq 1} f(n) n^{-s}
+    \end{equation*}
+    where the right sum converges (but not absolutely) for $\Re(s) > 0$.
+\end{proposition}
+\begin{proof}
+    Let $c = \sum_{x \in (\Z/q\Z)^\units} \chi(x)$.
+    For the direction $\Rightarrow$ assume that $c \neq 0$.
+    Then have for $\Re(s) > 1$ that
+    \begin{align*}
+        \sgn(c) \sum_{n \geq 1} \tilde{\chi}(n) n^{-s} &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \sgn(c) \tilde{\chi}(qn + k) (qn + k)^{-s} \\
+        &\geq \sum_{n \geq 1} \ \sum_{0 \leq k < 1}\sgn(c) \tilde{\chi}(qn + k) (qn + n)^{-s} \\
+        &= \sum_{n \geq 1} \sgn(c) (qn + n)^{-s} \underbrace{\sum_{0 \leq k < q} \tilde{\chi}(qn + k)}_{= c} \\
+        &\geq \frac {|c|} {(q + 1)^s} \sum_{n \geq 1} n^{-s} = \frac {|c|} {(q + 1)^s} \zeta(s)
+    \end{align*}
+    which clearly has a pole at $s = 1$. Hence $\lim_{s \to 1^+} L(s, \tilde{\chi})$ cannot exist.
+
+    For the other direction, assume that $c = 0$.
+    Again, have for $\Re(s) > 1$ that
+    \begin{align*}
+        \sum_{n \geq 1} \tilde{\chi}(n) n^{-s} &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \tilde{\chi}(qn + k) (qn + k)^{-s} \\
+        &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \tilde{\chi}(qn + k) \Bigl( (qn)^{-s} + (qn + k)^{-s} - (qn)^{-s} \Bigr)
+    \end{align*}
+    Observe that by Bernoulli's inequality, have
+    \begin{align*}
+        (qn)^{-s} - (qn + k)^{-s} &= \frac {(qn)^s - (qn + k)^s} {(q^2n^2 + qnk)^s} = (qn)^{s} \frac {1 - (1 + k(qn)^{-1})^s} {(q^2n^2 + qnk)^s} \\
+        &\leq (qn)^s \frac {sk(qn)^{-1}} {(q^2n^2 + qnk)^s} = \frac {sk} {qn(qn + k)^s} = O(sn^{-s - 1})
+    \end{align*}
+    As $\chi((\Z/q\Z)^\units) \subseteq \C$ is finite, find $C > 0$ with $|\tilde{\chi}(n)| \leq C$ for all $n \in \N$. Then
+    \begin{align*}
+        \sum_{n \geq X} \tilde{\chi}(n) n^{-s} &= O(qCX^{-s}) + \sum_{n \geq X/q} \ \sum_{0 \leq k < q} \tilde{\chi}(qn + k) \Bigl( (qn)^{-s} + O(sn^{-s - 1}) \Bigr) \\
+        &= O(qCX^{-s}) + \sum_{n \leq X/q} \Bigl( (qn)^{-s} c + \sum_{0 \geq k < q} O(Csn^{-s - 1}) \Bigr) = \\
+        &= O(qCX^{-s}) + 0 + O\Bigl( Cqs \sum_{n \geq X/q} n^{-s - 1} \Bigr) \\
+        &\leq O(qCX^{-s}) + O\Bigl( Cqs\zeta(s + 1) \Bigr)
+    \end{align*}
+    which is well-defined and finite for $\Re(s) > 0$.
+    Further, the expression converges uniformly (as a function in $s$ on a neighborhood of $1$) to $0$ as $X \to \infty$. 
+    So
+    \begin{equation*}
+        \sum_{n < X} \tilde{\chi}(n) n^{-s} \quad \text{converges uniformly to} \quad \sum_{n \geq 1} \tilde{\chi}(n) n^{-s}
+    \end{equation*}
+    as $X \to \infty$ (on a neighborhood of $1$). 
+    Thus the limit is continuous and a continuation of $L(s, \tilde{\chi})$ which is defined on $\Re(s) > 1$.
+    From this it follows that $\lim_{s \to 1} L(s, \tilde{\chi})$ exists and is equal to $\sum_n \tilde{\chi}(n) n^{-s}$.
+\end{proof}
+Applied to our example, we find
+\begin{example}
+    Let $f: \N \to \C$ be the Dirichlet character from Example~\ref{ex:nontrivial_dirichlet_character_mod_4} with corresponding group homomorphism $\chi: (\Z/4\Z)^\units \to \C$.
+    Then
+    \begin{equation*}
+        \sum_{x \in (\Z/4\Z)^*} \chi(x) = \chi(1) + \chi(3) = 1 - 1 = 0
+    \end{equation*}
+    and so by Lemma~\ref{prop:dirichlet_series_at_one} the limit $\lim_{s \to 1^+} L(s, f)$ exists.
+    The lemma further yields that
+    \begin{align*}
+        \lim_{s \to 1} L(s, f) &= \sum_{n \geq 1} f(n) n^{-1} = \sum_{n \geq 0} \frac {f(4n + 1)} {4n + 1} + \frac {f(4n + 3)} {4n + 3} = \sum_{n \geq 0} \frac 1 {4n + 1} - \frac 1 {4n + 3} \\
+        &= 2 \sum_{n \geq 0} \frac 1 {(4n + 1)(4n + 3)} > 0
+    \end{align*}
+    is positive.
+\end{example}
+
 \printbibliography

### 2021-11-30 Analytic number theory/submission.tex
added proof of dirichlets prime number theorem

@@
 \usepackage[T1]{fontenc}
-\usepackage[ngerman]{babel}
+\usepackage[english]{babel}
 \usepackage{amsmath}
@@
 \newtheorem{example}[definition]{Example}
+\newtheorem{corollary}[definition]{Corollary}
 
@@
 \maketitle
-
 We use the convention that $\N = \{ n \in \Z \ | \ n \geq 0 \}$.
+Further, we write $a \divides b$ if $a$ divides $b$ and $a \perp b$ if $a$ and $b$ are coprime.
+Finally, let $\primes$ be the set of prime numbers in $\N$.
 
@@
 \end{proof}
-\begin{proposition}[Part 1 (ii)]
+\begin{proposition}
     \label{prop:dirichlet_series_at_one}
@@
 Applied to our example, we find
-\begin{example}
+\begin{example}[Part 1 (ii)]
     Let $f: \N \to \C$ be the Dirichlet character from Example~\ref{ex:nontrivial_dirichlet_character_mod_4} with corresponding group homomorphism $\chi: (\Z/4\Z)^\units \to \C$.
@@
     is positive. 
+    Wolfram Alpha \cite{wolfram_alpha} can give an explicit value to this sum, using the digamma function $\psi$. Namely
+    \begin{equation*}
+        \sum_{x \in (\Z/4\Z)^\units} f(n) n^{-1} = \frac 1 4 (\psi(\frac 7 4) - \psi(\frac 5 4))
+    \end{equation*}
+    which seems to be $\frac 1 4$.
 \end{example}
+Now we want to study the series
+\begin{equation*}
+    \sum_p f(p) p^{-s}
+\end{equation*}
+For this, we are first interested in how many primes $\equiv 1, 3 \mod 4$ there are.
+\begin{lemma}
+    \label{prop:prime_factor_3_mod_4}
+    Let $n \equiv 3 \mod 4$. Then $n$ has a prime factor $p \equiv 3 \mod 4$.
+\end{lemma}
+\begin{proof}
+    Use induction on $n$.
+    If $n = 3$, the claim is trivial. 
+    So let $n > 3$. If $n$ is prime, the claim again follows.
+    Otherwise, have $n = ab$ with nontrivial divisors $a, b$.
+    However, $3 \equiv n$ is not a square modulo $4$, so find that $a \not\equiv b \mod 4$.
+    As both $a$ and $b$ must be odd, we see that either $a \equiv 3 \mod 4$ or $b \equiv 3 \mod 4$ and the claim follows by the induction hypothesis.
+\end{proof}
+\begin{corollary}[Part 1 (iii)]
+    There are infinitely many primes $p$ with $p \equiv 3 \mod 4$.
+\end{corollary}
+\begin{proof}
+    It suffices to show that there is a prime number $q \equiv 3 \mod 4$ with $q \geq N$ for every $N \in \N$.
+    Let
+    \begin{equation*}
+        P := \prod_{p \in \primes, \ p \leq N} p
+    \end{equation*}
+\end{proof}
+For the case of primes $\equiv 1 \mod 4$, I have remembered the two-square theorem and its connection to primes in the ring $\Z[i]$ of Gaussian integers, and somehow my train of thoughts went into Algebraic Number Theory.
+After some research, I have found an exercise in \cite[Chapter I, §10]{neukirch} that requires the reader to prove the following proposition.
+\begin{proposition}
+    Let $q \geq 3$ be an integer.
+    Then there are infinitely many primes $p$ with $p \equiv 1 \mod q$.
+\end{proposition}
+\begin{proof}
+    Assume there were only finitely many such primes $p_i$, then we have their product $P = \prod_i p_i \in \Z$.
+    Consider now the $q$-th cyclotomic polynomial $\Phi_q$.
+    Clearly $\Phi_q(qPX) - 1 \in \Q[X]$ has at most $\phi(q)$ zeros, so there exists some $x \in \Z$ with $\Phi_q(qPx) \neq 1$ (this ``Ansatz'' was given as a hint).
+
+    Let now $K = \Q(\omega_q)$ be the $q$-th cyclotomic number field with a primitive $q$-th root of unity $\omega_q$ (i.e. $\Phi_q(\omega_q) = 0$).
+    Let further $\mathcal{O} \subseteq K$ be the ring of integral elements over $\Z$ in $K$.
+    The prime decomposition law for Dedekind ring extension \cite[Chapter I, Prop 8.3]{neukirch} tells us that for a prime $p$, the ideal $(p)$ is reducible in $\mathcal{O}$ if and only if $\Phi_q \mod p$ is reducible.
+    As $(\Z/p\Z)^\units$ is cyclic of order $p - 1$, this is the case if and only if $q \divides p - 1$, i.e. $p \equiv 1 \mod q$.
+
+    Now consider the element $\alpha = \omega_q - xqP \in \mathcal{O}$. Then
+    \begin{align*}
+        N_{K/\Q}(\alpha) &= \prod_{\sigma: K \to \C \ \text{$\Q$-field homomorphism}} \sigma(\omega_q - xqP) \\
+        &= \prod_{\sigma} (\sigma(\omega_q) - xqP) = \mathrm{MiPo}_\Q(\omega_q)(xqP) = \Phi_q(xqP) \neq 1
+    \end{align*}
+    as $\mathrm{MiPo}_\Q(\omega_q) = \prod_\sigma (\sigma(\omega_q) - X)$.
+    Hence, $\alpha$ is not a unit in $\mathcal{O}$.
+    On the other hand, $(\alpha)$ is coprime to $(p_i)$ for each $p_i$, as 
+    \begin{equation*}
+        \omega_q = \alpha - xqP \in (\alpha) + (p_i) \quad \text{and} \quad \omega_q \in \mathcal{O}^\units
+    \end{equation*}
+    By our assumption, the only prime ideals in $\mathcal{O}$ are the prime ideal factors of $(p_i)$ and $(p)$ for $p \neq p_i$.
+    Thus, the prime ideal factorization of $(\alpha)$ consists only of prime ideals $(p), p \neq p_i$ and it follows that $(\alpha) = (n)$ for some integer $n \geq 2$.
+    As $\omega_q$ and $xqP \in \Z$ are $\Q$-linearly independent, we see that $n \divides \omega_q$ and $n \divides xqP$.
+    However, the former is a contradiction, as $\omega_q \in \mathcal{O}^\units$ is a unit and no $n \geq 2$ is a unit.
+\end{proof}
+The book also mentions that the general case can be proven by using L-series in algebraic number fields.
+\begin{corollary}[Part 1 (iii)]
+    There are infinitely many primes $p$ with $p \equiv 1 \mod 4$.
+\end{corollary}
 

### 2021-11-30 Analytic number theory/submission.tex
Extedned ANT

@@
 
+\theoremstyle{definition}
 \newtheorem{definition}{Definition}
 \newtheorem{lemma}[definition]{Lemma}
+\newtheorem{remark}[definition]{Remark}
 \newtheorem{proposition}[definition]{Proposition}
@@
 
-\section{Part 1}
+\section{Part I}
 
@@
 \end{proof}
-\begin{example}[Part 1 (i)]
+For simplicity of notation we sometimes will identify a Dirichlet character and its group homomorphism if it is always clear which one is meant.
+\begin{example}[Ex (i)]
     \label{ex:nontrivial_dirichlet_character_mod_4}
@@
 Applied to our example, we find
-\begin{example}[Part 1 (ii)]
+\begin{example}[Ex (ii)]
     Let $f: \N \to \C$ be the Dirichlet character from Example~\ref{ex:nontrivial_dirichlet_character_mod_4} with corresponding group homomorphism $\chi: (\Z/4\Z)^\units \to \C$.
@@
 \end{proof}
-\begin{corollary}[Part 1 (iii)]
+\begin{corollary}[Ex (iii)]
     There are infinitely many primes $p$ with $p \equiv 3 \mod 4$.
@@
 \begin{proof}
-    It suffices to show that there is a prime number $q \equiv 3 \mod 4$ with $q \geq N$ for every $N \in \N$.
-    Let
+    Assume there were only finitely many, say $p_1, ..., p_N$.
+    Let $P := p_1 ... p_N$ if $N$ is even and $P := p_1^2 p_2 ... p_N$ if $N$ is odd.
+    Then
     \begin{equation*}
-        P := \prod_{p \in \primes, \ p \leq N} p
+        P \equiv 3^{2 \lceil \frac N 2 \rceil} \equiv 1^{\lceil \frac N 2 \rceil} = 1 \mod 4
     \end{equation*}
+    Thus, by Lemma~\ref{prop:prime_factor_3_mod_4}, $P + 2$ has a prime factor $q \equiv 3 \mod 4$.
+    However, $q \neq p_i$ as $p_i \perp P + 2$ for all $i$ (if $p_i \divides P + 2$, then $p_i \divides P + 2 - P = 2$, a contradiction).
+    This contradicts our assumption.
 \end{proof}
@@
 \begin{proposition}
+    \label{prop:primes_1_mod_q}
     Let $q \geq 3$ be an integer.
@@
 The book also mentions that the general case can be proven by using L-series in algebraic number fields.
-\begin{corollary}[Part 1 (iii)]
+\begin{corollary}[Ex (iii)]
     There are infinitely many primes $p$ with $p \equiv 1 \mod 4$.
 \end{corollary}
+\begin{proof}
+    This is just a special case of Prop.~\ref{prop:primes_1_mod_q}.
+\end{proof}
+\begin{example}[Ex (iii)]
+    Using a computer, we can also study the actual frequency of prime numbers $\equiv 1, 3 \mod 4$ among e.g. the first $10^8$ integers.
+    This seems to indicate that both numbers are asymptotically equal.
+    For example, there are 332180 primes $\equiv 1 \mod 4$ and 332398 primes $\equiv 3 \mod 4$ smaller than $10^8$.
+    To find these numbers, the following python code was used.
+    \lstinputlisting[language = python]{./primes.py}
+\end{example}
+
+\section{Part II}
+We have already shown that Dirichlet characters are, in principle, group homomorphisms $(\Z/q\Z)^\units \to \C^\units$.
+If we now assume $q$ to be prime, we get an even nicer characterization.
+\begin{corollary}[Ex (i)]
+    \label{prop:dirichlet_character_image_group}
+    Let $\chi, \chi': \N \to \C$ be Dirichlet characters mod $q$ and $r$ a primitive root modulo $q$.
+    If $\chi(r) = \chi'(r)$, then $\chi = \chi'$.
+    Further, have that $\chi(n)^{q - 1} = 1$ for all $n \in \N$ with $n \perp q$.
+\end{corollary}
+\begin{proof}
+    The properties follow directly from Lemma~\ref{prop:characterization_dirichlet_character}.
+    Let $f, f': (\Z/q\Z)^\units \to \C^\units$ be the associated group homomorphisms of $\chi, \chi'$ as in Lemma~\ref{prop:characterization_dirichlet_character}.
+    If $f(r) = \chi(r) = \chi'(r) = f'(r)$ then clearly $f = f'$, as these are group homomorphisms and $\langle r \rangle = (\Z/q\Z)^\units$.
+    Hence $\chi = \chi'$.
+
+    Further, have for $n \in \N$ with $n \perp q$ that $n \in (\Z/q\Z)^\units$ and thus
+    \begin{equation*}
+        n^{q - 1} = n^{\phi(q)} = n^{|(\Z/q\Z)^\units|} = 1 
+    \end{equation*}
+    As $f$ is a group homomorphism, find
+    \begin{equation*}
+        \chi(n)^{q - 1} = f(n)^{q - 1} = f(n^{q - 1}) = f(1) = 1
+    \end{equation*}
+\end{proof}
+This correspondence also works in the other direction.
+\begin{corollary}[Ex (ii)]
+    \label{prop:dirichlet_character_primitive_root}
+    Let $\omega \in \C$ be a $(q - 1)$-th root of unity, i.e. $\omega^{q - 1} = 1$ and let $r \in (\Z/q\Z)^\units$ be a primitive root.
+    Then
+    \begin{equation*}
+        g: \N \to \C, \quad n \mapsto \begin{cases}
+            \omega^{\log_r n} & \text{if $n \perp q$} \\
+            0 & \text{otherwise}
+        \end{cases}
+    \end{equation*}
+    is a well-defined Dirichlet character.
+\end{corollary}
+\begin{proof}
+    Follows again directly from Lemma~\ref{prop:characterization_dirichlet_character}, as $r \mapsto \omega$ induces a unique group homomorphism $(\Z/q\Z)^\units \to \C^\units$.
+    The associated Dirichlet character is obviously $g$.
+\end{proof}
+Note that the image of a group homomorphism $\chi: (\Z/q\Z)^\units \to \C^\units$ is a subgroup of $\C^\units$.
+Using Corollary~\ref{prop:dirichlet_character_image_group}, we can describe it quite concretely.
+\begin{proposition}
+    Let $\chi: \N \to \C$ be a Dirichlet character with group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$.
+    Then $\mathrm{im}f \leq S$ is a subgroup where $S = \{ \omega_q^k \ | \ k \in \Z \}$ is the group of $q$-th roots of unity.
+
+    It is a fact from Algebra that $S \cong (\Z/q\Z)^\units$, hence Dirichlet characters modulo a prime $q$ are in 1-to-1 correspondence with the endomorphism monoid $\mathrm{End}((\Z/q\Z)^\units)$.
+\end{proposition}
+\begin{proof}
+    We have that $S = \{ x \in \C^\units \ | \ x^{q - 1} = 1 \}$ and the claim directly follows from Corollary~\ref{prop:dirichlet_character_image_group}.
+\end{proof}
+Note that the endomorphism monoid $\mathrm{End}((\Z/q\Z)^\units)$ is not a group, except in the trivial case $q = 2$.
+The reason is that e.g. the trivial group homomorphism $r \mapsto 1$ is not surjective and thus not invertible.
+
+By Corollary~\ref{prop:dirichlet_character_primitive_root} each group endomorphism $f \in \mathrm{End}((\Z/q\Z)^\units)$ is determined by its value at a primitive root of unity $r \in (\Z/q\Z)^\units$, hence
+\begin{equation*}
+    |\mathrm{End}((\Z/q\Z)^\units)| = |(\Z/q\Z)^\units| = q - 1
+\end{equation*}
+It follows that there are exactly $q - 1$ distinct Dirichlet characters modulo a prime $q$.
+\begin{remark}
+    It is again a fact that $(\Z/p^k\Z)^\units$ is cyclic for an odd prime $p$ and $k \geq 1$.
+    Hence, everything up to now can also be done for odd prime powers, if we replace $q - 1$ by $\phi(q)$.
+\end{remark}
+Because of Lemma~\ref{prop:dirichlet_series_at_one} it might seem like a good idea to study in which cases the value $\sum_{x \in (\Z/q\Z)^\units} \chi(x)$ is zero.
+\begin{proposition}[Ex (iii)]
+    Let $\chi_0$ be the trivial Dirichlet character given by $r \mapsto 1$.
+    Then
+    \begin{align*}
+        \sum_{a \in (\Z/q\Z)^\units} \chi(a) &= \begin{cases}
+            q - 1 & \text{if $\chi = \chi_0$} \\
+            0 & \text{otherwise}
+        \end{cases}, \\
+        \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(a) &= \begin{cases}
+            q - 1 & \text{if $a \equiv 1 \mod q$} \\
+            0 & \text{otherwise}
+        \end{cases}
+    \end{align*}
+    Furthermore, for $b \perp q$ have
+    \begin{equation*}
+        \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(a)\overline{\chi(b)} = \begin{cases}
+            q - 1 & \text{if $a \equiv b \mod q$} \\
+            0 & \text{otherwise}
+        \end{cases}
+    \end{equation*}
+\end{proposition}
+\begin{proof}
+    Clearly
+    \begin{equation*}
+        \sum_{a \in (\Z/q\Z)^\units} \chi_0(a) = q - 1 \quad \text{and} \quad \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(1) = \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} 1 = q - 1
+    \end{equation*}
+    So it is left to show that we get zero in the other cases.
+
+    Consider a Dirichlet character $\chi \neq \chi_0$ given by $r \mapsto \xi$ for a $q$-th root of unity $\xi \neq 1$.
+    Then
+    \begin{equation*}
+        \sum_{a \in (\Z/q\Z)^\units} \chi(a) = \sum_{k = 0}^{q - 2} \chi(r^k) = \sum_{k = 0}^{q - 2} \xi^k = \frac {1 - \xi^{q - 1}} {q - \xi} = 0 
+    \end{equation*}
+    By using the earlier results on the structure of $\mathrm{End}((\Z/q\Z)^\units)$ we see that for $a = r^k \not\equiv 1 \mod q$, have
+    \begin{align*}
+        \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(a) &= \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(r)^k \\
+        &= \sum_{\xi \ \text{$q$-th root of unity}} \xi^k = \sum_{l = 0}^{q - 2} \omega^{kl} = \frac {1 - (\omega^{q - 1})^k} {1 - \omega^k} = 0 
+    \end{align*}
+    where $\omega$ is a primitive $q$-th root of unity.
+
+    For the last part, note that for any $q$-th root of unity $\xi$, we have $\xi\overline{\xi} \in \R$ with $\xi\overline{\xi} = |\xi|^2 > 0$.
+    Furthermore, $\overline{\xi}$ is also a $q$-th root of unity, and so we see that $\xi\overline{\xi} = 1$.
+    It follows that for any Dirichlet character $\chi$ have $\overline{\chi}(a) = \chi(a^{-1})$ (where the inversion happens in $(\Z/q\Z)^\units$).
+    Thus
+    \begin{equation*}
+        \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(a)\overline{\chi}(b) = \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(ab^{-1}) = \begin{cases}
+            q - 1 & \text{if $ab^{-1} = 1 \in (\Z/q\Z)^\units$} \\
+            0 & \text{otherwise}
+        \end{cases}
+    \end{equation*}
+    The condition $ab^{-1} = 1$ is equivalent to $a \equiv b \mod q$, so the claim follows.
+\end{proof}
 

### 2021-11-30 Analytic number theory/primes.py

@@ -1,0 +1,27 @@
+import itertools
+import math
+
+def primes():
+    yield 2
+    found_primes = [2]
+    for n in itertools.count(3):
+        for p in found_primes:
+            if n % p == 0:
+                break
+            elif p >= math.sqrt(n):
+                yield n
+                found_primes.append(n)
+                break
+
+def primes_leq(n):
+    return itertools.takewhile(lambda p: p <= n, primes())
+
+for i in range(1, 8):
+    print("Consider interval [1, 10**" + str(i) + "]")
+    print("  Number of primes = 1 mod 4 is " + str(
+        sum(1 for p in primes_leq(10**i) if (p - 1) % 4 == 0)
+    ))
+    print("  Number of primes = 3 mod 4 is " + str(
+        sum(1 for p in primes_leq(10**i) if (p - 3) % 4 == 0)
+    ))
+    print()

### 2021-11-30 Analytic number theory/submission.tex
improved notation

@@
     \begin{align*}
-        \{ \chi: (\Z/q\Z)^\units \to \C^\units \ | \ \chi \ \text{group hom} \} &\to \{ \chi: \N \to \C \ | \ \chi \ \text{Dirichlet character mod $q$} \} \\
-        \chi &\mapsto \tilde{\chi} := \left( \N \to \C, \ n \mapsto \begin{cases}
-            \chi([n]_q) & \text{if $n \perp q$} \\
+        \{ f: (\Z/q\Z)^\units \to \C^\units \ | \ f \ \text{group hom} \} &\to \{ \chi: \N \to \C \ | \ \chi \ \text{Dirichlet character mod $q$} \} \\
+        f &\mapsto \chi_f := \left( \N \to \C, \ n \mapsto \begin{cases}
+            f([n]) & \text{if $n \perp q$} \\
             0 & \text{otherwise}
@@
 \begin{proof}
-    First of all, we show that the map is well-defined. Let $\chi: (\Z/q\Z)^\units \to \C^\units$ be a (multiplicative) group homomorphism, and we show that $\tilde{\chi}$ is a Dirichlet character.
+    First of all, we show that the map is well-defined. Let $f: (\Z/q\Z)^\units \to \C^\units$ be a (multiplicative) group homomorphism, and we show that $\chi_f$ is a Dirichlet character.
 
-    Note that property (ii) and (iii) directly follow from the definition, as $\tilde{\chi}(n)$ only depends on the value of $n \mod q$.
+    Note that property (ii) and (iii) directly follow from the definition, as $\chi_f(n)$ only depends on the value of $n \mod q$.
     So consider some $a, b \in \N$.
@@
     \begin{equation*}
-        \tilde{\chi}(a)\tilde{\chi}(b) = \chi([a])\chi([b]) = \chi([ab]) = \tilde{\chi}(ab)
+        \chi_f(a)\chi_f(b) = \chi([a])\chi([b]) = \chi([ab]) = \chi_f(ab)
     \end{equation*}
@@
 
-    On the other hand, if $a \not\perp q$ or $b \not\perp q$ have $\chi(a) = 0$ resp. $\chi(b) = 0$.
+    On the other hand, if $a \not\perp q$ or $b \not\perp q$ have $\chi_f(a) = 0$ resp. $\chi_f(b) = 0$.
     We also have in this case that $ab \not\perp q$ and so
     \begin{equation*}
-        \chi(a)\chi(b) = 0 = \chi(ab)
+        \chi_f(a)\chi_f(b) = 0 = \chi_f(ab)
     \end{equation*}
     Now it is left to show that the correspondence is a bijection.
-    Clearly, if $\chi \neq \xi$ then $\chi(x) \neq \xi(x)$ for some $x \in (\Z/q\Z)^\units$ and so $\tilde{\chi}(n) \neq \tilde{\xi}(n)$ for some representative $n \in \N$ of $x$.
+    Clearly, if $f \neq g$ then $f(x) \neq g(x)$ for some $x \in (\Z/q\Z)^\units$ and so $\chi_f(n) \neq \chi_g(n)$ for some representative $n \in \N$ of $x$.
 
-    To show surjectivity, consider some Dirichlet character $f: \N \to \C$ and construct a group homomorphism $\chi: (\Z/q\Z)^\units \to \C^\units$. 
-    For each $x \in (\Z/q\Z)^\units$, there is a representative $n \in \N$ of $x$ and as $f(n)$ does not depend on the choice of $n$, we may define $\chi(x) := f(n)$.
-    Note that as $x \in (\Z/q\Z)^\units$, we find $n \perp q$ and so $f(n) \neq 0$, i.e. $f(n) \in \C^*$.
+    To show surjectivity, consider some Dirichlet character $\chi: \N \to \C$ and construct a group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$. 
+    For each $x \in (\Z/q\Z)^\units$, there is a representative $n \in \N$ of $x$ and as $\chi(n)$ does not depend on the choice of $n$, we may define $f(x) := \chi(n)$.
+    Note that as $x \in (\Z/q\Z)^\units$, we find $n \perp q$ and so $\chi(n) \neq 0$, i.e. $\chi(n) \in \C^*$.
     Then clearly for $a, b \in (\Z/q\Z)^*$ with representatives $n, m \in \N$ have
     \begin{equation*}
-        \chi(ab) = f(nm) = f(n)f(m) = \chi(a)\chi(b)
+        f(ab) = \chi(nm) = \chi(n)\chi(m) = f(a)f(b)
     \end{equation*}
-    So $\chi$ is a well-defined group homomorphism and we obviously have $\tilde{\chi} = f$.
+    So $f$ is a well-defined group homomorphism and we obviously have $\chi_f = \chi$.
 \end{proof}
@@
 \begin{proof}
-    This follows directly from Lemma~\ref{prop:characterization_dirichlet_character}, as $f = \tilde{\chi}$ for the group homomorphism
+    This follows directly from Lemma~\ref{prop:characterization_dirichlet_character}, as $f = \chi_g$ for the group homomorphism
     \begin{equation*}
-        \chi: (\Z/4\Z)^\units = \{ 1, 3 \} \to \C^*, \quad 1 \mapsto 1, \ 3 \mapsto -1
+        g: (\Z/4\Z)^\units = \{ 1, 3 \} \to \C^*, \quad 1 \mapsto 1, \ 3 \mapsto -1
     \end{equation*}
@@
 \begin{proof}
-    By Lemma~\ref{prop:characterization_dirichlet_character}, we know that $\chi$ corresponds to a group homomorphism $\chi': (\Z/q\Z)^\units \to \C^\units$ such that $\chi(\N) = \chi((\Z/q\Z)^*) \cup \{ 0 \} \subseteq \C$ is a finite subset of $\C$.
+    By Lemma~\ref{prop:characterization_dirichlet_character}, we know that $\chi$ corresponds to a group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$ such that $\chi(\N) = f((\Z/q\Z)^*) \cup \{ 0 \} \subseteq \C$ is a finite subset of $\C$.
     Hence, there is $C > 0$ with $|\chi(n)| \leq C$ for all $n \in \N$, and it follows that
     \begin{equation*}
-        \sum_{1 \leq n \leq X} \left| f(n) n^{-s} \right| \leq \sum_{1 \leq n \leq X} C \left| n^{-s} \right| \leq C \sum_{1 \leq n \leq X} n^{-1 - \epsilon}
+        \sum_{1 \leq n \leq X} \left| \chi(n) n^{-s} \right| \leq \sum_{1 \leq n \leq X} C \left| n^{-s} \right| \leq C \sum_{1 \leq n \leq X} n^{-1 - \epsilon} \leq C \sum_{n \geq 1} n^{-1 - \epsilon}
     \end{equation*}
@@
     \label{prop:dirichlet_series_at_one}
-    Let $\chi: (\Z/q\Z)^\units \to \C^\units$ be a group homomorphism. Then for the associated Dirichlet character $\tilde{\chi}$ we have that
+    Let $f: (\Z/q\Z)^\units \to \C^\units$ be a group homomorphism. Then for the associated Dirichlet character $\chi = \chi_f$ we have that
     \begin{equation*}
-        \lim_{s \to 1^+} L(s, \tilde{\chi}) \ \text{exists} \ \Leftrightarrow \ \sum_{x \in (\Z/q\Z)^\units} \chi(x) = 0
+        \lim_{s \to 1^+} L(s, \chi) \ \text{exists} \ \Leftrightarrow \ \sum_{x \in (\Z/q\Z)^\units} f(x) = 0
     \end{equation*}
-    In this case, have that
+    In this case, have that $L(s, \chi)$ is well-defined, $\lim_{t \to s} L(t, \chi)$ exists and
     \begin{equation*}
-        \lim_{s \to 1^+} L(s, \tilde{\chi}) = \sum_{n \geq 1} f(n) n^{-s}
+        \lim_{t \to s} L(t, \chi) = \sum_{n \geq 1} \chi(n) n^{-s}
     \end{equation*}
-    where the right sum converges (but not absolutely) for $\Re(s) > 0$.
+    where the right sum converges (but not absolutely), for all $\Re(s) > 0$.
 \end{proposition}
 \begin{proof}
-    Let $c = \sum_{x \in (\Z/q\Z)^\units} \chi(x)$.
+    Let $c = \sum_{x \in (\Z/q\Z)^\units} f(x)$.
     For the direction $\Rightarrow$ assume that $c \neq 0$.
@@
     \begin{align*}
-        \sgn(c) \sum_{n \geq 1} \tilde{\chi}(n) n^{-s} &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \sgn(c) \tilde{\chi}(qn + k) (qn + k)^{-s} \\
-        &\geq \sum_{n \geq 1} \ \sum_{0 \leq k < 1}\sgn(c) \tilde{\chi}(qn + k) (qn + n)^{-s} \\
-        &= \sum_{n \geq 1} \sgn(c) (qn + n)^{-s} \underbrace{\sum_{0 \leq k < q} \tilde{\chi}(qn + k)}_{= c} \\
+        \sgn(c) \sum_{n \geq 1} \chi(n) n^{-s} &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \sgn(c) \chi(qn + k) (qn + k)^{-s} \\
+        &\geq \sum_{n \geq 1} \ \sum_{0 \leq k < 1}\sgn(c) \chi(qn + k) (qn + n)^{-s} \\
+        &= \sum_{n \geq 1} \sgn(c) (qn + n)^{-s} \underbrace{\sum_{0 \leq k < q} \chi(qn + k)}_{= c} \\
         &\geq \frac {|c|} {(q + 1)^s} \sum_{n \geq 1} n^{-s} = \frac {|c|} {(q + 1)^s} \zeta(s)
     \end{align*}
-    which clearly has a pole at $s = 1$. Hence $\lim_{s \to 1^+} L(s, \tilde{\chi})$ cannot exist.
+    which clearly has a pole at $s = 1$. Hence $\lim_{s \to 1^+} L(s, \chi_f)$ cannot exist.
 
@@
     \begin{align*}
-        \sum_{n \geq 1} \tilde{\chi}(n) n^{-s} &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \tilde{\chi}(qn + k) (qn + k)^{-s} \\
-        &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \tilde{\chi}(qn + k) \Bigl( (qn)^{-s} + (qn + k)^{-s} - (qn)^{-s} \Bigr)
+        \sum_{n \geq 1} \chi(n) n^{-s} &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \chi(qn + k) (qn + k)^{-s} \\
+        &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \chi(qn + k) \Bigl( (qn)^{-s} + (qn + k)^{-s} - (qn)^{-s} \Bigr)
     \end{align*}
@@
     \end{align*}
-    As $\chi((\Z/q\Z)^\units) \subseteq \C$ is finite, find $C > 0$ with $|\tilde{\chi}(n)| \leq C$ for all $n \in \N$. Then
+    As $\chi((\Z/q\Z)^\units) \subseteq \C$ is finite, find $C > 0$ with $|\chi_f(n)| \leq C$ for all $n \in \N$. Then
     \begin{align*}
-        \sum_{n \geq X} \tilde{\chi}(n) n^{-s} &= O(qCX^{-s}) + \sum_{n \geq X/q} \ \sum_{0 \leq k < q} \tilde{\chi}(qn + k) \Bigl( (qn)^{-s} + O(sn^{-s - 1}) \Bigr) \\
+        \sum_{n \geq X} \chi(n) n^{-s} &= O(qCX^{-s}) + \sum_{n \geq X/q} \ \sum_{0 \leq k < q} \chi(qn + k) \Bigl( (qn)^{-s} + O(sn^{-s - 1}) \Bigr) \\
         &= O(qCX^{-s}) + \sum_{n \leq X/q} \Bigl( (qn)^{-s} c + \sum_{0 \geq k < q} O(Csn^{-s - 1}) \Bigr) = \\
@@
     which is well-defined and finite for $\Re(s) > 0$.
-    Further, the expression converges uniformly (as a function in $s$ on a neighborhood of $1$) to $0$ as $X \to \infty$. 
+    Further, the expression converges uniformly (as a function in $s$ on $\Re(s) \geq \epsilon > 0$) to $0$ as $X \to \infty$. 
     So
     \begin{equation*}
-        \sum_{n < X} \tilde{\chi}(n) n^{-s} \quad \text{converges uniformly to} \quad \sum_{n \geq 1} \tilde{\chi}(n) n^{-s}
+        \sum_{n < X} \chi(n) n^{-s} \quad \text{converges uniformly to} \quad \sum_{n \geq 1} \chi(n) n^{-s}
     \end{equation*}
-    as $X \to \infty$ (on a neighborhood of $1$). 
-    Thus the limit is continuous and a continuation of $L(s, \tilde{\chi})$ which is defined on $\Re(s) > 1$.
-    From this it follows that $\lim_{s \to 1} L(s, \tilde{\chi})$ exists and is equal to $\sum_n \tilde{\chi}(n) n^{-s}$.
+    as $X \to \infty$ (on a $\Re(s) \geq \epsilon > 0$). 
+    Thus the limit is continuous and a continuation of $L(s, \chi_f)$ defined on $\Re(s) > 1$.
+    From this it follows that $\lim_{t \to s} L(t, \chi_f)$ exists and is equal to $\sum_n \chi_f(n) n^{-s}$.
 \end{proof}
@@
 \begin{example}[Ex (ii)]
-    Let $f: \N \to \C$ be the Dirichlet character from Example~\ref{ex:nontrivial_dirichlet_character_mod_4} with corresponding group homomorphism $\chi: (\Z/4\Z)^\units \to \C$.
+    Let $f: \N \to \C$ be the Dirichlet character from Example~\ref{ex:nontrivial_dirichlet_character_mod_4} with corresponding group homomorphism $g: (\Z/4\Z)^\units \to \C$.
     Then
     \begin{equation*}
-        \sum_{x \in (\Z/4\Z)^*} \chi(x) = \chi(1) + \chi(3) = 1 - 1 = 0
+        \sum_{x \in (\Z/4\Z)^*} g(x) = g(1) + g(3) = 1 - 1 = 0
     \end{equation*}
@@
     \label{prop:dirichlet_character_image_group}
-    Let $\chi, \chi': \N \to \C$ be Dirichlet characters mod $q$ and $r$ a primitive root modulo $q$.
+    Let $\chi, \chi': \N \to \C$ be Dirichlet characters mod $q$ and $r$ a representative of a primitive root modulo $q$.
     If $\chi(r) = \chi'(r)$, then $\chi = \chi'$.
@@
     Let $f, f': (\Z/q\Z)^\units \to \C^\units$ be the associated group homomorphisms of $\chi, \chi'$ as in Lemma~\ref{prop:characterization_dirichlet_character}.
-    If $f(r) = \chi(r) = \chi'(r) = f'(r)$ then clearly $f = f'$, as these are group homomorphisms and $\langle r \rangle = (\Z/q\Z)^\units$.
+    If $f([r]) = \chi(r) = \chi'(r) = f'([r])$ then clearly $f = f'$, as these are group homomorphisms and $\langle [r] \rangle = (\Z/q\Z)^\units$.
     Hence $\chi = \chi'$.
 
-    Further, have for $n \in \N$ with $n \perp q$ that $n \in (\Z/q\Z)^\units$ and thus
+    Further, have for $n \in \N$ with $n \perp q$ that $[n] \in (\Z/q\Z)^\units$ and thus
     \begin{equation*}
-        n^{q - 1} = n^{\phi(q)} = n^{|(\Z/q\Z)^\units|} = 1 
+        [n]^{q - 1} = [n]^{\phi(q)} = [n]^{|(\Z/q\Z)^\units|} = 1 
     \end{equation*}
@@
     \begin{equation*}
-        \chi(n)^{q - 1} = f(n)^{q - 1} = f(n^{q - 1}) = f(1) = 1
+        \chi(n)^{q - 1} = f([n])^{q - 1} = f([n]^{q - 1}) = f(1) = 1
     \end{equation*}
@@
     \label{prop:dirichlet_character_primitive_root}
-    Let $\omega \in \C$ be a $(q - 1)$-th root of unity, i.e. $\omega^{q - 1} = 1$ and let $r \in (\Z/q\Z)^\units$ be a primitive root.
+    Let $\omega \in \C$ be a $(q - 1)$-th root of unity, i.e. $\omega^{q - 1} = 1$ and let $r \in \Z$ be a representative of a primitive root modulo $q$.
     Then
@@
 \begin{proof}
-    Follows again directly from Lemma~\ref{prop:characterization_dirichlet_character}, as $r \mapsto \omega$ induces a unique group homomorphism $(\Z/q\Z)^\units \to \C^\units$.
+    Follows again directly from Lemma~\ref{prop:characterization_dirichlet_character}, as $[r] \mapsto \omega$ induces a unique group homomorphism $(\Z/q\Z)^\units \to \C^\units$.
     The associated Dirichlet character is obviously $g$.
 \end{proof}
-Note that the image of a group homomorphism $\chi: (\Z/q\Z)^\units \to \C^\units$ is a subgroup of $\C^\units$.
+Note that the image of a group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$ is a subgroup of $\C^\units$.
 Using Corollary~\ref{prop:dirichlet_character_image_group}, we can describe it quite concretely.
@@
     Let $\chi: \N \to \C$ be a Dirichlet character with group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$.
-    Then $\mathrm{im}f \leq S$ is a subgroup where $S = \{ \omega_q^k \ | \ k \in \Z \}$ is the group of $q$-th roots of unity.
+    Then $\mathrm{im}f \leq S$ is a subgroup where $S_q := \{ \omega_q^k \ | \ k \in \Z \}$ is the group of $q$-th roots of unity.
 
-    It is a fact from Algebra that $S \cong (\Z/q\Z)^\units$, hence Dirichlet characters modulo a prime $q$ are in 1-to-1 correspondence with the endomorphism monoid $\mathrm{End}((\Z/q\Z)^\units)$.
+    It is a fact from Algebra that $S_q \cong (\Z/q\Z)^\units$, hence Dirichlet characters modulo a prime $q$ are in 1-to-1 correspondence with the endomorphisms $\mathrm{End}((\Z/q\Z)^\units)$ of $(\Z/q\Z)^\units$.
 \end{proposition}
 \begin{proof}
-    We have that $S = \{ x \in \C^\units \ | \ x^{q - 1} = 1 \}$ and the claim directly follows from Corollary~\ref{prop:dirichlet_character_image_group}.
+    We have that $S_q = \{ x \in \C^\units \ | \ x^{q - 1} = 1 \}$ and the claim directly follows from Corollary~\ref{prop:dirichlet_character_image_group}.
 \end{proof}
@@
 The reason is that e.g. the trivial group homomorphism $r \mapsto 1$ is not surjective and thus not invertible.
-
+\begin{definition}
+    Denote by $\mathrm{Dir}(q)$ the set of Dirichlet characters modulo $q$.
+\end{definition}
 By Corollary~\ref{prop:dirichlet_character_primitive_root} each group endomorphism $f \in \mathrm{End}((\Z/q\Z)^\units)$ is determined by its value at a primitive root of unity $r \in (\Z/q\Z)^\units$, hence
 \begin{equation*}
-    |\mathrm{End}((\Z/q\Z)^\units)| = |(\Z/q\Z)^\units| = q - 1
+    |\mathrm{Dir}(q)| = |\mathrm{End}((\Z/q\Z)^\units)| = |(\Z/q\Z)^\units| = q - 1
 \end{equation*}
@@
         \end{cases}, \\
-        \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(a) &= \begin{cases}
+        \sum_{\chi \in \mathrm{Dir}(q)} \chi(a) &= \begin{cases}
             q - 1 & \text{if $a \equiv 1 \mod q$} \\
@@
     \begin{equation*}
-        \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(a)\overline{\chi(b)} = \begin{cases}
+        \sum_{\chi \in \mathrm{Dir}(q)} \chi(a)\overline{\chi(b)} = \begin{cases}
             q - 1 & \text{if $a \equiv b \mod q$} \\
@@
     \begin{equation*}
-        \sum_{a \in (\Z/q\Z)^\units} \chi_0(a) = q - 1 \quad \text{and} \quad \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(1) = \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} 1 = q - 1
+        \sum_{a \in (\Z/q\Z)^\units} \chi_0(a) = q - 1 \quad \text{and} \quad \sum_{\chi \in \mathrm{Dir}(q)} \chi(1) = \sum_{\chi \in \mathrm{Dir}(q)} 1 = q - 1
     \end{equation*}
@@
     \end{equation*}
-    By using the earlier results on the structure of $\mathrm{End}((\Z/q\Z)^\units)$ we see that for $a = r^k \not\equiv 1 \mod q$, have
+    By using the earlier results on the structure of $\mathrm{Dir}(q)$ we see that for $a = r^k \not\equiv 1 \mod q$, have
     \begin{align*}
-        \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(a) &= \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(r)^k \\
+        \sum_{\chi \in \mathrm{Dir}(q)} \chi(a) &= \sum_{\chi \in \mathrm{Dir}(q)} \chi(r)^k \\
         &= \sum_{\xi \ \text{$q$-th root of unity}} \xi^k = \sum_{l = 0}^{q - 2} \omega^{kl} = \frac {1 - (\omega^{q - 1})^k} {1 - \omega^k} = 0 
@@
     For the last part, note that for any $q$-th root of unity $\xi$, we have $\xi\overline{\xi} \in \R$ with $\xi\overline{\xi} = |\xi|^2 > 0$.
-    Furthermore, $\overline{\xi}$ is also a $q$-th root of unity, and so we see that $\xi\overline{\xi} = 1$.
-    It follows that for any Dirichlet character $\chi$ have $\overline{\chi}(a) = \chi(a^{-1})$ (where the inversion happens in $(\Z/q\Z)^\units$).
+    Furthermore, $\overline{\xi}$ is also a $q$-th root of unity, and so we see that $\xi\overline{\xi} = 1$ (the only real, positive root of unity is 1).
+    It follows that for any Dirichlet character $\chi$ have $\overline{\chi([a])} = \chi([a]^{-1})$.
     Thus
     \begin{equation*}
-        \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(a)\overline{\chi}(b) = \sum_{\chi \in \mathrm{End}((\Z/q\Z)^\units)} \chi(ab^{-1}) = \begin{cases}
-            q - 1 & \text{if $ab^{-1} = 1 \in (\Z/q\Z)^\units$} \\
+        \sum_{\chi \in \mathrm{Dir}(q)} \chi(a)\overline{\chi(b)} = \sum_{\chi \in \mathrm{Dir}(q)} \chi([a][b]^{-1}) = \begin{cases}
+            q - 1 & \text{if $[a][b]^{-1} = 1 \in (\Z/q\Z)^\units$} \\
             0 & \text{otherwise}

### 2021-12-01 Analytic number theory/submission.tex
Almost finished ANT

@@
     \end{equation*}
-    In this case, have that $L(s, \chi)$ is well-defined, $\lim_{t \to s} L(t, \chi)$ exists and
+    If this is the case, then
     \begin{equation*}
-        \lim_{t \to s} L(t, \chi) = \sum_{n \geq 1} \chi(n) n^{-s}
+        \lim_{s \to 1} L(s, \chi) = \sum_{n \geq 1} \frac {\chi(n)} n
     \end{equation*}
-    where the right sum converges (but not absolutely), for all $\Re(s) > 0$.
+    where the right-hand side converges (but not absolutely).
 \end{proposition}
@@
     \begin{align*}
-        \sgn(c) \sum_{n \geq 1} \chi(n) n^{-s} &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \sgn(c) \chi(qn + k) (qn + k)^{-s} \\
-        &\geq \sum_{n \geq 1} \ \sum_{0 \leq k < 1}\sgn(c) \chi(qn + k) (qn + n)^{-s} \\
-        &= \sum_{n \geq 1} \sgn(c) (qn + n)^{-s} \underbrace{\sum_{0 \leq k < q} \chi(qn + k)}_{= c} \\
+        \sgn(c) \sum_{n \geq 1} \chi(n) n^{-s} &= \sum_{n \geq 0} \ \sum_{0 < k \leq q} \sgn(c) \chi(qn + k) (qn + k)^{-s} \\
+        &\geq \sum_{n \geq 0} \ \sum_{0 < k \leq q}\sgn(c) \chi(qn + k) (qn + n)^{-s} \\
+        &= \sum_{n \geq 0} \sgn(c) (qn + n)^{-s} \underbrace{\sum_{0 < k \leq q} \chi(qn + k)}_{= c} \\
         &\geq \frac {|c|} {(q + 1)^s} \sum_{n \geq 1} n^{-s} = \frac {|c|} {(q + 1)^s} \zeta(s)
@@
     For the other direction, assume that $c = 0$.
-    Again, have for $\Re(s) > 1$ that
+    Observe that by Bernoulli's inequality, have for $0 < s \leq 1$ that
     \begin{align*}
-        \sum_{n \geq 1} \chi(n) n^{-s} &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \chi(qn + k) (qn + k)^{-s} \\
-        &= \sum_{n \geq 1} \ \sum_{0 \leq k < q} \chi(qn + k) \Bigl( (qn)^{-s} + (qn + k)^{-s} - (qn)^{-s} \Bigr)
-    \end{align*}
-    Observe that by Bernoulli's inequality, have
-    \begin{align*}
-        (qn)^{-s} - (qn + k)^{-s} &= \frac {(qn)^s - (qn + k)^s} {(q^2n^2 + qnk)^s} = (qn)^{s} \frac {1 - (1 + k(qn)^{-1})^s} {(q^2n^2 + qnk)^s} \\
+        (qn)^{-s} - (qn + k)^{-s} &= \frac {(qn + k)^s - (qn)^s} {(q^2n^2 + qnk)^s} = (qn)^{s} \frac {(1 + k(qn)^{-1})^s - 1} {(q^2n^2 + qnk)^s} \\
         &\leq (qn)^s \frac {sk(qn)^{-1}} {(q^2n^2 + qnk)^s} = \frac {sk} {qn(qn + k)^s} = O(sn^{-s - 1})
     \end{align*}
-    As $\chi((\Z/q\Z)^\units) \subseteq \C$ is finite, find $C > 0$ with $|\chi_f(n)| \leq C$ for all $n \in \N$. Then
+    If $s > 1$ and $k \leq q$, then also $(qn)^{-s} - (qn + k)^{-s} = O(sn^{-(1 + \epsilon)})$ for some small enough $0 < \epsilon < 1$.
+    As $\chi((\Z/q\Z)^\units) \subseteq \C$ is finite, find $C > 0$ with $|\chi_f(n)| \leq C$ for all $n \in \N$. 
+    Then for all $s \geq \epsilon$ and $X \leq Y$ it holds
     \begin{align*}
-        \sum_{n \geq X} \chi(n) n^{-s} &= O(qCX^{-s}) + \sum_{n \geq X/q} \ \sum_{0 \leq k < q} \chi(qn + k) \Bigl( (qn)^{-s} + O(sn^{-s - 1}) \Bigr) \\
-        &= O(qCX^{-s}) + \sum_{n \leq X/q} \Bigl( (qn)^{-s} c + \sum_{0 \geq k < q} O(Csn^{-s - 1}) \Bigr) = \\
-        &= O(qCX^{-s}) + 0 + O\Bigl( Cqs \sum_{n \geq X/q} n^{-s - 1} \Bigr) \\
-        &\leq O(qCX^{-s}) + O\Bigl( Cqs\zeta(s + 1) \Bigr)
+        &\sum_{X \leq n \leq Y} \chi(n) n^{-s} \\
+        =& \ O(qCX^{-s} + qCY^{-s}) + \sum_{X/q \leq n \leq Y/q} \ \sum_{0 < k \leq q} \chi(qn + k) \Bigl( (qn)^{-s} + \underbrace{(qn + k)^{-s} - (qn)^{-s}}_{= O(sn^{-(1 + \epsilon)})} \Bigr) \\
+        =& \ O(qCX^{-s}) + \sum_{X/q \leq n \leq Y/q} \Bigl( (qn)^{-s} c + \sum_{0 < k \leq q} O(Csn^{-(1 + \epsilon)}) \Bigr) = \\
+        =& \ O(qCX^{-s}) + 0 + O\Bigl( Cqs \sum_{X/q \leq n \leq Y/q} n^{-(1 + \epsilon)} \Bigr) \\
+        =& \ O(qCX^{-s}) + O\Bigl( Cqs \sum_{X/q \leq n} n^{-(1 + \epsilon)} \Bigr)
     \end{align*}
-    which is well-defined and finite for $\Re(s) > 0$.
-    Further, the expression converges uniformly (as a function in $s$ on $\Re(s) \geq \epsilon > 0$) to $0$ as $X \to \infty$. 
+    which is well-defined and finite.
+    Further, the expression converges uniformly (as a function in $s$ on $[\epsilon, \infty[$) to $0$ as $X \to \infty$. 
     So
@@
     \end{equation*}
-    as $X \to \infty$ (on a $\Re(s) \geq \epsilon > 0$). 
-    Thus the limit is continuous and a continuation of $L(s, \chi_f)$ defined on $\Re(s) > 1$.
-    From this it follows that $\lim_{t \to s} L(t, \chi_f)$ exists and is equal to $\sum_n \chi_f(n) n^{-s}$.
+    as $X \to \infty$ (on $[\epsilon, \infty[$). 
+    Thus the limit is continuous and extends $L(s, \chi_f)$ defined on $]1, \infty[$.
+    It follows that $\lim_{t \to s} L(t, \chi_f)$ exists and is equal to $\sum_{n \geq 1} \chi(n) n^{-s}$.
 \end{proof}
@@
 If we now assume $q$ to be prime, we get an even nicer characterization.
+So for the whole section, assume that $q \geq 3$ is a prime.
 \begin{corollary}[Ex (i)]
@@
 \begin{proposition}[Ex (iii)]
+    \label{prop:finite_sums_characters}
     Let $\chi_0$ be the trivial Dirichlet character given by $r \mapsto 1$.
@@
     \end{equation*}
-    By using the earlier results on the structure of $\mathrm{Dir}(q)$ we see that for $a = r^k \not\equiv 1 \mod q$, have
+    By using the earlier results on the structure of $\mathrm{Dir}(q)$ we see that for $a \equiv r^k \not\equiv 1 \mod q$, have
     \begin{align*}
@@
     \end{align*}
-    where $\omega$ is a primitive $q$-th root of unity.
+    where $\omega \in \C$ is a primitive $q$-th root of unity and $r \in \Z$ is a primitive root modulo $q$.
 
@@
 \end{proof}
+Using these basic results, we can now prove facts on the Dirichlet series of characters.
+\begin{proposition}[Ex (iv)]
+    \label{prop:representation_mangoldt_series_congruent_a}
+    Let $a \perp q$. Then for $\Re(s) > 1$ have
+    \begin{equation*}
+        \sum_{n \equiv a \mod q} \frac {\Lambda(n)} {n^s} = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
+    \end{equation*}
+    (All those series obviously converge absolutely since $\Re(s) > 1$)
+\end{proposition}
+\begin{proof}
+    By Prop.~\ref{prop:finite_sums_characters} we have for all $n \in \N$ that
+    \begin{equation*}
+        \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \chi(n) = \begin{cases}
+            1 & \text{if $a \equiv n \mod q$} \\
+            0 & \text{otherwise}
+        \end{cases}
+    \end{equation*}
+    It follows that
+    \begin{align*}
+        \sum_{n \equiv a \mod q} \Lambda(n) n^{-s} =& \sum_{n \geq 1} \Lambda(n) n^{-s} \begin{cases}
+            1 & \text{if $a \equiv n \mod q$} \\
+            0 & \text{otherwise}
+        \end{cases} \\
+        =& \sum_{n \geq 1} \Lambda(n) n^{-s} \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \chi(n) \\
+        =& \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \Lambda(n) \chi(n) n^{-s} 
+    \end{align*}
+    as infinite summation clearly commutes with finite sums.
+\end{proof}
+\begin{example}[Ex (v)]
+    We consider the Dirichlet characters mod 5.
+    A (primitive) 5-th root of unity $\omega_5 \in \C$ is given by $\omega_5 = \exp(2\pi i/5)$.
+    On the other hand, a primitive root modulo 5 is e.g. given by $r = 2$ since $2^2 \equiv -1 \mod 5$.
+    Thus we have $5 - 1 = 4$ Dirichlet characters mod 5, namely those given by
+    \begin{align*}
+        1 &\mapsto 1,\ 2 \mapsto \omega_5 = \exp(2\pi i/5),\ 3 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 4 \mapsto \omega_5^2 = \exp(4\pi i/5),\ \\
+        1 &\mapsto 1,\ 2 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 3 \mapsto \omega_5 = \exp(2\pi i/5),\ 4 \mapsto \omega_5^4 = \exp(8\pi i/5),\ \\
+        1 &\mapsto 1,\ 2 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 3 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 4 \mapsto \omega_5^1 = \exp(2\pi i/5),\ \\
+        1 &\mapsto 1,\ 2 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 3 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 4 \mapsto \omega_5^3 = \exp(6\pi i/5),\ \\
+    \end{align*}
+\end{example}
+
+\section{Part III}
+Again, let $q \geq 3$ be a prime.
+Let further $\chi$ be a Dirichlet character mod $q$.
+\begin{proposition}[Ex (i)]
+    \label{prop:logarithmic_derivative_L}
+    For $\Re(s) > 1$ have that
+    \begin{equation*}
+        \frac {L(s, \chi)'} {L(s, \chi)} = \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
+    \end{equation*}
+\end{proposition}
+\begin{proof}
+    Consider any $\epsilon > 0$. The series
+    \begin{equation*}
+        \sum_{n \geq 1} \frac d {ds} \chi(n) n^{-s} = \sum_{n \geq 1} \chi(n) \log(n) n^{-s}
+    \end{equation*}
+    converges uniformly on $\Re(s) \geq 1 + \epsilon$, as $|\chi(n)| \leq C$ for some $C > 0$ and all $n \in \N$ (by the lecture, we know that $\sum_n \log(n) n^{-s}$ converges uniformly on $\Re(s) \geq 1 + \epsilon$).
+    Hence, we may interchange summation and differentiation to get
+    \begin{equation*}
+        L(s, \chi)' = \sum_{n \geq 1} \chi(n) \frac d {ds} n^{-s} = \sum_{n \geq 1} \chi(n) \log(n) n^{-s}
+    \end{equation*}
+    for $\Re(s) \geq 1 + \epsilon$.
+    As $\epsilon > 0$ was arbitrary, we get
+    \begin{equation*}
+        L(s, \chi)' = \sum_{n \geq 1} \chi(n) \log(n) n^{-s}
+    \end{equation*}
+    for all $\Re(s) > 1$.
+
+    Furthermore, $\chi$ and $\mu$ are multiplicative, and hence so is $(\chi\mu)(n) := \chi(n)\mu(n)$.
+    Thus we have the Euler products
+    \begin{equation*}
+        \sum_{n \geq 1} \mu(n) \chi(n) n^{-s} = \prod_{p \in \primes} \ \sum_{k \in \N} \mu(p^k) \chi(p^k) p^{-sk} = \prod_{p \in \primes} (1 - \chi(p)p^{-s})
+    \end{equation*}
+    and
+    \begin{equation*}
+        \sum_{n \geq 1} \chi(n) n^{-s} = \prod_{p \in \primes} \ \sum_{k \in \N} \chi(p^k) p^{-sk} = \prod_{p \in \primes} \frac 1 {1 - \chi(p)p^{-s}}
+    \end{equation*}
+    Everything converges absolutely for $\Re(s) > 1$, and so it follows
+    \begin{equation*}
+        \frac 1 {L(s, \chi)} = \sum_{n \geq 1} (\chi\mu)(n) n^{-s}
+    \end{equation*}
+    By the compatibility of Dirichlet convolution and Dirichlet summation, we now find
+    \begin{equation*}
+        L(s, \chi)' \frac 1 {L(s, \chi)} = \Bigl( \sum_{n \geq 1} \chi(n) \log(n) n^{-s} \Bigr) \Bigl( \sum_{n \geq 1} \chi(n) \mu(n) n^{-s} \Bigr) = \sum_{n \geq 1} (\chi\log * \chi\mu)(n) n^{-s}
+    \end{equation*}
+    and so it is left to show that $\chi\log * \chi\mu = \chi\Lambda$.
+
+    This is true, as for all $n \in \N$ it holds
+    \begin{align*}
+        (\chi\log * \chi\mu)(n) &= \sum_{ab = n} \chi(a)\chi(b) \log(a)\mu(b) \\
+        &= \sum_{ab = n} \chi(ab) \log(a)\mu(b) = \chi(n) \sum_{ab = n} \log(a) \mu(b) \\
+        &= \chi(n) (\log * \mu)(n) = (\chi\Lambda)(n)
+    \end{align*}
+\end{proof}
+Now we want to find an analytic continuation of $L(s, \chi)$ to $\Re(s) > 0$.
+First of all, we consider $\chi_0$.
+\begin{proposition}[Ex (ii)]
+    \label{prop:formula_trivial_L_series}
+    For $\Re(s) > 1$ we have
+    \begin{equation*}
+        L(s, \chi_0) = (1 - q^{-s}) \zeta(s)
+    \end{equation*}
+    In particular, $L(s, \chi_0)$ has a meromorphic continuation to $\Re(s) > 0$ with only one simple pole at $s = 1$.
+\end{proposition}
+\begin{proof}
+    As $\chi_0$ is fully multiplicative, we have the Euler product
+    \begin{align*}
+        L(s, \chi_0) =& \sum_{n \geq 1} \chi_0(n) n^{-s} = \prod_{p \in \primes} \frac 1 {1 - \chi_0(p)p^{-s}} = \prod_{p \neq q} \frac 1 {1 - p^{-s}} \\
+        =& (1 - q^{-s}) \prod_{p \in \primes} \frac 1 {1 - p^{-s}} = (1 - q^{-s}) \zeta(s)
+    \end{align*}
+    as all products converge absolutely.
+\end{proof}
+For the other Dirichlet characters, the situation is slightly more complicated.
+First, we will bound the value of the partial sums of the Dirichlet series for $0 < \Re(s) \leq 1$.
+\begin{lemma}
+    \label{prop:bound_partsums_character}
+    Let $\chi \neq \chi_0$ be a Dirichlet character mod $q$ and consider the sum function
+    \begin{equation*}
+        A(n) := \sum_{1 \leq k \leq n} \chi(k)
+    \end{equation*}
+    Then $|A(n)| \leq q$ for all $n \in \N$.
+\end{lemma}
+\begin{proof}
+    Have
+    \begin{align*}
+        |A(n)| =& \ \Bigl| \sum_{1 \leq k \leq n} \chi(k) \Bigr| \leq \Bigl| \sum_{q\lfloor n/q \rfloor < l \leq n} \chi(l) \Bigr| + \Bigl| \sum_{0 \leq k < \lfloor n/q \rfloor} \ \underbrace{\sum_{0 < l \leq q} \chi(kq + l)}_{= 0 \ \text{by Prop.~\ref{prop:finite_sums_characters}}} \Bigr| \\
+        =& \ \Bigl| \sum_{q\lfloor n/q \rfloor < l \leq n} \chi(l) \Bigr| \leq \sum_{q\lfloor n/q \rfloor < l \leq n} |\chi(l)| = \sum_{q\lfloor n/q \rfloor < l \leq n} 1 \\
+        =& q(n/q - \lfloor n/q \rfloor) \leq q
+    \end{align*}
+    for all $n \in \N$.
+\end{proof}
+\begin{lemma}[Ex (iii)]
+    \label{prop:character_partsums_bounded}
+    Let $\chi \neq \chi_0$ be a Dirichlet character.
+    Then for $\Re(s) > 0$ have
+    \begin{equation*}
+        \Bigl| \sum_{1 \leq n \leq X} \chi(n) n^{-s} \Bigr| \leq q + \frac {q|s|} {\Re(s)} = O\left( \frac {q|s|} {\Re(s)} \right)
+    \end{equation*}
+    and in particular, this does not depend on $X$.
+\end{lemma}
+\begin{proof}
+    Using partial summation yields
+    \begin{align*}
+        \sum_{1 \leq n \leq X} \chi(n) n^{-s} =& \sum_{1 - \epsilon < n \leq X} \chi(n) n^{-s} \\
+        =& \underbrace{A(1 - \epsilon)}_{= 0} (1 - \epsilon)^{-s} - A(X) X^{-s} + s\int_{1 - \epsilon}^X A(t) t^{-(s + 1)} dt \\
+        =& -A(X) X^{-s} + s\int_1^X A(t) t^{-(s + 1)} dt
+    \end{align*}
+    So
+    \begin{align*}
+        \Bigl| \sum_{1 \leq n \leq X} \chi(n) n^{-s} \Bigr| \leq& \ |A(X) X^{-s}| + |s| \int_1^X |A(t) t^{-(s + 1)}| dt \\
+        \leq& \ q X^{-\Re(s)} + |s| \int_1^X q t^{-\Re(s) - 1} dt \\
+        =& \ q X^{-\Re(s)} + q|s| \left( \frac 1 {\Re(s)} - \frac 1 {X^{\Re(s)}\Re(s)} \right) \\
+        \leq& \ q + q \frac {|s|} {\Re(s)} = O\left( \frac {q|s|} {\Re(s)} \right)
+    \end{align*}
+    for $\Re(s) > 0$.
+\end{proof}
+Now we can show the analytic continuation of $L(s, \chi)$ to $\Re(s) > 0$.
+\begin{proposition}[Ex (iv)]
+    Let $\chi \neq \chi_0$ be a Dirichlet character mod $q$.
+    Then
+    \begin{align*}
+        L(s, \chi) = s \int_1^\infty A(t) t^{-(s + 1)} dt
+    \end{align*}
+    for $\Re(s) > 1$.
+    Further, the right-hand side is a holomorphic function on $\Re(s) > 0$ and thus provides an analytic continuation of $L(s, \chi)$ to $\Re(s) > 0$.
+\end{proposition}
+\begin{proof}
+    Similar to the proof of Lemma~\ref{prop:character_partsums_bounded}, partial summation yields
+    \begin{align*}
+        \sum_{n \geq 1} \chi(n) n^{-s} = s \int_1^\infty A(t) t^{-(s + 1)} dt
+    \end{align*}
+    By Lemma~\ref{prop:character_partsums_bounded}, this is bounded and hence well-defined and finite for $\Re(s) > 0$.
+    Further, the integral converges absolutely by Lemma~\ref{prop:bound_partsums_character}, and thus is holomorphic on $\Re(s) > 0$.
+\end{proof}
+\begin{corollary}[Ex (iv)]
+    \label{prop:logarithmic_derivative_L_bounded}
+    The function $L(s, \chi)'/L(s, \chi)$ is bounded on a neighborhood of $1$, provided that $L(1, \chi) \neq 0$.
+\end{corollary}
+\begin{proof}
+    As $L(s, \chi)'/L(s, \chi)$ is meromorphic on $\Re(s) > 0$, we know that it is holomorphic on some neighborhood of $1$ unless it has a pole at $s = 1$.
+    In the third exercise class of ANT, it was shown that this would imply $L(1, \chi) = 0$ or $L(s, \chi)'$ has a pole at $s = 1$.
+
+    However, the derivative of a holomorphic function is again holomorphic, so $L(s, \chi)'$ has no pole at $s = 1$.
+    Provided that $L(1, \chi) \neq 0$, it follows that $L(s, \chi)'/L(s, \chi)$ is holomorphic on a compact neighborhood of $1$, so bounded.
+\end{proof}
+Now we can show the main result of this miniproject.
+We will prove one auxiliary lemma before.
+\begin{lemma}
+    For $a \perp q$, the function
+    \begin{equation*}
+        \rho_q(s) := \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
+    \end{equation*}
+    is a meromorphic function on $\Re(s) > 0$ with a simple pole at $s = 1$. 
+\end{lemma}
+\begin{proof}
+    By Prop.~\ref{prop:logarithmic_derivative_L}, we have for $\chi \in \mathrm{Dir}(q)$ that
+    \begin{equation*}
+        \frac {\overline{\chi(a)}} {q - 1} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s} = \frac {\overline{\chi(a)}} {q - 1} \frac {L(s, \chi)'} {L(s, \chi)}
+    \end{equation*}
+    If $\chi \neq \chi_0$, then Corollary~\ref{prop:logarithmic_derivative_L_bounded} shows that this function is holomorphic on $\Re(s) > 0$.
+
+    If $\chi = \chi_0$ on the other hand, Prop.~\ref{prop:formula_trivial_L_series} shows that
+    \begin{equation*}
+        \frac {L(s, \chi_0)'} {L(s, \chi_0)}
+    \end{equation*}
+    is the logarithmic derivative of $L(s, \chi_0) = (1 - q^{-s}) \zeta(s)$ which has a simple pole at $s = 1$.
+    Hence, also $L(s, \chi_0)'/L(s, \chi_0)$ has a simple pole at $s = 1$.
+    And as $a \perp q$, we see that $\chi_0(a) = 1$ and thus also
+    \begin{equation*}
+        \frac {\overline{\chi_0(a)}} {q - 1} \sum_{n \geq 1} \frac {\Lambda(n) \chi_0(n)} {n^s} = \frac {\overline{\chi_0(a)}} {q - 1} \frac {L(s, \chi_0)'} {L(s, \chi_0)}
+    \end{equation*}
+    has a simple pole at $s = 1$.
+
+    Together, this yields that the sum of those functions
+    \begin{equation*}
+        \rho_a(s) = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
+    \end{equation*}
+    is a meromorphic function with a simple pole at $s = 1$.
+\end{proof}
+\begin{proposition}
+    Assume that $L(1, \chi) \neq 0$ for all $\chi \in \mathrm{Dir}(q)$.
+    Then for all $a \perp q$ there are infinitely many primes $p \equiv a \mod q$.
+\end{proposition}
+\begin{proof}
+    Assume the opposite, i.e. the only primes $p \in \primes$ with $p \equiv a \mod q$ are $p_1, ..., p_N$.
+    By Prop.~\ref{prop:representation_mangoldt_series_congruent_a} we have that
+
+\end{proof}
 

### 2021-12-01 Analytic number theory/submission.tex
Proved main theorem of ANT

@@
 Now we can show the main result of this miniproject.
-We will prove one auxiliary lemma before.
+We will prove two auxiliary lemmas before.
 \begin{lemma}
+    \label{prop:rho_pole_at_one}
     For $a \perp q$, the function
     \begin{equation*}
-        \rho_q(s) := \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
+        \rho_a(s) := \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
     \end{equation*}
-    is a meromorphic function on $\Re(s) > 0$ with a simple pole at $s = 1$. 
+    is a meromorphic function on $\Re(s) > 0$ with a simple poles at $1$ (and possibly other poles on $\Re(s) > 0$).
 \end{lemma}
@@
     \end{equation*}
-    If $\chi \neq \chi_0$, then Corollary~\ref{prop:logarithmic_derivative_L_bounded} shows that this function is holomorphic on $\Re(s) > 0$.
+    If $\chi \neq \chi_0$, then Corollary~\ref{prop:logarithmic_derivative_L_bounded} shows that this function has no pole at $s = 1$.
 
@@
     \begin{equation*}
-        \frac {L(s, \chi_0)'} {L(s, \chi_0)}
+        L(s, \chi_0) = (1 - q^{-s}) \zeta(s)
     \end{equation*}
-    is the logarithmic derivative of $L(s, \chi_0) = (1 - q^{-s}) \zeta(s)$ which has a simple pole at $s = 1$.
-    Hence, also $L(s, \chi_0)'/L(s, \chi_0)$ has a simple pole at $s = 1$.
-    And as $a \perp q$, we see that $\chi_0(a) = 1$ and thus also
+    Hence
+    \begin{equation*}
+        \frac {L(s, \chi_0)'} {L(s, \chi_0)} = \frac { \log(q)q^{-s} \zeta(s) + (1 - q^{-s}) \zeta'(s) } { (1 - q^{-s})\zeta(s) } = \frac {\log(q)} {q^s - 1} + \frac {\zeta'(s)} {\zeta(s)}
+    \end{equation*}
+    has a simple pole at $s = 1$.
+    Since $a \perp q$, we see that $\chi_0(a) = 1$ and thus also
     \begin{equation*}
@@
 \end{proof}
-\begin{proposition}
-    Assume that $L(1, \chi) \neq 0$ for all $\chi \in \mathrm{Dir}(q)$.
+\begin{lemma}
+    \label{prop:correlation_theta_Psi}
+    Let $a \perp q$ and define
+    \begin{equation*}
+        \Psi_a(x) := \sum_{n < x, \ n \equiv a \mod q} \Lambda(n)
+    \end{equation*}
+    and
+    \begin{equation*}
+        \theta_a(x) := \sum_{p < x, \ p \equiv a \mod q} \log(p)
+    \end{equation*}
+    Then
+    \begin{equation*}
+        \Psi_a(x) - \theta_a(x) = O(x^{1/2}\log(x))
+    \end{equation*}
+\end{lemma}
+\begin{proof}
+    Have
+    \begin{align*}
+        \Psi_a(x) - \theta_a(x) =& \sum_{p^k < x, \ p^k \equiv a \mod q} \log(p) - \sum_{p < x, \ p \equiv a \mod q} \log(p) \\
+        =& \sum_{p^k < x, \ k \geq 2, \ p^k \equiv a \mod q} \log(p) \leq \sum_{p^k < x, \ k \geq 2} \log(p) \\
+        =& \Psi(x) - \theta(x) = O(x^{1/2}\log(x))
+    \end{align*}
+    where the last equality was proven in the lecture.
+\end{proof}
+\begin{proposition}[Ex (v)]
+    Assume that $L(1, \chi) \neq 0$ for all $\chi \in \mathrm{Dir}(q) \setminus \{ \chi_0 \}$.
     Then for all $a \perp q$ there are infinitely many primes $p \equiv a \mod q$.
@@
 \begin{proof}
-    Assume the opposite, i.e. the only primes $p \in \primes$ with $p \equiv a \mod q$ are $p_1, ..., p_N$.
-    By Prop.~\ref{prop:representation_mangoldt_series_congruent_a} we have that
+    Assume not, then $\theta_a(x)$ is bounded, i.e. $\theta_a(x) = O(1)$.
+    With Lemma~\ref{prop:correlation_theta_Psi} it follows that $\Psi_a(x) = O(x^{1/2} \log x)$.
 
+    By Prop.~\ref{prop:representation_mangoldt_series_congruent_a} we have that for $\Re(s) > 1$
+    \begin{equation*}
+        \rho_a(s) = \sum_{n \equiv a \mod q} \Lambda(n) n^{-s}
+    \end{equation*}
+    Partial summation yields that for $\Re(s) > 1$ have
+    \begin{align*}
+        \rho_a(s) =& \sum_{n \equiv a \mod q} \Lambda(n) n^{-s} \\
+        =& \lim_{t \to \infty} \Bigl( \underbrace{ t^{-s} \sum_{n < t, \ n \equiv a \mod q} \Lambda(n) }_{ = t^{-s} \Psi_a(t) = t^{-s} O(t\log t) = o(1)} \Bigr) 
+        + s \int_1^\infty \Bigl( \underbrace{\sum_{n < t, \ n \equiv a \mod q} \Lambda(n) }_{ = \Psi_a(t)} \Bigr) t^{-(s + 1)} dt \\
+        =& s \int_1^\infty \Psi_a(t) t^{-s - 1} dt = s \int_1^\infty O(t^{1/2}\log t) t^{-s - 1} dt \\
+        =& O\left( |s| \int_1^\infty \log(t) t^{-\Re(s) - 1/2} dt \right) \\
+        =& O\left( |s| \left( \frac 1 {1/2 - \Re(s)} 1^{1/2 - \Re(s)} + \frac 1 {1/2 - \Re(s)} \int_1^\infty t^{-\Re(s) - 1/2} dt \right) \right) \\
+        =& O\left( |s| \frac 1 {(1/2 - \Re(s))^2} \right)
+    \end{align*}
+    However this function has no pole at $s = 1$, a contradiction to Lemma~\ref{prop:rho_pole_at_one}.
 \end{proof}

### 2021-12-01 Combinatorics/submission.tex
Created basic files
Added ANT to the right file and extended it somewhat
Started Combinatorics

--- 2021-11-29 Algebraic geometry/submission.tex
@@
 \usepackage{amssymb}
+\usepackage{amsthm}
 \usepackage{listings}
@@
 
-\title{Miniproject - Algebraic Geometry}
+\title{Miniproject - Combinatorics}
 \author{Simon Pohmann}
@@
 \newcommand{\C}{\mathbb{C}}
-\newcommand{\I}{\mathbb{I}}
-\newcommand{\V}{\mathbb{V}}
-\newcommand{\divides}{\ | \ }
+
 \newcommand\restr[2]{{
@@
 
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newtheorem{lemma}[definition]{Lemma}
+\newtheorem{remark}[definition]{Remark}
+\newtheorem{proposition}[definition]{Proposition}
+\newtheorem{example}[definition]{Example}
+\newtheorem{corollary}[definition]{Corollary}
+
 \begin{document}
@@
 
-\printbibliography
+We use the convention that $\N = \{ n \in \Z \ | \ n \geq 0 \}$.
+
+\section{Part I}
+
+\begin{proposition}
+    \label{prop:definition_rank_function}
+    Let $P$ be a graded poset in which every maximal chain has length $n + 1$. Then the function
+    \begin{equation*}
+        r: P \to \{ 0, ..., n \}, \quad x \mapsto \max\{ k \in \N \ | \ \exists a_1, ..., a_k \in P: \ a_1 < a_2 < ... < a_k < x \}
+    \end{equation*}
+    is well-defined and the unique function with $x < y$ implies $r(x) < r(y)$ for all $x, y \in P$.
+    We call it the \emph{rank function} of $P$.
+\end{proposition}
+\begin{proof}
+    Clearly $r$ is well-defined, as for every increasing sequence $a_1 < ... < a_k < x$, we have the chain $C := \{ a_1, ..., a_k, x \}$ of size $k + 1$.
+    Hence by assumption, $k \leq n$ and so $r(x)$ is finite and in $\{ 0, ..., n \}$.
+
+    Further, consider $x < y$ in $P$.
+    We have a sequence $a_1 < ... < a_{r(x)} < x$ by definition of $r$.
+    It follows that there is an increasing sequence $a_1 < ... < a_{r(x)} < x < y$ and so $r(y) \geq r(k) + 1 > r(x)$.
+
+    Lastly, assume there was another function $r': P \to \{ 0, ..., n \}$ with this property.
+    Consider any $x \in P$.
+    By definition of $r$, there is an increasing sequence $a_1 < ... < a_{r(x)} < x$ in $P$.
+    Now consider a maximal chain $C$ containing the chain $\{ a_1, ..., a_{r(x)}, x \}$.
+
+    Say $C = \{ b_1, ..., b_{n + 1} \}$ with $b_1 < ... < b_{n + 1}$ and $x = b_j$.
+    Note that we have the increasing sequence $b_1 < ... < b_{j - 1} < b_j = x$ and so by the definition of $r$, find $j \leq r(x) + 1$.
+    On the other hand, have $a_1, ..., a_{r(x)} \in C$ and thus $j = r(x) + 1$, i.e.
+    \begin{equation*}
+        a_1 = b_1, \ ..., \ a_{r(x)} = b_{r(x)}, \ x = b_{r(x) + 1}
+    \end{equation*}
+    As $b_i < b_{i + 1}$, we know that $r'(b_i) < r'(b_{i + 1})$ and inductively, we see $r'(b_i) \geq i - 1$.
+    However, $r'(b_{n + 1}) \leq n$ and thus $r'(b_i) = i - 1$.
+    Finally it follows that $r'(x) = r'(b_{r(x) + 1}) = r(x)$.
+\end{proof}
+Now we will show some basic properties of the rank function.
+\begin{proposition}
+    Let $P$ be a graded poset of maximal rank $n$ with rank function $r$.
+    Then
+    \begin{itemize}
+        \item $x \in P$ is minimal iff $r(x) = 0$ and maximal iff $r(x) = n$.
+        \item If $x < y$ and $r(x) + 1 \neq r(y)$ then there is $z \in P$ with $x < z < y$.
+        \item If $x < y$ then there is an increasing sequence $x < a_1 < ... < a_{r(y) - r(x) - 1} < y$ in $P$. 
+    \end{itemize}
+\end{proposition}
+\begin{proof}
+    For (i), let $x \in P$ be minimal. Then there is no increasing sequence $a_1 < x$ in $P$, so $r(x) \leq 0$.
+    Conversely, let $r(x) = 0$. Assume there was $y \in P$ with $y < x$, then $r(y) < r(x) = 0$, a contradiction.
+    The analogous statement for maximal elements is proved in the same way.
+
+    For (iii), consider $x < y$ in $P$. Then the chain $\{ x, y \}$ is contained in a maximal chain $C \subseteq P$.
+    Say $C = \{ b_1, ..., b_{n + 1} \}$ with $b_1 < ... < b_{n + 1}$.
+
+    Hence we find $r(b_i) < r(b_{i + 1})$ and so inductively that $r(b_i) \geq i - 1$ and $r(b_i) \leq i - 1$ since $r(b_1) \geq 0$ and $r(b_{n + 1}) \leq n$.
+    It follows that $r(b_i) = i - 1$ and so $x = b_{r(x) + 1}, y = {r(y) + 1}$.
+    Therefore, we have a chain
+    \begin{equation*}
+        x < b_{r(x) + 2} < ... < b_{r(y)} < y
+    \end{equation*}
+    of length $r(y) - r(x) - 1$.
+    Statement (ii) follows directly, as in this setting, have $r(y) \geq r(x) + 2$ and so $r(y) - r(x) - 1 \neq 0$.
+\end{proof}
+
+\section{Part II}
+\begin{proposition}
+    For a graded poset $P$ with layers $L_0, ..., L_n$ the following statements are equivalent:
+    \begin{itemize}
+        \item For every antichain $A \subseteq P$ have
+        \begin{equation*}
+            \sum_{i = 0}^n \frac {|A \cap L_i|} {|L_i|} \leq 1
+        \end{equation*}
+        \item For each $1 \leq i \leq n$ and $F \subseteq L_i$ have
+        \begin{equation*}
+            \frac {|\partial F|} {|L_{i - 1}|} \geq \frac {|F|} {|L_i|}
+        \end{equation*}
+        where
+        \begin{equation*}
+            \partial F := \{ a \in L_{i - 1} \ | \ \exists b \in F: \ a \leq b \}
+        \end{equation*}
+        \item There exists a (nonempty) sequence of maximal chains $C_1, ..., C_t$ such that for all $1 \leq i \leq n$ we have:
+        \begin{equation*}
+            |\{ j \ | \ x \in C_j \}| = |\{ j \ | \ y \in C_j \}| \ \text{for all $x, y \in L_i$}
+        \end{equation*}
+    \end{itemize}
+\end{proposition}
+\begin{proof}
+    We show (ii) $\Rightarrow$ (i) $\Rightarrow$ (iii) $\Rightarrow$ (ii).
+    For convenience of notation, write
+    \begin{equation*}
+        A_i := \bigcup_{i \leq j \leq n} A \cap L_j
+    \end{equation*}
+
+    \paragraph{(ii) $\Rightarrow$ (i)} Define sets
+    \begin{equation*}
+        G_n := A \cap L_n \quad \text{and} \quad G_i := \partial G_{i + 1} \cup (A \cap L_i) \ \text{for $0 \leq i < n$}
+    \end{equation*}
+    We show by induction that for $a \in G_i$ there is some $b \in A_i$ with $a \leq b$ and that we have the inequality
+    \begin{equation*}
+        \sum_{j = i}^n \frac {|A \cap L_j|} {|L_j|} \leq \frac {|G_i|} {|L_i|}
+    \end{equation*}
+    The base case is trivial, so let $i < n$.
+    Consider some $a \in G_i$.
+    If $a \in \partial G_{i + 1}$, then there is $b \in G_{i + 1}$ with $a \leq b$.
+    By induction hypothesis, have $c \in A_{i + 1} \supseteq A_i$ with $b \leq c$ and thus $a \leq c$.
+    Otherwise, find $a \in A \cap L_i$ and so $a \leq a$ with $a \in A \cap L_i \subseteq A_i$.
+
+    To show the inequality, note that $\partial G_{i + 1}$ and $A \cap L_i$ are disjoint.
+    Indeed, if $a \in \partial G_{i + 1} \cap A \cap L_i$ then there is $b \in G_{i + 1}$ with $a \leq b$, and further by induction hypothesis there is $c \in A_{i + 1}$ with $a \leq b \leq c$.
+    However, $a \in L_i$ and so $a \neq c$.
+    So we found $a \leq c$ comparable elements in the antichain $A$, a contradiction.
+
+    So we get
+    \begin{align*}
+        \sum_{j = i}^n \frac {|A \cap L_j|} {|L_j|} =& \frac {|A \cap L_i|} {|L_i|} + \sum_{j = i + 1}^n \frac {|A \cap L_j|} {|L_j|} \\
+        \leq& \frac {|A \cap L_i|} {|L_i|} + \frac {|G_{i + 1}|} {|L_{i + 1}|} \leq \frac {|A \cap L_i|} {|L_i|} + \frac {|\partial G_{i + 1}|} {|L_i|} \\
+        =& \frac {|A \cap L_i| + |\partial G_{i + 1}|} {|L_i|} = \frac {|G_i|} {|L_i|}
+    \end{align*}
+    Finally, we have that $G_0 \subseteq L_0$, so
+    \begin{equation*}
+        \sum_{j = 0}^n \frac {|A \cap L_j|} {|L_j|} \leq \frac {|G_i|} {|L_i|} \leq 1
+    \end{equation*}
+
+    \paragraph{(i) $\Rightarrow$ (iii)}
+\end{proof}
+
 \end{document}

### 2021-12-01 Combinatorics/submission.tex
Added further implication in Part 2 to Combinatorics

@@
 \begin{proof}
-    We show (ii) $\Rightarrow$ (i) $\Rightarrow$ (iii) $\Rightarrow$ (ii).
     For convenience of notation, write
@@
 
-    So we get
+    Now we get by using the assumption that
     \begin{align*}
@@
 
-    \paragraph{(i) $\Rightarrow$ (iii)}
+    \paragraph{(ii) $\Rightarrow$ (iii)} Use induction on $n$.
+    Again, the base case is trivial, just take chains $\{x\}$ for each $x \in A = L_0$.
+    So assume that $n > 0$. The set
+    \begin{equation*}
+        A' := \bigcup_{i = 0}^{n - 1} L_i
+    \end{equation*}
+    is a graded poset of maximal rank $n - 1$, and hence there are maximal chains $C_1, ..., C_t \subseteq A'$ such that for all $1 \leq i \leq n - 1$ have
+    \begin{equation*}
+        |\{j \ | \ x \in C_j\}| = |\{j \ | \ y \in C_j\}| \ \text{for all $x, y \in L_i$}
+    \end{equation*}
+    by induction hypothesis.
+    Let now $V_1 = V_2 := [t] \times L_n$ and consider the bipartite graph $G := (V_1 \sqcup V_2, E)$ where $E$ is defined as follows:
+    \begin{equation*}
+        \{ \underbrace{(i, a)}_{\in V_1}, \underbrace{(j, b)}_{\in V_2} \} \in E \ \Leftrightarrow \ \max C_j < a
+    \end{equation*}
+    We use Hall's theorem to show that $G$ has a perfect matching.
+
+    Consider any $W = \{ (i_1, a_1), ..., (i_w, a_w) \} \subseteq V_1$ and let $F = \{ a_1, ..., a_w \}$.
+    Then
+    \begin{equation*}
+        W \subseteq [t] \times F \ \Rightarrow \ |W| \leq t|F|
+    \end{equation*}
+    By choice of $C_1, ..., C_t$, we have that the number of $j$ with $x \in C_j$ is the same for all $x \in L_{n - 1}$, say $k$.
+    Since the $C_i$ are maximal chains, each intersects $L_{n - 1}$ in exactly one element.
+    So have bijection
+    \begin{align*}
+        \{ (x, i) \ | \ x \in L_{n - 1}, 1 \leq i \leq t, x \in C_i\} \to \{ i \ | \ 1 \leq i \leq t \}, \quad (x, i) \mapsto i
+    \end{align*}
+    where the set on the left-hand side has size $k |L_{n - 1}|$. It follows that $k|L_{n - 1}| = t$.
+
+    Using this, we find
+    \begin{align*}
+        N(W) =& \{ (j, b) \ | \ b \in L_n, \exists a \in F: \max C_j < a \} \\
+        =& L_n \times \{ j \ | \ \exists a \in F: \max C_j = a \} \\
+        =& L_n \times \{ j \ | \ \max C_j \in \partial F \}
+    \end{align*}
+    and so
+    \begin{align*}
+        |N(W)| = |L_n| \sum_{C_j \cap \partial F \neq \emptyset} 1 = |L_n| \sum_{x \in \partial F} \sum_{x \in C_j} 1 = |L_n| \sum_{x \in \partial F} k = |L_n| |\partial F| k
+    \end{align*}
+    Together with the assumption that $|\partial F| |L_n| \geq |F| |L_{n - 1}|$ we see that
+    \begin{equation*}
+        |W| \leq t |F| = k |L_{n - 1}| |F| \leq k |\partial F| |L_n| = |N(W)|
+    \end{equation*}
+    So Hall's theorem yields a perfect matching $M \subseteq E$ from $V_1$ to $V_2$.
+    As $|V_1| = |V_2|$, this is already a 1-to-one correspondence.
+
+    Now consider the sets
+    \begin{equation*}
+        C'_m := C_j \cup \{ a \} \ \text{where} \ m = \{\underbrace{(i, a)}_{\in V_1}, \underbrace{(j, b)}_{\in V_2}\} \in M
+    \end{equation*}
+    These are chains, as $\max C_j < a$ for each $C'_m$.
+    Further, for each $x, y \in L_i, i < n$ have that
+    \begin{equation*}
+        |\{ C'_m \ | \ x \in C'_m \}| = |L_n \times \{ j \ | \ x \in C_j \}| = |L_n \times \{ j \ | \ y \in C_j \}| = |\{ C'_m \ | \ y \in C'_m \}|
+    \end{equation*}
+    as $M$ is a matching from $V_2$ to $V_1$.
+    Finally, for all $x \in L_n$ we have that
+    \begin{align*}
+        |\{ C'_m \ | \ x \in C'_m \}| =& |\{ m \in M \ | \ \exists i, v \in V_2: m = \{ (i, x), v \} \}| = |\{ (i, x) \ | \ (i, x) \in V_1 \}| = t
+    \end{align*}
+    as $M$ is a matching from $V_1$ to $V_2$.
+    \paragraph{(iii) $\Rightarrow$ (i)}
 \end{proof}

### 2021-12-01 Combinatorics/submission.tex
Finished part 2 combinatorics

@@
         \end{equation*}
-        \item For each $1 \leq i \leq n$ and $F \subseteq L_i$ have
+        \item For each $1 < i \leq n$ and $F \subseteq L_i$ have
         \begin{equation*}
@@
 \begin{proof}
-    For convenience of notation, write
-    \begin{equation*}
-        A_i := \bigcup_{i \leq j \leq n} A \cap L_j
-    \end{equation*}
-
-    \paragraph{(ii) $\Rightarrow$ (i)} Define sets
-    \begin{equation*}
-        G_n := A \cap L_n \quad \text{and} \quad G_i := \partial G_{i + 1} \cup (A \cap L_i) \ \text{for $0 \leq i < n$}
-    \end{equation*}
-    We show by induction that for $a \in G_i$ there is some $b \in A_i$ with $a \leq b$ and that we have the inequality
-    \begin{equation*}
-        \sum_{j = i}^n \frac {|A \cap L_j|} {|L_j|} \leq \frac {|G_i|} {|L_i|}
-    \end{equation*}
-    The base case is trivial, so let $i < n$.
-    Consider some $a \in G_i$.
-    If $a \in \partial G_{i + 1}$, then there is $b \in G_{i + 1}$ with $a \leq b$.
-    By induction hypothesis, have $c \in A_{i + 1} \supseteq A_i$ with $b \leq c$ and thus $a \leq c$.
-    Otherwise, find $a \in A \cap L_i$ and so $a \leq a$ with $a \in A \cap L_i \subseteq A_i$.
-
-    To show the inequality, note that $\partial G_{i + 1}$ and $A \cap L_i$ are disjoint.
-    Indeed, if $a \in \partial G_{i + 1} \cap A \cap L_i$ then there is $b \in G_{i + 1}$ with $a \leq b$, and further by induction hypothesis there is $c \in A_{i + 1}$ with $a \leq b \leq c$.
-    However, $a \in L_i$ and so $a \neq c$.
-    So we found $a \leq c$ comparable elements in the antichain $A$, a contradiction.
-
-    Now we get by using the assumption that
-    \begin{align*}
-        \sum_{j = i}^n \frac {|A \cap L_j|} {|L_j|} =& \frac {|A \cap L_i|} {|L_i|} + \sum_{j = i + 1}^n \frac {|A \cap L_j|} {|L_j|} \\
-        \leq& \frac {|A \cap L_i|} {|L_i|} + \frac {|G_{i + 1}|} {|L_{i + 1}|} \leq \frac {|A \cap L_i|} {|L_i|} + \frac {|\partial G_{i + 1}|} {|L_i|} \\
-        =& \frac {|A \cap L_i| + |\partial G_{i + 1}|} {|L_i|} = \frac {|G_i|} {|L_i|}
-    \end{align*}
-    Finally, we have that $G_0 \subseteq L_0$, so
-    \begin{equation*}
-        \sum_{j = 0}^n \frac {|A \cap L_j|} {|L_j|} \leq \frac {|G_i|} {|L_i|} \leq 1
-    \end{equation*}
-
+    Show the directions (ii) $\Rightarrow$ (iii) $\Rightarrow$ (i) $\Rightarrow$ (ii)
     \paragraph{(ii) $\Rightarrow$ (iii)} Use induction on $n$.
@@
     by induction hypothesis.
-    Let now $V_1 = V_2 := [t] \times L_n$ and consider the bipartite graph $G := (V_1 \sqcup V_2, E)$ where $E$ is defined as follows:
+    Let now $V_1, V_2 := [t] \times L_n$ (treat them as disjoint) and consider the bipartite graph $G := (V_1 \sqcup V_2, E)$ where $E$ is defined as follows:
     \begin{equation*}
@@
     \begin{align*}
-        |N(W)| = |L_n| \sum_{C_j \cap \partial F \neq \emptyset} 1 = |L_n| \sum_{x \in \partial F} \sum_{x \in C_j} 1 = |L_n| \sum_{x \in \partial F} k = |L_n| |\partial F| k
+        |N(W)| = |L_n| \sum_{\max C_j \in \partial F} 1 = |L_n| \sum_{x \in \partial F} \sum_{x \in C_j} 1 = |L_n| \sum_{x \in \partial F} k = |L_n| |\partial F| k
     \end{align*}
@@
     as $M$ is a matching from $V_1$ to $V_2$.
-    \paragraph{(iii) $\Rightarrow$ (i)}
+
+    \paragraph{(iii) $\Rightarrow$ (i)} Let $C_1, ..., C_t$ be a sequence of maximal chains given by the assumption.
+    For $1 \leq i \leq n$ let $k_i$ be the number of different $j$ such that a fixed element $x \in L_i$ is contained in exactly the $C_j$.
+    By assumption, this does not depend on $x$.
+
+    As in the direction above, we see that $k_i |L_i| = t$ because each $C_j$ intersects $L_i$ in exactly one element, so there is a bijection
+    \begin{align*}
+        \{ (x, j) \ | \ x \in L_i, 1 \leq j \leq t, x \in C_j\} \to \{ j \ | \ 1 \leq j \leq t \}, \quad (x, j) \mapsto j
+    \end{align*}
+    and the set on the left has size $k_i |L_i|$.
+
+    Since each $C_j$ is a chain and $A$ is an antichain, we find that $A$ and $C_j$ intersect in at most one element.
+    So
+    \begin{align*}
+        t \geq& |\{ j \ | \ A \cap C_j \neq \emptyset \}| = \sum_{a \in A} |\{ j \ | \ a \in C_j \}| = \sum_{i = 0}^n \ \sum_{a \in A \cap L_i} |\{ j \ | \ a \in C_j \}| \\
+        =& \sum_{i = 0}^n \ \sum_{a \in A \cap L_i} k_i = \sum_{i = 0}^n k_i |A \cap L_i| = \sum_{i = 0}^n \frac {|A \cap L_i|} {|L_i|} t
+    \end{align*}
+    The claim follows by canceling $t$.
+
+    \paragraph{(i) $\Rightarrow$ (ii)}
+    Consider $A := F \cup (L_{i - 1} \setminus \partial F)$.
+    This is clearly an antichain, as for $x \in F, y \in L_{i - 1} \setminus \partial F$ have $y \not< x$.
+    However, $r(y) < r(x)$ so also $x \not< y$, thus $x$ and $y$ are incomparable.
+    Clearly elements from the same layer are incomparable.
+
+    Thus, the assumption yields that
+    \begin{equation*}
+        \frac {|L_{i - 1}| - |\partial F|} {|L_{i - 1}|} + \frac {|F|} {|L_i|} = \frac {|A \cap L_{i - 1}|} {|L_{i - 1}|} + \frac {|A \cap L_i|} {|L_i|} = \sum_{j = 0}^n \frac {|A \cap L_j|} {|L_j|} \leq 1
+    \end{equation*}
+    This gives
+    \begin{equation*}
+        1 + \frac {|F|} {|L_i|} \leq 1 + \frac {|\partial F|} {|L_{i - 1}|}
+    \end{equation*}
+    and the claim follows.
 \end{proof}

### 2021-12-02 Combinatorics/submission.tex
added part 3 combinatorics

@@
 \begin{proposition}
+    \label{prop:characterization_lym}
     For a graded poset $P$ with layers $L_0, ..., L_n$ the following statements are equivalent:
@@
 
-    Using this, we find
+    Since $\max C_j \in L_{n - 1}$ for all $j$, we have
     \begin{align*}
         N(W) =& \{ (j, b) \ | \ b \in L_n, \exists a \in F: \max C_j < a \} \\
-        =& L_n \times \{ j \ | \ \exists a \in F: \max C_j = a \} \\
+        =& L_n \times \{ j \ | \ \exists a \in F: \max C_j < a \} \\
         =& L_n \times \{ j \ | \ \max C_j \in \partial F \}
     \end{align*}
-    and so
+    and so by the above
     \begin{align*}
@@
 \end{proof}
+\section{Part III}
+We even show the slightly stronger stronger statement that the implication to the second condition of Prop.\ref{prop:characterization_lym} already holds ``locally'', i.e. for each layer separately.
+\begin{proposition}
+    Let $P$ be a graded poset with layers $L_0, ..., L_n$ and let $0 < i \leq n$ such that
+    \begin{itemize}
+        \item Each element $a \in L_i$ covers the same number of elements in $L_{i - 1}$
+        \item Each element $a \in L_{i - 1}$ is covered by the same number of elements in $L_i$
+    \end{itemize}
+    Then for each $F \subseteq L_i$ have
+    \begin{equation*}
+        \frac {|\partial F|} {|L_{i - 1}|} \geq \frac {|F|} {|L_i|}
+    \end{equation*}
+    In particular, if this is true for all $i$, then all the equivalent conditions from Prop.~\ref{prop:characterization_lym} follow.
+\end{proposition}
+\begin{proof}
+    Assume that for all $a \in L_i$
+    \begin{equation*}
+        |\{ b \in L_{i - 1} \ | \ \text{$a$ covers $b$} \}| = k \in \N
+    \end{equation*}
+    and for all $b \in L_{i - 1}$
+    \begin{equation*}
+        |\{ a \in L_i \ | \ \text{$a$ covers $b$} \}| = l \in \N
+    \end{equation*}
+    Double-counting pairs $(a, b) \in L_i \times L_{i - 1}$ such that $a$ covers $b$ yields $k|L_i| = l|L_{i - 1}|$.
+    Now consider $F \subseteq L_i$.
+    Note that by definition of $\partial F$, we have for all $a \in F$ that
+    \begin{equation*}
+        \{ b \in \partial F \ | \ \text{$a$ covers $b$} \} = \{ b \in L_{i - 1} \ | \ \text{$a$ covers $b$} \} = \partial \{a\} \subseteq \partial F
+    \end{equation*}
+    Again by double-counting pairs $(a, b) \in F \times \partial F$ such that $a$ covers $b$, we find
+    \begin{align*}
+        k|F| =& \sum_{a \in F} k = \sum_{a \in F} |\{ b \in L_{i - 1} \ | \ \text{$a$ covers $b$} \}| = \sum_{a \in F} |\{ b \in \partial F \ | \ \text{$a$ covers $b$} \}| \\
+        =& |\{ (a, b) \in F \times \partial F \ | \ \text{$a$ covers $b$} \}| = \sum_{b \in \partial F} |\{ a \in F \ | \ \text{$a$ covers $b$}\}| \\
+        \leq& \sum_{b \in \partial F} |\{ a \in L_i \ | \ \text{$a$ covers $b$}\}| = \sum_{b \in \partial F} l = l |\partial F|
+    \end{align*}
+    Hence
+    \begin{equation*}
+        \frac {|\partial F|} {|L_{i - 1}|} = \frac {l |\partial F|} {l |L_{i - 1}|} \leq \frac {k |F|} {k |L_i|} = \frac {|F|} {|L_i|}
+    \end{equation*}
+\end{proof}
 

### 2021-12-02 Combinatorics/submission.tex
added computation of number of partitions into k sets

@@
 \newcommand{\C}{\mathbb{C}}
+\newcommand{\powerset}{\mathfrak{P}}
 
@@
 \end{proof}
+
 \section{Part III}
@@
 
+\section{Part IV}
+\begin{example}
+    Let $\Pi = \{ \pi \subseteq \powerset(n) \ | \ \text{$\pi$ partition} \}$ be the poset of partitions ordered by refinement.
+    Then $\Pi$ is a graded poset with rank function
+    \begin{equation*}
+        r: \Pi \to \{ 0, ..., n - 1 \}, \quad \pi \mapsto n - |\pi|
+    \end{equation*}
+\end{example}
+\begin{proof}
+    First of all, have $1 \leq |X| \leq n$ for all subsets $X \subseteq \powerset(n)$, hence the function $r$ is well-defined.
+    Next we show that for all $x < y$ have $r(x) < r(y)$.
+    However, if $x$ is a proper refinement of $y$, then clearly $|x| > |y|$, so $r(x) < r(y)$.
+
+    Now assume there is a maximal chain $\pi_1 < ... < \pi_t$ in $\Pi$.
+    As the chain is maximal and $\Pi$ has the maximal element $[n]$, we may assume that $\pi_t = [n]$ and thus $r(\pi_t) = n - 1$.
+    Similarly, we may assume that $p_1 = \powerset(n)$ and so $r(\pi_1) = 0$.
+    We have to show that $t = n$, and so it suffices to show that $r(\pi_i) = 1 + r(\pi_{i - 1})$ for all $0 < i \leq t$.
+
+    Assume not, i.e. $|\pi_{i - 1}| \geq 2 + |\pi_i|$ for some $0 < i \leq t$.
+    Since $\pi_{i - 1}$ is a refinement of $\pi_i$, we find that
+    \begin{equation*}
+        \pi_{i - 1} = \{ A_{11}, ..., A_{1m_1}, \ ..., \ A_{n1}, ..., A_{nm_n} \} \quad \text{with} \quad \pi_i = \Bigl\{ \bigcup_{j \leq m_1} A_{1j}, ..., \bigcup_{j \leq m_n} A_{nj} \Bigr\}
+    \end{equation*}
+    where $n = |\pi_i|$ and $\sum_j m_j = |\pi_{i - 1}| \geq 2 + n$.
+    Hence, for at least two different $s, r \leq n$ we have $m_s, m_r \geq 2$.
+    Now define
+    \begin{equation*}
+        \tilde{\pi} := \{ A_{jk} \ | \ j \neq s \} \cup \Bigl\{ \bigcup_{j \leq m_s} A_{sj} \Bigr\}
+    \end{equation*}
+    Then clearly $\pi_{i - 1} < \tilde{\pi} \leq \pi_i$.
+    However, we know that $\bigcup_j A_{rj} \in \pi_i$ but $\bigcup_j A_{rj} \notin \tilde{\pi}$.
+    Thus $\pi_{i - 1} < \tilde{\pi} < \pi_i$ and we found a longer chain
+    \begin{equation*}
+        \pi_1 < ... < \pi_{i - 1} < \tilde{\pi} < \pi_i < ... < \pi_t
+    \end{equation*}
+    which contradicts the assumed maximality. The claim follows.
+\end{proof}
+\begin{proposition}
+    \label{prop:partitions_recursion}
+    For the number $S(m, k) := |\{ \pi \in \Pi \ | \ |\pi| = k\}|$ we have recursion
+    \begin{equation*}
+        S(m, 1) = 1 \quad \text{and} \quad S(m, k) = \sum_{n = 1}^{m - 1} {m - 1 \choose n} S(n, k - 1)
+    \end{equation*}
+    where $1 \leq k \leq m$.
+\end{proposition}
+\begin{proof}
+    Use induction on $k$. 
+    The base case $k = 1$ is trivial, so let $k > 1$.
+    For any partition $\pi \in \Pi_m$, denote by $A(1, \pi)$ the unique set $A \in \pi$ with $1 \in A$.
+    We find
+    \begin{align*}
+        S(m, k) =& |\{ \pi \in \Pi_m \ | \ |\pi| = k \}| = \Bigl| \bigcup_{\emptyset \neq A \subseteq [m], \ 1 \in A} \{ \pi \in \Pi_m \ | \ |\pi| = k, A(1, \pi) = A \} \Bigr| \\
+        =& \sum_{\emptyset \neq A \subseteq [m], \ 1 \in A} |\{ \pi \in \Pi_m \ | \ |\pi| = k, A(1, \pi) = A \}| \\
+        =& \sum_{\emptyset \neq A \subseteq [m], \ 1 \in A} |\{ \pi \in \Pi_m \ | \ |\pi \setminus \{A\}| = k - 1, A(1, \pi) = A\}| \\
+        =& \sum_{\emptyset \neq A \subseteq [m], \ 1 \in A} |\{ \pi \in \Pi_{m - |A|} \ | \ |\pi| = k - 1 \}| \\
+        =& \sum_{i = 1}^m \ \sum_{A \subseteq [m], \ |A| = i, \ 1 \in A} |\{ \pi \in \Pi_{m - i} \ | \ |\pi| = k - 1 \} \\
+        =& \sum_{i = 1}^m {m - 1 \choose i - 1} S(m - i, k - 1) = \sum_{i = 0}^{m - 1} {m - 1 \choose m - i - 1} S(i, k - 1) \\
+        =& \sum_{i = 1}^{m - 1} {m - 1 \choose i} S(i, k - 1)
+    \end{align*}
+    as for $k > 1$ have that $S(0, k) = 0$.
+\end{proof}
+\begin{example}
+    Have for $m \geq 3$ that
+    \begin{equation*}
+        S(m, 2) = 2^{m - 1} - 1 \quad \text{and} \quad S(m, 3) = \frac 1 2 (3^{m - 1} - 2^m + 1)
+    \end{equation*}
+
+    Note that this is the partition into \emph{exactly} $k$ sets; 
+    I am not completely sure what the exercise description tells us to show, but if it is about the number of ways of decomposing $[m]$ into \emph{at most} $k$ sets, then have
+    \begin{equation*}
+        \Sigma S(m, k)(2) = 2^{m - 1} \quad \text{and} \quad \Sigma S(m, k)(3) = 3^{m - 1} = \frac 1 2 3^{m - 1} - \frac 1 2
+    \end{equation*}
+    for $m \geq 3$.
+    Here $\Sigma S(m, k) = \sum_{l \leq k} S(m, l)$ is the number of partitions of $[m]$ into at most $k$ sets.
+\end{example}
+\begin{proof}
+    By Prop.~\ref{prop:partitions_recursion} have that for $m \geq 1$ we have $S(m, 1) = 1$.
+    Further, for $m \geq 2$ have
+    \begin{equation*}
+        S(m, 2) = \sum_{n = 1}^{m - 1} {m - 1 \choose n} 1 = 2^{m - 1} - 1
+    \end{equation*}
+    Applying this once more yields for $m \geq 3$ that
+    \begin{align*}
+        S(m, 3) =& \sum_{n = 1}^{m - 1} {m - 1 \choose n} (2^{n - 1} - 1) = \frac 1 2 \sum_{n = 1}^{m - 1} {m - 1 \choose n} 2^n - \sum_{n = 1}^{m - 1} {m - 1 \choose n} 1 \\
+        =&\frac 1 2 \sum_{n = 0}^{m - 1} {m - 1 \choose n} 2^n - \frac 1 2 - \sum_{n = 0}^{m - 1} {m - 1 \choose n} 1 + 1 \\
+        =& \frac 1 2 (1 + 2)^{m - 1} - 2^{m - 1} + \frac 1 2 = \frac 1 2 (3^{m - 1} - 2^m + 1)
+    \end{align*}
+\end{proof}
+
 \end{document}

### 2021-12-02 Combinatorics/submission.tex
Finished combinatorics part 4

@@
 \begin{example}
-    Let $\Pi = \{ \pi \subseteq \powerset(n) \ | \ \text{$\pi$ partition} \}$ be the poset of partitions ordered by refinement.
+    Let $\Pi_m = \{ \pi \subseteq \powerset(n) \ | \ \text{$\pi$ partition} \}$ be the poset of partitions ordered by refinement.
     Then $\Pi$ is a graded poset with rank function
@@
     \begin{equation*}
-        \Sigma S(m, k)(2) = 2^{m - 1} \quad \text{and} \quad \Sigma S(m, k)(3) = 3^{m - 1} = \frac 1 2 3^{m - 1} - \frac 1 2
+        \Sigma S(m, k)(2) = 2^{m - 1} \quad \text{and} \quad \Sigma S(m, k)(3) = 3^{m - 1} = \frac 1 2 3^{m - 1} + \frac 1 2
     \end{equation*}
@@
     Here $\Sigma S(m, k) = \sum_{l \leq k} S(m, l)$ is the number of partitions of $[m]$ into at most $k$ sets.
-\end{example}
     \begin{proof}
@@
     \end{proof}
+    Let $m$ be even and consider $\mathcal{A} \subseteq \Pi_m$ of partitions of $[m]$ into two equally sized sets.
+    Then
+    \begin{equation*}
+        |\mathcal{A}| = \frac 1 2 {m \choose m/2}
+    \end{equation*}
+    \begin{proof}
+        Consider the map
+        \begin{equation*}
+            f: [m]^{(m/2)} \to \mathcal{A}, \quad A \mapsto \{ A, [m] \setminus A \}
+        \end{equation*}
+        Then for $A$ and $B \neq A, [m] \setminus A$ have that $\{ A, [m] \setminus A \} \neq \{ B, [m] \setminus B \}$.
+        Conversely, $A$ and $[m] \setminus A$ have the same image under $f$.
+        This shows that $f$ is 2-to-1 and thus 
+        \begin{equation*}
+            |\mathcal{A}| = \frac 1 2 \left| [m]^{(m/2)} \right| = \frac 1 2 {m \choose m/2}
+        \end{equation*}
+    \end{proof}
+    Further have
+    \begin{equation*}
+        |\partial \mathcal{A}| = {m \choose m/2} \left( 2^{m/2 - 1} - 1 \right)
+    \end{equation*}
+    \begin{proof}
+        Consider the map
+        \begin{align*}
+            g: \underbrace{\{ (A, B, C) \ | \ A \in [m]^{(m/2)}, \{ A, B, C \} \in \Pi_m \}}_{ =: \mathcal{G} } \to \partial \mathcal{A}, \quad (A, B, C) &\mapsto \{ A, B, C \}
+        \end{align*}
+        Note that $g$ is well-defined, as for $A \in [m]^{(m/2)}, \{ A, B, C \} \in \Pi_m$ have that $\pi := \{ A, B, C \}$ is a partition in $L_{m - 3}$ that refines the partition $\{ A, B \cup C \} \in \mathcal{A} \subseteq L_{m - 2}$.
+        Further, it is easy to see that $g$ is surjective, as every partition $\pi \in \partial \mathcal{A}$ satisfies $|\pi| = 3$ and has some $A \in \pi$ with $|A| = m/2$.
+
+        To complete the proof, we investigate to what ``extend $g$ is injective''.
+
+        Assume $g(A, B, C) = g(A', B', C')$. As $B, C, B', C' \neq \emptyset$ and $|B \cup C| = |B' \cup C'| = m/2$, we see that $A = A'$.
+        Further, we must then have that $\{ B, C \} = \{ B', C' \}$, hence $(A, B, C) = (A', B', C')$ or $(A, B, C) = (A', C', B')$ (clearly $B \neq C, B' \neq C'$).
+        This shows that the map $g$ is 2-to-1.
+
+        Using this, we find
+        \begin{align*}
+            |\partial \mathcal{A}| =& \frac 1 2 |\mathcal{G}| = \frac 1 2 \sum_{A \in [m]^{(m/2)}} |\{ (B, C) \ | \ \{ B, C \} \ \text{partition of} \ [m] \setminus A \}| \\
+            =& \frac 1 2 \sum_{A \in [m]^{(m/2)}} 2 S(m/2, 2) = \sum_{A \in [m]^{(m/2)}} 2^{m/2 - 1} - 1 = {m \choose m/2} \left( 2^{m/2 - 1} - 1 \right)
+        \end{align*}
+    \end{proof}
+    We can now plug this into the second condition of Prop.~\ref{prop:characterization_lym} to see
+    \begin{align*}
+        \frac {|\partial \mathcal{A}|} {|L_{n - 3}|} &= \frac {{m \choose m/2}\left( 2^{m/2 - 1} - 1\right)} {S(m, 3)} = \frac {{m \choose m/2}\left( 2^{m/2 - 1} - 1\right)} {\frac 1 2 \left( 3^{m - 1} - 2^m + 1 \right)} \\
+        &\quad \sim \frac {2^{m + m/2}} {\sqrt{n}(3^{m - 1} - 2^m)} \sim \frac {3 \left( 2^{3/2} \right)^m} {\sqrt{n} 3^m} = \frac 3 {\sqrt{n}} c^m
+    \end{align*}
+    and
+    \begin{align*}
+        \frac {|\mathcal{A}|} {|L_{n - 2}|} &= \frac {\frac 1 2 {m \choose m/2}} {S(m, 2)} = \frac {{m \choose m/2}} {2^m - 2} \sim \frac {2^m} {\sqrt{n}2^m} = \frac 1 {\sqrt{n}}
+    \end{align*}
+    for some $0 < c < 1$ (here $\sim$ means asymptotically equivalent as $m \to \infty$).
+    In particular, find for sufficiently large $m$ that
+    \begin{equation*}
+        \frac {|\partial \mathcal{A}|} {|L_{n - 3}|} < \frac {|\mathcal{A}|} {|L_{n - 2}|}
+    \end{equation*}
+    and so the conditions of Prop.~\ref{prop:characterization_lym} are not satisfied.
+\end{example}
 

### 2021-12-02 Combinatorics/submission.tex
Started part 5 of combinatorics

@@
     Let $\Pi_m = \{ \pi \subseteq \powerset(n) \ | \ \text{$\pi$ partition} \}$ be the poset of partitions ordered by refinement.
-    Then $\Pi$ is a graded poset with rank function
+    Then $\Pi_m$ is a graded poset with rank function
     \begin{equation*}
-        r: \Pi \to \{ 0, ..., n - 1 \}, \quad \pi \mapsto n - |\pi|
+        r: \Pi_m \to \{ 0, ..., n - 1 \}, \quad \pi \mapsto n - |\pi|
     \end{equation*}
@@
 
-    Now assume there is a maximal chain $\pi_1 < ... < \pi_t$ in $\Pi$.
-    As the chain is maximal and $\Pi$ has the maximal element $[n]$, we may assume that $\pi_t = [n]$ and thus $r(\pi_t) = n - 1$.
+    Now assume there is a maximal chain $\pi_1 < ... < \pi_t$ in $\Pi_m$.
+    As the chain is maximal and $\Pi_m$ has the largest element $[n]$, we may assume that $\pi_t = [n]$ and thus $r(\pi_t) = n - 1$.
     Similarly, we may assume that $p_1 = \powerset(n)$ and so $r(\pi_1) = 0$.
@@
     where $n = |\pi_i|$ and $\sum_j m_j = |\pi_{i - 1}| \geq 2 + n$.
-    Hence, for at least two different $s, r \leq n$ we have $m_s, m_r \geq 2$.
-    Now define
+    Hence, there is one $s \leq n$ with $m_s \geq 3$ or two different $s, r \leq n$ with $m_s, m_r \geq 2$.
+
+    In the first case, consider
+    \begin{equation*}
+        \tilde{\pi} := \{ A_{jk} \ | \ j \neq s \} \cup \Bigl\{ A_{s1}, \bigcup_{2 \leq j \leq m_s} A_{sj} \Bigr\}
+    \end{equation*}
+    and in the second case, consider
     \begin{equation*}
@@
     \end{equation*}
-    Then clearly $\pi_{i - 1} < \tilde{\pi} \leq \pi_i$.
-    However, we know that $\bigcup_j A_{rj} \in \pi_i$ but $\bigcup_j A_{rj} \notin \tilde{\pi}$.
-    Thus $\pi_{i - 1} < \tilde{\pi} < \pi_i$ and we found a longer chain
+    Then $\pi_{i - 1} < \tilde{\pi} < \pi_i$ and we found a longer chain
     \begin{equation*}
@@
     \label{prop:partitions_recursion}
-    For the number $S(m, k) := |\{ \pi \in \Pi \ | \ |\pi| = k\}|$ we have recursion
+    For the number $S(m, k) := |\{ \pi \in \Pi_m \ | \ |\pi| = k\}|$ we have recursion
     \begin{equation*}
@@
 
+\section{Part V}
+\begin{example}
+    Let $\mathcal{P}_{k, d} := \{ 0, ..., k \}^d$ partially ordered by elementwise ordering.
+    Then $\mathcal{P}_{k, d}$ is a graded poset with rank function
+    \begin{equation*}
+        r: \mathcal{P}_{k, d} \to \{ 0, ..., kd \}, \quad a \mapsto \sum_i a_i
+    \end{equation*}
+\end{example}
+\begin{proof}
+    First, we show that for $a < b$ have $r(a) < r(b)$.
+    If $a < b$, then we find that $a_j \leq b_j$ for all $j$ and $a_i \neq b_i$, so $a_i < b_i$ for some $i$.
+    Hence
+    \begin{equation*}
+        r(a) = \sum_j a_j = a_i + \sum_{j \neq i} a_j \leq a_i + \sum_{j \neq i} b_j < b_i + \sum_{j \neq i} b_j = \sum_j b_j = r(b)
+    \end{equation*}
+    Now assume that we have a maximal chain $a_1 < ... < a_t$ in $\mathcal{P}_{k, d}$.
+    Since $\mathcal{P}_{k, d}$ has the smallest element $0 = (0, ..., 0)$ and the largest element $k = (k, ..., k)$, we see that $p_1 = 0$ and $p_t = k$.
+    We want to show $t = kd + 1$, so it suffices to show that $r(a_i) = r(a_{i - 1}) + 1$ for all $0 < i \leq t$.
+
+    Assume not, then 
+    \begin{equation*}
+        r(a_i) - r(a_{i - 1}) = \sum_j a_{ij} - a_{(i - 1)j} \geq 2
+    \end{equation*}
+    For all $j$ we have $a_{ij} \geq a_{(i - 1)j}$ and so there is $s \leq d$ with $a_{is} - a_{(i - 1)s} \geq 2$ or there are different $r, s \leq d$ with $a_{ir} - a_{(i - 1)r}, a_{is} - a_{(i - 1)s} \geq 1$.
+    In both cases, find
+    \begin{equation*}
+        \tilde{a} \in \mathcal{P}_{k, d} \ \text{defined by} \ \tilde{a}_j = \begin{cases}
+            a_{(i - 1)j} & \text{if $j \neq s$} \\
+            a_{(i - 1)j} + 1 & \text{otherwise}
+        \end{cases}
+    \end{equation*}
+    with $a_{i - 1} < \tilde{a} < a_i$. However, this gives a longer chain
+    \begin{equation*}
+        a_1 < ... < a_{i - 1} < \tilde{a} < a_i < ... < a_t
+    \end{equation*}
+    which contradicts the assumed maximality. The claim follows.
+\end{proof}
 \end{document}

### 2021-12-03 Combinatorics/submission.tex
Added some computations for the size of L_i of multi-subsets of {0, ..., k}^d

@@
 \end{proof}
+\begin{definition}
+    Let $P$ be a graded poset with layers $L_0, ..., L_n$.
+    A symmetric chain in $P$ is a chain $C \subseteq P$ such that there is $i \leq n/2$ with
+    \begin{equation*}
+        \forall 0 \leq j \leq n: \ C \cap L_j \neq \emptyset \ \Leftrightarrow \ i \leq j \leq n - i
+    \end{equation*}
+    A decomposition $\mathcal{C}$ of $P$ into chains is called symmetric chain decomposition, if all $C \in \mathcal{C}$ are symmetric.
+\end{definition}
+Note that this definition is compatible with the definition of a symmetric chain for the classical graded poset $\powerset(n)$.
+\begin{proposition}
+    Let $k, d \geq 1$. Then $\mathcal{P}_{k, d}$ has a symmetric chain decomposition.
+\end{proposition}
+\begin{proof}
+
+\end{proof}
+\begin{proposition}
+    Let $M(k, d, n) := |\{ x \in \mathcal{P}_{k, d} \ | \ r(x) = n\}|$. Then for $k, d \geq 1$ we have the recurrence relation
+    \begin{equation*}
+        M(k, 1, n) = \begin{cases}
+            1 & \text{if $0 \leq n \leq k$} \\
+            0 & \text{otherwise}
+        \end{cases}
+        \quad \text{and} \quad
+        M(k, d, n) = \sum_{i = 0}^k M(k, d - 1, n - i)
+    \end{equation*}
+\end{proposition}
+\begin{corollary}
+    Let $k, d \geq 1$. Then
+    \begin{align*}
+        M(k, 2, n) := \begin{cases}
+            0 & \text{if $n > 2k$} \\
+            k + 1 & \text{if $k < n \leq 2k$} \\
+            n + 1 & \text{if $0 \leq n \leq k$} \\
+            0 & \text{if $n < 0$}
+        \end{cases}
+    \end{align*}
+    and
+    \begin{align*}
+        M(k, 3, n) := \begin{cases}
+            0 & \text{if $n > 3k$} \\
+            (k + 1)^2 & \text{if $2k < n \leq 3k$} \\
+            (k + 1)(2n + 2 - k) / 2 & \text{if $k < n \leq 2k$} \\
+            {n + 1 \choose 2} & \text{if $0 \leq n \leq k$} \\
+            0 & \text{if $n < 0$}
+        \end{cases}
+    \end{align*}
+\end{corollary}
+\begin{proof}
+    Just use the recurrence relation twice.
+    The only nontrivial computation is if $k < n \leq 2k$ and $d = 3$; We find
+    \begin{align*}
+        &\sum_{i = 0}^k M(k, 2, n) = \sum_{i = 0}^n M(k, 2, n) = \sum_{i = 0}^{n - 2k - 1} 0 + \sum_{i = n - 2k}^{n - k - 1} (k + 1) + \sum_{i = n - k}^n (i + 1) \\
+        =& (k + 1)(n - k - 1 - (n - 2k) + 1) + \frac {(n + 1)(n + 2)} 2 - \frac {(n - k)(n - k + 1)} 2 \\
+        =& k(k + 1) + kn + n + 1 - \frac {k^2} 2 + \frac k 2 = \frac {(k + 1)(2n + 2 - k)} 2
+    \end{align*}
+\end{proof}
 \end{document}

### 2021-12-05 Algebraic geometry/submission.tex
started with algebraic geometry

@@
 \newcommand{\V}{\mathbb{V}}
+\newcommand{\sgn}{\mathrm{sgn}}
+\newcommand{\extpow}{\mathchoice{{\textstyle\bigwedge}}
+    {{\bigwedge}}
+    {{\textstyle\wedge}}
+    {{\scriptstyle\wedge}}}
+\newcommand{\vspan}{\mathrm{span}}
 \newcommand{\divides}{\ | \ }
@@
 
+\newtheorem{definition}{Definition}
+\newtheorem{lemma}[definition]{Lemma}
+\newtheorem{example}[definition]{Example}
+
 \begin{document}
@@
 
-\printbibliography
+\begin{definition}
+    Let $V$ be a vector space.
+    Then define the $d$-th exterior power as
+    \begin{equation*}
+        \extpow^d(V) := V^{\otimes d} \ / \ \sum_{i = 1}^{d - 1} V^{\otimes (i - 1)} \otimes \bigl\{ v \otimes v' + v' \otimes v \ \bigm| \ v, v' \in V \bigr\} \otimes V^{\otimes (d - i - 1)}
+    \end{equation*}
+    Use the notation $v_1 \wedge ... \wedge v_d := \overline{v_1 \otimes ... \otimes v_d} \in \extpow^k(V)$.
+\end{definition}
+
+\begin{lemma}
+    \label{prop:basic_properties_exterior_product}
+    Let $v_1, ..., v_d \in V$. Have for $\pi \in S_d$ that
+    \begin{equation*}
+        v_{\pi(1)} \wedge ... \wedge v_{\pi(k)} = \sgn(\pi) (v_1 \wedge ... \wedge v_d)
+    \end{equation*}
+    Furthermore if $v_i = v_j$ for some $i \neq j$, then
+    \begin{equation*}
+        v_1 \wedge ... \wedge v_d = 0
+    \end{equation*}
+\end{lemma}
+\begin{proof}
+    Note that
+    \begin{equation*}
+        u \otimes v \otimes v' \otimes w = -(u \otimes v' \otimes v \otimes w)
+    \end{equation*}
+    for all $u \in \extpow^{i - 1}(V), w \in \extpow^{(d - i - 1)}(V), v, v' \in V$.
+
+    Every $\pi \in S_d$ has a decomposition $\pi = \xi_1 ... \xi_n$ into transpositions $\xi_i$.
+    Applying this inductively, we find that
+    \begin{equation*}
+        v_1 \wedge ... \wedge v_d = \sgn(\xi_i ... \xi_n) (v_{(\xi_i ... \xi_n)(1)} \wedge ... v_{(\xi_i ... \xi_n)(k)})
+    \end{equation*}
+    and so
+    \begin{equation*}
+        v_1 \wedge ... \wedge v_d = \sgn(\pi) (v_{\pi(1)} \wedge ... \wedge v_{\pi(k)})
+    \end{equation*}
+
+    Furthermore, we find that
+    \begin{equation*}
+        u \otimes v \otimes v \otimes w = -(u \otimes v \otimes v \otimes w) = 0
+    \end{equation*}
+    must be zero.
+    Hence, if $v_1, ..., v_d \in V$ with $v_i = v_j$ for some $i \neq j$, then there is a permutation $\pi \in S_d$ with $\pi(1) = i, \pi(2) = j$ and
+    \begin{equation*}
+        v_1 \wedge ... \wedge v_d = (\sgn(\pi))(v_i \wedge v_j \wedge v_{\pi(3)} \wedge ... \wedge v_{\pi(k)}) = \sgn(\pi) 0 = 0
+    \end{equation*}
+\end{proof}
+
+\begin{lemma}[1a]
+    Let $\dim(V) \leq 3$. Then every element of $\extpow^k(V)$ is decomposable.
+\end{lemma}
+\begin{proof}
+    Now let $v_1, v_2, v_3$ be a set of generators of $V$.
+    Consider $u_1 = \sum \lambda_i v_i, u_2 = \sum_i \mu_i v_i, u_3 = \sum_i \rho_i v_i$.
+    Then by applying Lemma~\ref{prop:basic_properties_exterior_product}, we see that 
+    \begin{align*}
+        u_1 \wedge u_2 =& \sum_{i, j} \ \lambda_i \mu_j (\underbrace{v_i \wedge v_j}_{\mathclap{\text{$= 0$ if $i = j$}}}) = \sum_{i < j} \lambda_i \mu_j (v_i \wedge v_j) - \sum_{i > j} \lambda_i \mu_j (v_i \wedge v_j) \\
+        =& \sum_{i < j} (\lambda_i \mu_j - \lambda_j \mu_i)(v_i \wedge v_j) = \alpha (v_1 \wedge v_2) + \beta (v_1 \wedge v_3) + \gamma (v_2 \wedge v_3) \\
+        =& \begin{cases}
+            \beta v_1 + \gamma v_2 \wedge \frac \alpha \beta v_2 + v_3 & \text{if $\beta \neq 0$} \\
+            \alpha v_1 - \gamma v_3 \wedge v_2 & \text{otherwise}
+        \end{cases}
+    \end{align*}
+    and
+    \begin{align*}
+        u_1 \wedge u_2 \wedge u_3 =& \sum_{i, j, l} \ \lambda_i \mu_j \rho_l (\underbrace{v_i \wedge v_j \wedge v_l}_{\mathclap{\text{$= 0$ unless $i, j, l$ pairwise distinct}}}) \\
+        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} (v_{\pi(1)} \wedge v_{\pi(2)} \wedge v_{\pi(3)}) \\
+        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi) (v_1 \wedge v_2 \wedge v_3) \\
+        =& (v_1 \wedge v_2 \wedge v_3) \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi)
+    \end{align*}
+    are decomposable.
+    Further, it is easy to see from Lemma~\ref{prop:basic_properties_exterior_product} that $\extpow^k(V) = \{ 0 \}$ for $k \geq 4$, which is trivially decomposable.
+\end{proof}
+
+\begin{example}[1b]
+    Consider $V = k^4$. 
+    Then the element $w := (e_1 \wedge e_2) + (e_3 \wedge e_4) \in \extpow^2(V)$ is not decomposable. 
+\end{example}
+\begin{proof}
+    Assume it was, then there are $a, b \in k^4$ such that
+    \begin{equation*}
+        w = \sum_i a_i e_i \wedge \sum_j b_j e_j = \sum_{i < j} (a_i b_j - a_j b_i) (e_i \wedge e_j)
+    \end{equation*}
+    In other words
+    \begin{equation*}
+        a_1b_2 - a_2b_1 = 1, \ a_3b_4 - a_4b_3 = 1, \ a_i b_j - a_j b_i = 0 \ \text{for all $(i, j) \neq (1, 2), (3, 4)$}
+    \end{equation*}
+    Clearly $a_1 b_2 \neq 0$ or $a_2 b_1 \neq 0$.
+    Similarly, have $a_3 b_4 \neq 0$ or $a_4 b_3 \neq 0$.
+    As all expressions are symmetric w.r.t swapping $a_1, b_2$ with $a_2, b_1$ and $a_3, b_4$ with $a_4, b_3$, we may assume wlog that $a_1 b_2, a_3 b_4 \neq 0$.
+
+    Have $a_1 b_4 = a_4 b_1$ and $a_2 b_4 = a_4 b_2$.
+    We know that $a_1 b_4 \neq 0$ and so
+    \begin{equation*}
+        \frac {a_2} {a_1} = \frac {a_2 b_4} {a_1 b_4} = \frac {a_4 b_2} {a_4 b_1} = \frac {b_2} {b_1} \ \Rightarrow \ a_2 b_1 = a_1 b_2
+    \end{equation*}
+    This contradicts $a_1 b_2 - a_2 b_1 = 1$.
+\end{proof}
+
+\begin{lemma}[1c]
+    Let $d$ be even.
+    An element $\omega \in \extpow^d V$ is decomposable if and only if $\omega \wedge \omega \in \extpow^{2d} V$ is zero.
+\end{lemma}
+\begin{proof}
+    The direction $\Rightarrow$ even holds generally. Assume $\omega = v_1 \wedge ... \wedge v_d$.
+    Then
+    \begin{equation*}
+        \omega \wedge \omega = v_1 \wedge ... \wedge v_d \wedge v_1 \wedge ... \wedge v_d = 0
+    \end{equation*}
+    by Lemma~\ref{prop:basic_properties_exterior_product}. 
+    The other direction is more interesting.
+
+    Let $\omega = v_1 + ... + v_t$ for linearly independent decomposable vectors $v_i \in \extpow^2 V$.
+    Then
+    \begin{align*}
+        0 =& \omega \wedge \omega = \sum_{i, j} v_i \wedge v_j = \sum_{i < j} (v_i \wedge v_j) + (v_j \wedge v_i) \\
+        =& \sum_{i < j} 2(v_i \wedge v_j) = 2\sum_i v_i \wedge \Bigl( \sum_{j > i} v_j \Bigr)
+    \end{align*}
+    Here we used that the permutation $\bigl(1 \ 2d\bigr)\bigl(2 \ (2d - 1)\bigr)...\bigl(d \ (d + 1)\bigr) \in S_{2d}$ has always sign $1$ (since $d$ is even).
+
+    Note that for any nonzero decomposable vector
+    \begin{equation*}
+        u_1 \wedge u_2 \in \Bigl( \extpow^2 \vspan\{v_2, ..., v_t\} \Bigr) \setminus \{0\}
+    \end{equation*}
+    find
+    \begin{equation*}
+        u_1, u_2 \in \vspan\{v_2, ..., v_t\}
+    \end{equation*}
+    In particular, we know that
+    \begin{equation*}
+        v_1 \wedge \Bigl( \sum_{j > i} v_j \Bigr) \in \extpow^2 \vspan\{v_2, ..., v_t\}
+    \end{equation*}
+    and so $v_1 \in \vspan\{v_2, ..., v_t\}$ unless $\sum_{j > i} v_j = 0$.
+    We assumed that the $v_i$ are linearly independent, so the former would give a contradiction.
+    Hence $\sum_{j > i} v_j = 0$ and thus $t = 1$, i.e. $\omega = v_1$ is decomposable.
+\end{proof}
+
 \end{document}

### 2021-12-05 Combinatorics/submission.tex
started with algebraic geometry

@@
 \begin{proposition}
+    \label{prop:biregular_implies_lym}
     Let $P$ be a graded poset with layers $L_0, ..., L_n$ and let $0 < i \leq n$ such that
@@
 \begin{example}
+    \label{ex:partitions_have_no_lym}
     Have for $m \geq 3$ that
@@
 \begin{proof}
+    Use induction on $d$.
+    The base case $d = 1$ is trivial, so assume that $d > 1$.
+    By induction hypothesis, have a symmetric chain decomposition $\mathcal{C}$ of $\mathcal{P}_{k, d - 1}$.
+    For some $C = \{ A_i, A_{i + 1}, ..., A_{d(k - 1) - i} \} \in \mathcal{C}, i < \frac n 2$ with $r(A_j) = j$ and $0 \leq l \leq k, n - 2i - 1$ consider now the chain
+    \begin{equation*}
+        \tilde{C}_l := \{ (A_{i + l}, j) \ | \ 0 \leq j \leq k - l \} \cup \{ (A_j, k - l) \ | \ i + l < j \leq d(k - 1) - (i + l) \}
+    \end{equation*}
+    Then $\tilde{C}_l$ is symmetric w.r.t. $i + l$, as for $i + l \leq j \leq dk - (i + l)$ we have
+    \begin{align*}
+        i + l \leq j \leq k + i \quad &\Rightarrow \quad (A_{i + l}, j - i - l) \in \tilde{C}_l, \\
+        k + i < j \leq dk - (i + l) \quad &\Rightarrow \quad (A_{j - k}, k - l) \in \tilde{C}_l
+    \end{align*}
+    Clearly the $\tilde{C}_l$ are chains and disjoint.
+    Hence, we find a symmetric chain decomposition
+    \begin{equation*}
+        \tilde{\mathcal{C}} := \Bigl\{ \tilde{C}_l \ \Bigm| \ C \in \mathcal{C} \ \text{symmetric chain w.r.t. $i$}, \ 0 \leq l \leq \min\{ k, n - 2i - 1 \} \Bigr\}
+    \end{equation*}
+    of $\mathcal{P}_{k, d}$.
+\end{proof}
+Note that for $k = 1$, this is exactly the proof that was done in the lecture to show that $\powerset(d)$ has a symmetric chain decomposition.
 
-\end{proof}
+\section{Part VI}
+First of all, in Example~\ref{ex:partitions_have_no_lym} we have already shown that the poset $\Pi_m$ does not satisfy the conditions from Prop.~\ref{prop:characterization_lym}.
+Now we want to investigate whether $\mathcal{P}_{k, d}$ does. 
+\begin{lemma}
+    Let $A$ be a poset with two layers $L_0 = \{ u_1, ..., u_m \}, L_1 = \{ v_1, ..., v_n \}$.
+    Then any of the conditions of Prop.~\ref{prop:characterization_lym} is equivalent to the following:
+
+    There exists a matrix $A = (a_{ij}) \in \Q_{\geq 0}^{m \times n}$ such that for all $i, j$
+    \begin{equation*}
+        e_i^T A 1 = e_j^T A 1 \quad \text{and} \quad 1^T A e_i = 1^T A e_j
+    \end{equation*}
+    and $a_{ij} = 0$ whenever $u_i \not< v_j$.
+\end{lemma}
+This lemma does not seem super useful at first, but it gives us a way to check in time polynomial in $O(|P|)$ whether a given poset $P$ satisfies the conditions from Prop.~\ref{prop:characterization_lym}, by using an LP solver.
+Note that this is not easily possible when working directly with any of the three conditions defined before.
+
+Using this, I could check that $\mathcal{P}_{k, d}$ indeed satisfies the conditions for reasonably sized $|\mathcal{P}_{k, d}|$ (e.g. for $k, d \approx 6$).
+Note that already for these ``small'' numbers, we get quite huge posets $|\mathcal{P}_{k, d}|$.
+Hence, I believe that this is true for all $\mathcal{P}_{k, d}$.
+
+My successful-looking attempt is based on the observation that elements of $\mathcal{P}_{k, d}$ ``behave similarly'' (in the sense that there is an element of the automorphism group $\mathrm{Aut}(\mathcal{P}_{k, d})$ mapping one to the other) if the have the same number of equally sized entries.
+This looks promising, as the proof for $\powerset(n)$ and equivalently the proof of Prop.~\ref{prop:biregular_implies_lym} relies on the fact that all elements in one layer of $\powerset(n)$ ``behave similarly'' in this sense.
+
+This is formalized in the next definition.
+\begin{definition}
+    Let $P = \mathcal{P}_{k, d}$. Then define
+    \begin{equation*}
+        P(n_0, ..., n_k) := \{ x \in P \ | \ |\{i \ | \ x(i) = j\}| = n_j \}
+    \end{equation*}
+    Further, for any subset $F \subseteq P$ write
+    \begin{equation*}
+        F(n_0, ..., n_k) := F \cap P(n_0, ..., n_k)
+    \end{equation*}
+\end{definition}
+\begin{lemma}
+    \label{prop:properties_n_distribution_subsets}
+    Have
+    \begin{equation*}
+        |P(n_0, ..., n_k)| = { n_0 + ... + n_k \choose n_0 } { n_1 + ... + n_k \choose n_1 } ... {n_{k - 1} + n_k \choose n_{k - 1}} {n_k \choose n_k}
+    \end{equation*}
+    Further, for all $n_i \in \Z$ with $\sum n_i = d$ and all $a \in P(n_0, ..., n_k), 0 \leq \delta < k$ have
+    \begin{align*}
+        |\partial a \cap P(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k)| &= n_{\delta + 1}, \\
+        |\partial^+ a \cap P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)| &= n_\delta
+    \end{align*}
+    even if any of the $n_i$ are negative.
+\end{lemma}
+
+\begin{proposition}
+    $\mathcal{P}_{k, d}$ satisfies the conditions of Prop.~\ref{prop:characterization_lym}.
+\end{proposition}
+\textit{Proof Attempt.}
+Fix a layer $L_l$ with $0 < l \leq kd$.
+Further, consider any subset $F \subseteq L_l$.
+Now define
+\begin{equation*}
+    U := \{ (n_0, ..., n_k) \ | \ n_i \in \Z, \ n_0 + ... + n_k = d, \ \sum_i i n_i = l \}
+\end{equation*}
+and
+\begin{equation*}
+    V := \{ (n_0, ..., n_k) \ | \ n_i \in \Z, \ n_0 + ... + n_k = d, \ \sum_i i n_i = l - 1 \}
+\end{equation*}
+Note that now
+\begin{align*}
+    L_l = \bigsqcup_{(n_0, ..., n_k) \in U} P(n_0, ..., n_k) \quad \text{and} \quad L_{l - 1} = \bigsqcup_{(n_0, ..., n_k) \in V} P(n_0, ..., n_k)
+\end{align*}
+Now make $V \sqcup U$ into a bipartite graph $G = (V \sqcup U, E)$ by defining for $(m_0, ..., m_k) \in V, (n_0, ..., n_k) \in U$
+\begin{align*}
+    &\{ (m_0, ..., m_k), (n_0, ..., n_k) \} \in E \\
+    &\Leftrightarrow \ \exists 0 \leq \delta < k: \ (n_0, ..., n_k) = (m_0, ..., m_\delta - 1, m_{\delta + 1} + 1, ..., m_k)
+\end{align*}
+Observe that the resulting graph is now $(k - 1)$-regular.
+For $e = \{ (n_0, ..., n_k), (n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k) \} \in E$ define now
+\begin{align*}
+    v_F(e) := \ &\frac {|\partial \bigl(F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)\bigr)(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} \\
+    - &\frac {|F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} {|P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} \\
+    \leq& \frac {|\partial F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} - \frac {|F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} {|P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|}
+\end{align*}
+where we define $|\emptyset|/|\emptyset| := 1$.
+Now consider the graded poset $A := P(n_0, ..., n_k) \sqcup P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)$ with two layers.
+By Lemma~\ref{prop:properties_n_distribution_subsets} we see that
+\begin{itemize}
+    \item Each element in the bottom layer $v \in L_0(A)$ of $A$ is covered by $n_\delta$ elements
+    \item Each element in the top layer $u \in L_1(A)$ of $A$ covers $n_{\delta + 1} + 1$ elements
+\end{itemize}
+Hence we can apply Prop.~\ref{prop:biregular_implies_lym} and see that $v_F(e) \geq 0$.
+Define
+\begin{equation*}
+    p(n_0, ..., n_k) := \frac {|P(n_0, ..., n_k)|} {|L_{\sum in_i}|}
+\end{equation*}
+We know that all $v_F(e) \geq 0$ and by using the $(k - 1)$-regularity, we see
+\begin{align*}
+    0 \leq &\sum_{e \in E} v_F(e) p(n_0, ..., n_k) \\
+    \leq &\sum_{e \in E} \left( \frac {|\partial F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} - \frac {|F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} {|P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} \right) p(n_0, ..., n_k) \\
+    = &(k - 1)\sum_{(n_0, ..., n_k) \in V} \frac {|\partial F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} p(n_0, ..., n_k) \\
+    - &\sum_{(n_0, ..., n_k) \in U} \frac {|F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} \sum_{0 \leq \delta < k} p(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k) \\
+    = &\frac {(k - 1) |\partial F|} {|L_{l - 1}|} - \sum_{(n_0, ..., n_k) \in U} \frac {|F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} \sum_{0 \leq \delta < k} p(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k) \\
+    = &\frac {(k - 1) |\partial F|} {|L_{l - 1}|} - \sum_{(n_0, ..., n_k) \in U} \frac {|F(n_0, ..., n_k)|} {|L_l|} \sum_{0 \leq \delta < k} \frac {(n_\delta + ...
++ n_k + 1)n_{\delta + 1}} {(n_\delta + 1)(n_{\delta + 1} + ...
++ n_k)}
+\end{align*}
+However, the sum
+\begin{equation*}
+    \sum_{0 \leq \delta < k} \frac {(n_\delta + ... + n_k + 1)n_{\delta + 1}} {(n_\delta + 1)(n_{\delta + 1} + ... + n_k)}
+\end{equation*}
+is not always $k - 1$, so this won't work out.
+
+On a higher level, everything I did was to reduce the problem to the case that $F$ is a disjoint union of the $P(n_0, ..., n_k)$ which is nice to see, but does not help too much.
+
 \begin{proposition}
@@
     \end{equation*}
+
+    We also have the recurrence relation
+    \begin{equation*}
+        M(k, d, n) = \sum_{i = 0}^{\lfloor n/k \rfloor} {d \choose i} M(k - 1, d - i, n - ki)
+    \end{equation*}
 \end{proposition}
-\begin{corollary}
+\begin{lemma}
+    Let $R$ be a ring extension of $\Q$ (commutative with one). 
+    For a polynomial $f \in R[X]$ there exists a unique polynomial $\Sigma f \in R[X]$ such that for all $x \in \Z, x \geq 0$ we have
+    \begin{equation*}
+        \Sigma f(x) = \sum_{i = 0}^x f(i)
+    \end{equation*}
+    Furthermore, $\Sigma$ is linear and $\deg(\Sigma f) = \deg(f) + 1$ and $\mathrm{lc}(\Sigma f) = \mathrm{lc}(f) / (\deg(f) + 1)$.
+\end{lemma}
+\begin{proof}
+    Use induction on $\deg(f)$.
+    As everything is linear, it suffices to show the claim for the monomials $X^d$.
+    Define then
+    \begin{equation*}
+        \Sigma X^d := \frac 1 {d + 1} (X + 1)^{d + 1} - \frac 1 {d + 1} \sum_{k = 0}^{d - 1} {d + 1 \choose k} \left( \Sigma X^k \right)
+    \end{equation*}
+    It follows that for all $x \geq 0$ have
+    \begin{align*}
+        &\left( \Sigma X^d \right)(x + 1) - \left( \Sigma X^d \right)(x) \\
+        =& \frac 1 {d + 1} \left( (x + 2)^{d + 1} - x^{d + 1} \right) - \frac 1 {d + 1} \sum_{k = 0}^{d - 1} {d + 1 \choose k} \left( \left( \Sigma X^k \right)(x + 1) - \left( \Sigma X^k \right)(x) \right) \\
+        =& \frac 1 {d + 1} \left( -(x + 1)^{d + 1} + \sum_{k = 0}^{d + 1} {d + 1 \choose k} (x + 1)^k \right) - \frac 1 {d + 1} \sum_{k = 0}^{d - 1} {d + 1 \choose k} (x + 1)^k \\
+        =& \frac 1 {d + 1} \left( \sum_{k = 0}^d {d + 1 \choose k} (x + 1)^k - \sum_{k = 0}^{d - 1} {d + 1 \choose k} (x + 1)^k \right) \\
+        =& \frac 1 {d + 1} {d + 1 \choose d} (x + 1)^d = (x + 1)^d
+    \end{align*}
+    As this holds for infinitely many $x$, we see that $(\Sigma X^d)(X + 1) - \Sigma X^d = (X + 1)^d$ and the claim follows.
+\end{proof}
+\begin{example}
     Let $k, d \geq 1$. Then
@@
             0 & \text{if $n > 2k$} \\
-            k + 1 & \text{if $k < n \leq 2k$} \\
+            2k - n + 1 & \text{if $k \leq n \leq 2k$} \\
             n + 1 & \text{if $0 \leq n \leq k$} \\
@@
     \end{align*}
-    and
-    \begin{align*}
-        M(k, 3, n) := \begin{cases}
-            0 & \text{if $n > 3k$} \\
-            (k + 1)^2 & \text{if $2k < n \leq 3k$} \\
-            (k + 1)(2n + 2 - k) / 2 & \text{if $k < n \leq 2k$} \\
-            {n + 1 \choose 2} & \text{if $0 \leq n \leq k$} \\
-            0 & \text{if $n < 0$}
-        \end{cases}
-    \end{align*}
-\end{corollary}
-\begin{proof}
-    Just use the recurrence relation twice.
-    The only nontrivial computation is if $k < n \leq 2k$ and $d = 3$; We find
-    \begin{align*}
-        &\sum_{i = 0}^k M(k, 2, n) = \sum_{i = 0}^n M(k, 2, n) = \sum_{i = 0}^{n - 2k - 1} 0 + \sum_{i = n - 2k}^{n - k - 1} (k + 1) + \sum_{i = n - k}^n (i + 1) \\
-        =& (k + 1)(n - k - 1 - (n - 2k) + 1) + \frac {(n + 1)(n + 2)} 2 - \frac {(n - k)(n - k + 1)} 2 \\
-        =& k(k + 1) + kn + n + 1 - \frac {k^2} 2 + \frac k 2 = \frac {(k + 1)(2n + 2 - k)} 2
-    \end{align*}
-\end{proof}
+    Note that if two cases are applicable, they both yield the same value.
+\end{example}
 \end{document}

### 2021-12-05 Combinatorics/src/main.rs

@@ -1,0 +1,78 @@
+extern crate feanor_la;
+extern crate mosek;
+
+use feanor_la::combinatorics::iters::*;
+use feanor_la::combinatorics::bitset::*;
+use feanor_la::la::mat::*;
+use feanor_la::algebra::rat::*;
+
+fn find_feasible_solution<M, V>(A: Matrix<M, r64>, b: Vector<V, r64>) -> Option<Vector<VectorOwned<f64>, f64>>
+    where M: MatrixView<r64>, V: VectorView<r64>
+{
+    let cast = |x: r64| (x.num() as f64) / (x.den() as f64);
+
+    let mut env = mosek::Env::new().unwrap();
+    let mut task = env.task().unwrap();
+    task.append_vars(A.col_count() as i32).unwrap();
+    task.append_cons(A.row_count() as i32).unwrap();
+    for j in 0..A.col_count() {
+        task.put_c_j(j as i32, 1.).unwrap();
+        task.put_var_bound(j as i32, mosek::MSK_BK_LO, 0.0, f64::INFINITY).unwrap();
+    }
+    for i in 0..A.row_count() {
+        let indices = A.row(i).iter().enumerate().filter(|(_, x)| **x != r64::ZERO).map(|(i, _)| i as i32).collect::<Vec<_>>();
+        let values = A.row(i).iter().filter(|x| **x != r64::ZERO).map(|x| cast(*x)).collect::<Vec<_>>();
+        task.put_a_row(i as i32, &indices, &values).unwrap();
+        task.put_con_bound(i as i32, mosek::MSK_BK_FX, cast(*b.at(i)), cast(*b.at(i))).unwrap();
+    }
+    task.optimize().unwrap();
+    if task.get_sol_sta(0).unwrap() == mosek::MSK_SOL_STA_PRIM_INFEAS_CER {
+        return None;
+    };
+    let mut result = (0..A.col_count()).map(|_| 0.0).collect::<Vec<_>>();
+    task.get_xx(0, &mut result).unwrap();
+    return Some(Vector::from_fn(result.len(), |i| result[i]));
+}
+
+fn main() {
+    let edges = |L: &[Box<[usize]>], U: &[Box<[usize]>]| cartesian_product(0..L.len(), 0..U.len())
+        .filter(|&(a, b)| {
+            (0..L[a].len()).all(|j| L[a][j] <= U[b][j])
+        }).collect::<Vec<_>>();
+
[…]

### 2021-12-06 Algebraic geometry/submission.tex
continued with algebraic geometry

@@
 \newcommand{\V}{\mathbb{V}}
+\newcommand{\Proj}{\mathbb{P}}
+\newcommand{\Aff}{\mathbb{A}}
+\newcommand{\GL}{\mathrm{GL}}
+\newcommand{\Gr}{\mathrm{Gr}}
 \newcommand{\sgn}{\mathrm{sgn}}
@@
     \end{equation*}
-    Use the notation $v_1 \wedge ... \wedge v_d := \overline{v_1 \otimes ... \otimes v_d} \in \extpow^k(V)$.
+    Use the notation $v_1 \wedge ... \wedge v_d := [v_1 \otimes ... \otimes v_d] \in \extpow^k(V)$.
 \end{definition}
@@
 
+\begin{lemma}[2a]
+    \label{prop:linear_transform_extpow}
+    Let $A = (a_{ij}) \in \GL_d(k)$ and $v_1, ..., v_d \in V$.
+    Then
+    \begin{equation*}
+        \Bigl( \sum_j a_{1j}v_j \Bigl) \wedge ... \wedge \Bigl( \sum_{j} a_{dj} v_j \Bigr) = \det(A) (v_1 \wedge ... \wedge v_d)
+    \end{equation*}
+\end{lemma}
+\begin{proof}
+    By a direct computation using Lemma~\ref{prop:basic_properties_exterior_product}, we find
+    \begin{align*}
+        &\Bigl( \sum_j a_{ij} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) = \sum_{j_1, ..., j_d} a_{1j_1} ... a_{dj_d} (v_{j_1} \wedge ... \wedge v_{j_d}) \\
+        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} (v_{\pi(1)} \wedge ... \wedge v_{\pi(d)}) \\
+        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} \sgn(\pi) (v_1 \wedge ... \wedge v_d) \\
+        = &(v_1 \wedge ... \wedge v_d) \ \sum_{\pi \in S_d} \sgn(\pi) \prod_{j = 1}^d a_{j\pi(j)} = \det(A) (v_1 \wedge ... \wedge v_d)
+    \end{align*}
+    where the last equality holds due to the Leibniz determinant formula.
+\end{proof}
+We see that if there are two bases $v_1, ..., v_d$ and $u_1, ..., u_d$ of a $d$-dimensional vector space $U$, then there exists a basis change matrix $A = (a_{ij}) \in \GL_d(k)$ with
+\begin{equation*}
+    u_i = \sum_j a_{ij} v_j
+\end{equation*}
+So by the Lemma, it follows that
+\begin{equation*}
+    u_1 \wedge ... \wedge u_d = \det(A) (v_1 \wedge ... \wedge v_d)
+\end{equation*}
+As $v_1, ..., v_d$ resp. $u_1, ..., u_d$ are bases, they are linearly independent and in particular, we see that
+\begin{equation*}
+    v_1 \wedge ... \wedge v_d \neq 0 \quad \text{and} \quad u_1 \wedge ... \wedge u_d \neq 0
+\end{equation*}
+Hence they have well-defined images $[v_1 \wedge ... \wedge v_d]$ resp. $[u_1 \wedge ... \wedge u_d]$ in the projective space $\Proj(\extpow^d V)$.
+By the above, find
+\begin{equation*}
+    [v_1 \wedge ... \wedge v_d] = [u_1 \wedge ... \wedge u_d]
+\end{equation*}
+This allows us to study the Grassmanian $\Gr(d, V)$ of a fixed vector space $V$.
+\begin{definition}
+    Define the map
+    \begin{equation*}
+        \phi: \Gr(d, V) \to \Proj(\extpow^d V), \quad \vspan\{v_1, ..., v_d\} \mapsto [v_1 \wedge ... \wedge v_d]
+    \end{equation*}
+    which is well-defined by Lemma~\ref{prop:linear_transform_extpow} as described above.
+\end{definition}
+\begin{lemma}[1a]
+    We have
+    \begin{equation*}
+        \mathrm{im}\phi = D := \{ [v] \in \Proj(\extpow^d V) \ | \ \text{$v$ decomposable}\}
+    \end{equation*}
+\end{lemma}
+\begin{proof}
+    First of all, note that the set $D$ is well-defined, as $v$ is decomposable if and only if $\lambda v$ is decomposable, for all $\lambda \in k^*$.
+
+    By definition of $\phi$, we can directly observe that $\mathrm{im}\phi \subseteq D$.
+    So consider an element $[v] \in D$.
+    As $v$ is decomposable, it follows that $v = v_1 \wedge ... \wedge v_d$ for $v_i \in V$.
+    Not it suffices to show that the $v_i$ are linearly independent, then clearly $\vspan\{v_1, ..., v_d\}$ is a well-defined $d$-dimensional vector subspace of $V$, thus an element of $\Gr(d, V)$.
+
+    Assume not, then there is a nonzero vector $a_1 \in k^d$ with $\sum a_{1i} v_i = 0$.
+    Clearly, we can extend $a_1$ to a basis $a_1, ..., a_d$ of $k^d$, which gives a matrix $A = (a_{ij}) \in \GL_d(k)$.
+
+    However by Lemma~\ref{prop:linear_transform_extpow} we now get
+    \begin{align*}
+        0 =& 0 \wedge \Bigl( \sum_j a_{2j} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) = \Bigl( \sum_j a_{1j} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) \\
+        =& \det(A) (v_1 \wedge ... \wedge v_d)
+    \end{align*}
+    and so $v = v_1 \wedge ... \wedge v_d = 0$ as $\det(A) \neq 0$.
+    However, $v$ was a representative of a point in $\Proj(\extpow^d V)$, a contradiction.
+    The claim follows.
+\end{proof}
 \end{document}

### 2021-12-06 Algebraic geometry/submission.tex
Proved first part of important lemma

@@
 \end{proof}
+\begin{definition}
+    Let $\Gr(d, n) := \Gr(d, k^n)$.
+\end{definition}
+In the lecture, we considered an embedding of $\Gr(d, n)$ into projective space given by minors of the basis matrix.
+This corresponds to the following definition.
+\begin{definition}
+    Define the map
+    \begin{align*}
+        \rho: \Gr(d, n) &\to \Proj\Bigl(k^{\{1, ..., n\}^{(d)}}\Bigr) \cong \Proj^{{n \choose d} - 1}, \\
+        \vspan\{v_1, ..., v_d\} &\mapsto \Bigl[ \det\left(\begin{matrix}
+            v_{1i_1} & ... & v_{di_1} \\
+            \vdots & \ddots & \vdots \\
+            v_{1i_d} & ... & v_{di_d}
+        \end{matrix}\right) \Bigr]_{\{i_1, ..., i_d\} \in \{1, ..., n\}^{(d)}}
+    \end{align*}
+    where $\{1, ..., n\}^{(d)} := \{ I \subset \{1, ..., n\} \ | \ \#I = d \}$ is the set of all $d$-element subsets of $\{1, ..., n\}$.
+\end{definition}
+\begin{lemma}
+    There is a linear isomorphism
+    \begin{align*}
+        f: \extpow^d k^n &\to k^{\{1, ..., n\}^{(d)}}, \\
+        \sum_j v_1^{(j)} \wedge ... \wedge v_d^{(j)} &\mapsto \Bigl( \sum_j \det\left(\begin{matrix}
+            v_{1i_1}^{(j)} & ... & v_{di_1}^{(j)} \\
+            \vdots & \ddots & \vdots \\
+            v_{1i_d}^{(j)} & ... & v_{di_d}^{(j)}
+        \end{matrix}\right) \Bigr)_{\{i_1, ..., i_d\} \in \{1, ..., n\}^{(d)}}
+    \end{align*}
+\end{lemma}
+\begin{proof}
+    For vectors $v_1, ..., v_d$ and $I = \{i_1, ..., i_d\} \in \{1, ..., n\}^{(d)}$ write
+    \begin{equation*}
+        A_I(v_1, ..., v_d) := \left(\begin{matrix*}
+            v_{1i_1} & ... & v_{di_1} \\
+            \vdots & \ddots & \vdots \\
+            v_{1i_d} & ... & v_{di_d}
+        \end{matrix*}\right)
+    \end{equation*}
+    First of all, we show that $f$ is well-defined.
+    Note that the tensor product can be described as
+    \begin{align*}
+        V^{\otimes d} := k^{V \times ...\times V} / \vspan\{ &\bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes \bigl(v_i + v'_i\bigl) \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \\
+        &- \bigl(v_1 \otimes ... \otimes v_d\bigl) - \bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes v'_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl), \\
+        & \bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes \lambda v_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \\
+        &- \lambda\bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes v_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \ | \ i \leq d, v_j, v'_i \in V\}
+    \end{align*}
+    where $v_1 \otimes ... \otimes v_d := \mathbb{1}_{(v_1, ..., v_d)}$.
+    Hence the external power can be described as
+    \begin{align*}
+        \extpow^d V := k^{V \times ... \times V} / \vspan\Bigl\{ &\bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes \bigl(v_i + v'_i\bigl) \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \\
+        &- \bigl(v_1 \otimes ... \otimes v_d\bigl) - \bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes v'_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl), \\
+        & \bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes \lambda v_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \\
+        &- \lambda\bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes v_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl), \\
+        &v_1 \otimes ... v_{j - 1} \otimes (v_j \otimes v_{j + 1} + v_{j + 1} \otimes v_j) \otimes v_{j + 1} \otimes ... \otimes v_d \\
+        &\quad | \ i \leq d, \ j \leq d - 1, \ v_1, ..., v_d, v'_i \in V\Bigr\}
+    \end{align*}
+    So it suffices to show that for all $I \in \{1, ..., n\}^{(d)}$ and vectors $v_1, ..., v_d, v'_i \in V$
+    \begin{align*}
+        \det(A_I(v_1, ..., v_i + v'_i, ..., v_d)) = \det(A_I(v_1, ..., v_d)) + \det(A_I(v_1, ..., v'_i, ..., v_d))
+    \end{align*}
+    and
+    \begin{align*}
+        \det(A_I(v_1, ..., \lambda v_i, ..., v_d)) = \lambda\det(A_I(v_1, ..., v_d))
+    \end{align*}
+    and
+    \begin{equation*}
+        \det(A_I(v_1, ..., v_{j + 1}, v_j, ..., v_d)) = -\det(A_I(v_1, ..., v_d))
+    \end{equation*}
+    However, these properties follow from the well-known properties of the determinant.
+    In particular, $\det$ is linear in each column and swapping columns negates the determinant.
+    It follows that $f$ is indeed well-defined.
+
+    It is clear by definition that $f$ is linear, so it is left to show that it is bijective. 
+\end{proof}
 \end{document}

### 2021-12-06 Algebraic geometry/submission.tex
proved the isomorphism

@@
 
+\section{Part I}
+
 \begin{definition}
@@
     \begin{equation*}
-        \extpow^d(V) := V^{\otimes d} \ / \ \sum_{i = 1}^{d - 1} V^{\otimes (i - 1)} \otimes \bigl\{ v \otimes v' + v' \otimes v \ \bigm| \ v, v' \in V \bigr\} \otimes V^{\otimes (d - i - 1)}
+        \extpow^d(V) := V^{\otimes d} \ / \ \sum_{i = 1}^{d - 1} V^{\otimes (i - 1)} \otimes \vspan\bigl\{ v \otimes v' + v' \otimes v \ \bigm| \ v, v' \in V \bigr\} \otimes V^{\otimes (d - i - 1)}
     \end{equation*}
@@
 
+\begin{lemma}
+    \label{prop:linear_transform_extpow}
+    Let $A = (a_{ij}) \in \GL_d(k)$ and $v_1, ..., v_d \in V$.
+    Then
+    \begin{equation*}
+        \Bigl( \sum_j a_{1j}v_j \Bigl) \wedge ... \wedge \Bigl( \sum_{j} a_{dj} v_j \Bigr) = \det(A) (v_1 \wedge ... \wedge v_d)
+    \end{equation*}
+\end{lemma}
+\begin{proof}
+    By a direct computation using Lemma~\ref{prop:basic_properties_exterior_product}, we find
+    \begin{align*}
+        &\Bigl( \sum_j a_{ij} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) = \sum_{j_1, ..., j_d} a_{1j_1} ... a_{dj_d} (v_{j_1} \wedge ... \wedge v_{j_d}) \\
+        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} (v_{\pi(1)} \wedge ... \wedge v_{\pi(d)}) \\
+        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} \sgn(\pi) (v_1 \wedge ... \wedge v_d) \\
+        = &(v_1 \wedge ... \wedge v_d) \ \sum_{\pi \in S_d} \sgn(\pi) \prod_{j = 1}^d a_{j\pi(j)} = \det(A) (v_1 \wedge ... \wedge v_d)
+    \end{align*}
+    where the last equality holds due to the Leibniz determinant formula.
+\end{proof}
+\begin{lemma}
+    \label{prop:extpow_zero_iff_independent}
+    For $v_1, ..., v_d \in V$ have
+    \begin{equation*}
+        v_1 \wedge ... \wedge v_d = 0 \ \Leftrightarrow \ v_1, ..., v_d \ \text{linearly dependent}
+    \end{equation*}
+\end{lemma}
+\begin{proof}
+    For the direction $\Rightarrow$, assume that $v_1, ..., v_d$ are not independent. 
+    Then there is a nonzero vector $a_1 \in k^d$ with $\sum a_{1i} v_i = 0$.
+    Clearly, we can extend $a_1$ to a basis $a_1, ..., a_d$ of $k^d$, which gives a matrix $A = (a_{ij}) \in \GL_d(k)$.
+
+    However by Lemma~\ref{prop:linear_transform_extpow} we now get
+    \begin{align*}
+        0 =& 0 \wedge \Bigl( \sum_j a_{2j} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) = \Bigl( \sum_j a_{1j} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) \\
+        =& \det(A) (v_1 \wedge ... \wedge v_d)
+    \end{align*}
+    and so $v = v_1 \wedge ... \wedge v_d = 0$ as $\det(A) \neq 0$.
+
+    Direction $\Leftarrow$ TODO
+\end{proof}
+\begin{lemma}
+    \label{prop:subspace_closed}
+    Let $v \in V$ and $u \in \extpow^{d - 1} U$ for a linear subspace $U \leq V$. 
+    If $u \neq 0$ then $v \in U$.
+\end{lemma}
+\begin{proof}
+    TODO
+\end{proof}
+
 \begin{lemma}[1c]
@@
     \end{equation*}
-    and so $v_1 \in \vspan\{v_2, ..., v_t\}$ unless $\sum_{j > i} v_j = 0$.
+    and so $v_1 \in \vspan\{v_2, ..., v_t\}$ unless $\sum_{j > i} v_j = 0$ by Lemma~\ref{prop:subspace_closed}.
     We assumed that the $v_i$ are linearly independent, so the former would give a contradiction.
@@
 
-\begin{lemma}[2a]
-    \label{prop:linear_transform_extpow}
-    Let $A = (a_{ij}) \in \GL_d(k)$ and $v_1, ..., v_d \in V$.
-    Then
-    \begin{equation*}
-        \Bigl( \sum_j a_{1j}v_j \Bigl) \wedge ... \wedge \Bigl( \sum_{j} a_{dj} v_j \Bigr) = \det(A) (v_1 \wedge ... \wedge v_d)
-    \end{equation*}
-\end{lemma}
-\begin{proof}
-    By a direct computation using Lemma~\ref{prop:basic_properties_exterior_product}, we find
-    \begin{align*}
-        &\Bigl( \sum_j a_{ij} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) = \sum_{j_1, ..., j_d} a_{1j_1} ... a_{dj_d} (v_{j_1} \wedge ... \wedge v_{j_d}) \\
-        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} (v_{\pi(1)} \wedge ... \wedge v_{\pi(d)}) \\
-        = &\sum_{\pi \in S_d} a_{1\pi(1)} ... a_{d\pi(d)} \sgn(\pi) (v_1 \wedge ... \wedge v_d) \\
-        = &(v_1 \wedge ... \wedge v_d) \ \sum_{\pi \in S_d} \sgn(\pi) \prod_{j = 1}^d a_{j\pi(j)} = \det(A) (v_1 \wedge ... \wedge v_d)
-    \end{align*}
-    where the last equality holds due to the Leibniz determinant formula.
-\end{proof}
-We see that if there are two bases $v_1, ..., v_d$ and $u_1, ..., u_d$ of a $d$-dimensional vector space $U$, then there exists a basis change matrix $A = (a_{ij}) \in \GL_d(k)$ with
+\section{Part II}
+
+In this part, we want to consider the connection of external powers to the Grassmanian.
+First of all, assume there are two bases $v_1, ..., v_d$ and $u_1, ..., u_d$ of a $d$-dimensional vector space $U$. 
+Then there exists a basis change matrix $A = (a_{ij}) \in \GL_d(k)$ with
 \begin{equation*}
@@
 \end{equation*}
-So by the Lemma, it follows that
+So by Lemma~\ref{prop:linear_transform_extpow}, it follows that
 \begin{equation*}
@@
 \end{equation*}
+by Lemma~\ref{prop:extpow_zero_iff_independent}.
 Hence they have well-defined images $[v_1 \wedge ... \wedge v_d]$ resp. $[u_1 \wedge ... \wedge u_d]$ in the projective space $\Proj(\extpow^d V)$.
@@
 
-    Assume not, then there is a nonzero vector $a_1 \in k^d$ with $\sum a_{1i} v_i = 0$.
-    Clearly, we can extend $a_1$ to a basis $a_1, ..., a_d$ of $k^d$, which gives a matrix $A = (a_{ij}) \in \GL_d(k)$.
-
-    However by Lemma~\ref{prop:linear_transform_extpow} we now get
-    \begin{align*}
-        0 =& 0 \wedge \Bigl( \sum_j a_{2j} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) = \Bigl( \sum_j a_{1j} v_j \Bigr) \wedge ... \wedge \Bigl( \sum_j a_{dj} v_j \Bigr) \\
-        =& \det(A) (v_1 \wedge ... \wedge v_d)
-    \end{align*}
-    and so $v = v_1 \wedge ... \wedge v_d = 0$ as $\det(A) \neq 0$.
-    However, $v$ was a representative of a point in $\Proj(\extpow^d V)$, a contradiction.
-    The claim follows.
+    This follows directly from Lemma~\ref{prop:extpow_zero_iff_independent}.
 \end{proof}
@@
     \end{align*}
-    where $v_1 \otimes ... \otimes v_d := \mathbb{1}_{(v_1, ..., v_d)}$.
+    where $v_1 \otimes ... \otimes v_d := \chi_{(v_1, ..., v_d)}$.
     Hence the external power can be described as
@@
     It is clear by definition that $f$ is linear, so it is left to show that it is bijective. 
+    To show surjectivity, note that the $\pm e_I, I \in \{1, ..., n\}^{(d)}$ form a basis of $k^{\{1, ..., n\}^{(d)}}$.
+    Clearly for $I = \{i_1, ..., i_d\}, J \in \{1, ..., n\}^{(d)}$ we have that
+    \begin{equation*}
+        f(e_{i_1} \wedge ... \wedge e_{i_d})_J = \det(A_J(e_{i_1}, ..., e_{i_j})) = \begin{cases}
+            0 & \text{if $J \not\subseteq I$} \\
+            \pm 1 & \text{if $J \subseteq I$}
+        \end{cases}
+    \end{equation*}
+    so $f(e_{i_1} \wedge ... \wedge e_{i_d}) = e_I$ and we deduce that $\mathrm{im}f = \Proj^{\{1, ..., k\}^{(d)}}$.
+
+    Finally, note that
+    \begin{equation*}
+        e_{i_1} \wedge ... \wedge e_{i_d}
+    \end{equation*}
+    for $i_1 < ... < i_d$ form a basis of $\extpow^d k^n$.
+    Clearly, they span $\extpow^d k^n$, and the following argument shows that they are linearly independent.
+    Assume
+    \begin{equation*}
+        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} (e_{i_1} \wedge ... \wedge e_{i_d}) = 0
+    \end{equation*}
+    Then
+    \begin{equation*}
+        0 = e_1 \wedge \Bigl( \sum_{1 < i_2 < ...
+< i_d} \lambda_{1, i_2, ..., i_d} (e_{i_2} \wedge ..
+\wedge e_{i_d}) \Bigr) + \sum_{1 < i_1 < ...
+< i_d} \lambda_{i_1, ..., i_d} (e_{i_1} \wedge ...
+\wedge e_{i_d} )
+    \end{equation*}
+    Clearly $e_1 \notin \vspan\{e_2, ..., e_n\}$ and so by Lemma~\ref{prop:subspace_closed} we see that
+    \begin{equation*}
+        \sum_{1 < i_2 < ... < i_d} \lambda_{1, i_2, ..., i_d} (e_{i_2} \wedge ... \wedge e_{i_d}) = 0
+    \end{equation*}
+    Repeating this argument inductively shows that $\lambda_{1, 2, ..., d} = 0$.
+    As $k^n$ is symmetric w.r.t. permuting the $e_j$, we see that all $\lambda_{i_1, ..., i_d} = 0$ are zero.
+
+    It follows that $\dim(\extpow^d k^n) = \dim(\Proj^{\{1, ..., n\}^{(d)}})$ and we find that $f$ is also injective.
 \end{proof}

### 2021-12-06 Algebraic geometry/submission.tex
Started proof of 2c in algebraic geometry
finished 2c algebraic geometry

@@
 \newtheorem{example}[definition]{Example}
+\newtheorem{proposition}[definition]{Proposition}
+\newtheorem{corollary}[definition]{Corollary}
 
@@
     Let $v \in V$ and $u \in \extpow^{d - 1} U$ for a linear subspace $U \leq V$. 
-    If $u \neq 0$ then $v \in U$.
+    If $v \wedge u \in \extpow^d U$ then $v \in U$ or $u = 0$.
 \end{lemma}
@@
 \end{proof}
+\begin{corollary}[2b]
+    Let $\bar{f}: \Proj(\extpow^d k^n) \to \Proj^{{n \choose d} - 1}$ be the map $f$ from before modulo $k^*$.
+    Then
+    \begin{equation*}
+        \rho = f \circ \phi
+    \end{equation*}
+    and in particular, we see that $\phi(Gr(d, n))$ is a projective variety and isomorphic to $\rho(\Gr(d, n))$.
+\end{corollary}
+\begin{proposition}[2c]
+    The map $\phi$ is injective.
+\end{proposition}
+\begin{proof}
+    Consider two $d$-dimensional subspaces $U, W$ of $k^n$ with $\phi(U) = \phi(W)$.
+    Let $u_1, ..., u_l$ be a basis of $U \cap W$ and extend it to bases $u_1, ..., u_d$ of $U$ and $u_1, ..., u_l, w_{l + 1}, ..., w_d$ of $W$.
+    As $\phi(U) = \phi(W)$, we can assume that the $u_i, w_i$ are scaled such that
+    \begin{align*}
+        0 =& (u_1 \wedge ... \wedge u_d) - (u_1 \wedge ... \wedge u_l \wedge w_{l + 1} \wedge ... \wedge w_d) \\
+        =& u_1 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr)
+    \end{align*}
+    By Lemma~\ref{prop:subspace_closed} we see that
+    \begin{equation*}
+        u_2 \wedge ... \wedge u_l \wedge \bigl( (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) \bigr) = 0
+    \end{equation*}
+    as $u_1 \notin \vspan\{u_2, ..., u_d, w_{l + 1}, ..., w_d\}$.
+    Inductively, this argument shows that
+    \begin{equation*}
+        (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) = 0
+    \end{equation*}
+    If $l < d$, we can now apply Lemma~\ref{prop:subspace_closed} again to see that
+    \begin{equation*}
+        u_{l + 1} \in \vspan\{ u_{l + 2}, ..., u_d, w_{l + 1}, ..., w_d \}
+    \end{equation*}
+    as $u_{l + 2} \wedge ... \wedge u_d \neq 0$ by Lemma~\ref{prop:extpow_zero_iff_independent}.
+    However, this contradicts the linear independence of $u_{l + 1}, ..., u_d, w_{l + 1}, ..., w_d$.
+    Hence it must be $l = d$ and so $U = W$.
+\end{proof}
 \end{document}

### 2021-12-06 Algebraic geometry/submission.tex
solved 3a algebraic geometry

@@
 \begin{lemma}[1c]
+    \label{prop:characterization_decomposable_d_even}
     Let $d$ be even.
@@
 \begin{lemma}
+    \label{prop:isomorphism_extpow_det}
     There is a linear isomorphism
@@
 \begin{corollary}[2b]
+    \label{prop:image_phi}
     Let $\bar{f}: \Proj(\extpow^d k^n) \to \Proj^{{n \choose d} - 1}$ be the map $f$ from before modulo $k^*$.
@@
 \end{proof}
+
+\section{Part III}
+In this part, we want to investigate the geometric properties of the Grassmanian resp. the image of $\phi$.
+First of all, we introduce coordinates on $\Proj(\extpow^d k^n)$.
+\begin{definition}
+    Note that in the proof of Lemma~\ref{prop:isomorphism_extpow_det} it was shown that $v_{i_1} \wedge ...
+\wedge v_{i_d}$ for $i_1 < ...
+< i_d$ is a basis of $\extpow^d k^n$ if $v_1, ..., v_n$ is a basis of $V$.
+    We introduce the homogeneous coordinates w.r.t. that basis, namely
+    \begin{align*}
+        x: \Proj(\extpow^d k^n) &\to \Proj_k^{\{1, ..., n\}^{(d)}} \cong \Proj_k^{{n \choose d} - 1}, \\
+        \Bigl[ \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} (v_{i_1} \wedge ... \wedge v_{i_d}) \Bigr] &\mapsto \bigl[ \lambda_{i_1, ..., i_d} \bigr]_{i_1 < ... < i_d}
+    \end{align*}
+    The individual coordinates will be denoted by $x_I$ for some $I \in \{1, ..., n\}^{(d)}$ or $x_{i_1, ..., i_d}$ for $i_1 < ... < i_d$.
+\end{definition}
+\begin{proposition}[3a]
+    For the embedding $\phi: \Gr(2, V) \to \extpow^2 V$ we have
+    \begin{equation*}
+        \Gr(2, V) \cong \mathrm{im}\phi = \V(I)
+    \end{equation*}
+    where
+    \begin{equation*}
+        I := \langle x_{i, j}x_{u, v} + x_{i, v}x_{j, u} - x_{i, u}x_{j, v} \ | \ i < j < u < v \rangle \leq k\bigl[\Proj(\extpow^d V)\bigr] = k[x_{i, j} \ | \ i < j]
+    \end{equation*}
+\end{proposition}
+\begin{proof}
+    By Lemma~\ref{prop:image_phi} we have that
+    \begin{equation*}
+        [\omega] \in \mathrm{im}\phi \ \Leftrightarrow \ \omega\ \text{decomposable}
+    \end{equation*}
+    and so by Lemma~\ref{prop:characterization_decomposable_d_even}
+    \begin{equation*}
+        \omega \in \mathrm{im}\phi \ \Leftrightarrow \ \omega \wedge \omega = 0
+    \end{equation*}
+    In $\Proj(\extpow^d V)$ we find that
+    \begin{align*}
+        &\Bigl( \sum_{i < j} x_{i, j} (e_i \wedge e_j) \Bigr) \wedge \Bigl( \sum_{u < v} x_{u, v} (e_u \wedge e_v) \Bigr) = \sum_{\substack{i < j\\u < v}} x_{i, j} x_{u, v} (e_i \wedge e_j \wedge e_u \wedge e_v) \\
+        =& \ 2\sum_{\substack{i < j < u < v}} x_{i, j} x_{u, v} (e_i \wedge e_j \wedge e_u \wedge e_v) + 2\sum_{\substack{i < u < j < v}} x_{i, j} x_{u, v} (e_i \wedge e_j \wedge e_u \wedge e_v) \\
+        &+ 2\sum_{\substack{u < i < j < v}} x_{i, j} x_{u, v} (e_i \wedge e_j \wedge e_u \wedge e_v) \\
+        =&2 \sum_{i < j < u < v} (x_{i, j} x_{u, v} - x_{i, u} x_{j, v} + x_{j, u} x_{i, v}) (e_i \wedge e_j \wedge e_u \wedge e_v)
+    \end{align*}
+    As the $e_i \wedge e_j \wedge e_u \wedge e_v$ are linearly independent, we see that for $[\omega] \in \Proj(\extpow^2 V)$ we have
+    \begin{equation*}
+        [\omega] \in \mathrm{im}\phi \ \Leftrightarrow \ \forall i < j < u < v: \ (x_{i, j} x_{u, v} + x_{i, v} x_{j, u} - x_{i, u} x_{j, v})(\omega) = 0
+    \end{equation*}
+    Hence $\mathrm{im}\phi = \V(I)$.
+\end{proof}
 \end{document}

### 2021-12-07 Algebraic geometry/submission.tex
Wrote sage script for alg geo

--- 2021-12-06 Algebraic geometry/submission.tex
@@
 
+\theoremstyle{definition}
 \newtheorem{definition}{Definition}
@@
 \end{proof}
+
+\section{Part III}
+In this part, we want to investigate the geometric properties of the Grassmanian resp. the image of $\phi$.
+First of all, we introduce coordinates on $\Proj(\extpow^d k^n)$.
+\begin{definition}
+    Note that in the proof of Lemma~\ref{prop:isomorphism_extpow_det} it was shown that $v_{i_1} \wedge ...
+\wedge v_{i_d}$ for $i_1 < ...
+< i_d$ is a basis of $\extpow^d k^n$ if $v_1, ..., v_n$ is a basis of $V$.
+    We introduce the homogeneous coordinates w.r.t. that basis, namely
+    \begin{align*}
+        x: \Proj(\extpow^d k^n) &\to \Proj_k^{\{1, ..., n\}^{(d)}} \cong \Proj_k^{{n \choose d} - 1}, \\
+        \Bigl[ \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} (v_{i_1} \wedge ... \wedge v_{i_d}) \Bigr] &\mapsto \bigl[ \lambda_{i_1, ..., i_d} \bigr]_{i_1 < ... < i_d}
+    \end{align*}
+    The individual coordinates will be denoted by $x_I$ for some $I \in \{1, ..., n\}^{(d)}$ or $x_{i_1, ..., i_d}$ for $i_1 < ... < i_d$.
+\end{definition}
+\begin{proposition}[3a]
+    \label{prop:equations_grassmanian_2}
+    For the embedding $\phi: \Gr(2, V) \to \extpow^2 V$ we have
+    \begin{equation*}
+        \Gr(2, V) \cong \mathrm{im}\phi = \V(I)
+    \end{equation*}
+    where
+    \begin{equation*}
+        I := \langle x_{i, j}x_{u, v} + x_{i, v}x_{j, u} - x_{i, u}x_{j, v} \ | \ i < j < u < v \rangle \leq k\bigl[\Proj(\extpow^d V)\bigr] = k[x_{i, j} \ | \ i < j]
+    \end{equation*}
+\end{proposition}
+\begin{proof}
+    By Lemma~\ref{prop:image_phi} we have that
+    \begin{equation*}
+        [\omega] \in \mathrm{im}\phi \ \Leftrightarrow \ \omega\ \text{decomposable}
+    \end{equation*}
+    and so by Lemma~\ref{prop:characterization_decomposable_d_even}
+    \begin{equation*}
+        \omega \in \mathrm{im}\phi \ \Leftrightarrow \ \omega \wedge \omega = 0
+    \end{equation*}
+    In $\Proj(\extpow^d V)$ we find that
+    \begin{align*}
+        &\Bigl( \sum_{i < j} x_{i, j} (e_i \wedge e_j) \Bigr) \wedge \Bigl( \sum_{u < v} x_{u, v} (e_u \wedge e_v) \Bigr) = \sum_{\substack{i < j\\u < v}} x_{i, j} x_{u, v} (e_i \wedge e_j \wedge e_u \wedge e_v) \\
+        =& \ 2\sum_{\substack{i < j < u < v}} x_{i, j} x_{u, v} (e_i \wedge e_j \wedge e_u \wedge e_v) + 2\sum_{\substack{i < u < j < v}} x_{i, j} x_{u, v} (e_i \wedge e_j \wedge e_u \wedge e_v) \\
+        &+ 2\sum_{\substack{u < i < j < v}} x_{i, j} x_{u, v} (e_i \wedge e_j \wedge e_u \wedge e_v) \\
+        =&2 \sum_{i < j < u < v} (x_{i, j} x_{u, v} - x_{i, u} x_{j, v} + x_{j, u} x_{i, v}) (e_i \wedge e_j \wedge e_u \wedge e_v)
+    \end{align*}
+    As the $e_i \wedge e_j \wedge e_u \wedge e_v$ are linearly independent, we see that for $[\omega] \in \Proj(\extpow^2 V)$ we have
+    \begin{equation*}
+        [\omega] \in \mathrm{im}\phi \ \Leftrightarrow \ \forall i < j < u < v: \ (x_{i, j} x_{u, v} + x_{i, v} x_{j, u} - x_{i, u} x_{j, v})(\omega) = 0
+    \end{equation*}
+    Hence $\mathrm{im}\phi = \V(I)$.
+\end{proof}
+\begin{example}[2b]
+    For $n = 4$, Prop.~\ref{prop:equations_grassmanian_2} yields that $\Gr(2, 4) \cong \mathrm{im}\phi = \V(I)$ where
+    \begin{equation*}
+        I = \langle x_{1, 2} x_{3, 4} + x_{1, 4} x_{2, 3} - x_{1, 3} x_{2, 4} \rangle \in k[x_{1, 2}, x_{1, 3}, x_{1, 4}, x_{2, 3}, x_{2, 4}, x_{3, 4}]
+    \end{equation*}
+    Changing the indices used for the coordinates, we find
+    \begin{equation*}
+        \Gr(2, 4) = \V(x_0 x_5 + x_2 x_3 - x_2 x_4)
+    \end{equation*}
+    which is exactly what we found in the lecture.
+\end{example}
+\begin{example}[2c]
+    For $n = 5$, Prop.~\ref{prop:equations_grassmanian_2} yields that $\Gr(2, 5) \cong \mathrm{im}\phi = \V(I)$ where
+    \begin{align*}
+        I = \langle &x_{1, 2} x_{3, 4} + x_{1, 4} x_{2, 3} - x_{1, 3} x_{2, 4}, \quad x_{1, 2} x_{3, 5} + x_{1, 5} x_{2, 3} - x_{1, 3} x_{2, 5}, \\
+        &x_{1, 2} x_{4, 5} + x_{1, 5} x_{2, 4} - x_{1, 4} x_{2, 5}, \quad x_{1, 3} x_{4, 5} + x_{1, 5} x_{3, 4} - x_{1, 4} x_{3, 5}, \\ 
+        &x_{2, 3} x_{4, 5} + x_{2, 5} x_{3, 4} - x_{2, 4} x_{3, 5} \rangle \leq k\bigl[ \Proj(\extpow^2 k^5) \bigr]
+    \end{align*}
+    Using the following Sage-code, we can compute the number of intersection points of $\Gr(2, 5)$ with 3-dimensional hyperplanes, and find a probable value for its degree.
+    \lstinputlisting{./examples.sage}
+\end{example}
 \end{document}

### 2021-12-07 Analytic number theory/submission.tex
Added part III (vi) to ant and fixed some minor points in all miniprojects

@@
     \begin{equation*}
-        L(s, f) := \sum_{n \geq 1} f(n) n^{-s}
+        L(s, \chi) := \sum_{n \geq 1} \chi(n) n^{-s}
     \end{equation*}
@@
     \begin{equation*}
-        \lim_{s \to 1} L(s, \chi) = \sum_{n \geq 1} \frac {\chi(n)} n
+        \lim_{s \to 1^+} L(s, \chi) = \sum_{n \geq 1} \frac {\chi(n)} n
     \end{equation*}
@@
     For the other direction, assume that $c = 0$.
+    We will only consider real $s$ now.
     Observe that by Bernoulli's inequality, have for $0 < s \leq 1$ that
@@
     Thus the limit is continuous and extends $L(s, \chi_f)$ defined on $]1, \infty[$.
-    It follows that $\lim_{t \to s} L(t, \chi_f)$ exists and is equal to $\sum_{n \geq 1} \chi(n) n^{-s}$.
+    It follows that $\lim_{t \to s^+} L(t, \chi_f)$ exists and is equal to $\sum_{n \geq 1} \chi(n) n^{-s}$.
 \end{proof}
@@
 \begin{example}[Ex (v)]
+    \label{ex:nontrivial_dirichlet_characters_mod_5}
     We consider the Dirichlet characters mod 5.
@@
     On the other hand, a primitive root modulo 5 is e.g. given by $r = 2$ since $2^2 \equiv -1 \mod 5$.
-    Thus we have $5 - 1 = 4$ Dirichlet characters mod 5, namely those given by
+    Thus we have the trivial Dirichlet character $\chi_0$ and $5 - 1 = 4$ nontrivial Dirichlet characters mod 5, namely those given by
     \begin{align*}
-        1 &\mapsto 1,\ 2 \mapsto \omega_5 = \exp(2\pi i/5),\ 3 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 4 \mapsto \omega_5^2 = \exp(4\pi i/5),\ \\
-        1 &\mapsto 1,\ 2 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 3 \mapsto \omega_5 = \exp(2\pi i/5),\ 4 \mapsto \omega_5^4 = \exp(8\pi i/5),\ \\
-        1 &\mapsto 1,\ 2 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 3 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 4 \mapsto \omega_5^1 = \exp(2\pi i/5),\ \\
-        1 &\mapsto 1,\ 2 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 3 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 4 \mapsto \omega_5^3 = \exp(6\pi i/5),\ \\
+        \chi_1: 1 &\mapsto 1,\ 2 \mapsto \omega_5 = \exp(2\pi i/5),\ 3 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 4 \mapsto \omega_5^2 = \exp(4\pi i/5),\ \\
+        \chi_2: 1 &\mapsto 1,\ 2 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 3 \mapsto \omega_5 = \exp(2\pi i/5),\ 4 \mapsto \omega_5^4 = \exp(8\pi i/5),\ \\
+        \chi_3: 1 &\mapsto 1,\ 2 \mapsto \omega_5^3 = \exp(6\pi i/5),\ 3 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 4 \mapsto \omega_5^1 = \exp(2\pi i/5),\ \\
+        \chi_4: 1 &\mapsto 1,\ 2 \mapsto \omega_5^4 = \exp(8\pi i/5),\ 3 \mapsto \omega_5^2 = \exp(4\pi i/5),\ 4 \mapsto \omega_5^3 = \exp(6\pi i/5),\ \\
     \end{align*}
@@
 \end{proof}
+\begin{example}[Ex (vi)]
+    For all the nontrivial Dirichlet characters $\chi_1, ..., \chi_4$ defined in Example~\ref{ex:nontrivial_dirichlet_characters_mod_5}, we have
+    \begin{equation*}
+        L(1, \chi_i) \neq 0
+    \end{equation*}
+    It follows that there are infinitely many primes $\equiv a \mod 5$, for all $a \perp 5$.
+\end{example}
+\begin{proof}
+    By Prop.~\ref{prop:dirichlet_series_at_one} we know that
+    \begin{equation*}
+        L(1, \chi_i) = \sum_{n \geq 1} \chi(n) n^{-s}
+    \end{equation*}
+    For the fifth root of unity $\omega \in \C$ such that $\chi_i(1) = \omega$, we thus find
+    \begin{align*}
+        L(1, \chi_i) =& \sum_{k \geq 0} \sum_{1 \leq n \leq 4} \frac {\chi(5k + n)} {(5k + n)^s} = \sum_{k \geq 0} \frac {\omega} {(5k + 1)^s} + \frac {\omega^2} {(5k + 2)^s} + \frac {\omega^3} {(5k + 3)^s} + \frac {\omega^4} {(5k + 4)^s} \\
+        =& \sum_{k \geq 0} \omega \Bigl( \underbrace{\frac 1 {(5k + 1)^s} - \frac 1 {(5k + 4)^s}}_{> 0} \Bigr) + \omega^2 \Bigl( \underbrace{\frac 1 {(5k + 2)^s} - \frac 1 {(5k + 3)^s}}_{> 0} \Bigr)
+    \end{align*}
+    Hence we have positive coefficients $a_k, b_k > 0$ with
+    \begin{equation*}
+        L(1, \chi_i) - \sum_{k \geq 0} a_k \omega + b_k \omega^2 = \omega \sum_{k \geq 0} a_k + b_k \omega
+    \end{equation*}
+    In particular,
+    \begin{equation*}
+        \Im\left( \frac {L(1, \chi_i)} {\omega} \right) = \sum_{k \geq 0} b_k \Im(\omega) = \Im(\omega) \underbrace{ \sum_{k \geq 0} b_k }_{> 0}
+    \end{equation*}
+    Since $\chi_i$ is a nontrivial Dirichlet character, we see that $\Im(\omega) \neq 0$ and so $\Im(L(1, \chi_i)/\omega) \neq 0$, thus $L(1, \chi_i) \neq 0$.
+\end{proof}
+\begin{remark}[Ex (vii)]
+    TODO
+\end{remark}
 

### 2021-12-07 Algebraic geometry/submission.tex
Fixed minor issues in alg geo
Added part III (vi) to ant and fixed some minor points in all miniprojects
Finished sketch of the lemma on the leading term ideal of I(Gr(2, V))

@@
 \usepackage{listings}
+\usepackage{stmaryrd}
 \usepackage[style=english]{csquotes}
@@
 \newcommand{\sgn}{\mathrm{sgn}}
+\newcommand{\contradiction}{\lightning}
 \newcommand{\extpow}{\mathchoice{{\textstyle\bigwedge}}
@@
     \begin{equation*}
-        u \otimes v \otimes v' \otimes w = -(u \otimes v' \otimes v \otimes w)
+        u \wedge v \wedge v' \wedge w = -(u \wedge v' \wedge v \wedge w)
     \end{equation*}
@@
     \begin{equation*}
-        u \otimes v \otimes v \otimes w = -(u \otimes v \otimes v \otimes w) = 0
+        u \wedge v \wedge v \wedge w = -(u \wedge v \wedge v \wedge w) = 0
     \end{equation*}
@@
 \begin{proof}
-    For the direction $\Rightarrow$, assume that $v_1, ..., v_d$ are not independent. 
+    For the direction $\Leftarrow$, assume that $v_1, ..., v_d$ are not independent. 
     Then there is a nonzero vector $a_1 \in k^d$ with $\sum a_{1i} v_i = 0$.
@@
 
-    Direction $\Leftarrow$ TODO
+    Direction $\Rightarrow$ TODO
 \end{proof}
@@
     \begin{equation*}
-        \rho = f \circ \phi
+        \rho = \bar{f} \circ \phi
     \end{equation*}
@@
     Using the following Sage-code, we can compute the number of intersection points of $\Gr(2, 5)$ with 3-dimensional hyperplanes, and find a probable value for its degree.
-    \lstinputlisting{./examples.sage}
+    \lstinputlisting[language = python]{./examples.sage}
+    This shows that the degree of $\Gr(2, 5)$ is indeed 5, as expected.
 \end{example}
+To investigate the properties of $\phi(\Gr(2, n))$ for larger $n$, we use one tool I encountered during an earlier course on Computational Commutative Algebra and Algebraic Geometry.
+\begin{proposition}[Macaulay Basis Theorem]
+    Let $\preceq$ be a graded monomial ordering on $R = k[x_0, ..., x_n]$.
+    Then for an ideal $I \leq R$ have that the monomials $x_0^{\alpha_0} ... x_n^{\alpha_n} \notin \mathrm{lt}(I)$ are a $k$-vector space basis of $R/I$.
+
+    Here $\mathrm{lt}(I)$ is the leading term ideal of $I$, i.e. the ideal generated by the leading terms of all $f \in I$, w.r.t. $\preceq$.
+\end{proposition}
+\begin{proof}
+    See \cite{kreuzer}.
+\end{proof}
+\begin{lemma}
+    Define the graded reverse monomial ordering $\preceq$ on $R := k[x_{i, j} \ | \ i < j]$ where the variables $x_{i, j}$ are ordered co-lexicographically w.r.t. $(i, j)$, i.e.
+    \begin{equation*}
+        x_{i, j} \leq x_{u, v} \ :\Leftrightarrow \ (i, j) \leq_{\text{colex}} (u, v)
+    \end{equation*}
+    Moreover, let
+    \begin{equation*}
+        I := \langle x_{i, j}x_{u, v} + x_{i, v}x_{j, u} - x_{i, u}x_{j, v} \ | \ i < j < u < v \rangle \leq R
+    \end{equation*}
+    be the ideal defining $\phi(\Gr(d, V))$ that was considered above. Then
+    \begin{equation*}
+        \mathrm{lt}(I) = J := \langle x_{i, v} x_{j, u} \ | \ i < j < u < v \rangle \leq R
+    \end{equation*}
+\end{lemma}
+\begin{proof}
+    Note that for $i < j < u < v$ have $x_{u, v}, x_{j, v} \succ x_{i, v} \succ x_{i, j}, x_{i, u}, x_{j, u}$.
+    Thus the leading term of $x_{i, j} x_{u, v} + x_{i, v} x_{j, u} - x_{i, u} x_{j, v}$ is
+    \begin{equation*}
+        \mathrm{lt}(x_{i, j} x_{u, v} + x_{i, v} x_{j, u} - x_{i, u} x_{j, v}) = x_{i, v} x_{j, u}
+    \end{equation*}
+    It follows that $J \subseteq \mathrm{lt}(I)$.
+
+    For the other direction, we use a quite lengthy degree argument.
+    Sadly, the argument I found is quite full of technical detail.
+    I try to present it as clearly as possible, at the cost of being not always completely formal. 
+    But honestly, the proof contains enough indices already.
+
+    Consider homogeneous polynomials $f_{i, j, u, v} \in R$ and
+    \begin{equation*}
+        F = \sum_{i < j < u < v} f_{i, j, u, v} \ (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v})
+    \end{equation*}
+    We want to show that $\mathrm{lt}(F) \in J$.
+
+    Let
+    \begin{equation*}
+        f_{i, j, u, v} = \sum_{\alpha \in \N^N} c^{(i, j, u, v)}_\alpha x^\alpha
+    \end{equation*}
+    Then
+    \begin{equation*}
+        F = \sum_{\alpha \in \N^N} \sum_{i < j < u < v} c^{(i, j, u, v)}_\alpha x^\alpha \ (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v})
+    \end{equation*}
+    and so there exists $\alpha \in \N^N$ and $\epsilon \in k^*$ with
+    \begin{equation*}
+        \mathrm{lt}(F) = \epsilon \cdot \mathrm{lt}\Bigl( \sum_{i < j < u < v} c_\alpha^{(i, j, u, v)} x^\alpha \ (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v}) \Bigr)
+    \end{equation*}
+    Hence, we may assume wlog that all the $f_{i, j, u, v}$ are scaled monomials.
+
+    Now, observe that all monomials in $F$ are of the form
+    \begin{align*}
+        \epsilon \ x_{i, v} \ x_{j, u} \ f_{i, j, u, v} \quad \text{or} \quad 
+        \epsilon \ x_{i, u} \ x_{j, v} \ f_{i, j, u, v} \quad \text{or} \quad 
+        \epsilon \ x_{i, j} \ x_{u, v} \ f_{i, j, u, v} 
+    \end{align*}
+    where $\epsilon \in k^*$ and $i < j < u < v$.
+    In particular, this is true for the leading term $\mathrm{lt}(F)$.
+    In the first of those case, clearly $\mathrm{lt}(F) \in J$.
+
+    So consider now the second case, i.e. $\mathrm{lt}(F) = \epsilon \ x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$.
+    Since $x_{i, v} \ x_{j, u} \ f_{i, j, u, v} \succ x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$, we see that the term $x_{i, v} \ x_{j, u} \ f_{i, j, u, v}$ cannot occur in $F$, i.e. must ``cancel out''.
+    Hence the monomial $\epsilon \ x_{i, v} \ x_{j, u} \ f_{i, j, u, v}$ has a nonzero coefficient in
+    \begin{equation*}
+        F - f_{i, j, u, v} x_{i, v} x_{j, u} = \sum_{\substack{a < b < c < d\\(a, b, c, d) \neq (i, j, u, v)}} f_{a, b, c, d} \ (x_{a, d} x_{b, c} - x_{a, c} x_{b, d} + x_{a, b} x_{c, d})
+    \end{equation*}
+    and so for $(a, b, c, d) \neq (i, j, u, v), \epsilon' \in k^*$ have that
+    \begin{align*}
+        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, d} \ x_{b, c} \quad \text{or}\\
+        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, c} \ x_{b, d} \quad \text{or}\\
+        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, b} \ x_{c, d}
+    \end{align*}
+    However, the second and third case imply that $f_{a, b, c, d} \ x_{a, d} \ x_{b, c} \succ f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$.
+    Hence, the ``new'' monomial $f_{a, b, c, d} \ x_{a, d} \ x_{b, c}$ also has to ``cancel out'' in the sum representation of $F$, as comes after $\mathrm{lt}(F) = \epsilon x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$ in the order $\preceq$.
+    So applying the whole argument inductively (induction on the number of monomials $\succ f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$ that occur in any of the polynomials we work with), we end up in the first case
+    \footnote{There is a small argument missing here, namely that we apply the next argument on each step of the induction, to show the claim for $f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$.
+However, it should be easy to see that this is possible.}.
+
+    If $(a, d) = (i, v)$ then $(b, c) \neq (j, u)$ and $x_{b, c} \divides f_{i, j, u, v}$.
+    Thus
+    \begin{equation*}
+        x_{b, c} \ x_{i, u} \ x_{j, v} \divides \mathrm{lt}(F) = \epsilon \ x_{i, u} \ x_{j, v} \ f_{i, j, u, v}
+    \end{equation*}
+    with $i < j < u < v$ and $i < b < c < v$. 
+    No matter how $j, u, b, c$ are ordered relatively to each other, we see that in each possible case $x_{b, c} \ x_{i, u} \ x_{j, v} \in J$:
+    \begin{align*}
+        j < u < b < c \ &\Rightarrow \ x_{j, v} x_{b, c} \in J \\
+        j < b < u < c \ &\Rightarrow \ x_{j, v} x_{b, c} \in J \\
+        j < b < c < u \ &\Rightarrow \ x_{i, u} x_{b, c} \in J \\
+        b < j < u < c \ &\Rightarrow \ f_{i, b, c, v} \ x_{i, c} \ x_{b, v} \succ f_{i, j, u, v} \ x_{i, u} \ x_{j, v} \ \contradiction \\
+        b < j < c < u \ &\Rightarrow \ x_{i, u} x_{b, c} \in J \\
+        b < c < j < u \ &\Rightarrow \ x_{i, u} x_{b, c} \in J \\
+    \end{align*}
+    Hence $\mathrm{lt}(F) \in J$.
+
+    It is now left to consider the case $(b, c) = (j, u)$ and the case $(a, d) \neq (i, v), (b, c) \neq (j, u)$.
+    The former can be dealt with in exactly the same way, by noting that $x_{a, d} \divides f_{i, j, u, v}$.
+    In the latter case, we even find $x_{a, d} \ x_{b, c} \divides f_{i, j, u, v}$ and a very similar argument works.
+
+    Finally, one must also consider the third ``big'' case, namely that
+    \begin{equation*}
+        \mathrm{lt}(F) = \epsilon \ x_{i, j} \ x_{u, v} \ f_{i, j, u, v} 
+    \end{equation*}
+    Again, you can do this similarly as before, but now two monomials ``cancel out''.
+    I will not present this here either.
+\end{proof}
+
+\printbibliography
 \end{document}

### 2021-12-08 Algebraic geometry/submission.tex
Added Dirichlet sum of f over primes to ANT

@@
 \newcommand{\sgn}{\mathrm{sgn}}
-\newcommand{\contradiction}{\lightning}
+\newcommand{\contradiction}{\text{contradiction}}
 \newcommand{\extpow}{\mathchoice{{\textstyle\bigwedge}}
@@
     For the other direction, we use a quite lengthy degree argument.
-    Sadly, the argument I found is quite full of technical detail.
-    I try to present it as clearly as possible, at the cost of being not always completely formal. 
-    But honestly, the proof contains enough indices already.
+    Sadly, the only argument I came up with is extremely technical.
+    We try to present it as clearly as possible, at the cost of only sketching some parts.
+    In the end, I checked it using Computer Algebra, and everything fits together.
 
@@
         j < b < c < u \ &\Rightarrow \ x_{i, u} x_{b, c} \in J \\
-        b < j < u < c \ &\Rightarrow \ f_{i, b, c, v} \ x_{i, c} \ x_{b, v} \succ f_{i, j, u, v} \ x_{i, u} \ x_{j, v} \ \contradiction \\
+        b < j < u < c \ &\Rightarrow \ f_{i, b, c, v} \ x_{i, c} \ x_{b, v} \succ f_{i, j, u, v} \ x_{i, u} \ x_{j, v}, \ \contradiction \\
         b < j < c < u \ &\Rightarrow \ x_{i, u} x_{b, c} \in J \\
@@
     Again, you can do this similarly as before, but now two monomials ``cancel out''.
-    I will not present this here either.
+    We will not present this here as well.
+\end{proof}
+
+\begin{lemma}
+    Let $n \geq 4$ and
+    \begin{equation*}
+        J := \{ \{ A, B \} \ | \ A, B \in X, \ A \cap B = \emptyset \} \subseteq X^{(2)}
+    \end{equation*}
+    be a set, where
+    \begin{equation*}
+        X := \{ 1, ..., n \}^{(2)}
+    \end{equation*}
+    Then for $k \geq 3$ have
+    \begin{equation*}
+        |\{ A \in X^{(k)} \ | \ J \subseteq A \}| = 
+    \end{equation*}
+\end{lemma}
+\begin{proof}
+    Use induction on $n$.
+    In the base case $n = 4$ have that
 \end{proof}

### 2021-12-08 Analytic number theory/submission.tex
Added Dirichlet sum of f over primes to ANT

@@
 \end{example}
-Now we want to study the series
+Interestingly, we can also study the series
 \begin{equation*}
@@
 \end{equation*}
-For this, we are first interested in how many primes $\equiv 1, 3 \mod 4$ there are.
+using Euler Products.
+\begin{example}[Ex (ii)]
+    \label{ex:dirichlet_sum_over_primes}
+    Have for $\Re(s) > 1$ that
+    \begin{equation*}
+        \sum_p \frac {f(p)} {p^s} = \log( L(f, s) ) + O( \zeta(2\Re(s)) )
+    \end{equation*}
+    In particular, we see that
+    \begin{equation*}
+        \lim_{s \to 1^+} \sum_p \frac {f(p)} {p^s}
+    \end{equation*}
+    exists.
+\end{example}
+\begin{proof}
+    By Taylor series expansion, see that
+    \begin{equation*}
+        \log(1 - x) = -x + O(|x|^2)
+    \end{equation*}
+    Hence for $\Re(s) > 1$ we can consider the logarithm of the Euler Product to find
+    \begin{align*}
+        \log( L(f, s) ) =& \log\Bigl( \prod_p \sum_{k \geq 0} \frac {f(p^k)} {p^{ks}} \Bigr) = \log\Bigl( \prod_p \frac 1 {1 - f(p)/p^s} \Bigr) \\
+        =& \sum_p -\log\Bigl( 1 - \frac {f(p)} {p^s} \Bigr) = \sum_p \frac {f(p)} {p^s} + O\Bigl( \frac {f(p)^2} {p^{2\Re(s)}} \Bigr) \\
+        = & \sum_p \frac {f(p)} {p^s} + O\Bigl( \underbrace{\sum_p \frac {f(p)} {p^{2\Re(s)}}}_{\leq \zeta(2\Re(s))} \Bigr) = \sum_p \frac {f(p)} {p^s} + O(\zeta(2\Re(s)))
+    \end{align*}
+\end{proof}
 \begin{lemma}
@@
     Using a computer, we can also study the actual frequency of prime numbers $\equiv 1, 3 \mod 4$ among e.g. the first $10^8$ integers.
-    This seems to indicate that both numbers are asymptotically equal.
+    This seems to indicate that both numbers are asymptotically equal, which seems natural, given the result of Example~\ref{ex:dirichlet_sum_over_primes}.
     For example, there are 332180 primes $\equiv 1 \mod 4$ and 332398 primes $\equiv 3 \mod 4$ smaller than $10^8$.

### 2021-12-08 Analytic number theory/submission.tex
Fixed ANT III (iii)

@@
 For the other Dirichlet characters, the situation is slightly more complicated.
-First, we will bound the value of the partial sums of the Dirichlet series for $0 < \Re(s) \leq 1$.
-\begin{lemma}
+First, we will bound the value of the partial sums of a Dirichlet character.
+\begin{lemma}[Ex (iii)]
     \label{prop:bound_partsums_character}
@@
 \end{proof}
-\begin{lemma}[Ex (iii)]
-    \label{prop:character_partsums_bounded}
-    Let $\chi \neq \chi_0$ be a Dirichlet character.
-    Then for $\Re(s) > 0$ have
-    \begin{equation*}
-        \Bigl| \sum_{1 \leq n \leq X} \chi(n) n^{-s} \Bigr| \leq q + \frac {q|s|} {\Re(s)} = O\left( \frac {q|s|} {\Re(s)} \right)
-    \end{equation*}
-    and in particular, this does not depend on $X$.
-\end{lemma}
-\begin{proof}
-    Using partial summation yields
-    \begin{align*}
-        \sum_{1 \leq n \leq X} \chi(n) n^{-s} =& \sum_{1 - \epsilon < n \leq X} \chi(n) n^{-s} \\
-        =& \underbrace{A(1 - \epsilon)}_{= 0} (1 - \epsilon)^{-s} - A(X) X^{-s} + s\int_{1 - \epsilon}^X A(t) t^{-(s + 1)} dt \\
-        =& -A(X) X^{-s} + s\int_1^X A(t) t^{-(s + 1)} dt
-    \end{align*}
-    So
-    \begin{align*}
-        \Bigl| \sum_{1 \leq n \leq X} \chi(n) n^{-s} \Bigr| \leq& \ |A(X) X^{-s}| + |s| \int_1^X |A(t) t^{-(s + 1)}| dt \\
-        \leq& \ q X^{-\Re(s)} + |s| \int_1^X q t^{-\Re(s) - 1} dt \\
-        =& \ q X^{-\Re(s)} + q|s| \left( \frac 1 {\Re(s)} - \frac 1 {X^{\Re(s)}\Re(s)} \right) \\
-        \leq& \ q + q \frac {|s|} {\Re(s)} = O\left( \frac {q|s|} {\Re(s)} \right)
-    \end{align*}
-    for $\Re(s) > 0$.
-\end{proof}
 Now we can show the analytic continuation of $L(s, \chi)$ to $\Re(s) > 0$.
@@
 \begin{proof}
-    Similar to the proof of Lemma~\ref{prop:character_partsums_bounded}, partial summation yields
+    Using partial summation, we find for some $0 < \epsilon < 1$ that
     \begin{align*}
-        \sum_{n \geq 1} \chi(n) n^{-s} = s \int_1^\infty A(t) t^{-(s + 1)} dt
+        \sum_{n \geq 1} \chi(n) n^{-s} =& A(1 - \epsilon) (1 - \epsilon)^{-s} - (-s) \int_{1 - \epsilon}^\infty A(t) t^{-(s + 1)} dt \\
+        =& s \int_1^\infty A(t) t^{-(s + 1)} dt
     \end{align*}
-    By Lemma~\ref{prop:character_partsums_bounded}, this is bounded and hence well-defined and finite for $\Re(s) > 0$.
     Further, the integral converges absolutely by Lemma~\ref{prop:bound_partsums_character}, and thus is holomorphic on $\Re(s) > 0$.

### 2021-12-08 Analytic number theory/submission.tex
Added result from literature search to ANT

--- 2021-12-08 Analytic number theory/submission.tex
@@
 \end{proof}
-\begin{lemma}[Ex (iii)]
-    \label{prop:character_partsums_bounded}
-    Let $\chi \neq \chi_0$ be a Dirichlet character.
-    Then for $\Re(s) > 0$ have
-    \begin{equation*}
-        \Bigl| \sum_{1 \leq n \leq X} \chi(n) n^{-s} \Bigr| \leq q + \frac {q|s|} {\Re(s)} = O\left( \frac {q|s|} {\Re(s)} \right)
-    \end{equation*}
-    and in particular, this does not depend on $X$.
-\end{lemma}
+This bound is already strong enough to show the analytic continuation of $L(s, \chi)$ to $\Re(s) > 0$.
+However, the best known results are significantly stronger than that.
+\begin{proposition}[Pólya–Vinogradov inequality]
+    Let $\chi \neq \chi_0$ be a Dirichlet character mod $q$. 
+    Then for all $n \in \N$, have $|A(n)| = O(\sqrt{q}\log(q))$.
+\end{proposition}
 \begin{proof}
-    Using partial summation yields
-    \begin{align*}
-        \sum_{1 \leq n \leq X} \chi(n) n^{-s} =& \sum_{1 - \epsilon < n \leq X} \chi(n) n^{-s} \\
-        =& \underbrace{A(1 - \epsilon)}_{= 0} (1 - \epsilon)^{-s} - A(X) X^{-s} + s\int_{1 - \epsilon}^X A(t) t^{-(s + 1)} dt \\
-        =& -A(X) X^{-s} + s\int_1^X A(t) t^{-(s + 1)} dt
-    \end{align*}
-    So
-    \begin{align*}
-        \Bigl| \sum_{1 \leq n \leq X} \chi(n) n^{-s} \Bigr| \leq& \ |A(X) X^{-s}| + |s| \int_1^X |A(t) t^{-(s + 1)}| dt \\
-        \leq& \ q X^{-\Re(s)} + |s| \int_1^X q t^{-\Re(s) - 1} dt \\
-        =& \ q X^{-\Re(s)} + q|s| \left( \frac 1 {\Re(s)} - \frac 1 {X^{\Re(s)}\Re(s)} \right) \\
-        \leq& \ q + q \frac {|s|} {\Re(s)} = O\left( \frac {q|s|} {\Re(s)} \right)
-    \end{align*}
-    for $\Re(s) > 0$.
+    See \cite[Ch. 23]{davenport}.
 \end{proof}

### 2021-12-08 Combinatorics/submission.tex
Added part III (vi) to ant and fixed some minor points in all miniprojects
Added the 'core theorem' of combinatorics

@@
     \label{prop:properties_n_distribution_subsets}
-    Have
+    The size of $|P(n_0, ..., n_k)|$ is given by the multinomial coefficient
     \begin{equation*}
-        |P(n_0, ..., n_k)| = { n_0 + ... + n_k \choose n_0 } { n_1 + ... + n_k \choose n_1 } ... {n_{k - 1} + n_k \choose n_{k - 1}} {n_k \choose n_k}
+        |P(n_0, ..., n_k)| = { d \choose n_0, ..., n_k } =  \frac {n!} {n_0! ... n_k!}
     \end{equation*}
-    Further, for all $n_i \in \Z$ with $\sum n_i = d$ and all $a \in P(n_0, ..., n_k), 0 \leq \delta < k$ have
+    if $n_0 + ... + n_k = d$ (otherwise, it is clearly zero).
+
+    Further, for all $n_0, ..., n_k \in \Z$ with $\sum n_i = d$ and all $a \in P(n_0, ..., n_k), 0 \leq \delta < k$ have
     \begin{align*}
@@
 \end{lemma}
+\begin{definition}
+    Define the \emph{core} of $\mathcal{P}_{k, d}$ as the poset
+    \begin{equation*}
+        \mathcal{C}_{k, d} := \{ (n_0, ..., n_k) \ | \ n_0 + ... + n_k = d \}
+    \end{equation*}
+    whose partial order is the transitive closure of the relation $\prec$ defined by
+    \begin{align*}
+        (n_0, ..., n_k) \prec (m_0, ..., m_k) \ :\Leftrightarrow \ \exists 0 \leq \delta < k: \ &m_\delta = n_\delta - 1, \ m_{\delta + 1} = n_{\delta + 1} - 1, \\
+        &\forall i \neq \delta, \delta + 1: m_i = n_i 
+    \end{align*}
+\end{definition}
+\begin{lemma}
+    The layers of $\mathcal{C}_{k, d}$ are
+    \begin{equation*}
+        L_i = \{ (n_0, ..., n_k) \ | \ \sum_j j n_j = i \}
+    \end{equation*}
+    Further, we have a surjective map
+    \begin{equation*}
+        R: \mathcal{P}_{k, d} \to \mathcal{C}_{k, d}, \quad A \mapsto \bigl( |\{j \ | \ A(j) = i\}| \bigr)_{0 \leq i \leq k}
+    \end{equation*}
+    that preserves the ordering and the fiber of a point $(n_0, ..., n_k)$ is exactly $P(n_0, ..., n_k)$.
+\end{lemma}
+
+\begin{proposition}
+    Assume that $\mathcal{C}_{k, d}$ satisfies a ``scaled variant'' of condition (3) of Prop.~\ref{prop:characterization_lym}, namely:
+    There exists a (finite) sequence $C'_1, ..., C'_t$ of maximal chains such that for a chain $C'$ chosen uniformly at random among them, we have
+    \begin{equation*}
+        \Pr[ (n_0, ..., n_k) \in C' ] = \frac {|P(n_0, ..., n_k)|} {|L_{\sum_i i n_i}|}
+    \end{equation*}
+    Then $\mathcal{P}_{k, d}$ satisfies the conditions of Prop.~\ref{prop:characterization_lym}.
+\end{proposition}
+\begin{proof}
+    Denote the two layers of $\mathcal{P}_{k, d}$ by $L_k$ and the two layers of $\mathcal{C}_{k, d}$ by $L'_k$.
+
+    Now consider a chain $C'_i$ from the assumption.
+    Note that by Lemma~\ref{prop:properties_n_distribution_subsets}, we see that for $(n_0, ..., n_k) \in C'_i$ have
+    \begin{itemize}
+        \item Every element in $P(n_0, ..., n_k)$ is covered by $n_\delta$ elements
+        \item Every element in $P(n_0, ..., n_k)$ covers $n_{\delta + 1}$ elements
+    \end{itemize}
+    The $P(n_0, ..., n_k)$ are exactly the layers of the poset $P'_i := \bigcup_{c \in C'_i} P(c)$.
+    Hence Prop.~\ref{prop:biregular_implies_lym} yields that there is a sequence of maximal chains
+    \begin{equation*}
+        C_{i, 1}, ..., C_{i, t_i}
+    \end{equation*}
+    in the poset $P'_i$ such that each element in $P(n_0, ..., n_k)$ is contained in $t_i/|P(n_0, ..., n_k)|$ of them.
+    Note that $R(C_{i, j}) := \{ R(x) \ | \ x \in C_{i, j} \} = C'_i$ holds.
+
+    Now consider a sequence $(\tilde{C}_i)_{i \in I}$ of maximal chains in the poset $A'$ that consists of the $C_{i, j}$ such that one $C_{i, j}$ occurs $\frac 1 {t t_i} |I|$ times.
+    Let $C$ be a chain chosen from them uniformly at random.
+    Observe that then $R(C)$ is a random variable uniformly distributed on the sequence $C'_1, ..., C'_t$.
+
+    Let $x \in L_k$ with $x \in P(n_0, ..., n_k)$.
+    Then
+    \begin{align*}
+        \Pr[x \in C] =& \sum_{1 \leq i \leq t} \Pr[x \in C \ | \ R(C) = C'_i] \ \Pr[R(C) = C'_i] \\
+        =& \sum_{1 \leq i \leq t} \underbrace{\Pr[x \in C \ | \ R(C) = C'_i]}_{ = 1 / |P(n_0, ..., n_k)| \ \text{if $(n_0, ..., n_k) \in C'_i$}} \frac 1 t \\
+        =& \sum_{\substack{1 \leq i \leq t\\(n_0, ..., n_k) \in C'_i}} \frac 1 {|P(n_0, ..., n_k)| t} \\
+        =& \frac t {|P(n_0, ..., n_k)| t} \underbrace{\Pr[(n_0, ..., n_k) \in R(C)]}_{= |P(n_0, ..., n_k)| / |L_k| \ \text{by assumption}} = \frac 1 {|L_k|}
+    \end{align*}
+    where the condition $R(C) = C'_i$ means equality in the index, not as sets 
+    (this makes a difference if the set $C'_i$ occurs more than once in the sequence $C'_1, ..., C'_t$).
+
+    Clearly, this shows that condition (3) of Prop.~\ref{prop:characterization_lym} is satisfied by $(\tilde{C}_i)_{i \in I}$ for $\mathcal{P}_{k, d}$.
+\end{proof}
 
@@
 \end{align*}
-Observe that the resulting graph is now $(k - 1)$-regular.
-For $e = \{ (n_0, ..., n_k), (n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k) \} \in E$ define now
-\begin{align*}
-    v_F(e) := \ &\frac {|\partial \bigl(F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)\bigr)(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} \\
-    - &\frac {|F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} {|P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} \\
-    \leq& \frac {|\partial F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} - \frac {|F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} {|P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|}
-\end{align*}
-where we define $|\emptyset|/|\emptyset| := 1$.
+Observe that the resulting graph is now $k$-regular.
 Now consider the graded poset $A := P(n_0, ..., n_k) \sqcup P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)$ with two layers.
@@
 \end{itemize}
-Hence we can apply Prop.~\ref{prop:biregular_implies_lym} and see that $v_F(e) \geq 0$.
+Hence we can apply Prop.~\ref{prop:biregular_implies_lym} and see that
+\begin{align*}
+    &{|P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} {|\partial \bigl(F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)\bigr)(n_0, ..., n_k)|} \\
+    \geq &{|P(n_0, ..., n_k)|} {|F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|}
+\end{align*}
+for each edge $e = \{ (n_0, ..., n_k), (n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k) \} \in E$.
+
 Define
 \begin{equation*}
-    p(n_0, ..., n_k) := \frac {|P(n_0, ..., n_k)|} {|L_{\sum in_i}|}
+    p(n_0, ..., n_k) := \frac {|L_{\sum in_i}|} {|P(n_0, ..., n_k)|} \quad \text{if $|P(n_0, ..., n_k)| \neq 0$}
 \end{equation*}
-We know that all $v_F(e) \geq 0$ and by using the $(k - 1)$-regularity, we see
+and $p(n_0, ..., n_k) = 1$ otherwise.
+
+By summing over all vertices and all adjacent edges, we then find
 \begin{align*}
-    0 \leq &\sum_{e \in E} v_F(e) p(n_0, ..., n_k) \\
-    \leq &\sum_{e \in E} \left( \frac {|\partial F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} - \frac {|F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} {|P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} \right) p(n_0, ..., n_k) \\
-    = &(k - 1)\sum_{(n_0, ..., n_k) \in V} \frac {|\partial F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} p(n_0, ..., n_k) \\
-    - &\sum_{(n_0, ..., n_k) \in U} \frac {|F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} \sum_{0 \leq \delta < k} p(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k) \\
-    = &\frac {(k - 1) |\partial F|} {|L_{l - 1}|} - \sum_{(n_0, ..., n_k) \in U} \frac {|F(n_0, ..., n_k)|} {|P(n_0, ..., n_k)|} \sum_{0 \leq \delta < k} p(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k) \\
-    = &\frac {(k - 1) |\partial F|} {|L_{l - 1}|} - \sum_{(n_0, ..., n_k) \in U} \frac {|F(n_0, ..., n_k)|} {|L_l|} \sum_{0 \leq \delta < k} \frac {(n_\delta + ...
-+ n_k + 1)n_{\delta + 1}} {(n_\delta + 1)(n_{\delta + 1} + ...
-+ n_k)}
+    \sum_{(n_0, ..., n_k) \in V}& \sum_{0 \leq \delta < k} \underbrace{|\partial \bigl(F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)\bigr)(n_0, ..., n_k)|}_{\leq |\partial F(n_0, ..., n_k)|} \cdot \\
+    &\underbrace{|P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)| \ p(n_0, .., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)}_{\text{$= 0$ if $P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k) = \emptyset$ and $|L_l|$ otherwise}} \\
+    \geq \sum_{(n_0, ..., n_k) \in V}& \sum_{0 \leq \delta < k} {|F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} {|P(n_0, ..., n_k)|} \cdot \\
+    &p(n_0, .., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)
 \end{align*}
-However, the sum
+It follows that
+\begin{align*}
+    &\sum_{(n_0, ..., n_k) \in V} {|\partial F(n_0, ..., n_k)|} \sum_{0 \leq \delta < k} {|L_l|} \\
+    \geq& \sum_{\substack{(n_0, ..., n_k) \in U\\P(n_0, ..., n_k) \neq \emptyset}} {|F(n_0, ..., n_k)|} p(n_0, ..., n_k) \sum_{0 \leq \delta < k} {|P(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k)|}
+\end{align*}
+and so
+\begin{align*}
+    k |L_l| |\partial F| \geq \ \sum_{\mathclap{\substack{(n_0, ..., n_k) \in U\\P(n_0, ..., n_k) \neq \emptyset}}} \ |F(n_0, ..., n_k)| |L_{l - 1}| \sum_{0 \leq \delta < k} \frac {|P(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k)| |L_l|} {|P(n_0, ..., n_k)| |L_{l - 1}|}
+\end{align*}
+However for $|P(n_0, ..., n_k)| \neq 0, \sum i n_i = l$, the expression
 \begin{equation*}
-    \sum_{0 \leq \delta < k} \frac {(n_\delta + ... + n_k + 1)n_{\delta + 1}} {(n_\delta + 1)(n_{\delta + 1} + ... + n_k)}
+    \sum_{0 \leq \delta < k} \frac {|P(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k)| \cdot |L_l|} {|P(n_0, ..., n_k)| \cdot |L_{l - 1}|} = \frac {|L_l|} {|L_{l - 1}|} \sum_{0 \leq \delta < k} \frac {n_{\delta + 1}} {n_\delta + 1}
 \end{equation*}
-is not always $k - 1$, so this won't work out.
+is not always $\geq k$, so this won't work out.
 
 On a higher level, everything I did was to reduce the problem to the case that $F$ is a disjoint union of the $P(n_0, ..., n_k)$ which is nice to see, but does not help too much.
+\begin{proof}
+    TODO
+\end{proof}
 
-\begin{proposition}
-    Let $M(k, d, n) := |\{ x \in \mathcal{P}_{k, d} \ | \ r(x) = n\}|$. Then for $k, d \geq 1$ we have the recurrence relation
-    \begin{equation*}
-        M(k, 1, n) = \begin{cases}
-            1 & \text{if $0 \leq n \leq k$} \\
-            0 & \text{otherwise}
-        \end{cases}
-        \quad \text{and} \quad
-        M(k, d, n) = \sum_{i = 0}^k M(k, d - 1, n - i)
-    \end{equation*}
-
-    We also have the recurrence relation
-    \begin{equation*}
-        M(k, d, n) = \sum_{i = 0}^{\lfloor n/k \rfloor} {d \choose i} M(k - 1, d - i, n - ki)
-    \end{equation*}
-\end{proposition}
-\begin{lemma}
-    Let $R$ be a ring extension of $\Q$ (commutative with one). 
-    For a polynomial $f \in R[X]$ there exists a unique polynomial $\Sigma f \in R[X]$ such that for all $x \in \Z, x \geq 0$ we have
-    \begin{equation*}
-        \Sigma f(x) = \sum_{i = 0}^x f(i)
-    \end{equation*}
-    Furthermore, $\Sigma$ is linear and $\deg(\Sigma f) = \deg(f) + 1$ and $\mathrm{lc}(\Sigma f) = \mathrm{lc}(f) / (\deg(f) + 1)$.
-\end{lemma}
-\begin{proof}
-    Use induction on $\deg(f)$.
-    As everything is linear, it suffices to show the claim for the monomials $X^d$.
-    Define then
-    \begin{equation*}
-        \Sigma X^d := \frac 1 {d + 1} (X + 1)^{d + 1} - \frac 1 {d + 1} \sum_{k = 0}^{d - 1} {d + 1 \choose k} \left( \Sigma X^k \right)
-    \end{equation*}
-    It follows that for all $x \geq 0$ have
-    \begin{align*}
-        &\left( \Sigma X^d \right)(x + 1) - \left( \Sigma X^d \right)(x) \\
-        =& \frac 1 {d + 1} \left( (x + 2)^{d + 1} - x^{d + 1} \right) - \frac 1 {d + 1} \sum_{k = 0}^{d - 1} {d + 1 \choose k} \left( \left( \Sigma X^k \right)(x + 1) - \left( \Sigma X^k \right)(x) \right) \\
-        =& \frac 1 {d + 1} \left( -(x + 1)^{d + 1} + \sum_{k = 0}^{d + 1} {d + 1 \choose k} (x + 1)^k \right) - \frac 1 {d + 1} \sum_{k = 0}^{d - 1} {d + 1 \choose k} (x + 1)^k \\
-        =& \frac 1 {d + 1} \left( \sum_{k = 0}^d {d + 1 \choose k} (x + 1)^k - \sum_{k = 0}^{d - 1} {d + 1 \choose k} (x + 1)^k \right) \\
-        =& \frac 1 {d + 1} {d + 1 \choose d} (x + 1)^d = (x + 1)^d
-    \end{align*}
-    As this holds for infinitely many $x$, we see that $(\Sigma X^d)(X + 1) - \Sigma X^d = (X + 1)^d$ and the claim follows.
-\end{proof}
-\begin{example}
-    Let $k, d \geq 1$. Then
-    \begin{align*}
-        M(k, 2, n) := \begin{cases}
-            0 & \text{if $n > 2k$} \\
-            2k - n + 1 & \text{if $k \leq n \leq 2k$} \\
-            n + 1 & \text{if $0 \leq n \leq k$} \\
-            0 & \text{if $n < 0$}
-        \end{cases}
-    \end{align*}
-    Note that if two cases are applicable, they both yield the same value.
-\end{example}
 \end{document}

### 2021-12-09 Combinatorics/submission.tex
Added more stuff about the algorithmic approach to combinatorics

@@
 \begin{lemma}
-    Let $A$ be a poset with two layers $L_0 = \{ u_1, ..., u_m \}, L_1 = \{ v_1, ..., v_n \}$.
-    Then any of the conditions of Prop.~\ref{prop:characterization_lym} is equivalent to the following:
+    \label{prop:lp_algorithm}
+    Let $P$ be a poset with layers $L_0, ..., L_d$.
+    Fix $0 < l \leq d$ and let $L_{l - 1} = \{ u_1, ..., u_m \}, L_l = \{ v_1, ..., v_n \}$.
 
-    There exists a matrix $A = (a_{ij}) \in \Q_{\geq 0}^{m \times n}$ such that for all $i, j$
+    Assume there exists a matrix $A = (a_{ij}) \in \Q_{\geq 0}^{m \times n}$ such that
+    \footnote{We use $1 = (1, ..., 1)^T$ as the vector consisting of $1$ only here.}
     \begin{equation*}
-        e_i^T A 1 = e_j^T A 1 \quad \text{and} \quad 1^T A e_i = 1^T A e_j
+        1^T A 1 = 1
     \end{equation*}
-    and $a_{ij} = 0$ whenever $u_i \not< v_j$.
+    and for all $i, j$
+    \begin{equation*}
+        e_i^T A 1 = \frac 1 {|L_0|} \quad \text{and} \quad 1^T A e_j = \frac 1 {|L_1|}
+    \end{equation*}
+    and $a_{ij} = 0$ whenever $u_i \not< v_j$ holds.
+
+    Then the conditions of Prop.~\ref{prop:characterization_lym} hold for the poset $L_{l - 1} \cup L_l$.
+    In particular, if the assumption holds for all $0 < l \leq d$, then the conditions of Prop.~\ref{prop:characterization_lym} hold for $P$.
 \end{lemma}
+\begin{proof}
+    Let $A = (a_{ij}) \in \Q_{\geq 0}^{m \times n}$ be this matrix.
+    Note that a maximal chain in $L_{l - 1} \cup L_l$ corresponds to a pair $u_i < v_j$.
+
+    Now consider a (finite) sequence of maximal chains $(C_k)_{k \in I}$ such that the chain corresponding to $u_i < v_j$ occurs $a_{ij} |I|$ times.
+    By the assumption, we know that for each $i$
+    \begin{equation*}
+        |\{k \ | \ u_i \in C_k\}| = \sum_{u_i < v_j} a_{ij}|I| = \frac 1 {|L_0|} |I|
+    \end{equation*}
+    and so each element $u_i \in L_{l - 1}$ is contained in the same number $|I| / |L_0|$ of chains $C_k$.
+
+    Similarly, for each $J$ have
+    \begin{equation*}
+        |\{k \ | \ v_j \in C_k\}| = \sum_{v_j > u_i} a_{ij}|I| = \frac 1 {|L_1|} |I|
+    \end{equation*}
+    The claim follows.
+\end{proof}
 This lemma does not seem super useful at first, but it gives us a way to check in time polynomial in $O(|P|)$ whether a given poset $P$ satisfies the conditions from Prop.~\ref{prop:characterization_lym}, by using an LP solver.
@@
 
-Using this, I could check that $\mathcal{P}_{k, d}$ indeed satisfies the conditions for reasonably sized $|\mathcal{P}_{k, d}|$ (e.g. for $k, d \approx 6$).
+Using this, I could check that $\mathcal{P}_{k, d}$ indeed satisfies the conditions for reasonably sized $|\mathcal{P}_{k, d}|$ (up to $k = d = 6$).
 Note that already for these ``small'' numbers, we get quite huge posets $|\mathcal{P}_{k, d}|$.
@@
 \begin{proposition}
+    \label{prop:core_of_multisets}
     Assume that $\mathcal{C}_{k, d}$ satisfies a ``scaled variant'' of condition (3) of Prop.~\ref{prop:characterization_lym}, namely:
@@
 \begin{proof}
-    Denote the two layers of $\mathcal{P}_{k, d}$ by $L_k$ and the two layers of $\mathcal{C}_{k, d}$ by $L'_k$.
+    Denote the layers of $\mathcal{P}_{k, d}$ by $L_k$ and the layers of $\mathcal{C}_{k, d}$ by $L'_k$.
 
@@
 
-    Now consider a sequence $(\tilde{C}_i)_{i \in I}$ of maximal chains in the poset $A'$ that consists of the $C_{i, j}$ such that one $C_{i, j}$ occurs $\frac 1 {t t_i} |I|$ times.
-    Let $C$ be a chain chosen from them uniformly at random.
-    Observe that then $R(C)$ is a random variable uniformly distributed on the sequence $C'_1, ..., C'_t$.
+    Now consider a sequence $(C_{i_h, j_h})_{h \in I}$ of maximal chains in the poset $A'$ that consists of the $C_{i, j}$ such that one $C_{i, j}$ occurs $\frac 1 {t t_i} |I|$ times.
+    Let $H$ be a random variable distributed uniformly on $I$.
+    Observe that then $i_H$ is a random variable distributed uniformly on $1, ..., t$.
 
@@
     \begin{align*}
-        \Pr[x \in C] =& \sum_{1 \leq i \leq t} \Pr[x \in C \ | \ R(C) = C'_i] \ \Pr[R(C) = C'_i] \\
-        =& \sum_{1 \leq i \leq t} \underbrace{\Pr[x \in C \ | \ R(C) = C'_i]}_{ = 1 / |P(n_0, ..., n_k)| \ \text{if $(n_0, ..., n_k) \in C'_i$}} \frac 1 t \\
+        \Pr[x \in C_{i_H, j_H}] =& \sum_{1 \leq i \leq t} \Pr[x \in C_{i_H, j_H} \ | \ i_H = i] \ \Pr[i_H = i] \\
+        =& \sum_{1 \leq i \leq t} \underbrace{\Pr[x \in C_{i_H, j_H} \ | \ i_H = i]}_{ = 1 / |P(n_0, ..., n_k)| \ \text{if $(n_0, ..., n_k) \in C'_i$}} \frac 1 t \\
         =& \sum_{\substack{1 \leq i \leq t\\(n_0, ..., n_k) \in C'_i}} \frac 1 {|P(n_0, ..., n_k)| t} \\
-        =& \frac t {|P(n_0, ..., n_k)| t} \underbrace{\Pr[(n_0, ..., n_k) \in R(C)]}_{= |P(n_0, ..., n_k)| / |L_k| \ \text{by assumption}} = \frac 1 {|L_k|}
+        =& \frac t {|P(n_0, ..., n_k)| t} \underbrace{\Pr[(n_0, ..., n_k) \in C'_{i_H}]}_{= |P(n_0, ..., n_k)| / |L_k| \ \text{by assumption}} = \frac 1 {|L_k|}
     \end{align*}
-    where the condition $R(C) = C'_i$ means equality in the index, not as sets 
-    (this makes a difference if the set $C'_i$ occurs more than once in the sequence $C'_1, ..., C'_t$).
 
-    Clearly, this shows that condition (3) of Prop.~\ref{prop:characterization_lym} is satisfied by $(\tilde{C}_i)_{i \in I}$ for $\mathcal{P}_{k, d}$.
+    Clearly, this shows that condition (3) of Prop.~\ref{prop:characterization_lym} is satisfied by $(C_{i_h, j_h})_{h \in I}$ for $\mathcal{P}_{k, d}$.
 \end{proof}
+After some reflection, one can observe that we did not really use any properties of $\mathcal{P}_{k, d}$.
+The fact that all elements in $P(n_0, ..., n_k)$ cover resp.
+are covered by the same number of elements requires only that $P(n_0, ..., n_k)$ is an orbit under the action of $\mathrm{Aut}(P)$, i.e.
+$P(n_0, ..., n_k) = \mathrm{Aut}(P).a$ for any $a \in P(n_0, ..., n_k)$
+(where the dot $.$ denotes the group action of $\mathrm{Aut}(P)$ on $P$).
 
+Hence, we get the following statement.
 \begin{proposition}
-    $\mathcal{P}_{k, d}$ satisfies the conditions of Prop.~\ref{prop:characterization_lym}.
+    Let $P$ be a graded poset. Define the \emph{core} $\mathcal{C}(P)$ of $P$ as the set of orbits under the action of $\mathrm{Aut}(P)$ 
+    \begin{equation*}
+        \mathcal{C}(P) := \{ \mathrm{Aut}(P).x \ | \ x \in P \}
+    \end{equation*}
+    with the induced partial ordering from the elements of each orbit, i.e.
+    \begin{equation*}
+        A < B \ :\Leftrightarrow \ \exists a \in A, b \in B: a < b
+    \end{equation*}
+    for $A, B \in \mathcal{C}(P)$.
+
+    If there exists a sequence of maximal chains $C'_1, ..., C'_t$ in $\mathcal{C}(P)$ such that for a chain $C$ chosen uniformly at random from among them, have
+    \begin{equation*}
+        \Pr[A \in C] = \frac {|A|} {|L_{r(A)}|}
+    \end{equation*}
+    for all $A \in \mathcal{C}(P)$, then $P$ satisfies the conditions of Prop.~\ref{prop:characterization_lym}.
 \end{proposition}
-\textit{Proof Attempt.}
-Fix a layer $L_l$ with $0 < l \leq kd$.
-Further, consider any subset $F \subseteq L_l$.
-Now define
+\begin{proof}
+    Exactly as above.
+\end{proof}
+I still do not know how to use this to prove that $\mathcal{P}_{k, d}$ does indeed satisfy Prop.~\ref{prop:characterization_lym}, but at least it provides a way for an even faster algorithm to test it for specific $k, d$.
+The idea is just that we can adjust the LP algorithm from Lemma~\ref{prop:lp_algorithm} to check the scaled variant, and so we get a polynomial time algorithm in $|\mathcal{C}_{k, d}|$.
+In particular, we have the following.
+\begin{lemma}
+    Let $L_{l - 1} = \{u_1, ..., u_m\}$ and $L_l = \{v_1, ..., v_n\}$ be two consecutive layers of $\mathcal{C}_{k, d}$.
+    Assume there exists a matrix $A = (a_{ij}) \in \Q_{\geq 0}^{m \times n}$ such that 
     \begin{equation*}
-    U := \{ (n_0, ..., n_k) \ | \ n_i \in \Z, \ n_0 + ... + n_k = d, \ \sum_i i n_i = l \}
+        1^T A 1 = 1
     \end{equation*}
-and
+    and for all $i, j$
     \begin{equation*}
-    V := \{ (n_0, ..., n_k) \ | \ n_i \in \Z, \ n_0 + ... + n_k = d, \ \sum_i i n_i = l - 1 \}
+        e_i^T A 1 = \frac {|P(u_i)|} {\sum_{u \in L_{l - 1}} |P(u)|} \quad \text{and} \quad 1^T A e_j = \frac {|P(v_j)|} {\sum_{v \in L_l} |P(v)|}
     \end{equation*}
-Note that now
-\begin{align*}
-    L_l = \bigsqcup_{(n_0, ..., n_k) \in U} P(n_0, ..., n_k) \quad \text{and} \quad L_{l - 1} = \bigsqcup_{(n_0, ..., n_k) \in V} P(n_0, ..., n_k)
-\end{align*}
-Now make $V \sqcup U$ into a bipartite graph $G = (V \sqcup U, E)$ by defining for $(m_0, ..., m_k) \in V, (n_0, ..., n_k) \in U$
-\begin{align*}
-    &\{ (m_0, ..., m_k), (n_0, ..., n_k) \} \in E \\
-    &\Leftrightarrow \ \exists 0 \leq \delta < k: \ (n_0, ..., n_k) = (m_0, ..., m_\delta - 1, m_{\delta + 1} + 1, ..., m_k)
-\end{align*}
-Observe that the resulting graph is now $k$-regular.
-Now consider the graded poset $A := P(n_0, ..., n_k) \sqcup P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)$ with two layers.
-By Lemma~\ref{prop:properties_n_distribution_subsets} we see that
-\begin{itemize}
-    \item Each element in the bottom layer $v \in L_0(A)$ of $A$ is covered by $n_\delta$ elements
-    \item Each element in the top layer $u \in L_1(A)$ of $A$ covers $n_{\delta + 1} + 1$ elements
-\end{itemize}
-Hence we can apply Prop.~\ref{prop:biregular_implies_lym} and see that
-\begin{align*}
-    &{|P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} {|\partial \bigl(F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)\bigr)(n_0, ..., n_k)|} \\
-    \geq &{|P(n_0, ..., n_k)|} {|F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|}
-\end{align*}
-for each edge $e = \{ (n_0, ..., n_k), (n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k) \} \in E$.
+    and $a_{ij} = 0$ whenever $u_i \not< v_j$ holds.
 
-Define
-\begin{equation*}
-    p(n_0, ..., n_k) := \frac {|L_{\sum in_i}|} {|P(n_0, ..., n_k)|} \quad \text{if $|P(n_0, ..., n_k)| \neq 0$}
-\end{equation*}
-and $p(n_0, ..., n_k) = 1$ otherwise.
+    Then the assumption of Prop.~\ref{prop:core_of_multisets} is fulfilled for $L_{l - 1} \cup L_l$.
+    In particular, if this holds for all $0 < l \leq kd$ then the assumption is fulfilled for the whole of $\mathcal{C}_{k, d}$ and it follows that $\mathcal{P}_{k, d}$ satisfies the conditions of Prop.~\ref{prop:characterization_lym}.
+\end{lemma}
+\begin{proof}
+    Exactly as in Lemma~\ref{prop:lp_algorithm}.
+\end{proof}
+Using a simple implementation of this approach, I could check that for some arbitrarily chosen values of $k, d$ up to $(k, d) = (8, 9)$, the poset $\mathcal{P}_{k, d}$ indeed satisfies the conditions of Prop.~\ref{prop:characterization_lym}.
 
-By summing over all vertices and all adjacent edges, we then find
-\begin{align*}
-    \sum_{(n_0, ..., n_k) \in V}& \sum_{0 \leq \delta < k} \underbrace{|\partial \bigl(F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)\bigr)(n_0, ..., n_k)|}_{\leq |\partial F(n_0, ..., n_k)|} \cdot \\
-    &\underbrace{|P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)| \ p(n_0, .., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)}_{\text{$= 0$ if $P(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k) = \emptyset$ and $|L_l|$ otherwise}} \\
-    \geq \sum_{(n_0, ..., n_k) \in V}& \sum_{0 \leq \delta < k} {|F(n_0, ..., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)|} {|P(n_0, ..., n_k)|} \cdot \\
-    &p(n_0, .., n_\delta - 1, n_{\delta + 1} + 1, ..., n_k)
-\end{align*}
-It follows that
-\begin{align*}
-    &\sum_{(n_0, ..., n_k) \in V} {|\partial F(n_0, ..., n_k)|} \sum_{0 \leq \delta < k} {|L_l|} \\
-    \geq& \sum_{\substack{(n_0, ..., n_k) \in U\\P(n_0, ..., n_k) \neq \emptyset}} {|F(n_0, ..., n_k)|} p(n_0, ..., n_k) \sum_{0 \leq \delta < k} {|P(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k)|}
-\end{align*}
-and so
-\begin{align*}
-    k |L_l| |\partial F| \geq \ \sum_{\mathclap{\substack{(n_0, ..., n_k) \in U\\P(n_0, ..., n_k) \neq \emptyset}}} \ |F(n_0, ..., n_k)| |L_{l - 1}| \sum_{0 \leq \delta < k} \frac {|P(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k)| |L_l|} {|P(n_0, ..., n_k)| |L_{l - 1}|}
-\end{align*}
-However for $|P(n_0, ..., n_k)| \neq 0, \sum i n_i = l$, the expression
-\begin{equation*}
-    \sum_{0 \leq \delta < k} \frac {|P(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k)| \cdot |L_l|} {|P(n_0, ..., n_k)| \cdot |L_{l - 1}|} = \frac {|L_l|} {|L_{l - 1}|} \sum_{0 \leq \delta < k} \frac {n_{\delta + 1}} {n_\delta + 1}
-\end{equation*}
-is not always $\geq k$, so this won't work out.
+\section{Appendix (Code described in Part VI)}
+To find the computational results mentioned above, I have implemented the described algorithm in Rust.
+For this, I use my own library containing a collection of math functions as well as Mosek LP solver \cite{mosek} and its rust binding library.
+After installing the Mosek binaries manually, it therefore suffices to add
+\begin{lstlisting}
+    feanor_la = { 
+        git = "https://github.com/feanorTheElf/FeanorLA.git"  
+    }
+    mosek = "0.2"
+\end{lstlisting}
+to the dependencies of your \texttt{Cargo.toml} file.
 
-On a higher level, everything I did was to reduce the problem to the case that $F$ is a disjoint union of the $P(n_0, ..., n_k)$ which is nice to see, but does not help too much.
-\begin{proof}
-    TODO
-\end{proof}
+After all dependencies are present, the following code will yield the result.
+\lstinputlisting{./src/main.rs}
 
+\printbibliography
 \end{document}

### 2021-12-09 Combinatorics/src/main.rs

@@ -6,7 +6,15 @@ use feanor_la::combinatorics::bitset::*;
 use feanor_la::la::mat::*;
 use feanor_la::algebra::rat::*;
 
-fn find_feasible_solution<M, V>(A: Matrix<M, r64>, b: Vector<V, r64>) -> Option<Vector<VectorOwned<f64>, f64>>
+///
+/// Uses the LP solver to find x >= 0
+/// with Ax = b or states that this does
+/// not exist.
+/// 
+fn find_feasible_solution<M, V>(
+    A: Matrix<M, r64>, 
+    b: Vector<V, r64>
+) -> Option<Vector<VectorOwned<f64>, f64>>
     where M: MatrixView<r64>, V: VectorView<r64>
 {
     let cast = |x: r64| (x.num() as f64) / (x.den() as f64);
@@ -15,64 +23,265 @@ fn find_feasible_solution<M, V>(A: Matrix<M, r64>, b: Vector<V, r64>) -> Option<
     let mut task = env.task().unwrap();
     task.append_vars(A.col_count() as i32).unwrap();
     task.append_cons(A.row_count() as i32).unwrap();
+
+    // initialize variable bounds and target function
     for j in 0..A.col_count() {
         task.put_c_j(j as i32, 1.).unwrap();
-        task.put_var_bound(j as i32, mosek::MSK_BK_LO, 0.0, f64::INFINITY).unwrap();
+        task.put_var_bound(
+            j as i32, mosek::MSK_BK_LO, 0.0, f64::INFINITY
+        ).unwrap();
     }
+    // initialize conditions
     for i in 0..A.row_count() {
-        let indices = A.row(i).iter().enumerate().filter(|(_, x)| **x != r64::ZERO).map(|(i, _)| i as i32).collect::<Vec<_>>();
-        let values = A.row(i).iter().filter(|x| **x != r64::ZERO).map(|x| cast(*x)).collect::<Vec<_>>();
+        // we need sparse format
+        let indices = A.row(i).iter().enumerate()
+            .filter(|(_, x)| **x != r64::ZERO)
+            .map(|(i, _)| i as i32)
+            .collect::<Vec<_>>();
+
+        let values = A.row(i).iter()
+            .filter(|x| **x != r64::ZERO)
+            .map(|x| cast(*x)).collect::<Vec<_>>();
+
         task.put_a_row(i as i32, &indices, &values).unwrap();
[…]

### 2021-12-09 Algebraic geometry/submission.tex
Added the degree formula for the Grassmanian
Added test for great new idea in alg geo

@@
 \newtheorem{corollary}[definition]{Corollary}
+\newtheorem{theorem}[definition]{Theorem}
 
@@
     \lstinputlisting[language = python]{./examples.sage}
-    This shows that the degree of $\Gr(2, 5)$ is indeed 5, as expected.
+    This shows that the degree of $\Gr(2, 5)$ is indeed 5, as expected from the degree formula mentioned in the lecture.
+    \begin{equation*}
+        \deg(\Gr(d, n)) = (d(n - d))! \frac {1! \cdot 2! \cdot ... \cdot (d - 1)!} {(n - d)! \cdot (n - d + 1)! \cdot ... \cdot (n - 1)!}
+    \end{equation*}
+    which yields
+    \begin{equation*}
+        \deg(\Gr(2, 5)) = 6! \frac {1!} {3! \cdot 4!} = \frac {6 \cdot 5} {3!} = 5
+    \end{equation*}
 \end{example}
@@
 
-\begin{lemma}
-    Let $n \geq 4$ and
+\paragraph{Another idea} Let
 \begin{equation*}
-        J := \{ \{ A, B \} \ | \ A, B \in X, \ A \cap B = \emptyset \} \subseteq X^{(2)}
+    m_n(d) := |\{ x^\alpha \ \text{monomial} \ | \ \deg(x^\alpha) = d, \ x_{iv}x_{ju} \ \not| \ x^\alpha \}|
 \end{equation*}
-    be a set, where
+and
 \begin{equation*}
-        X := \{ 1, ..., n \}^{(2)}
+    s_n(d) := |\{ x^\alpha \ \text{multilinear monomial} \ | \ \deg(x^\alpha) = d, \ x_{iv}x_{ju} \ \not| \ x^\alpha \}|
 \end{equation*}
-    Then for $k \geq 3$ have
+Then for sufficiently large $d$ have
 \begin{equation*}
-        |\{ A \in X^{(k)} \ | \ J \subseteq A \}| = 
+    m_n(d) = \sum_{i = 0}^n s_n(i) \left(\!\!{i \choose d - i}\!\!\right) = \sum_{i = 0}^n s_n(i) {d - 1 \choose i - 1}
 \end{equation*}
-\end{lemma}
-\begin{proof}
-    Use induction on $n$.
-    In the base case $n = 4$ have that
-\end{proof}
+Note now that we are only interested in the leading term of the polynomial, which is (more or less) given by the largest $i \leq n$ such that $s_n(i) \neq 0$.
+So in fact, it suffices to find this.
 
+For example, the dimension of $\Gr(2, n)$ is the size of the largest independent set $- 1$ in this strange graph I have been considering.
+
+For example, I claim:
+\begin{theorem}
+    \begin{equation*}
+        \dim(\Gr(2, n)) = 2n - 4
+    \end{equation*}
+\end{theorem}
 \printbibliography

### 2021-12-10 Algebraic geometry/submission.tex
Added proposition on degree & dimension of Gr(2, n) to alg geo

--- 2021-12-08 Algebraic geometry/submission.tex
@@
 \begin{proposition}[Macaulay Basis Theorem]
+    \label{prop:macaulay_basis_theorem}
     Let $\preceq$ be a graded monomial ordering on $R = k[x_0, ..., x_n]$.
@@
 \begin{lemma}
+    \label{prop:leading_term_ideal_grassmanian}
     Define the graded reverse monomial ordering $\preceq$ on $R := k[x_{i, j} \ | \ i < j]$ where the variables $x_{i, j}$ are ordered co-lexicographically w.r.t. $(i, j)$, i.e.
@@
 
+\begin{definition}
+    Consider the graph $G_n = (V_n, E_n)$ where $V_n = \{ (i, j) \ | \ 0 \leq i < j \leq n \}$ and
+    \begin{equation*}
+        E_n = \{ \{ (i, v), (j, u) \} \ | \ 0 \leq i < j < u < v \leq n \}
+    \end{equation*}
+    Let further
+    \begin{equation*}
+        s_n(d) := |\{ I \subseteq V_n \ | \ I \ \text{independent set of size $d$}\}|
+    \end{equation*}
+\end{definition}
+
+\begin{proposition}
+    Let $d$ be the largest integer such that $s_n(d) \neq 0$, i.e. the size of the largest independent set in $G_n$.
+    Then
+    \begin{equation*}
+        \dim(\Gr(2, n)) = d - 1
+    \end{equation*}
+    and
+    \begin{equation*}
+        \deg(\Gr(2, n)) = s_n(d)
+    \end{equation*}
+\end{proposition}
+\begin{proof}
+    By Lemma~\ref{prop:leading_term_ideal_grassmanian} we know
+    \begin{equation*}
+        J = \mathrm{lt}(\I(\Gr(2, n))) = \langle x_{i, v} x_{j, u} \ | \ i < j < u < v \rangle \leq R := k[x_{i, j} \ | \ i < j]
+    \end{equation*}
+    Let $N = {n \choose 2}$ be the number of variables in $R$, i.e. $\{x_1, ..., x_N\} = \{ x_{i, j} \ | \ i < j \}$. Now we find for sufficiently large $m$ that
+    \begin{align*}
+        &|\{ x^\alpha \ \text{monomial in $R$} \ | \ \deg(x^\alpha) = m, \ \forall i < j < u < v: x_{iv} x_{ju} \ \nmid \ x^\alpha \}| \\
+        =\ &|\{ x^\alpha \ \text{monomial in $R$} \ | \ \deg(x^\alpha) = m, \ \forall i < j < u < v: x_{iv} x_{ju} \ \nmid \ \mathrm{sqfr}(x^\alpha) \}| \\
+        =\ &\Bigl| \bigcup_{\substack{\alpha \in \{0, 1\}^N\\x_{iv} x_ju \ \nmid \ x^\alpha}} \{ x^\alpha x^\beta \ | \ \deg(x^\beta) = m - \deg(x^\alpha), \ \forall i: \alpha_i = 0 \Rightarrow \beta_i = 0 \} \Bigr| \\
+        =& \sum_{\substack{\alpha \in \{0, 1\}^N\\x_{iv} x_ju \ \nmid \ x^\alpha}} \left(\!\!{\deg(x^\alpha) \choose m - \deg(x^\alpha)}\!\!\right) = \sum_{l = 0}^N \sum_{\substack{\alpha \in \{0, 1\}^N\\\sum_j \alpha_j = l\\x_{i, v} x_{j, u} \ \nmid \ x^\alpha}} \left(\!\!{ l \choose m - l }\!\!\right) \\
+        =& \sum_{l = 0}^N s_n(l) \left(\!\!{ l \choose m - l }\!\!\right) = \sum_{l = 0}^N s_n(l) {m - 1 \choose l - 1}
+    \end{align*}
+    where $\mathrm{sqrf}(f)$ denotes the square-free part of $f$.
+    This holds, as by definition of $s_n$ and $E_n$ we find
+    \begin{equation*}
+        s_n(l) = |\bigl\{ I \subseteq \{ x_{i, j} \} \ \bigm| \ \forall i < j < u < v: x_{i, v} x_{j, u} \ \nmid \ xy \ \text{for all} \ x, y \in I \bigr\}|
+    \end{equation*}
+    Now Macaulay's basis theorem~\ref{prop:macaulay_basis_theorem} yields that for sufficiently large $m$ have
+    \begin{align*}
+        \dim_k (R/\I(\Gr(2, n))) =& |\bigl\{ x^\alpha \ \text{monomial in $R$} \ \bigm| \ \deg(x^\alpha) = m, \ x^\alpha \notin \mathrm{lt}(\I(\Gr(2, n))) \bigr\}| \\
+        =& \sum_{l = 0}^N s_n(l) {m - 1 \choose l - 1}
+    \end{align*}
+    Hence we find for the Hilbert polynomial that
+    \begin{equation*}
+        p_{\Gr(2, n)} = \sum_{l = 0}^N s_n(l) {m - 1 \choose l - 1}
+    \end{equation*}
+    and in particular, it has the leading term $s_n(d) {m - 1 \choose d - 1}$.
+    The claim follows by the characterization of degree and dimension using the Hilbert polynomial that we did in the lecture.
+\end{proof}
 \begin{lemma}
-    Let $n \geq 4$ and
-    \begin{equation*}
-        J := \{ \{ A, B \} \ | \ A, B \in X, \ A \cap B = \emptyset \} \subseteq X^{(2)}
-    \end{equation*}
-    be a set, where
-    \begin{equation*}
-        X := \{ 1, ..., n \}^{(2)}
-    \end{equation*}
-    Then for $k \geq 3$ have
-    \begin{equation*}
-        |\{ A \in X^{(k)} \ | \ J \subseteq A \}| = 
-    \end{equation*}
+    The largest independent set in $G_n$ is of size $2n - 4$.
 \end{lemma}
-\begin{proof}
-    Use induction on $n$.
-    In the base case $n = 4$ have that
-\end{proof}
-
 \printbibliography

### 2021-12-10 Algebraic geometry/submission.tex
Added graphs and statement about the largest independent set in the graphs to alg geo

@@
 \usepackage[language=english, backend=biber, style=alphabetic, sorting=nyt]{biblatex}
+\usepackage{tikz}
 
@@
 \end{proof}
+To apply this, first of all we have to collect information about the leading term ideal of $\I(\Gr(2, n))$.
+This is done in the following lemma.
 \begin{lemma}
@@
 \begin{proof}
+    The idea is to apply Macaulay's basis theorem to get information about the Hilbert function of $\Gr(2, n)$.
+    To this end, observe that all the monomials generating $\mathrm{lt}(\I(\Gr(2, n)))$ are square-free.
+    Hence, we can partition all monomials not in $\mathrm{lt}(\I(\Gr(2, n)))$ into sets depending on which variables occur in them.
+    Doing this shows that leading coefficient of the Hilbert polynomial depends only on the groups with the maximal count of monomials.
+    These monomials then form a maximal independent set in $G_n$, which allows us to relate degree and dimension of $\Gr(2, n)$ to $s_n(d)$.
+
     By Lemma~\ref{prop:leading_term_ideal_grassmanian} we know
@@
 \end{proof}
+Now we want to study how the independent sets in $G_n$ look like.
+\begin{example}
+    \label{ex:Gn}
+    The graph $G_4$ is the following
+    \\\includegraphics[width = \textwidth]{graph4.pdf}
+    The graph $G_5$ is the following
+    \\\includegraphics[width = \textwidth]{graph5.pdf}
+    The graph $G_6$ is the following
+    \\\includegraphics[width = \textwidth]{graph6.pdf}
+\end{example}
 \begin{lemma}
@@
 \end{lemma}
+\begin{proof}
+    The idea is to write the graph in layers (or as a kind of ``pyramid'') as displayed in Example~\ref{ex:Gn}.
+    Then we can ``push'' an independent set onto the bottom layer, by repeatedly taking vertices in the set that are maximally high up and on the outside, and replacing them by their ``child''. 
+    This shows the claim, as the bottom layer (plus the 4 unconnected vertices) has size $2n - 4$.
+\end{proof}
 \printbibliography

### 2021-12-10 Algebraic geometry/submission.tex
Added statement on Gr(2, 6) to alg geo

@@
 \begin{lemma}
-    The largest independent set in $G_n$ is of size $2n - 4$.
+    The largest independent set in $G_n$ is of size $2n - 3$.
 \end{lemma}
@@
     Then we can ``push'' an independent set onto the bottom layer, by repeatedly taking vertices in the set that are maximally high up and on the outside, and replacing them by their ``child''. 
-    This shows the claim, as the bottom layer (plus the 4 unconnected vertices) has size $2n - 4$.
+    This shows the claim, as the bottom layer (plus the 4 unconnected vertices) has size $2n - 3$.
 \end{proof}
+
+\begin{corollary}
+    Have $\dim(\Gr(2, n)) = 2n - 4$.
+\end{corollary}
+\begin{proof}
+    Follows directly from the previous two statements.
+\end{proof}
+
+\begin{corollary}
+    Have $\dim(\Gr(2, 6)) = 8$ and $\deg(\Gr(2, 6)) = 14$.
+\end{corollary}
+\begin{proof}
+    The dimension follows directly from the previous general case.
+    For the degree, just count the maximal independent sets in $G_6$, as displayed in Example~\ref{ex:Gn}.
+    This is slightly tricky, but it is not too hard to see that there are exactly 15 of them.
+\end{proof}
+Of course, the above statement on $\Gr(2, 6)$ can also easily be found using Computer Algebra.
+For example, the following Sage script shows that
+\begin{equation*}
+    p_{\Gr(2, 6)} = \frac 1 {2880} t^8 + \frac 1 {120} t^7 + \frac {41} {480} t^6 + \frac {39} {80} t^5 + \frac {541} {320} t^4 + \frac {291} {80} t^3 + \frac {3401} {720} t^2 + \frac {101} {30} t + 1
+\end{equation*}
+from which we easily deduce that
+\begin{equation*}
+    \dim(\Gr(2, 6)) = 8 \quad \text{and} \quad \deg(\Gr(2, 6)) = \frac 1 {2880} \cdot 8! = 14
+\end{equation*}
+\lstinputlisting[language = python]{./gr26.sage}
 \printbibliography

### 2021-12-10 Algebraic geometry/submission.tex
Added proof of the graph lemma to alg geo

@@
     Then we can ``push'' an independent set onto the bottom layer, by repeatedly taking vertices in the set that are maximally high up and on the outside, and replacing them by their ``child''. 
-    This shows the claim, as the bottom layer (plus the 4 unconnected vertices) has size $2n - 3$.
+    This shows the claim, as the bottom layer (plus the 4 unconnected vertices, which we also define to be in the bottom layer) has size $2n - 3$.
+
+    Define the ``layer function''
+    \begin{equation*}
+        l: V \to \N, \quad (i, j) \mapsto \min\{i - 1, n - j\}
+    \end{equation*}
+    and the ``width function''
+    \begin{equation*}
+        w: V \to \N, \quad (i, j) \mapsto j - i - 1
+    \end{equation*}
+    Let $I$ be an independent set that is not contained in the lower layer (i.e. there exists $(i, j) \in I$ with $l((i, j)) > 0$). 
+    Define now the compression $C(I) := (I \setminus \{(i, j)\}) \cup \{(i - 1, j + 1)\}$ where $(i, j) \in I$ is a vertex with
+    \begin{equation*}
+        l((i, j)) = \max_{(a, b) \in I} l((a, b)) \quad \text{and} \quad w((i, j)) = \min_{(a, b) \in I, l((u, v)) = l((i, v))} w((a, b))
+    \end{equation*}
+    Then clearly $\sum_{\alpha \in C(I)} l(\alpha) < \sum_{\alpha \in I} l(\alpha)$ and we claim that $C(I)$ is an independent set.
+
+    Assume not, i.e. there is $(a, b) \in I \cap C(I)$ such that $\{(i - 1, j + 1), (a, b)\} \in E$.
+    As $I$ is independent, find that we cannot have $a < i < j < b$.
+    Thus in particular, we have not $a < i - 1 < j - 1 < b$ and so
+    \begin{equation*}
+        i - 1 < a < b < j + 1
+    \end{equation*}
+    Since $(a, b) \neq (i, j)$, we either have $a = i, b < j$ or $b = j, a > i$.
+
+    In the first case, see that $l((a, b)) = \min\{a - 1, n - b\} \geq \min\{i - 1, n - j\} = l((i, j))$.
+    By choice of $(i, j)$, it follows that we must have equality $l((a, b)) = l((i, j))$.
+    Since $b < j$ we see that $\min\{a - 1, n - b\} > \min\{i - 1, n - j\}$ unless $\min\{i - 1, n - j\} = i - 1$, so $n - j \geq i - 1$.
+    In particular, also $\min\{a - 1, n - b\} = i - 1$ and so $a - 1 = i - 1$.
+    It follows that
+    \begin{equation*}
+        w((i, j)) = j - i - 1 = j - a - 1 > b - a - 1 = w((a, b))
+    \end{equation*}
+    which is a contradiction to the choice of $(i, j) \in I$ as $l((a, b)) = l((i, j))$.
+    The second case can be handled in the same way.
+
+    Now we know that $C(I)$ is an independent set with $\sum_{\alpha \in C(I)} l(\alpha) < \sum_{\alpha \in I} l(\alpha)$.
+    Since these sums take values in $\N$ which is well-ordered, we cannot have an infinite sequence
+    \begin{equation*}
+        I, C(I), C^2(I), C^3(I), ...
+    \end{equation*}
+    and thus at some point, we find $C^k(I)$ is contained in layer 0.
+    Now note that $C$ does not decrease the size, i.e. $|C(I)| = |I|$ and so $|C^k(I)| = |I|$.
+    However, there are only $(n - 2) + (n - 2) + 1 = 2n - 3$ elements in layer 0 and the claim follows.
 \end{proof}
-
 \begin{corollary}
@@
 \end{proof}
-
+I also think that it is not too difficult to show that
+\begin{equation*}
+    s_n(2n - 3) = \frac {(2(n - 2))!} {(n - 2)! (n - 1)!}
+\end{equation*}
+which then shows the degree formula for the case $d = 2$.
+However, this is not a lecture on graph theory or combinatorics, and I already spent a lot of hours on this problem (and there are other mini projects as well :)).
+So I will not do the proof here, but I think it is already very interesting to see those graphs and the connection of $\deg(\Gr(2, n))$ to combinatorial problems.
+Finally, in the case of $n = 6$ we can simply count the independent sets by hand, and find the following result.
 \begin{corollary}
-    Have $\dim(\Gr(2, 6)) = 8$ and $\deg(\Gr(2, 6)) = 14$.
+    Have $\dim(\Gr(2, 6)) = 8$ and $\deg(\Gr(2, 6)) = 15$.
 \end{corollary}

### 2021-12-10 Algebraic geometry/submission.tex
changed layout of alg geo

@@
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{lemma}[definition]{Lemma}
-\newtheorem{example}[definition]{Example}
-\newtheorem{proposition}[definition]{Proposition}
-\newtheorem{corollary}[definition]{Corollary}
-\newtheorem{theorem}[definition]{Theorem}
+\newtheorem{definition}[subsection]{Definition}
+\newtheorem{remark}[subsection]{Remark}
+\newtheorem{lemma}[subsection]{Lemma}
+\newtheorem{example}[subsection]{Example}
+\newtheorem{proposition}[subsection]{Proposition}
+\newtheorem{corollary}[subsection]{Corollary}
+\newtheorem{theorem}[subsection]{Theorem}
 
@@
 
-\begin{lemma}[1a]
+\begin{lemma}[Question (a)]
     Let $\dim(V) \leq 3$. Then every element of $\extpow^k(V)$ is decomposable.
@@
 
-\begin{example}[1b]
+\begin{example}[Question (b)]
     Consider $V = k^4$. 
@@
 
-\begin{lemma}[1c]
+\begin{lemma}[Question (c)]
     \label{prop:characterization_decomposable_d_even}
@@
 In this part, we want to consider the connection of external powers to the Grassmanian.
+\begin{remark}[Question (a)]
     First of all, assume there are two bases $v_1, ..., v_d$ and $u_1, ..., u_d$ of a $d$-dimensional vector space $U$. 
@@
     \end{equation*}
+\end{remark}
 This allows us to study the Grassmanian $\Gr(d, V)$ of a fixed vector space $V$.
@@
 \end{proof}
-\begin{corollary}[2b]
+\begin{corollary}[Question (b)]
     \label{prop:image_phi}
@@
 \end{corollary}
-\begin{proposition}[2c]
+\begin{proposition}[Question (c)]
     The map $\phi$ is injective.
@@
 \end{definition}
-\begin{proposition}[3a]
+\begin{proposition}[Question (a)]
     \label{prop:equations_grassmanian_2}
@@
 \end{proof}
-\begin{example}[2b]
+\begin{example}[Question (b)]
     For $n = 4$, Prop.~\ref{prop:equations_grassmanian_2} yields that $\Gr(2, 4) \cong \mathrm{im}\phi = \V(I)$ where
@@
 \end{example}
-\begin{example}[2c]
+\begin{example}[Question (c), (d)]
     For $n = 5$, Prop.~\ref{prop:equations_grassmanian_2} yields that $\Gr(2, 5) \cong \mathrm{im}\phi = \V(I)$ where
@@
 Finally, in the case of $n = 6$ we can simply count the independent sets by hand, and find the following result.
-\begin{corollary}
+\begin{corollary}[Question (e)]
     Have $\dim(\Gr(2, 6)) = 8$ and $\deg(\Gr(2, 6)) = 15$.

### 2021-12-10 Algebraic geometry/submission.tex
added proof of important subspace lemma to alg geo

@@
 \begin{lemma}
+    \label{prop:subspace_closed}
+    Let $v \in V$ and $u \in \extpow^{d - 1} U$ for a linear subspace $U \leq V$. 
+    If $v \wedge u \in \extpow^d U$ then $v \in U$ or $u = 0$.
+\end{lemma}
+\begin{proof}
+    wlog $U$ is finite-dimensional, so there is a basis $u_1, ..., u_m$ of $U$.
+    Then
+    \begin{equation*}
+        u = \sum_{\{i_1, ..., i_{d - 1}\} \in \{1, ..., m\}^{(d - 1)}} \lambda_{i_1, ..., i_{d - 1}} (u_{i_1} \wedge ... \wedge u_{i_{d - 1}})
+    \end{equation*}
+    So
+    \begin{equation*}
+        v \wedge u = \sum_{\{i_1, ..., i_{d - 1}\} \in \{1, ..., m\}^{(d - 1)}} \lambda_{i_1, ..., i_{d - 1}} (v \wedge u_{i_1} \wedge ... \wedge u_{i_{d - 1}}) \in \extpow^d U
+    \end{equation*}
+    It follows that
+    \begin{align*}
+        w := &\sum_{\{i_1, ..., i_{d - 1}\} \in \{1, ..., m\}^{(d - 1)}} \lambda_{i_1, ..., i_{d - 1}} (v \otimes u_{i_1} \otimes ... \otimes u_{i_{d - 1}}) \\
+        &\in U^{\otimes d} + \sum_{i = 1}^{d - 1} V^{\otimes (i - 1)} \otimes \vspan\bigl\{ v \otimes v' + v' \otimes v \ \bigm| \ v, v' \in V \bigr\} \otimes V^{\otimes (d - i - 1)}
+    \end{align*}
+    hence $w$ is contained in
+    \begin{equation*}
+        \bigl( V \otimes U^{\otimes(d - 1)}\bigr) \cap \Bigl( U^{\otimes d} + \sum_{i = 1}^{d - 1} V^{\otimes (i - 1)} \otimes \vspan\bigl\{ v \otimes v' + v' \otimes v \bigr\} \otimes V^{\otimes (d - i - 1)} \Bigr)
+    \end{equation*}
+    However
+    \begin{equation*}
+        \bigl( V \otimes U^{\otimes(d - 1)}\bigr) \cap \Bigl( U^{\otimes d} + \sum_{i = 1}^{d - 1} V^{\otimes (i - 1)} \otimes \vspan\bigl\{ v \otimes v' + v' \otimes v \bigr\} \otimes V^{\otimes (d - i - 1)} \Bigr) = U^{\otimes d}
+    \end{equation*}
+    and so $w \in U^{\otimes d}$.
+
+    Furthermore, we know by definition of $w$ that
+    \begin{equation*}
+        w \in \vspan\{v\} \otimes U^{\otimes(d - 1)}
+    \end{equation*}
+    However, if $v \notin U$ then $(\vspan\{v\} \otimes U^{\otimes(d - 1)}) \cap U^{\otimes d} = \{ 0 \}$ and we see that $w = 0$.
+    We have that
+    \begin{equation*}
+        w = v \otimes \sum_{\{i_1, ..., i_{d - 1}\} \in \{1, ..., m\}^{(d - 1)}} \lambda_{i_1, ..., i_d} (u_{i_1} \otimes ... \otimes u_{i_{d - 1}})
+    \end{equation*}
+    As $v \neq 0$ (otherwise $v \in U$), we see that thus
+    \begin{equation*}
+        \sum_{\{i_1, ..., i_{d - 1}\} \in \{1, ..., m\}^{(d - 1)}} \lambda_{i_1, ..., i_d} (u_{i_1} \otimes ... \otimes u_{i_{d - 1}}) = 0
+    \end{equation*}
+    and so $u = 0$.
+\end{proof}
+\begin{lemma}
     \label{prop:extpow_zero_iff_independent}
@@
 
-    Direction $\Rightarrow$ TODO
-\end{proof}
-\begin{lemma}
-    \label{prop:subspace_closed}
-    Let $v \in V$ and $u \in \extpow^{d - 1} U$ for a linear subspace $U \leq V$. 
-    If $v \wedge u \in \extpow^d U$ then $v \in U$ or $u = 0$.
-\end{lemma}
-\begin{proof}
-    TODO
+    For the other direction, let $v_1, ..., v_d$ be linearly independent.
+    Assume that $v_1 \wedge ... \wedge v_d = 0$, i.e.
+    \begin{equation*}
+        v_1 \otimes ... \otimes v_d = \sum_{i = 0} u^{(i)}_1 \otimes ... \otimes u^{(i)}_d
+    \end{equation*}
 \end{proof}

### 2021-12-12 Algebraic geometry/submission.tex
Completely and rigorously reproved the independence lemma

--- 2021-12-10 Algebraic geometry/submission.tex
@@
 
+For this document, let $V$ be a finitely dimensional vector space with basis $B = (b_1, ..., b_n)$.
+
 \section{Part I}
-
+First of all, I will include here a more formal definition of the exterior product, which is required for rigorous proofs later on.
 \begin{definition}
-    Let $V$ be a vector space.
-    Then define the $d$-th exterior power as
+    Define the $d$-th exterior power of $V$ as a quotient of the free vector space of $B \times ... \times B$ as follows
+    \begin{align*}
+        \extpow^d V := \mathrm{Fr}\Bigl(\bigtimes_{i = 1}^d B\Bigr) \ \bigm/ \ U
+    \end{align*}
+    where
+    \begin{align*}
+        U = \vspan \bigl\{ (v_1, ..., v_d) + (v_1, ..., v_{i - 1}, v_{i + 1}, v_i, v_{i + 2}, ..., v_d) \ \bigm| \ v_1, ..., v_d \in B, 1 \leq i < d \bigr\}
+    \end{align*}
+    Consider also the map
     \begin{equation*}
-        \extpow^d(V) := V^{\otimes d} \ / \ \sum_{i = 1}^{d - 1} V^{\otimes (i - 1)} \otimes \vspan\bigl\{ v \otimes v' + v' \otimes v \ \bigm| \ v, v' \in V \bigr\} \otimes V^{\otimes (d - i - 1)}
+        \wedge: \bigtimes_{i = 1}^d V \to \extpow^d V, \quad \Bigl( \sum_{i = 1}^n \lambda_{1i} b_i, ..., \sum_{i = 1}^n \lambda_{di} b_i \Bigr) \mapsto \sum_{1 \leq i_1, ..., i_d \leq n} \lambda_{1i_1} ...
+\lambda_{di_d} (b_{i_1}, ..., b_{i_d})
     \end{equation*}
-    Use the notation $v_1 \wedge ... \wedge v_d := [v_1 \otimes ... \otimes v_d] \in \extpow^k(V)$.
+    and use the notation $v_1 \wedge ... \wedge v_d$ to denote the image of $(v_1, ..., v_d)$ under this map.
 \end{definition}
-
+First of all, we show some basic properties of the exterior product.
+It is straightforward to see that the exterior product is multilinear, i.e.
+$v_1 \wedge ...
+\wedge (v_i + v'_i) \wedge ...
+\wedge v_d = (v_1 \wedge ...
+\wedge v_d) + (v_1 \wedge ...
+\wedge v'_i \wedge ...
+\wedge v_d)$.
+More interesting are the following properties.
 \begin{lemma}
@@
 \begin{proof}
-    Note that
+    Clearly the vectors $b_{i_1} \wedge ... \wedge b_{i_d}$ span $\extpow^d V$.
+    So let
+    \begin{equation*}
+        u = \sum_{i_1, ..., i_{j - 1}} \lambda_{i_1, ..., i_{j - 1}} (b_1 \wedge ...
+\wedge b_{j - 1}), \quad w = \sum_{i_1, ..., i_{d - j - 1}} \mu_{i_1, ..., i_d} (b_{i_1} \wedge ...
+\wedge b_{d - j - 1})
+    \end{equation*}
+    be arbitrary vectors in $\extpow^{j - 1} V$ resp. $\extpow^{d - j - 1} V$ for some $1 \leq j \leq d - 1$.
+    Note that for $v = \sum \tau_i b_i, v' = \sum \tau'_i b_i \in V$ have then
+    \begin{align*}
+        &(u \wedge v \wedge v' \wedge w) + (u \wedge v' \wedge v \wedge w) = \sum_{i_1, ..., i_{j - 1}, i_{j + 2}, ..., i_d} \quad \sum_{0 \leq i, i' \leq n} \lambda_{i_1, ..., i_{j - 1}} \mu_{i_{j + 2}, ..., i_d} \tau_i \tau'_{i'} \\
+        &\Bigl(\underbrace{\bigl( b_{i_1} \wedge ...
+\wedge b_{i_j} \wedge b_{i_{j + 1}} \wedge ...
+\wedge b_{i_d}\bigr) + \bigl( b_{i_1} \wedge ...
+\wedge b_{i_{j - 1}} \wedge b_{i_{j + 1}} \wedge b_{i_j} \wedge b_{i_{j + 2}} \wedge ...
+\wedge b_{i_d} \bigr)}_{= 0 \ \text{as it is an element of the space $U$}} \Bigl) \\
+        &= 0
+    \end{align*}
+    for all $u \in \extpow^{i - 1}(V), w \in \extpow^{(d - i - 1)}(V)$.
+    Hence
     \begin{equation*}
@@
     \end{equation*}
-    for all $u \in \extpow^{i - 1}(V), w \in \extpow^{(d - i - 1)}(V), v, v' \in V$.
 
@@
 \end{proof}
+The next two lemmas are quite fundamental, as they can be used as a basic tool to prove linear independence in the exterior product.
+\begin{lemma}
+    \label{prop:basis_product_independence}
+    The vectors $b_{i_1} \wedge ... \wedge b_{i_d}$ for $i_1 < ... < i_d$ form a basis of $\extpow^d V$.
+\end{lemma}
+\begin{proof}
+    This proof is slightly technical, as I wanted to provide a rigorous proof using only the definition of $\extpow^d V$ and some properties of the symmetric group $S_d$.
+    The core idea is to show the linear independence by going to down to the free product underlying $\extpow^d V$, and then show that we cannot use the vectors $(b_{i_1}, ..., b_{i_d}) + (b_{i_1}, ..., b_{i_{j + 1}}, b_{i_j}, ..., i_d)$ to create a nontrivial linear combination.
+    Namely, assuming we have such a nontrivial linear combination, we can group it into the part where the order of the $i_1, ..., i_d$ has even/odd parity.
+    The vectors with $i_1 < ... < i_d$ clearly are all on one side, and from this we can derive the claim.
+
+    Note that by definition, the vectors $b_{i_1} \wedge ... \wedge b_{i_d}$ for any $1 \leq i_1, ..., i_d \leq n$ span $\extpow^d V$.
+    By Lemma~\ref{prop:basic_properties_exterior_product}, we can rewrite any of them (that is nonzero) to be of the above form, so clearly the $b_{i_1} \wedge ...
+\wedge b_{i_d}$ for $i_1 < ...
+< i_d$ span $\extpow^d V$.
+
+    It is left to show that they are linearly independent.
+    Assume
+    \begin{equation*}
+        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} \bigl( b_{i_1} \wedge ... \wedge b_{i_d} \bigr) = 0
+    \end{equation*}
+    Then clearly
+    \begin{equation*}
+        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} \bigl( b_{i_1}, ..., b_{i_d} \bigr) \in U
+    \end{equation*}
+    where $U$ is the vector space from the definition of $\extpow^d V$.
+    So
+    \begin{align*}
+        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} \bigl( b_{i_1}, ..., b_{i_d} \bigr) = &\sum_{j, \ i_1, ..., i_d} \mu_{j, i_1, ..., i_d} \\
+        &\Bigl( \bigl( b_{i_1}, ..., b_{i_d} \bigr) + \bigl( b_{i_1}, ..., b_{i_{j - 1}}, b_{i_{j + 1}}, b_{i_j}, b_{i_{j + 2}}, ..., b_{i_d} \bigr) \Bigr)
+    \end{align*}
+    Note that we can assume wlog that the sum on the right-hand side goes only over $i_1, ..., i_d$ distinct.
+    The reason is that the other vectors on the right-hand side are contained in
+    \begin{equation*}
+       \vspan \{ (b_{i_1}, ..., b_{i_d}) \ | \ \text{$i_1, ..., i_d$ not distinct} \}
+    \end{equation*}
+    which only trivially intersects the space
+    \begin{equation*}
+        \vspan\{ (b_{i_1}, ..., b_{i_d}) \ | \ \text{$i_1, ..., i_d$ distinct} \}
+    \end{equation*}
+    due to the properties of the free product (the spaces share now basis vectors).
+
+    Now consider for $i_1, ..., i_d$ distinct the ``sorting permutation'' $\sigma_i \in S_d$, which is the unique permutation such that $i_{\sigma(1)} < ... < i_{\sigma(d)}$.
+    Then
+    \begin{align*}
+        \sum_{i_1 < ...
+< i_d} \lambda_{i_1, ..., i_d} \underbrace{\bigl( b_{i_1}, ..., b_{i_d} \bigr)}_{\sgn(\sigma_i) = 1 \ \text{as} \ \sigma_i = \mathrm{id}} = &\sum_{\substack{j, \ i_1, ..., i_d\\\sgn(\sigma_i) = 1}} \underbrace{\sgn(\sigma_i) \bigl( \mu_{j, i_1, ..., i_d} - \mu_{j, i_1, ..., i_{j + 1}, i_j, ..., i_d} \bigr)}_{=: \mu'_{j, i_1, ..., i_d}} \\
+        &\Bigl( \bigl( b_{i_1}, ..., b_{i_d} \bigr) + \bigl( b_{i_1}, ..., b_{i_{j - 1}}, b_{i_{j + 1}}, b_{i_j}, b_{i_{j + 2}}, ..., b_{i_d} \bigr) \Bigr)
+    \end{align*}
+    This yields
+    \begin{align*}
+        &-\sum_{\substack{j, \ i_1, ..., i_d\\\sgn(\sigma_i) = 1}} \Bigl( \mu'_{j, i_1, ..., i_d} - \begin{cases}
+            \lambda_{i_1, ..., i_d} & \text{if $i_1 < ... < i_d, j = 0$} \\
+            0 & \text{otherwise}
+        \end{cases} \Bigr) (b_{i_1}, ..., b_{i_d}) \\
+        =& \sum_{\substack{j, \ i_1, ..., i_d\\\sgn(\sigma_i) = -1}} \mu'_{j, i_1, ..., i_{j + 1}, i_j, ..., i_d} (b_{i_1}, ..., b_{i_d})
+    \end{align*}
+    However, all vectors on the left-hand side are contained in
+    \begin{equation*}
+        \vspan \{(b_{i_1}, ..., b_{i_d}) \ | \ \sgn(\sigma_i) = 1 \}
+    \end{equation*}
+    and all vectors on the right-hand side are contained in
+    \begin{equation*}
+        \vspan \{(b_{i_1}, ..., b_{i_d}) \ | \ \sgn(\sigma_i) = -1 \}
+    \end{equation*}
+    These two spaces intersect trivially, and so find
+    \begin{equation*}
+        \sum_{\substack{j, \ i_1, ..., i_d\\\sgn(\sigma_i) = -1}} \mu'_{j, i_1, ..., i_{j + 1}, i_j, ..., i_d} (b_{i_1}, ..., b_{i_d}) = 0
+    \end{equation*}
+    Clearly the different $(b_{i_1}, ..., b_{i_d})$ are linearly independent, so find that all $\mu'_{j, i_1, ..., i_d} = 0$.
+    Observe now that thus all $\lambda_{i_1, ..., i_d} = 0$ and the claim is shown.
+\end{proof}
+\begin{lemma}
+    \label{prop:subspace_closed}
+    Let $v \in V$ and $w \in \extpow^{d - 1} W$ for a linear subspace $W \leq V$. 
+    If $v \wedge w \in \extpow^d W$ then $v \in W$ or $w = 0$.
+    Here
+    \begin{equation*}
+        \extpow^d W := \{ w_1 \wedge ... \wedge w_d \ | \ w_i \in W \} \leq \extpow^d V
+    \end{equation*}
+    is a subspace of $\extpow^d V$.
+\end{lemma}
+\begin{proof}
+    wlog assume that $b_1, ..., b_m$ are a basis of $U$.
+    Then
+    \begin{equation*}
+        w = \sum_{i_1 < ... < i_{d - 1} < m} \lambda_{i_1, ..., i_{d - 1} \leq m} (b_{i_1} \wedge ... \wedge b_{i_{d - 1}})
+    \end{equation*}
+    So with $v = \sum_i \mu_i b_i$ get
+    \begin{align*}
+        v \wedge w =& \sum_{i_1 < ... < i_{d - 1} \leq m} \lambda_{i_1, ..., i_{d - 1}} (v \wedge b_{i_1} \wedge ... \wedge b_{i_{d - 1}}) \\
+        =& \sum_{i_1 \leq n, \ i_1 < ... < i_{d - 1} \leq m} \mu_{i_1} \lambda_{i_2, ..., i_d} (b_{i_1} \wedge ... \wedge b_{i_d})
+    \end{align*}
+    By assumption, we also find
+    \begin{align*}
+        v \wedge w =& \sum_{i_1 < ... < i_d \leq m} \tau_{i_1, ..., i_d} (b_{i_1} \wedge ... \wedge b_{i_d})
+    \end{align*}
+    Both representations are equal, hence
+    \begin{equation*}
+        \sum_{i_1 \leq n, \ i_2 < ... < i_d \leq m} \Bigl( \mu_{i_1}\lambda_{i_2, ..., i_d} - \begin{cases}
+            \tau_{i_1, ..., i_d} & \text{if $i_1 \leq m$} \\
+            0 & \text{otherwise}
+        \end{cases} \Bigr) (b_{i_1} \wedge ... \wedge b_{i_d}) = 0
+    \end{equation*}
+    Hence by the previous Lemma~\ref{prop:basis_product_independence}, we see that for all $i_2 < ... < i_d \leq m < i_1 \leq n$ have
+    \begin{equation*}
+        0 = \mu_{i_1}\lambda_{i_2, ..., i_d} - \begin{cases}
+            \tau_{i_1, ..., i_d} & \text{if $i_1 \leq m$} \\
+            0 & \text{otherwise}
+        \end{cases}
+    \end{equation*}
+    So in particular find for all $i_2, ..., i_d \leq m < i_1 \leq n$ that
+    \begin{equation*}
+        \mu_{i_1} \lambda_{i_2, ..., i_d} = 0
+    \end{equation*}
+    Hence either $\mu_{i_1} = 0$ for all $i_1 > m$ and so $v \in U$, or all $\lambda_{i_2, ..., i_d} = 0$ (for $i_2 < ... < i_d \leq m$) and so $w = 0$.
+\end{proof}
 \begin{lemma}
@@
 
-    Direction $\Rightarrow$ TODO
-\end{proof}
-\begin{lemma}
-    \label{prop:subspace_closed}
-    Let $v \in V$ and $u \in \extpow^{d - 1} U$ for a linear subspace $U \leq V$. 
-    If $v \wedge u \in \extpow^d U$ then $v \in U$ or $u = 0$.
-\end{lemma}
-\begin{proof}
+    For the other direction, let $v_1, ..., v_d$ be linearly independent.
     TODO

### 2021-12-12 Algebraic geometry/submission.tex
Fixed first part of proof of isomorphism in alg geo

@@
     \end{equation*}
-    So in particular find for all $i_2, ..., i_d \leq m < i_1 \leq n$ that
+    So in particular find for all $i_2 < ... < i_d \leq m < i_1 \leq n$ that
     \begin{equation*}
@@
     For the other direction, let $v_1, ..., v_d$ be linearly independent.
-    TODO
+    Clearly, we can extend them to a basis $v_1, ..., v_n$ of $V$.
+    We then see that there is a matrix $A = (a_{ij}) \in \GL_n(k)$ with $v_i = \sum_j a_{ij} b_j$.
+    So by Lemma~\ref{prop:linear_transform_extpow} have
+    \begin{equation*}
+        v_1 \wedge ... \wedge v_n = \underbrace{\det(A)}_{\neq 0} (b_1 \wedge ... \wedge b_n) \neq 0
+    \end{equation*}
+    So clearly $v_1 \wedge ... \wedge v_d \neq 0$ as $0 \wedge (v_{d + 1} \wedge ... \wedge v_n) = 0$ for all $v_{d + 1}, ..., v_n \in V$.
 \end{proof}
@@
     \end{align*}
-    Here we used that the permutation $\bigl(1 \ 2d\bigr)\bigl(2 \ (2d - 1)\bigr)...\bigl(d \ (d + 1)\bigr) \in S_{2d}$ has always sign $1$ (since $d$ is even).
+    Here we used that the reversing permutation $\bigl(1 \ 2d\bigr)\bigl(2 \ (2d - 1)\bigr)...\bigl(d \ (d + 1)\bigr) \in S_{2d}$ has even parity, i.e. $\sgn(\cdot) = 1$ (since $d$ is even).
 
-    Note that for any nonzero decomposable vector
+    Now note that
     \begin{equation*}
-        u_1 \wedge u_2 \in \Bigl( \extpow^2 \vspan\{v_2, ..., v_t\} \Bigr) \setminus \{0\}
+        v_1 \wedge \Bigl( \sum_{j > 1} v_j \Bigr) = 0 \in \extpow^2 \vspan\{v_2, ..., v_t\}
     \end{equation*}
-    find
-    \begin{equation*}
-        u_1, u_2 \in \vspan\{v_2, ..., v_t\}
-    \end{equation*}
-    In particular, we know that
-    \begin{equation*}
-        v_1 \wedge \Bigl( \sum_{j > i} v_j \Bigr) \in \extpow^2 \vspan\{v_2, ..., v_t\}
-    \end{equation*}
-    and so $v_1 \in \vspan\{v_2, ..., v_t\}$ unless $\sum_{j > i} v_j = 0$ by Lemma~\ref{prop:subspace_closed}.
+    and so $v_1 \in \vspan\{v_2, ..., v_t\}$ unless $\sum_{j > 1} v_j = 0$ by Lemma~\ref{prop:subspace_closed}.
     We assumed that the $v_i$ are linearly independent, so the former would give a contradiction.
-    Hence $\sum_{j > i} v_j = 0$ and thus $t = 1$, i.e. $\omega = v_1$ is decomposable.
+    Hence $\sum_{j > 1} v_j = 0$ and thus $t = 1$, i.e. $\omega = v_1$ is decomposable.
 \end{proof}
@@
 
-In this part, we want to consider the connection of external powers to the Grassmanian.
+In this part, we want to consider the connection of exterior powers to the Grassmanian.
 \begin{remark}[Question (a)]
@@
     First of all, we show that $f$ is well-defined.
-    Note that the tensor product can be described as
+    Clearly $f$ is well-defined on the decomposable vectors, as the determinant is negated by swapping columns.
+
+    Now we have to show that $f$ yields the same value for different sum representations of an element of $\extpow^d V$.
+    The idea is just that the determinant is linear in each column, but the details will be slightly technical.
+
+    Assume
+    \begin{equation*}
+        \sum_l v_1^{(l)} \wedge ... \wedge v_d^{(l)} = \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} (e_{i_1} \wedge ... \wedge e_{i_d})
+    \end{equation*}
+    Then clearly
     \begin{align*}
-        V^{\otimes d} := k^{V \times ...\times V} / \vspan\{ &\bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes \bigl(v_i + v'_i\bigl) \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \\
-        &- \bigl(v_1 \otimes ... \otimes v_d\bigl) - \bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes v'_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl), \\
-        & \bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes \lambda v_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \\
-        &- \lambda\bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes v_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \ | \ i \leq d, v_j, v'_i \in V\}
+        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} \det(A_I(e_{i_1}, ..., e_{i_d})) = \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} \begin{cases}
+            1 & \text{if $I = \{i_1, ..., i_d\}$} \\
+            0 & \text{otherwise}
+        \end{cases} = \lambda_I
     \end{align*}
-    where $v_1 \otimes ... \otimes v_d := \chi_{(v_1, ..., v_d)}$.
-    Hence the external power can be described as
+    So it suffices to show that for all $I = \{i_1, ..., i_d\} \in \{1, ..., n\}^{(d)}$ have
+    \begin{equation*}
+        \sum_l \det(A_I(v_1^{(l)}, ..., v_d^{(l)})) = \lambda_I
+    \end{equation*}
+    Assume that $v_j^{(l)} = \sum_i \mu_{l, j, i} e_i$. Since the determinant is linear in each column, find
     \begin{align*}
-        \extpow^d V := k^{V \times ... \times V} / \vspan\Bigl\{ &\bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes \bigl(v_i + v'_i\bigl) \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \\
-        &- \bigl(v_1 \otimes ... \otimes v_d\bigl) - \bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes v'_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl), \\
-        & \bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes \lambda v_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl) \\
-        &- \lambda\bigl(v_1 \otimes ... \otimes v_{i - 1} \otimes v_i \otimes v_{i + 1} \otimes ... \otimes v_d\bigl), \\
-        &v_1 \otimes ... v_{j - 1} \otimes (v_j \otimes v_{j + 1} + v_{j + 1} \otimes v_j) \otimes v_{j + 1} \otimes ... \otimes v_d \\
-        &\quad | \ i \leq d, \ j \leq d - 1, \ v_1, ..., v_d, v'_i \in V\Bigr\}
+        &\sum_l \det(A_I(v_1^{(l)}, ..., v_d^{(l)})) = \sum_l \sum_{1 \leq j_1, ..., j_d \leq n} \mu_{l, 1, j_1} \cdot ... \cdot \mu_{l, d, j_d} \det(A_I(e_{j_1}, ..., e_{j_d})) \\
+        =& \sum_l \sum_{j_1, ..., j_d \ \text{distinct}} \mu_{l, 1, j_1} \cdot ... \cdot \mu_{l, d, j_d} \cdot \begin{cases}
+            \pm 1 & \text{if $\{j_1, ..., j_d\} = I$} \\
+            0 & \text{otherwise}
+        \end{cases} \\
+        =& \sum_l \sum_{\pi \in S_d} \sgn(\pi) \mu_{l, 1, i_{\pi(1)}} \cdot ... \cdot \mu_{l, d, i_{\pi(d)}}
     \end{align*}
-    So it suffices to show that for all $I \in \{1, ..., n\}^{(d)}$ and vectors $v_1, ..., v_d, v'_i \in V$
+    On the other hand, observe that also $\wedge$ is multilinear (i.e. linear in each component), so
+    \begin{align*}
+        &\sum_l v_1^{(l)} \wedge ... \wedge v_d^{(l)} = \sum_l \sum_{1 \leq j_1, ..., j_d \leq n} \mu_{l, 1, j_1} \cdot ... \cdot \mu_{l, d, j_d} \bigl( e_{i_1} \wedge ... \wedge e_{i_d} \bigr) \\
+        =& \sum_l \sum_{j_1, ..., j_d \ \text{distinct}} \mu_{l, 1, j_1} \cdot ... \cdot \mu_{l, d, j_d} \bigl( e_{i_1} \wedge ... \wedge e_{i_d} \bigr) \\
+        =& \sum_l \sum_{i_1 < ... < i_d} (e_{i_1} \wedge ... \wedge e_{i_d}) \sum_{\pi \in S_d} \sgn(\pi) \mu_{l, 1, i_{\pi(1)}} \cdot ... \cdot \mu_{l, d, i_{\pi(d)}}
+    \end{align*}
+    By Lemma~\ref{prop:basis_product_independence} the $e_{i_1} \wedge ... \wedge e_{i_d}$ are a basis, and so we must already have that
+    \begin{equation*}
+        \lambda_{i_1, ..., i_d} = \sum_l \sum_{\pi \in S_d} \sgn(\pi) \mu_{l, 1, i_{\pi(1)}} \cdot ... \cdot \mu_{l, d, i_{\pi(d)}}
+    \end{equation*}
+    This shows the well-definedness.
+
     \begin{align*}

### 2021-12-13 Algebraic geometry/submission.tex
added rust syntax highlighting to combinatorics

@@
 \end{proof}
-
+For the next parts of the mini project, we first need more basic properties of the exterior product.
 \begin{lemma}
@@
 \end{proof}
-
+Now we can see that in general, the exterior product contains not decomposable elements.
 \begin{lemma}[Question (c)]
@@
 \end{definition}
-\begin{lemma}[1a]
+\begin{lemma}[Question (a)]
     We have
@@
 
-    \begin{align*}
-        \det(A_I(v_1, ..., v_i + v'_i, ..., v_d)) = \det(A_I(v_1, ..., v_d)) + \det(A_I(v_1, ..., v'_i, ..., v_d))
-    \end{align*}
-    and
-    \begin{align*}
-        \det(A_I(v_1, ..., \lambda v_i, ..., v_d)) = \lambda\det(A_I(v_1, ..., v_d))
-    \end{align*}
-    and
-    \begin{equation*}
-        \det(A_I(v_1, ..., v_{j + 1}, v_j, ..., v_d)) = -\det(A_I(v_1, ..., v_d))
-    \end{equation*}
-    However, these properties follow from the well-known properties of the determinant.
-    In particular, $\det$ is linear in each column and swapping columns negates the determinant.
-    It follows that $f$ is indeed well-defined.
-
     It is clear by definition that $f$ is linear, so it is left to show that it is bijective. 
@@
     \end{equation*}
-    so $f(e_{i_1} \wedge ... \wedge e_{i_d}) = e_I$ and we deduce that $\mathrm{im}f = \Proj^{\{1, ..., k\}^{(d)}}$.
+    so $f(e_{i_1} \wedge ... \wedge e_{i_d}) = e_I$ and we deduce that $\mathrm{im}f = k^{\{1, ..., k\}^{(d)}}$.
 
@@
     \end{equation*}
-    for $i_1 < ... < i_d$ form a basis of $\extpow^d k^n$.
-    Clearly, they span $\extpow^d k^n$, and the following argument shows that they are linearly independent.
-    Assume
-    \begin{equation*}
-        \sum_{i_1 < ... < i_d} \lambda_{i_1, ..., i_d} (e_{i_1} \wedge ... \wedge e_{i_d}) = 0
-    \end{equation*}
-    Then
-    \begin{equation*}
-        0 = e_1 \wedge \Bigl( \sum_{1 < i_2 < ...
-< i_d} \lambda_{1, i_2, ..., i_d} (e_{i_2} \wedge ..
-\wedge e_{i_d}) \Bigr) + \sum_{1 < i_1 < ...
-< i_d} \lambda_{i_1, ..., i_d} (e_{i_1} \wedge ...
-\wedge e_{i_d} )
-    \end{equation*}
-    Clearly $e_1 \notin \vspan\{e_2, ..., e_n\}$ and so by Lemma~\ref{prop:subspace_closed} we see that
-    \begin{equation*}
-        \sum_{1 < i_2 < ... < i_d} \lambda_{1, i_2, ..., i_d} (e_{i_2} \wedge ... \wedge e_{i_d}) = 0
-    \end{equation*}
-    Repeating this argument inductively shows that $\lambda_{1, 2, ..., d} = 0$.
-    As $k^n$ is symmetric w.r.t. permuting the $e_j$, we see that all $\lambda_{i_1, ..., i_d} = 0$ are zero.
-
+    for $i_1 < ... < i_d$ form a basis of $\extpow^d k^n$ by Lemma~\ref{prop:basis_product_independence}.
     It follows that $\dim(\extpow^d k^n) = \dim(\Proj^{\{1, ..., n\}^{(d)}})$ and we find that $f$ is also injective.
@@
     as $u_1 \notin \vspan\{u_2, ..., u_d, w_{l + 1}, ..., w_d\}$.
-    Inductively, this argument shows that
+    Inductively, this argument shows that for all $2 \leq j \leq l + 1$
+    \begin{equation*}
+        u_j \wedge ... \wedge u_l \wedge (u_{l + 1} \wedge ... \wedge u_d) - (w_{l + 1} \wedge ... \wedge w_d) = 0
+    \end{equation*}
+    Hence
     \begin{equation*}
@@
 In this part, we want to investigate the geometric properties of the Grassmanian resp. the image of $\phi$.
-First of all, we introduce coordinates on $\Proj(\extpow^d k^n)$.
+In particular, we focus on the case $d = 2$, i.e. examine the variety $\Gr(2, V)$ for different finite-dimensional $V$.
+To use our standard methods of Algebraic Geometry, we first introduce coordinates on $\Proj(\extpow^d k^n)$.
 \begin{definition}
-    Note that in the proof of Lemma~\ref{prop:isomorphism_extpow_det} it was shown that $v_{i_1} \wedge ...
+    Note that in the proof of Lemma~\ref{prop:basis_product_independence} it was shown that $v_{i_1} \wedge ...
 \wedge v_{i_d}$ for $i_1 < ...
@@
     \begin{equation*}
-        \omega \in \mathrm{im}\phi \ \Leftrightarrow \ \omega \wedge \omega = 0
+        [\omega] \in \mathrm{im}\phi \ \Leftrightarrow \ \omega \wedge \omega = 0
     \end{equation*}
-    In $\Proj(\extpow^d V)$ we find that
+    We find that
     \begin{align*}
@@
         I = \langle x_{1, 2} x_{3, 4} + x_{1, 4} x_{2, 3} - x_{1, 3} x_{2, 4} \rangle \in k[x_{1, 2}, x_{1, 3}, x_{1, 4}, x_{2, 3}, x_{2, 4}, x_{3, 4}]
-    \end{equation*}
-    Changing the indices used for the coordinates, we find
-    \begin{equation*}
-        \Gr(2, 4) = \V(x_0 x_5 + x_2 x_3 - x_2 x_4)
     \end{equation*}
@@
     Let $\preceq$ be a graded monomial ordering on $R = k[x_0, ..., x_n]$.
-    Then for an ideal $I \leq R$ have that the monomials $x_0^{\alpha_0} ... x_n^{\alpha_n} \notin \mathrm{lt}(I)$ are a $k$-vector space basis of $R/I$.
+    Then for an ideal $I \leq R$ have that the list of all monomials $x_0^{\alpha_0}, ..., x_n^{\alpha_n} \notin \mathrm{lt}(I)$ not contained in $\mathrm{lt}(I)$ are a $k$-vector space basis of $R/I$.
 
@@
 
-    Consider homogeneous polynomials $f_{i, j, u, v} \in R$ and
+    Consider an arbitrary element $F$ of $I$, given by homogeneous polynomials $f_{i, j, u, v} \in R$ via
     \begin{equation*}
@@
     \begin{equation*}
-        F - f_{i, j, u, v} x_{i, v} x_{j, u} = \sum_{\substack{a < b < c < d\\(a, b, c, d) \neq (i, j, u, v)}} f_{a, b, c, d} \ (x_{a, d} x_{b, c} - x_{a, c} x_{b, d} + x_{a, b} x_{c, d})
+        F - f_{i, j, u, v} \ x_{i, v} \ x_{j, u} = \sum_{\substack{a < b < c < d\\(a, b, c, d) \neq (i, j, u, v)}} f_{a, b, c, d} \ (x_{a, d} x_{b, c} - x_{a, c} x_{b, d} + x_{a, b} x_{c, d})
     \end{equation*}
@@
     However, the second and third case imply that $f_{a, b, c, d} \ x_{a, d} \ x_{b, c} \succ f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$.
-    Hence, the ``new'' monomial $f_{a, b, c, d} \ x_{a, d} \ x_{b, c}$ also has to ``cancel out'' in the sum representation of $F$, as comes after $\mathrm{lt}(F) = \epsilon x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$ in the order $\preceq$.
+    Hence, the ``new'' monomial $f_{a, b, c, d} \ x_{a, d} \ x_{b, c}$ also has to ``cancel out'' in the sum representation of $F$, as it is greater than $\mathrm{lt}(F) = \epsilon x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$ in the order $\preceq$.
     So applying the whole argument inductively (induction on the number of monomials $\succ f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$ that occur in any of the polynomials we work with), we end up in the first case
@@
         =\ &\Bigl| \bigcup_{\substack{\alpha \in \{0, 1\}^N\\x_{iv} x_ju \ \nmid \ x^\alpha}} \{ x^\alpha x^\beta \ | \ \deg(x^\beta) = m - \deg(x^\alpha), \ \forall i: \alpha_i = 0 \Rightarrow \beta_i = 0 \} \Bigr| \\
-        =& \sum_{\substack{\alpha \in \{0, 1\}^N\\x_{iv} x_ju \ \nmid \ x^\alpha}} \left(\!\!{\deg(x^\alpha) \choose m - \deg(x^\alpha)}\!\!\right) = \sum_{l = 0}^N \sum_{\substack{\alpha \in \{0, 1\}^N\\\sum_j \alpha_j = l\\x_{i, v} x_{j, u} \ \nmid \ x^\alpha}} \left(\!\!{ l \choose m - l }\!\!\right) \\
+        =& \sum_{\substack{\alpha \in \{0, 1\}^N\\x_{iv} x_{ju} \ \nmid \ x^\alpha}} \left(\!\!{\deg(x^\alpha) \choose m - \deg(x^\alpha)}\!\!\right) = \sum_{l = 0}^N \sum_{\substack{\alpha \in \{0, 1\}^N\\\sum_j \alpha_j = l\\x_{i, v} x_{j, u} \ \nmid \ x^\alpha}} \left(\!\!{ l \choose m - l }\!\!\right) \\
         =& \sum_{l = 0}^N s_n(l) \left(\!\!{ l \choose m - l }\!\!\right) = \sum_{l = 0}^N s_n(l) {m - 1 \choose l - 1}
@@
     Now note that $C$ does not decrease the size, i.e. $|C(I)| = |I|$ and so $|C^k(I)| = |I|$.
-    However, there are only $(n - 2) + (n - 2) + 1 = 2n - 3$ elements in layer 0 and the claim follows.
+    However, there are only $(n - 2) + (n - 2) + 1 = 2n - 3$ elements in layer 0 and we see that there is no independent set of size $> 2n - 3$.
+
+    On the other hand, it is easy to observe that the 0-th layer
+    \begin{equation*}
+        I = \{ v \in V \ | \ l(v) = 0 \}
+    \end{equation*}
+    is indeed an independent set, as for all elements $(i, j) \in I$ have either $i = 1$ or $j = n$.
 \end{proof}
@@
 \begin{corollary}[Question (e)]
-    Have $\dim(\Gr(2, 6)) = 8$ and $\deg(\Gr(2, 6)) = 15$.
+    Have $\dim(\Gr(2, 6)) = 8$ and $\deg(\Gr(2, 6)) = 14$.
 \end{corollary}
@@
     For the degree, just count the maximal independent sets in $G_6$, as displayed in Example~\ref{ex:Gn}.
-    This is slightly tricky, but it is not too hard to see that there are exactly 15 of them.
+    This is slightly tricky, but it is not too hard to see that there are exactly 14 of them.
 \end{proof}

### 2021-12-13 Algebraic geometry/submission.tex
started rewrite of leading term ideal lemma in alg geo

@@
 \end{proof}
+\begin{proof}
+    Consider the direction $\supseteq$.
+    Consider an element
+    \begin{equation*}
+        F = \sum_{a < b < c < d} f_{a, b, c, d} (x_{a, d} x_{b, c} - x_{a, c} x_{b, d} + x_{a, b} x_{c, d}) \in a
+    \end{equation*}
+    We want to show that $\mathrm{lt}(F) \in b$.
+    With the decomposition of $f_{a, b, c, d}$ into homogeneous components
+    \begin{equation*}
+        f_{a, b, c, d} = \sum_d f_{a, b, c, d}^{(d)}
+    \end{equation*}
+    we find that
+    \begin{equation*}
+        \mathrm{lt}(F) = \mathrm{lt}\Bigl( \sum_{a < b < c < d} f_{a, b, c, d}^{(\deg(\mathrm{lt}(F)) - 2)} (x_{a, d} x_{b, c} - x_{b, d} x_{a, c} + x_{a, b} x_{c, d}) \Bigr)
+    \end{equation*}
+    and so we may consider only the case that the $f_{a, b, c, d}$ are homogeneous of same degree $d := \deg(\mathrm{lt}(F)) - 2$.
+    Now write for $a < b < c < d$
+    \begin{equation*}
+        f_{a, b, c, d} = \sum_{s = 1}^{N_{a, b, c, d}} t_{a, b, c, d, s}
+    \end{equation*}
+    with nonzero terms $t_{a, b, c, d, s} \in R$.
+
+    Hence we have
+    \begin{equation*}
+        F = \sum_{a < b < c < d, \ s} t_{a, b, c, d, s} (x_{a, d} x_{b, c} - x_{a, c} x_{b, d} + x_{a, b} x_{c, d})
+    \end{equation*}
+    By sorting according to the monomial ordering, find
+    \begin{align*}
+        t_{a_1, b_1, c_1, d_1, s_1} \ x_{a_1, d_1} \ x_{b_1, c_1} \succeq t_{a_2, b_2, c_2, d_2, s_2} \ x_{a_2, d_2} \ x_{b_2, c_2} \succeq ... \\
+    \end{align*}
+    for some $a_i < b_i < c_i < d_i, \ i \leq N$.
+
+    \paragraph{Case 1} Assume that there is $i \leq N$ such that
+    \begin{equation*}
+        \mathrm{lt}(F) \equiv t_{a_i, b_i, c_i, d_i, s_i} \ x_{a_i, d_i} \ x_{b_i, c_i}
+    \end{equation*}
+    Here we use $\equiv$ to mean that both sides are equal up to multiplication by a scaling factor $\epsilon \in k^*$.
+    We are only interested in divisibility in $R$, so units do not matter, and notation would be unnecessarily blown up if we always had to include some $\epsilon \in k^*$.
+
+    Then we are already done, as
+    \begin{equation*}
+        t_{a_i, b_i, c_i, d_i, s_i} \ x_{a_i, d_i} \ x_{b_i, c_i} \in J
+    \end{equation*}
+
+    \paragraph{Case 2} Assume that there is $i \leq N$ such that
+    \begin{equation*}
+        \mathrm{lt}(F) \equiv t_{a_i, b_i, c_i, d_i, s_i} \ x_{b_i, d_i} \ x_{a_i, c_i}
+    \end{equation*}
+    Note that
+    \begin{equation*}
+        t_{a_i, b_i, c_i, d_i, s_i} \ x_{a_i, d_i} \ x_{b_i, c_i} \succ t_{a_i, b_i, c_i, d_i, s_i} \ x_{b_i, d_i} \ x_{a_i, c_i} \equiv \mathrm{lt}(F)
+    \end{equation*}
+    Hence the former term does not occur in $F$, and so must ``cancel out'' in the sum representation of $F$.
+    However, the other term (or terms) with whom this cancels out might still be of the form $t_{(...)} \ x_{b_i, d_i} \ x_{a_i, c_i}$.
+    Thus, we have to use some kind of induction to go to the beginning of the cancellation chain.
+
+    \subparagraph{Claim} For all $j \leq i$ have that there exists an $l \leq N$ with
+    \begin{align*}
+        x_{a_l, d_l} \divides t_{a_j, b_j, c_j, d_j, s_j} \quad \text{or} 
+    \end{align*}
+    and
+    \begin{align*}
+        x_{b_l, c_l} \divides t_{a_j, b_j, c_j, d_j, s_j} \quad \text{or} \quad a_l < a_j < c_j < d_l \quad \text{or} \quad a_l < b_j < d_j < d_l
+    \end{align*}
+
+    \begin{equation*}
+        x_{a_l, d_l} \divides t_{a_j, b_j, c_j, d_j, s_j} \quad \text{or} \quad x_{b_l, c_l} \divides t_{a_j, b_j, c_j, d_j, s_j}
+    \end{equation*}
+
+    For the proof, use induction on $j$.
+    First consider the case $j = 1$. We have that
+    \begin{equation*}
+        \underbrace{t_{a_1, b_1, c_1, d_1, s_1} \ x_{a_1, d_1} \ x_{b_1, c_1}}_{=: T} \succeq t_{a_i, b_i, c_i, d_i, s_i} \ x_{a_i, d_i} \ x_{b_i, c_i} \succ t_{a_i, b_i, c_i, d_i, s_i} \ x_{b_i, d_i} \ x_{a_i, c_i} \equiv \mathrm{lt}(F)
+    \end{equation*}
+    Hence the term $T$ must cancel out in the sum representation of $F$, so there must be some $l \neq 1$ with
+    \begin{equation*}
+        T \equiv t_{a_l, b_l, c_l, d_l, s_l} \ x_{a_l, d_l} \ x_{b_l, c_l}
+    \end{equation*}
+    Note that $T$ cannot cancel out with a term of the form $t_{(...)} \ x_{b_l, d_l} \ x_{a_l, c_l}$ as $T \succ$ all terms of this form.
+    Hence the term that $T$ cancels out with must be of the above form.
+
+    We also have that $T \succ$ all terms of the form $t_{a_1, b_1, c_1, d_1, s'}$ for $s' \neq s_1$.
+    So either $(a_l, d_l) \neq (a_1, d_1)$ or $(b_l, c_l) \neq (b_1, c_1)$.
+    If $(a_l, d_l) \neq (a_1, d_1)$ and $(b_l, c_l) \neq (b_1, c_1)$, we are clearly done.
+    Assume $(a_l, d_l) \neq (a_1, d_1)$ and $(b_l, c_l) = (b_1, c_1)$.
+    Then
+    \begin{equation*}
+        x_{a_l, d_l} \divides t_{a_1, b_1, c_1, d_1, s_1}
+    \end{equation*}
+    So it is left to show that
+    \begin{equation*}
+        a_l < a_1 < c_1 < d_l \quad \text{or} \quad a_l < b_1 < d_1 < d_l
+    \end{equation*}
+    Since $b_1 = b_l, c_1 = c_l$, the only possible relative ordering of $a_l, d_l, a_1, d_1$ such that this is not satisfied is
+    \begin{equation*}
+        a_1 < a_l < a_d < d_1
+    \end{equation*}
+
+    Now we consider the induction step, so assume $j > 1$. 
+    Again have that
+    \begin{equation*}
+        \underbrace{t_{a_j, b_j, c_j, d_j, s_j} \ x_{a_j, d_j} \ x_{b_j, c_j}}_{=: T} \succeq t_{a_i, b_i, c_i, d_i, s_i} \ x_{a_i, d_i} \ x_{b_i, c_i} \succ t_{a_i, b_i, c_i, d_i, s_i} \ x_{b_i, d_i} \ x_{a_i, c_i} \equiv \mathrm{lt}(F)
+    \end{equation*}
+    and so $T$ must cancel out in the sum representation of $F$.
+    If one of the terms that $T$ cancels out with is of the form
+    \begin{equation*}
+        t_{a_l, b_l, c_l, d_l, s_l} \ x_{a_l, d_l} \ x_{b_l, c_l}
+    \end{equation*}
+    then we can proceed exactly as in the base case.
+
+    The only difference is that now there are more possibilities for the terms that $T$ might cancel out with.
+    In particular, it is now possible that the we only find
+    \begin{equation*}
+        T \equiv t_{a_m, b_m, c_m, d_m, s_m} \ x_{b_m, d_m} \ x_{a_m, c_m}
+    \end{equation*}
+    for some $m < j$ with $(a_m, b_m, c_m, d_m) \neq (a_j, b_j, c_j, d_j)$.
+    However, then we can apply the induction hypothesis to see that
+    \begin{equation*}
+        x_{a_l, d_l} \divides t_{a_m, b_m, c_m, d_m, s_m} \quad \text{or} \quad x_{b_l, c_l} \divides t_{a_m, b_m, c_m, d_m, s_m}
+    \end{equation*}
+    Clearly
+    \begin{equation*}
+        x_{a_l, d_l}, \ x_{b_l, c_l} \perp x_{b_m, d_m} x_{a_m, c_m}
+    \end{equation*}
+    and so 
+    \begin{equation*}
+        x_{a_l, d_l} \divides t_{a_j, b_j, c_j, d_j, s_j} \quad \text{or} \quad x_{b_l, c_l} \divides t_{a_j, b_j, c_j, d_j, s_j}
+    \end{equation*}
+    So the claim is shown now.
+
+    To complete case 2, we now apply the claim to $j = i$ and see that
+    \begin{equation*}
+        x_{a_l, d_l} \divides t_{a_i, b_i, c_i, d_i, s_i} \quad \text{or} \quad x_{b_l, c_l} \divides t_{a_i, b_i, c_i, d_i, s_i}
+    \end{equation*}
+    Hence
+    \begin{equation*}
+        x_{a_l, d_l} \ x_{b_i, d_i} \ x_{a_i, c_i} \divides \mathrm{lt}(F) \quad \text{or} \quad x_{b_l, c_l} \ x_{b_i, d_i} \ x_{a_i, c_i} \divides \mathrm{lt}(F)
+    \end{equation*}
+\end{proof}
 

### 2021-12-14 Algebraic geometry/submission.tex
Fixed alg geo, hopefully finally

--- 2021-12-13 Algebraic geometry/submission.tex
@@
     \label{prop:leading_term_ideal_grassmanian}
-    Define the graded reverse monomial ordering $\preceq$ on $R := k[x_{i, j} \ | \ i < j]$ where the variables $x_{i, j}$ are ordered co-lexicographically w.r.t. $(i, j)$, i.e.
+    Define the graded reverse monomial ordering $\preceq$ on $R := k[x_{i, j} \ | \ i < j]$ where the variables $x_{i, j}$ are ordered lexicographically w.r.t. $(i, j)$, i.e.
     \begin{equation*}
-        x_{i, j} \leq x_{u, v} \ :\Leftrightarrow \ (i, j) \leq_{\text{colex}} (u, v)
+        x_{i, j} \leq x_{u, v} \ :\Leftrightarrow \ (i, j) \leq_{\text{lex}} (u, v)
     \end{equation*}
@@
 \begin{proof}
-    Note that for $i < j < u < v$ have $x_{u, v}, x_{j, v} \succ x_{i, v} \succ x_{i, j}, x_{i, u}, x_{j, u}$.
-    Thus the leading term of $x_{i, j} x_{u, v} + x_{i, v} x_{j, u} - x_{i, u} x_{j, v}$ is
+    We show that the set $G = \{ x_{iv} x_{ju} - x_{iu} x_{jv} + x_{ij} x_{uv} \ | \ i < j < u < v \}$ is a Gröbner basis of $I$.
+    The claim then follows by the properties of Gröbner basis.
+
+    To do this, we consider for $a < b < c < d$ and $i < j < u < v$ the polynomial
+    \begin{align*}
+        S := &\frac {\mathrm{lcm}(x_{iv} x_{ju}, \ x_{ad} x_{bc})} {x_{iv} x_{ju}} (x_{iv} x_{ju} - x_{iu} x_{jv} + x_{ij} x_{uv}) \\
+        &- \frac {\mathrm{lcm}(x_{iv} x_{ju}, \ x_{ad} x_{bc})} {x_{ad} x_{bc}} (x_{ad} x_{bc} - x_{ac} x_{bd} + x_{ab} x_{cd})
+    \end{align*}
+    and show that they are reduced to $0$ by multivariate polynomial division by $G$.
+
+    \paragraph{Case 1} If $(i, v) = (a, d)$ and $(j, u) \neq (b, c)$. Then
     \begin{equation*}
-        \mathrm{lt}(x_{i, j} x_{u, v} + x_{i, v} x_{j, u} - x_{i, u} x_{j, v}) = x_{i, v} x_{j, u}
+        \mathrm{lcm}(x_{iv} x_{ju}, \ x_{ad} x_{bc}) = x_{ju} x_{ad} x_{bc}
     \end{equation*}
-    It follows that $J \subseteq \mathrm{lt}(I)$.
+    and so
+    \begin{equation*}
+        S = -x_{au} x_{jd} x_{bc} + x_{aj} x_{ud} x_{bc} + x_{ac} x_{ju} x_{bd} - x_{ab} x_{ju} x_{cd}
+    \end{equation*}
+    wlog assume that $j < b$, so $\mathrm{lt}(F) = -x_{au} x_{jd} x_{bc}$.
+    Then there are three sub-cases.
+    \subparagraph{Case 1.1} If $j < u < b < c < d$. 
+    Then the only way to do cancel the leading term by polynomial division is to divide by $x_{jd} x_{bc} - x_{jc} x_{bd} + x_{jb} x_{cd}$ to get
+    \begin{equation*}
+        S' = x_{aj} x_{ud} x_{bc} + x_{ac} x_{ju} x_{bd} - x_{au} x_{jc} x_{bd} - x_{ab} x_{ju} x_{cd} + x_{au} x_{jb} x_{cd}
+    \end{equation*}
+    So $\mathrm{lt}(S') = x_{aj} x_{ud} x_{bc}$ and the only way to cancel the leading term is to divide by $x_{ud} x_{bc} - x_{uc} x_{bd} + x_{ub} x_{cd}$ to get
+    \begin{equation*}
+        S'' = x_{ac} x_{ju} x_{bd} - x_{au} x_{jc} x_{bd} + x_{aj} x_{uc} x_{bd} - x_{ab} x_{ju} x_{cd} + x_{au} x_{jb} x_{cd} - x_{aj} x_{ub} x_{cd}
+    \end{equation*}
+    Now $\mathrm{lt}(S'') = x_{ac} x_{ju} x_{bd}$ and the only way to cancel the leading term is to divide by $x_{ac} x_{ju} - x_{au} x_{jc} + x_{aj} x_{uc}$ to get
+    \begin{equation*}
+        S''' = -x_{ab} x_{ju} x_{cd} + x_{au} x_{jb} x_{cd} - x_{aj} x_{ub} x_{cd}
+    \end{equation*}
+    Now $\mathrm{lt}(S''') = -x_{ab} x_{ju} x_{cd}$ and the only way to cancel the leading term is to divide by $x_{ab} x_{ju} - x_{au} x_{jb} + x_{aj} x_{ub}$ to get $0$.
+    So this subcase is finished.
 
-    For the other direction, we use a quite lengthy degree argument.
-    Sadly, the only argument I came up with is extremely technical.
-    We try to present it as clearly as possible, at the cost of only sketching some parts.
-    In the end, I checked it using Computer Algebra, and everything fits together.
+    You can now do all other cases in exactly the same way, however this is quite a huge lot of effort.
+    Therefore, I will not do it here.
 
-    Consider an arbitrary element $F$ of $I$, given by homogeneous polynomials $f_{i, j, u, v} \in R$ via
+    However, observe that $S$ only depends on the relative order of $i, j, u, v, a, b, c, d$.
+    All possible orders of those are already present if we consider
     \begin{equation*}
-        F = \sum_{i < j < u < v} f_{i, j, u, v} \ (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v})
+        1 \leq i < j < u < v \leq 8 \quad \text{and} \quad 1 \leq a < b < c < d \leq 8
     \end{equation*}
-    We want to show that $\mathrm{lt}(F) \in J$.
+    In other words, it suffices to show that $G$ is a Gröbner basis in the case $n = 8$.
+    By hand, this requires exactly the same computation as started above, but it can be very easily checked using Computer Algebra.
+    I have done this, and the result is as expected.
+\end{proof}
+At first glance, this lemma above seems quite deep, but it really is a repetitive application of the theory of Gröbner basis.
 
-    Let
-    \begin{equation*}
-        f_{i, j, u, v} = \sum_{\alpha \in \N^N} c^{(i, j, u, v)}_\alpha x^\alpha
-    \end{equation*}
-    Then
-    \begin{equation*}
-        F = \sum_{\alpha \in \N^N} \sum_{i < j < u < v} c^{(i, j, u, v)}_\alpha x^\alpha \ (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v})
-    \end{equation*}
-    and so there exists $\alpha \in \N^N$ and $\epsilon \in k^*$ with
-    \begin{equation*}
-        \mathrm{lt}(F) = \epsilon \cdot \mathrm{lt}\Bigl( \sum_{i < j < u < v} c_\alpha^{(i, j, u, v)} x^\alpha \ (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v}) \Bigr)
-    \end{equation*}
-    Hence, we may assume wlog that all the $f_{i, j, u, v}$ are scaled monomials.
-
-    Now, observe that all monomials in $F$ are of the form
-    \begin{align*}
-        \epsilon \ x_{i, v} \ x_{j, u} \ f_{i, j, u, v} \quad \text{or} \quad 
-        \epsilon \ x_{i, u} \ x_{j, v} \ f_{i, j, u, v} \quad \text{or} \quad 
-        \epsilon \ x_{i, j} \ x_{u, v} \ f_{i, j, u, v} 
-    \end{align*}
-    where $\epsilon \in k^*$ and $i < j < u < v$.
-    In particular, this is true for the leading term $\mathrm{lt}(F)$.
-    In the first of those case, clearly $\mathrm{lt}(F) \in J$.
-
-    So consider now the second case, i.e. $\mathrm{lt}(F) = \epsilon \ x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$.
-    Since $x_{i, v} \ x_{j, u} \ f_{i, j, u, v} \succ x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$, we see that the term $x_{i, v} \ x_{j, u} \ f_{i, j, u, v}$ cannot occur in $F$, i.e. must ``cancel out''.
-    Hence the monomial $\epsilon \ x_{i, v} \ x_{j, u} \ f_{i, j, u, v}$ has a nonzero coefficient in
-    \begin{equation*}
-        F - f_{i, j, u, v} \ x_{i, v} \ x_{j, u} = \sum_{\substack{a < b < c < d\\(a, b, c, d) \neq (i, j, u, v)}} f_{a, b, c, d} \ (x_{a, d} x_{b, c} - x_{a, c} x_{b, d} + x_{a, b} x_{c, d})
-    \end{equation*}
-    and so for $(a, b, c, d) \neq (i, j, u, v), \epsilon' \in k^*$ have that
-    \begin{align*}
-        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, d} \ x_{b, c} \quad \text{or}\\
-        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, c} \ x_{b, d} \quad \text{or}\\
-        f_{i, j, u, v} \ x_{i, v} \ x_{j, u} &= \epsilon' f_{a, b, c, d} \ x_{a, b} \ x_{c, d}
-    \end{align*}
-    However, the second and third case imply that $f_{a, b, c, d} \ x_{a, d} \ x_{b, c} \succ f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$.
-    Hence, the ``new'' monomial $f_{a, b, c, d} \ x_{a, d} \ x_{b, c}$ also has to ``cancel out'' in the sum representation of $F$, as it is greater than $\mathrm{lt}(F) = \epsilon x_{i, u} \ x_{j, v} \ f_{i, j, u, v}$ in the order $\preceq$.
-    So applying the whole argument inductively (induction on the number of monomials $\succ f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$ that occur in any of the polynomials we work with), we end up in the first case
-    \footnote{There is a small argument missing here, namely that we apply the next argument on each step of the induction, to show the claim for $f_{i, j, u, v} \ x_{i, v} \ x_{j, u}$.
-However, it should be easy to see that this is possible.}.
-
-    If $(a, d) = (i, v)$ then $(b, c) \neq (j, u)$ and $x_{b, c} \divides f_{i, j, u, v}$.
-    Thus
-    \begin{equation*}
-        x_{b, c} \ x_{i, u} \ x_{j, v} \divides \mathrm{lt}(F) = \epsilon \ x_{i, u} \ x_{j, v} \ f_{i, j, u, v}
-    \end{equation*}
-    with $i < j < u < v$ and $i < b < c < v$. 
-    No matter how $j, u, b, c$ are ordered relatively to each other, we see that in each possible case $x_{b, c} \ x_{i, u} \ x_{j, v} \in J$:
-    \begin{align*}
-        j < u < b < c \ &\Rightarrow \ x_{j, v} x_{b, c} \in J \\
-        j < b < u < c \ &\Rightarrow \ x_{j, v} x_{b, c} \in J \\
-        j < b < c < u \ &\Rightarrow \ x_{i, u} x_{b, c} \in J \\
-        b < j < u < c \ &\Rightarrow \ f_{i, b, c, v} \ x_{i, c} \ x_{b, v} \succ f_{i, j, u, v} \ x_{i, u} \ x_{j, v}, \ \contradiction \\
-        b < j < c < u \ &\Rightarrow \ x_{i, u} x_{b, c} \in J \\
-        b < c < j < u \ &\Rightarrow \ x_{i, u} x_{b, c} \in J \\
-    \end{align*}
-    Hence $\mathrm{lt}(F) \in J$.
-
-    It is now left to consider the case $(b, c) = (j, u)$ and the case $(a, d) \neq (i, v), (b, c) \neq (j, u)$.
-    The former can be dealt with in exactly the same way, by noting that $x_{a, d} \divides f_{i, j, u, v}$.
-    In the latter case, we even find $x_{a, d} \ x_{b, c} \divides f_{i, j, u, v}$ and a very similar argument works.
-
-    Finally, one must also consider the third ``big'' case, namely that
-    \begin{equation*}
-        \mathrm{lt}(F) = \epsilon \ x_{i, j} \ x_{u, v} \ f_{i, j, u, v} 
-    \end{equation*}
-    Again, you can do this similarly as before, but now two monomials ``cancel out''.
-    We will not present this here as well.
-\end{proof}
-
+Now we have to study the structure of monomials generating $J = \langle x_{i, v} x_{j, u} \ | \ i < j < u < v \rangle$.
+At first glance, this seemed to me to be much simpler than the above, but in fact it turns out not to be, as there is some subtle combinatorial structure involved.
+Hence, we will first introduce the combinatorial framework in which we will work now.
 \begin{definition}
@@
 \end{definition}
-
+It might be possible to see from the definition how independent sets in this graph are connected to monomials in $J$.
+If not, the connection is explained in the proof of the next theorem.
 \begin{proposition}
@@
 which then shows the degree formula for the case $d = 2$.
-However, this is not a lecture on graph theory or combinatorics, and I already spent a lot of hours on this problem (and there are other mini projects as well :)).
+However, this is not a lecture on graph theory or combinatorics, and I already spent much more time on this Miniproject than on the others.
 So I will not do the proof here, but I think it is already very interesting to see those graphs and the connection of $\deg(\Gr(2, n))$ to combinatorial problems.

### 2021-12-14 Combinatorics/submission.tex
added rust syntax highlighting to combinatorics
Fixed alg geo, hopefully finally

@@
 \usepackage{listings}
+\usepackage{listings-rust}
 \usepackage[style=english]{csquotes}
@@
 \section{Part I}
-
+First of all, we introduce the notion of a rank function on a graded poset.
 \begin{proposition}
@@
     \end{equation*}
-    is well-defined and the unique function with $x < y$ implies $r(x) < r(y)$ for all $x, y \in P$.
+    is well-defined and the unique function such that $x < y$ implies $r(x) < r(y)$ for all $x, y \in P$.
     We call it the \emph{rank function} of $P$.
@@
     Hence we find $r(b_i) < r(b_{i + 1})$ and so inductively that $r(b_i) \geq i - 1$ and $r(b_i) \leq i - 1$ since $r(b_1) \geq 0$ and $r(b_{n + 1}) \leq n$.
-    It follows that $r(b_i) = i - 1$ and so $x = b_{r(x) + 1}, y = {r(y) + 1}$.
+    It follows that $r(b_i) = i - 1$ and so $x = b_{r(x) + 1}, y = b_{r(y) + 1}$.
     Therefore, we have a chain
@@
 \section{Part II}
+In this part, we want to study whether graded posets satisfy an analogue of the LYM inequality.
 \begin{proposition}
@@
     \paragraph{(ii) $\Rightarrow$ (iii)} Use induction on $n$.
-    Again, the base case is trivial, just take chains $\{x\}$ for each $x \in A = L_0$.
+    The base case is trivial, just take chains $\{x\}$ for each $x \in A = L_0$.
     So assume that $n > 0$. The set
@@
     by induction hypothesis.
-    Let now $V_1, V_2 := [t] \times L_n$ (treat them as disjoint) and consider the bipartite graph $G := (V_1 \sqcup V_2, E)$ where $E$ is defined as follows:
+    Let now $V_1 := \{1\} \times [t] \times L_n$ and $V_2 := \{2\} \times [t] \times L_n$ and consider the bipartite graph $G := (V_1 \sqcup V_2, E)$ where $E$ is defined as follows:
     \begin{equation*}
-        \{ \underbrace{(i, a)}_{\in V_1}, \underbrace{(j, b)}_{\in V_2} \} \in E \ \Leftrightarrow \ \max C_j < a
+        \{ \underbrace{(1, i, a)}_{\in V_1}, \underbrace{(2, j, b)}_{\in V_2} \} \in E \ \Leftrightarrow \ \max C_j < a
     \end{equation*}
-    We use Hall's theorem to show that $G$ has a perfect matching.
+    We use Hall's theorem to show that $G$ has a matching.
 
-    Consider any $W = \{ (i_1, a_1), ..., (i_w, a_w) \} \subseteq V_1$ and let $F = \{ a_1, ..., a_w \}$.
+    Consider any $W = \{ (1, i_1, a_1), ..., (1, i_w, a_w) \} \subseteq V_1$ and let $F = \{ a_1, ..., a_w \}$.
     Then
@@
     \begin{align*}
-        N(W) =& \{ (j, b) \ | \ b \in L_n, \exists a \in F: \max C_j < a \} \\
-        =& L_n \times \{ j \ | \ \exists a \in F: \max C_j < a \} \\
-        =& L_n \times \{ j \ | \ \max C_j \in \partial F \}
+        N(W) =& \{ (2, j, b) \ | \ b \in L_n, \exists a \in F: \max C_j < a \} \\
+        =& \{2\} \times \{ j \ | \ \exists a \in F: \max C_j < a \} \times L_n \\
+        =& \{2\} \times \{ j \ | \ \max C_j \in \partial F \} \times L_n
     \end{align*}
@@
     \end{equation*}
-    So Hall's theorem yields a perfect matching $M \subseteq E$ from $V_1$ to $V_2$.
+    So Hall's theorem yields a matching $M \subseteq E$ from $V_1$ to $V_2$.
     As $|V_1| = |V_2|$, this is already a 1-to-one correspondence.
@@
     \begin{equation*}
-        C'_m := C_j \cup \{ a \} \ \text{where} \ m = \{\underbrace{(i, a)}_{\in V_1}, \underbrace{(j, b)}_{\in V_2}\} \in M
+        C'_m := C_j \cup \{ a \} \ \text{where} \ m = \{\underbrace{(1, i, a)}_{\in V_1}, \underbrace{(2, j, b)}_{\in V_2}\} \in E
     \end{equation*}
@@
 After all dependencies are present, the following code will yield the result.
-\lstinputlisting{./src/main.rs}
+\lstinputlisting[language = rust]{./src/main.rs}
 

### 2021-12-14 Combinatorics/submission.tex
Added literature search results to combinatorics

@@
     \begin{equation*}
-        C'_m := C_j \cup \{ a \} \ \text{where} \ m = \{\underbrace{(1, i, a)}_{\in V_1}, \underbrace{(2, j, b)}_{\in V_2}\} \in E
+        C'_m := C_j \cup \{ a \} \ \text{for each} \ m = \{\underbrace{(1, i, a)}_{\in V_1}, \underbrace{(2, j, b)}_{\in V_2}\} \in M
     \end{equation*}
@@
     \begin{equation*}
-        |\{ C'_m \ | \ x \in C'_m \}| = |L_n \times \{ j \ | \ x \in C_j \}| = |L_n \times \{ j \ | \ y \in C_j \}| = |\{ C'_m \ | \ y \in C'_m \}|
+        |\{ m \ | \ x \in C'_m \}| = |L_n \times \{ j \ | \ x \in C_j \}| = |L_n \times \{ j \ | \ y \in C_j \}| = |\{ C'_m \ | \ y \in C'_m \}|
     \end{equation*}
@@
 \section{Part III}
-We even show the slightly stronger stronger statement that the implication to the second condition of Prop.\ref{prop:characterization_lym} already holds ``locally'', i.e. for each layer separately.
+In this part, we show that sufficiently symmetric posets satisfy the conditions introduced in the previous part.
+We even show a slightly stronger stronger statement than required in the task, namely that the implication to the second condition of Prop.\ref{prop:characterization_lym} already holds ``locally'', i.e.
+for each layer separately.
 \begin{proposition}
@@
 \begin{example}
-    Let $\Pi_m = \{ \pi \subseteq \powerset(n) \ | \ \text{$\pi$ partition} \}$ be the poset of partitions ordered by refinement.
+    Let $\Pi_m = \{ \pi \subseteq \powerset(m) \ | \ \text{$\pi$ partition} \}$ be the poset of partitions ordered by refinement.
     Then $\Pi_m$ is a graded poset with rank function
     \begin{equation*}
-        r: \Pi_m \to \{ 0, ..., n - 1 \}, \quad \pi \mapsto n - |\pi|
+        r: \Pi_m \to \{ 0, ..., m - 1 \}, \quad \pi \mapsto m - |\pi|
     \end{equation*}
@@
 
-    Now assume there is a maximal chain $\pi_1 < ... < \pi_t$ in $\Pi_m$.
-    As the chain is maximal and $\Pi_m$ has the largest element $[n]$, we may assume that $\pi_t = [n]$ and thus $r(\pi_t) = n - 1$.
-    Similarly, we may assume that $p_1 = \powerset(n)$ and so $r(\pi_1) = 0$.
-    We have to show that $t = n$, and so it suffices to show that $r(\pi_i) = 1 + r(\pi_{i - 1})$ for all $0 < i \leq t$.
+    Now assume there is a maximal chain $\pi_1 < ... < \pi_t$ in $\Pi_m$, and want to show that $t = m$.
+    As the chain is maximal and $\Pi_m$ has the largest element $[m]$, we may assume that $\pi_t = [m]$ and thus $r(\pi_t) = m - 1$.
+    Similarly, we may assume that $p_1 = \{ \{a\} \ | \ a \in [m]\}$ and so $r(\pi_1) = 0$.
+    So it suffices to show that $r(\pi_i) = 1 + r(\pi_{i - 1})$ for all $0 < i \leq t$.
 
@@
     \begin{align*}
-        \frac {|\partial \mathcal{A}|} {|L_{n - 3}|} &= \frac {{m \choose m/2}\left( 2^{m/2 - 1} - 1\right)} {S(m, 3)} = \frac {{m \choose m/2}\left( 2^{m/2 - 1} - 1\right)} {\frac 1 2 \left( 3^{m - 1} - 2^m + 1 \right)} \\
-        &\quad \sim \frac {2^{m + m/2}} {\sqrt{n}(3^{m - 1} - 2^m)} \sim \frac {3 \left( 2^{3/2} \right)^m} {\sqrt{n} 3^m} = \frac 3 {\sqrt{n}} c^m
+        \frac {|\partial \mathcal{A}|} {|L_{m - 3}|} &= \frac {{m \choose m/2}\left( 2^{m/2 - 1} - 1\right)} {S(m, 3)} = \frac {{m \choose m/2}\left( 2^{m/2 - 1} - 1\right)} {\frac 1 2 \left( 3^{m - 1} - 2^m + 1 \right)} \\
+        &\quad \sim \frac {2^{m + m/2}} {\sqrt{m}(3^{m - 1} - 2^m)} \sim \frac {3 \left( 2^{3/2} \right)^m} {\sqrt{m} 3^m} = \frac 3 {\sqrt{m}} c^m
     \end{align*}
@@
     \begin{align*}
-        \frac {|\mathcal{A}|} {|L_{n - 2}|} &= \frac {\frac 1 2 {m \choose m/2}} {S(m, 2)} = \frac {{m \choose m/2}} {2^m - 2} \sim \frac {2^m} {\sqrt{n}2^m} = \frac 1 {\sqrt{n}}
+        \frac {|\mathcal{A}|} {|L_{m - 2}|} &= \frac {\frac 1 2 {m \choose m/2}} {S(m, 2)} = \frac {{m \choose m/2}} {2^m - 2} \sim \frac {2^m} {\sqrt{m}2^m} = \frac 1 {\sqrt{m}}
     \end{align*}
     for some $0 < c < 1$ (here $\sim$ means asymptotically equivalent as $m \to \infty$).
-    In particular, find for sufficiently large $m$ that
+    In particular, find for all $\epsilon > 0$ and sufficiently large $m$ that
     \begin{equation*}
-        \frac {|\partial \mathcal{A}|} {|L_{n - 3}|} < \frac {|\mathcal{A}|} {|L_{n - 2}|}
+        \frac {|\partial \mathcal{A}|} {|L_{m - 3}|} < \epsilon \frac {|\mathcal{A}|} {|L_{m - 2}|}
     \end{equation*}
@@
     By induction hypothesis, have a symmetric chain decomposition $\mathcal{C}$ of $\mathcal{P}_{k, d - 1}$.
-    For some $C = \{ A_i, A_{i + 1}, ..., A_{d(k - 1) - i} \} \in \mathcal{C}, i < \frac n 2$ with $r(A_j) = j$ and $0 \leq l \leq k, n - 2i - 1$ consider now the chain
+    Now consider some $C = \{ A_i, A_{i + 1}, ..., A_{d(k - 1) - i} \} \in \mathcal{C}, i < \frac n 2$ with $r(A_j) = j$.
+    For each $0 \leq l \leq k, n - 2i - 1$ define the chain
     \begin{equation*}
-        \tilde{C}_l := \{ (A_{i + l}, j) \ | \ 0 \leq j \leq k - l \} \cup \{ (A_j, k - l) \ | \ i + l < j \leq d(k - 1) - (i + l) \}
+        \tilde{C}_l := \{ \underbrace{(A_{i + l}, j)}_{\mathclap{:= (a_1, ..., a_{d - 1}, j) \ \text{if} \ A_{i + l} = (a_1, ..., a_{d - 1})}} \ | \ 0 \leq j \leq k - l \} \cup \{ (A_j, k - l) \ | \ i + l < j \leq d(k - 1) - (i + l) \}
     \end{equation*}
@@
     Now consider a (finite) sequence of maximal chains $(C_k)_{k \in I}$ such that the chain corresponding to $u_i < v_j$ occurs $a_{ij} |I|$ times.
-    By the assumption, we know that for each $i$
+    By the assumption, we know that for each $i$ have
     \begin{equation*}
@@
 
-My successful-looking attempt is based on the observation that elements of $\mathcal{P}_{k, d}$ ``behave similarly'' (in the sense that there is an element of the automorphism group $\mathrm{Aut}(\mathcal{P}_{k, d})$ mapping one to the other) if the have the same number of equally sized entries.
-This looks promising, as the proof for $\powerset(n)$ and equivalently the proof of Prop.~\ref{prop:biregular_implies_lym} relies on the fact that all elements in one layer of $\powerset(n)$ ``behave similarly'' in this sense.
+My successful-looking attempt at proving this is based on the observation that elements of $\mathcal{P}_{k, d}$ ``behave similarly'' (in the sense that there is an element of the automorphism group $\mathrm{Aut}(\mathcal{P}_{k, d})$ mapping one to the other) if the have the same number of equally sized entries.
+This looks promising, as the proof for $\powerset(n)$ relies on the fact that all elements in one layer of $\powerset(n)$ ``behave similarly'' in this sense.
+In particular, note that Prop.~\ref{prop:biregular_implies_lym} would already be applicable in such a case.
 
@@
     \begin{equation*}
-        P(n_0, ..., n_k) := \{ x \in P \ | \ |\{i \ | \ x(i) = j\}| = n_j \}
+        P(n_0, ..., n_k) := \bigl\{ x \in P \ \bigm| \ |\{i \ | \ x(i) = j\}| = n_j \bigl\}
     \end{equation*}
@@
     \begin{equation*}
-        |P(n_0, ..., n_k)| = { d \choose n_0, ..., n_k } =  \frac {n!} {n_0! ... n_k!}
+        |P(n_0, ..., n_k)| = { d \choose n_0, ..., n_k } =  \frac {d!} {n_0! ... n_k!}
     \end{equation*}
-    if $n_0 + ... + n_k = d$ (otherwise, it is clearly zero).
+    if $n_0 + ... + n_k = d$ and $n_i \geq 0$ (otherwise, it is clearly zero).
 
@@
 \end{lemma}
+\begin{proof}
+    For $n_0 + ... + n_k = d$ and $n_i \geq 0$ we have
+    \begin{align*}
+        &|P(n_0, ..., n_k)| = |\bigl\{ x \in P \ \bigm| \ |\{i \ | \ x(i) = j\}| = n_j\bigl\}| \\
+        =& \sum_{A_0 \in [d]^{(n_0)}} |\bigl\{ x \in \{0, ..., k\}^{[d] \setminus A_0} \ \bigm| \ |\{i \ | \ x(i) = j\}| = n_j\bigl\}| \\
+        =& \sum_{A_0 \in [d]^{(n_0)}} \sum_{A_1 \in ([d] \setminus A_0)^{(n_1)}} |\bigl\{ x \in \{0, ..., k\}^{[d] \setminus A_0 \setminus A_1} \ \bigm| \ |\{i \ | \ x(i) = j\}| = n_j\bigl\}| \\
+        =& \ ... \\
+        =& \sum_{A_0 \in [d]^{(n_0)}} ... \sum_{A_k \in ([d] \setminus A_0 \setminus ... \setminus A_{k - 1})^{(n_k)}} 1 \\
+        =& \sum_{A_0 \in [d]^{(n_0)}} ... \sum_{A_{k - 1} \in ([d] \setminus A_0 \setminus ... \setminus A_{k - 2})^{(n_k)}} {d - n_0 - ... - n_{k - 1} \choose n_k} \\
+        =& \ ... \\
+        =& {d \choose n_0} {d - n_0 \choose n_1} ... {d - n_0 - ... - n_{k - 1} \choose n_k} = \prod_i \frac {(d - n_0 - ... - n_{i - 1})!} {n_i! (d - n_0 - ... - n_i!)} \\
+        =& \frac {d!} {n_0! ... n_k!} \prod_i \frac {(d - n_0 - ... - n_i)!} {(d - n_0 - ... - n_i)!} = \frac {d!} {n_0! ... n_k!}
+    \end{align*}
+    Further have for all $n_0 + ... + n_k = d$ and $a \in P(n_0, ..., n_k)$ that there is a bijection
+    \begin{align*}
+        \{ i \in [d] \ | \ a(i) = \delta + 1 \} &\to \partial a \cap P(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k), \\
+        i &\mapsto f_{a, i}: j \mapsto \begin{cases}
+            a(j) & \text{if $j \neq i$} \\
+            a(j) - 1 & \text{otherwise}
+        \end{cases}
+    \end{align*}
+    It is easy to see that the image of some $i$ is indeed an element of $\partial a$ and of $P(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k)$.
+    Clearly the function is also injective, and surjectivity can be shown by considering some $b \in \partial a \cap P(n_0, ..., n_\delta + 1, n_{\delta + 1} - 1, ..., n_k)$ and showing by induction that
+    \begin{equation*}
+        \{ i \ | \ b(i) = j \} = \{ i \ | \ a(i) = j \}
+    \end{equation*}
+    for all $j \neq \delta, \delta + 1$.
+    Note that the set $\{ i \in [d] \ | \ a(i) = \delta + 1 \}$ has size exactly $n_{\delta + 1}$ and so the claim follows.
+
+    The analogue statement for the upper shadow of $a$ can be proven in the same way.
+\end{proof}
 \begin{definition}
@@
     \end{equation*}
-    that preserves the ordering and the fiber of a point $(n_0, ..., n_k)$ is exactly $P(n_0, ..., n_k)$.
+    that preserves the ordering and the fibre of a point $(n_0, ..., n_k)$ is exactly $P(n_0, ..., n_k)$.
 \end{lemma}
+\begin{proof}
+    All of these statements are very easy to check.
+\end{proof}
 
@@
 
+After quite a long time trying to prove that $\mathcal{P}_{k, d}$ satisfies an LYM-inequality analogue, I finally gave up and searched the literature.
+There I found that $\mathcal{P}_{k, d}$ is also called divisor lattice and indeed we have the following statement.
+\begin{proposition}
+    $\mathcal{P}_{k, d}$ satisfies the conditions of Prop.~\ref{prop:characterization_lym}, i.e. an LYM-inequality.
+\end{proposition}
+\begin{proof}
+    See e.g. \cite[Theorem 4.2.3]{anderson}.
+\end{proof}
+Interestingly, I have also found a variant of the LYM inequality for the poset $\Pi_m$ that we studied earlier.
+\begin{proposition}
+    Let $\mathcal{A} \subseteq \Pi_m$ be a nonempty antichain. Then define
+    \begin{equation*}
+        a_{n_1, ..., n_k} := |\bigl\{ A \in \mathcal{A} \ \bigm| \ |A| = k, \ |\{ S \in A \ | \ |S| = j \}| = n_j \bigr\}|
+    \end{equation*}
+    the number of partitions $A \in \mathcal{A}$ such that the classes in $A$ have sizes $n_1, ..., n_k$.
+    Then
+    \begin{equation*}
+        \sum_{k \geq 1} \sum_{n_1, ..., n_k} \frac {a_{n_1, ..., n_k} k!} {{m \choose n_1, ..., n_k} {m - 1 \choose k - 1}} \leq 1
+    \end{equation*}
+\end{proposition}
+\begin{proof}
+    See \cite{lym_partitions}.
+\end{proof}
+
 \section{Appendix (Code described in Part VI)}

### 2021-12-15 Combinatorics/submission.tex
Added final thoughts to combinatorics

@@
     \begin{equation*}
-        \Pr[ (n_0, ..., n_k) \in C' ] = \frac {|P(n_0, ..., n_k)|} {|L_{\sum_i i n_i}|}
+        \Pr[ (n_0, ..., n_k) \in C' ] = \frac {|P(n_0, ..., n_k)|} {|L_{r(n_0, ..., n_k)}|}
     \end{equation*}
@@
     for $A, B \in \mathcal{C}(P)$.
+    Note that then $\mathcal{C}(P)$ is a graded poset.
 
@@
 \begin{proof}
-    Exactly as above.
+    Exactly as in Prop.~\ref{prop:core_of_multisets}.
 \end{proof}
@@
 
-After quite a long time trying to prove that $\mathcal{P}_{k, d}$ satisfies an LYM-inequality analogue, I finally gave up and searched the literature.
+After quite a long time trying to prove that this holds generally, I finally gave up and searched the literature.
 There I found that $\mathcal{P}_{k, d}$ is also called divisor lattice and indeed we have the following statement.
@@
 \end{proof}
-Interestingly, I have also found a variant of the LYM inequality for the poset $\Pi_m$ that we studied earlier.
+Interestingly, I have also found a variant of the LYM inequality (``pseudo-LYM inequality'') for the poset $\Pi_m$ that we studied earlier.
 \begin{proposition}
@@
     \begin{equation*}
-        a_{n_1, ..., n_k} := |\bigl\{ A \in \mathcal{A} \ \bigm| \ |A| = k, \ |\{ S \in A \ | \ |S| = j \}| = n_j \bigr\}|
+        a(n_1, ..., n_k) := |\bigl\{ A \in \mathcal{A} \ \bigm| \ |A| = k, \ |\{ S \in A \ | \ |S| = j \}| = n_j \bigr\}|
     \end{equation*}
@@
     \begin{equation*}
-        \sum_{k \geq 1} \sum_{n_1, ..., n_k} \frac {a_{n_1, ..., n_k} k!} {{m \choose n_1, ..., n_k} {m - 1 \choose k - 1}} \leq 1
+        \sum_{k \geq 1} \sum_{n_1, ..., n_k} \frac {a(n_1, ..., n_k) k!} {{m \choose n_1, ..., n_k} {m - 1 \choose k - 1}} \leq 1
     \end{equation*}
@@
 \end{proof}
+Note that the total number of partitions $\pi$ such that the classes in $\pi$ have sizes $n_1, ..., n_k$ is given by an expression involving the multinomial coefficient, namely
+\begin{equation*}
+    |\bigl\{ \pi \in \Pi_m \ \bigm| \ |\pi| = k, |\{ S \in \pi \ | \ |S| = j\}| = n_j \bigr\}| = {m \choose n_1, ..., n_k} \underbrace{ \prod_i \frac 1 {|\{ j \ | \ n_j = i\}|!} }_{=: \gamma(n_1, ..., n_k)}
+\end{equation*}
+Intuitively, the reason is that there are $m!$ ways to order the elements $[m]$, and after splitting such a sequence in chunks of sizes $n_1, ..., n_k$, there are $n_1!
+\cdot ...
+\cdot n_k!$ ways to order the element within the chunks.
+Hence the multinomial coefficient
+\begin{equation*}
+    {m \choose n_1, ..., n_k}
+\end{equation*}
+gives the number of ways to distribute the elements of $[m]$ into ordered buckets of sizes $n_1, ..., n_k$.
+A partition corresponds to unordered buckets, i.e. swapping chunks of equal size does not change the partition.
+There are $1/\gamma(n_1, ..., n_k)$ ways to do so, and hence we get the expression mentioned above.
+
+Furthermore, the number $a(n_1, ..., n_k)$ and the underlying set do not depend on the order of $n_1, ..., n_k$.
+Hence, the partitions $A \in \mathcal{A}$ such that the classes of $A$ have sizes $n_1, ..., n_k$ might be counted multiple times.
+Note that the number of different orderings of $n_1, ..., n_k$ is given by $k!/\gamma(n_1, ..., n_k)$.
+Hence
+\begin{equation*}
+    \sum_{n_1, ..., n_k} \frac 1 {k!} {m \choose n_1, ..., n_k} = |L_{m - k}|
+\end{equation*}
+just counts all the partitions in one layer of $\Pi_m$.
+
+Now note also that
+\begin{equation*}
+    {m - 1 \choose k - 1}
+\end{equation*}
+is exactly the number of different sequences $n_1 \leq ... \leq n_k$ by the ``stars and bars'' method.
+Then one can see that the expression
+\begin{equation*}    
+    \sum_{k \geq 1} \sum_{n_1, ..., n_k} \frac {a(n_1, ..., n_k) k!} {{m \choose n_1, ..., n_k} {m - 1 \choose k - 1}} = \sum_{k \geq 1} \frac 1 {{m - 1 \choose k - 1}} \sum_{n_1, ..., n_k} \frac {a(n_1, ..., n_k)} {\frac 1 {k!} {m \choose n_1, ..., n_k}}
+\end{equation*}
+is very similar to the LYM inequality.
+The only difference is that elements elements corresponding to different class sizes $n_1, ..., n_k$ might receive slightly different weight, depending on how many duplicate $n_i$ occur in that sequence.
+
+Finally, there is still one interesting thought I had while thinking about the above inequality.
+Note that the decomposition
+\begin{equation*}
+    \Pi_m = \bigcup_{k \geq 1, \ n_1 \leq ... \leq n_k} \{ \pi \in \Pi_m \ | \ |\pi| = k, |\{ S \in \pi \ | \ |S| = j \}| = n_j \}
+\end{equation*}
+corresponds exactly to the core $\mathcal{C}(\Pi_m)$ of $\Pi_m$ as discussed above.
+In particular, the decomposition is exactly
+\begin{equation*}
+    \Pi_m = \bigcup \ \{ \mathrm{Aut}(\Pi_m).\pi \ | \ \pi \in \Pi_m \}
+\end{equation*}
 

### 2021-12-15 Analytic number theory/submission.tex
small fixed, mainly to ANT

@@
 For simplicity of notation we sometimes will identify a Dirichlet character and its group homomorphism if it is always clear which one is meant.
-\begin{example}[Ex (i)]
+\begin{example}[Question (i)]
     \label{ex:nontrivial_dirichlet_character_mod_4}
@@
 \begin{proof}
-    By Lemma~\ref{prop:characterization_dirichlet_character}, we know that $\chi$ corresponds to a group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$ such that $\chi(\N) = f((\Z/q\Z)^*) \cup \{ 0 \} \subseteq \C$ is a finite subset of $\C$.
+    By Lemma~\ref{prop:characterization_dirichlet_character}, we know that $\chi$ corresponds to a group homomorphism
+    \begin{equation*}
+        f: (\Z/q\Z)^\units \to \C^\units
+    \end{equation*}
+    such that $\chi(\N) = f((\Z/q\Z)^*) \cup \{ 0 \} \subseteq \C$ is a finite subset of $\C$.
     Hence, there is $C > 0$ with $|\chi(n)| \leq C$ for all $n \in \N$, and it follows that
     \begin{equation*}
-        \sum_{1 \leq n \leq X} \left| \chi(n) n^{-s} \right| \leq \sum_{1 \leq n \leq X} C \left| n^{-s} \right| \leq C \sum_{1 \leq n \leq X} n^{-1 - \epsilon} \leq C \sum_{n \geq 1} n^{-1 - \epsilon}
+        \sum_{1 \leq n \leq X} \left| \chi(n) n^{-s} \right| \leq \sum_{1 \leq n \leq X} C \left| n^{-s} \right| \leq C \sum_{1 \leq n \leq X} \left| n^{-s} \right|
     \end{equation*}
-    which is finite.
+    We know that the series
+    \begin{equation*}
+        \sum_{n \geq 1} n^{-s}
+    \end{equation*}
+    converges uniformly on $\Re(s) \geq 1 + \epsilon$ and so the claim follows.
 \end{proof}
@@
         =& \ O(qCX^{-s}) + 0 + O\Bigl( Cqs \sum_{X/q \leq n \leq Y/q} n^{-(1 + \epsilon)} \Bigr) \\
-        =& \ O(qCX^{-s}) + O\Bigl( Cqs \sum_{X/q \leq n} n^{-(1 + \epsilon)} \Bigr)
+        =& \ O(qCX^{-s}) + O\Bigl( Cqs \sum_{n \geq X/q} n^{-(1 + \epsilon)} \Bigr)
     \end{align*}
@@
 Applied to our example, we find
-\begin{example}[Ex (ii)]
+\begin{example}[Question (ii)]
     Let $f: \N \to \C$ be the Dirichlet character from Example~\ref{ex:nontrivial_dirichlet_character_mod_4} with corresponding group homomorphism $g: (\Z/4\Z)^\units \to \C$.
@@
 using Euler Products.
-\begin{example}[Ex (ii)]
+\begin{example}[Question (ii)]
     \label{ex:dirichlet_sum_over_primes}
@@
 \end{proof}
-\begin{corollary}[Ex (iii)]
+\begin{corollary}[Question (iii)]
     There are infinitely many primes $p$ with $p \equiv 3 \mod 4$.
@@
 \end{proof}
-For the case of primes $\equiv 1 \mod 4$, I have remembered the two-square theorem and its connection to primes in the ring $\Z[i]$ of Gaussian integers, and somehow my train of thoughts went into Algebraic Number Theory.
+For the case of primes $\equiv 1 \mod 4$, I have remembered Fermat's theorem on the sum of two squares and its connection to primes in the ring $\Z[i]$ of Gaussian integers, and somehow my train of thoughts went into Algebraic Number Theory.
 After some research, I have found an exercise in \cite[Chapter I, §10]{neukirch} that requires the reader to prove the following proposition.
@@
 The book also mentions that the general case can be proven by using L-series in algebraic number fields.
-\begin{corollary}[Ex (iii)]
+I am pretty sure that those are exactly the functions $L(\chi, s)$ that we defined above.
+\begin{corollary}[Question (iii)]
     There are infinitely many primes $p$ with $p \equiv 1 \mod 4$.
@@
 \end{proof}
-\begin{example}[Ex (iii)]
+\begin{example}[Question (iii)]
     Using a computer, we can also study the actual frequency of prime numbers $\equiv 1, 3 \mod 4$ among e.g. the first $10^8$ integers.
@@
 So for the whole section, assume that $q \geq 3$ is a prime.
-\begin{corollary}[Ex (i)]
+\begin{corollary}[Question (i)]
     \label{prop:dirichlet_character_image_group}
@@
 This correspondence also works in the other direction.
-\begin{corollary}[Ex (ii)]
+\begin{corollary}[Question (ii)]
     \label{prop:dirichlet_character_primitive_root}
@@
 \end{proof}
-Note that the endomorphism monoid $\mathrm{End}((\Z/q\Z)^\units)$ is not a group, except in the trivial case $q = 2$.
-The reason is that e.g. the trivial group homomorphism $r \mapsto 1$ is not surjective and thus not invertible.
+Note that the endomorphisms $\mathrm{End}((\Z/q\Z)^\units)$ form a ring w.r.t. pointwise multiplication and composition
+(this is the case for the endomorphisms of any abelian group).
+In particular, the endomorphisms and so the Dirichlet characters form a group w.r.t. pointwise multiplication.
 \begin{definition}
@@
 \end{definition}
-By Corollary~\ref{prop:dirichlet_character_primitive_root} each group endomorphism $f \in \mathrm{End}((\Z/q\Z)^\units)$ is determined by its value at a primitive root of unity $r \in (\Z/q\Z)^\units$, hence
+By Corollary~\ref{prop:dirichlet_character_image_group} each Dirichlet character resp.
+group endomorphism of $(\Z/q\Z)^\units$ is determined by its value at a primitive root of unity $r \in (\Z/q\Z)^\units$.
+Further, by Corollary~\ref{prop:dirichlet_character_primitive_root}, we also have a Dirichlet character resp. group endomorphism for each possible value at a primitive root of unity.
+Hence
 \begin{equation*}
@@
 Because of Lemma~\ref{prop:dirichlet_series_at_one} it might seem like a good idea to study in which cases the value $\sum_{x \in (\Z/q\Z)^\units} \chi(x)$ is zero.
-\begin{proposition}[Ex (iii)]
+\begin{proposition}[Question (iii)]
     \label{prop:finite_sums_characters}
@@
 
-    Consider a Dirichlet character $\chi \neq \chi_0$ given by $r \mapsto \xi$ for a $q$-th root of unity $\xi \neq 1$.
+    Consider a Dirichlet character $\chi \neq \chi_0$ given by $r \mapsto \xi$ for a primitive $q$-th root of unity $\xi \neq 1$.
     Then
@@
     \end{align*}
-    where $\omega \in \C$ is a primitive $q$-th root of unity and $r \in \Z$ is a primitive root modulo $q$.
+    where $\omega \in \C$ is any primitive $q$-th root of unity and $r \in \Z$ is a primitive root modulo $q$.
 
@@
 Using these basic results, we can now prove facts on the Dirichlet series of characters.
-\begin{proposition}[Ex (iv)]
+\begin{proposition}[Question (iv)]
     \label{prop:representation_mangoldt_series_congruent_a}
@@
 \end{proof}
-\begin{example}[Ex (v)]
+\begin{example}[Question (v)]
     \label{ex:nontrivial_dirichlet_characters_mod_5}
@@
 Let further $\chi$ be a Dirichlet character mod $q$.
-\begin{proposition}[Ex (i)]
+\begin{proposition}[Question (i)]
     \label{prop:logarithmic_derivative_L}
@@
 First of all, we consider $\chi_0$.
-\begin{proposition}[Ex (ii)]
+\begin{proposition}[Question (ii)]
     \label{prop:formula_trivial_L_series}
@@
 First, we will bound the value of the partial sums of a Dirichlet character.
-\begin{lemma}[Ex (iii)]
+\begin{lemma}[Question (iii)]
     \label{prop:bound_partsums_character}
@@
 Now we can show the analytic continuation of $L(s, \chi)$ to $\Re(s) > 0$.
-\begin{proposition}[Ex (iv)]
+\begin{proposition}[Question (iv)]
     Let $\chi \neq \chi_0$ be a Dirichlet character mod $q$.
@@
     \end{align*}
-    Further, the integral converges absolutely by Lemma~\ref{prop:bound_partsums_character}, and thus is holomorphic on $\Re(s) > 0$.
+    Further, the integral converges absolutely for $\Re(s) > 0$ and uniformly for $\Re(s) \geq \epsilon$ for all $\epsilon > 0$ by Lemma~\ref{prop:bound_partsums_character}.
+    Thus it is holomorphic on $\Re(s) > 0$.
 \end{proof}
-\begin{corollary}[Ex (iv)]
+\begin{corollary}[Question (iv)]
     \label{prop:logarithmic_derivative_L_bounded}
@@
     \end{equation*}
-    is a meromorphic function on $\Re(s) > 0$ with a simple poles at $1$ (and possibly other poles on $\Re(s) > 0$).
+    defined on $\Re(s) > 1$ has a meromorphic continuation to $\Re(s) > 0$ with a simple poles at $1$ (and possibly other poles on $\Re(s) > 0$), provided that $L(\chi, 1) \neq 0$ for all $\chi \in \mathrm{Dir}(q) \setminus \{ \chi_0 \}$.
 \end{lemma}
 \begin{proof}
-    By Prop.~\ref{prop:logarithmic_derivative_L}, we have for $\chi \in \mathrm{Dir}(q)$ that
+    By Prop.~\ref{prop:logarithmic_derivative_L}, we have for $\chi \in \mathrm{Dir}(q)$ and $\Re(s) > 1$ that
     \begin{equation*}
@@
     \end{equation*}
-    If $\chi \neq \chi_0$, then Corollary~\ref{prop:logarithmic_derivative_L_bounded} shows that this function has no pole at $s = 1$.
+    Hence
+    \begin{equation*}
+        \rho_a(s) := \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \frac {L(s, \chi)'} {L(s, \chi)}
+    \end{equation*}
+    for $\Re(s) > 1$ and the right-hand side is a meromorphic continuation of $\rho_a(s)$ to $\Re(s) > 0$.
+
+    If $\chi \neq \chi_0$, then Corollary~\ref{prop:logarithmic_derivative_L_bounded} shows that the function
+    \begin{equation*}
+        \frac {\overline{\chi(a)}} {q - 1} \cdot \frac {L(s, \chi)'} {L(s, \chi)}
+    \end{equation*}
+    has no pole at $s = 1$.
 
@@
     \begin{equation*}
-        \frac {\overline{\chi_0(a)}} {q - 1} \sum_{n \geq 1} \frac {\Lambda(n) \chi_0(n)} {n^s} = \frac {\overline{\chi_0(a)}} {q - 1} \frac {L(s, \chi_0)'} {L(s, \chi_0)}
+        \frac {\overline{\chi_0(a)}} {q - 1} \cdot \frac {L(s, \chi_0)'} {L(s, \chi_0)}
     \end{equation*}
@@
     \begin{equation*}
-        \rho_a(s) = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
+        \rho_a(s) = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {L(\chi, s)'} {L(\chi, s)}
     \end{equation*}
@@
 \end{proof}
-\begin{proposition}[Ex (v)]
+\begin{proposition}[Question (v)]
+    \label{prop:infinite_primes_congruent}
     Assume that $L(1, \chi) \neq 0$ for all $\chi \in \mathrm{Dir}(q) \setminus \{ \chi_0 \}$.
@@
 \end{proof}
-\begin{example}[Ex (vi)]
+\begin{example}[Question (vi)]
     For all the nontrivial Dirichlet characters $\chi_1, ..., \chi_4$ defined in Example~\ref{ex:nontrivial_dirichlet_characters_mod_5}, we have
@@
     Since $\chi_i$ is a nontrivial Dirichlet character, we see that $\Im(\omega) \neq 0$ and so $\Im(L(1, \chi_i)/\omega) \neq 0$, thus $L(1, \chi_i) \neq 0$.
+    The claim now follows by Prop.~\ref{prop:infinite_primes_congruent}.
 \end{proof}
-\begin{remark}[Ex (vii)]
+\begin{remark}[Question (vii)]
     TODO

### 2021-12-15 Combinatorics/submission.tex
small fixed, mainly to ANT

@@
     \begin{itemize}
-        \item Every element in $P(n_0, ..., n_k)$ is covered by $n_\delta$ elements
-        \item Every element in $P(n_0, ..., n_k)$ covers $n_{\delta + 1}$ elements
+        \item Every element in $P(n_0, ..., n_k)$ is covered by $n_\delta$ elements in $P'_i$
+        \item Every element in $P(n_0, ..., n_k)$ covers $n_{\delta + 1}$ elements in $P'_i$
     \end{itemize}
-    The $P(n_0, ..., n_k)$ are exactly the layers of the poset $P'_i := \bigcup_{c \in C'_i} P(c)$.
+    where $P'_i \subseteq P$ is the graded poset that is given by the preimage of $C'_i$ under the canonical map $\mathcal{P}_{k, d} \to \mathcal{C}_{k, d}$, i.e.
+    \begin{equation*}
+        P'_i := \bigcup_{c \in C'_i} P(c) = R^{-1}(C'_i)
+    \end{equation*}
+    The $P(n_0, ..., n_k)$ are exactly the layers of the poset $P'_i$.
     Hence Prop.~\ref{prop:biregular_implies_lym} yields that there is a sequence of maximal chains
@@
 Using a simple implementation of this approach, I could check that for some arbitrarily chosen values of $k, d$ up to $(k, d) = (8, 9)$, the poset $\mathcal{P}_{k, d}$ indeed satisfies the conditions of Prop.~\ref{prop:characterization_lym}.
+Note that for this choice of $k, d$ we already have that $|\mathcal{P}_{8, 9}| = 134217728$ which is absolutely infeasible for more naive approaches.
 

### 2021-12-16 Analytic number theory/submission.tex
Done my best to answer (vii) in ANT

@@
 \end{proof}
-The book also mentions that the general case can be proven by using L-series in algebraic number fields.
+In a later chapter, the book also proves the general result \cite[Chapter VII, Theorem 5.14]{neukirch}.
 I am pretty sure that those are exactly the functions $L(\chi, s)$ that we defined above.
@@
 \end{proof}
+Finally, we want to reflect on the general approach and highlight how we used of Dirichlet characters.
 \begin{remark}[Question (vii)]
-    TODO
+    Roughly speaking, both the approach used in the lecture and in this Miniproject consists of three steps.
+    \begin{itemize}
+        \item Relate the frequency of considered primes to the poles of a Dirichlet series, using partial summation or Perron's formula.
+
+        \item Express the above series as logarithmic derivative of a second function.
+        This then relates poles to zeros, by the properties of the Taylor series expansion of meromorphic functions.
+
+        \item Investigate the zeros of the second function.
+    \end{itemize}
+
+    It seems like the magic happens mostly in the second step.
+    The crucial part here is the connection between multiplicative arithmetic and Dirichlet series.
+    In particular, this gives us nice identities like the Euler product.
+    However, this will be completely destroyed when we consider functions that are not multiplicative at all.
+
+    More concretely, consider
+    \begin{equation*}
+        f: \N \to \C, \quad n \mapsto \begin{cases}
+            1 & \text{if $n \equiv a \mod q$} \\
+            0 & \text{otherwise}
+        \end{cases}
+    \end{equation*}
+    Note that this function is not multiplicative.
+    After applying the first step, we are interested in the poles of the meromorphic function
+    \begin{equation*}
+        \sum_{n \geq 1} f(n) \Lambda(n) n^{-s}
+    \end{equation*}
+    I will not prove this here, but via partial summation, we can find a meromorphic continuation to $\Re(s) > 0$.
+
+    However, here we get stuck.
+    It might seem natural to consider the function
+    \begin{equation*}
+        \zeta_a(s) := \sum_{n \geq 1} f(n) n^{-s}
+    \end{equation*}
+    which also has a meromorphic continuation to $\Re(s) > 0$.
+    Its derivative is clearly given by
+    \begin{equation*}
+        \zeta_a'(s) = \sum_{n \geq 1} f(n) \log(n) n^{-s}
+    \end{equation*}
+    To continue, we might try to consider
+    \begin{equation*}
+        \zeta_a'(s)\Bigl( \sum_{n \geq 1} \mu(n) f(n) n^{-s} \Bigr) = \sum_{n \geq 1} \frac {(f\log * f\mu)(n)} {n^s}
+    \end{equation*}
+    But since $f$ has no nice compatibility with multiplication or $*$, it is not easy to make something of this.
+    In particular
+    \begin{equation*}
+        f\Lambda \neq f\log * f\mu \quad \text{and} \quad \frac 1 {\zeta_a(s)} \neq \sum_{n \geq 1} f(n) \mu(n) n^{-s}
+    \end{equation*}
+    Note that we find $n \equiv a \mod q$ such that $n$ has no nontrivial factor $\equiv a \mod q$.
+    E.g. take $n = 9 \equiv 4 \mod 5$, then
+    \begin{equation*}
+        \log(3) = (f\Lambda)(6) \neq \sum_{cd = 9} f(c)\log(c)f(d)\mu(d) = 0
+    \end{equation*}
+    Furthermore, the equality
+    \begin{equation*}
+        \frac 1 {\zeta_a(s)} = \sum_{n \geq 1} f(n) \mu(n) n^{-s}
+    \end{equation*}
+    would imply
+    \begin{equation*}
+        1 = \zeta_a(s) \sum_{n \geq 1} f(n) \mu(n) n^{-s} = \sum_{n \geq 1} \frac {(f * f\mu)(n)} {n^s}
+    \end{equation*}
+    which in turns implies that $f * f\mu = \delta$.
+    However, we clearly find counterexamples for that, e.g. for $q = 5, a = 4$ find $(f * f\mu)(1) = 0$.
+    The underlying reason is that the divisors of $n$ may lie in a different congruence class modulo $q$ than $n$.
+
+    In some sense, this whole miniproject was just about using the decomposition
+    \begin{equation*}
+        f = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \chi
+    \end{equation*}
+    as then the Dirichlet series become Dirichlet series over $\chi$ instead of $f$, which is much better manageable.
 \end{remark}

### 2021-12-16 Analytic number theory/submission.tex
Improved display of mod in ANT

@@
 \begin{definition}
-    Let $q \geq 2$, then a \emph{Dirichlet character (mod $q$)} is a function $\chi: \N \to \C$ such that
+    Let $q \geq 2$, then a \emph{Dirichlet character (modulo $q$)} is a function $\chi: \N \to \C$ such that
     \begin{itemize}
@@
     \label{prop:characterization_dirichlet_character}
-    We have a one-to-one correspondence between Dirichlet characters mod $q$ and group homomorphisms $(\Z/q\Z)^\units \to \C^\units$ via
+    We have a one-to-one correspondence between Dirichlet characters modulo $q$ and group homomorphisms $(\Z/q\Z)^\units \to \C^\units$ via
     \begin{align*}
@@
 
-    Note that property (ii) and (iii) directly follow from the definition, as $\chi_f(n)$ only depends on the value of $n \mod q$.
+    Note that property (ii) and (iii) directly follow from the definition, as $\chi_f(n)$ only depends on the value of $n$ modulo $q$.
     So consider some $a, b \in \N$.
@@
         f: \N \to \C, \quad n \mapsto \begin{cases}
-            0 & \text{if $n \equiv 0, 2 \mod 4$} \\
-            1 & \text{if $n \equiv 1 \mod 4$} \\
-            -1 & \text{if $n \equiv 3 \mod 4$}
+            0 & \text{if $n \equiv 0, 2 \pmod 4$} \\
+            1 & \text{if $n \equiv 1 \pmod 4$} \\
+            -1 & \text{if $n \equiv 3 \pmod 4$}
         \end{cases}
@@
     \end{equation*}
-    (this is a group homomorphism, as $3^2 = 9 \equiv 1 \mod 4$)
+    (this is a group homomorphism, as $3^2 = 9 \equiv 1 \pmod 4$)
 \end{proof}
@@
     \label{prop:prime_factor_3_mod_4}
-    Let $n \equiv 3 \mod 4$. Then $n$ has a prime factor $p \equiv 3 \mod 4$.
+    Let $n \equiv 3 \pmod 4$. Then $n$ has a prime factor $p \equiv 3 \pmod 4$.
 \end{lemma}
@@
     Otherwise, have $n = ab$ with nontrivial divisors $a, b$.
-    However, $3 \equiv n$ is not a square modulo $4$, so find that $a \not\equiv b \mod 4$.
-    As both $a$ and $b$ must be odd, we see that either $a \equiv 3 \mod 4$ or $b \equiv 3 \mod 4$ and the claim follows by the induction hypothesis.
+    However, $3 \equiv n$ is not a square modulo $4$, so find that $a \not\equiv b \pmod 4$.
+    As both $a$ and $b$ must be odd, we see that either $a \equiv 3$ or $b \equiv 3 \pmod 4$ and the claim follows by the induction hypothesis.
 \end{proof}
 \begin{corollary}[Question (iii)]
-    There are infinitely many primes $p$ with $p \equiv 3 \mod 4$.
+    There are infinitely many primes $p$ with $p \equiv 3 \pmod 4$.
 \end{corollary}
@@
     \begin{equation*}
-        P \equiv 3^{2 \lceil \frac N 2 \rceil} \equiv 1^{\lceil \frac N 2 \rceil} = 1 \mod 4
+        P \equiv 3^{2 \lceil \frac N 2 \rceil} \equiv 1^{\lceil \frac N 2 \rceil} = 1 \pmod 4
     \end{equation*}
-    Thus, by Lemma~\ref{prop:prime_factor_3_mod_4}, $P + 2$ has a prime factor $q \equiv 3 \mod 4$.
+    Thus, by Lemma~\ref{prop:prime_factor_3_mod_4}, $P + 2$ has a prime factor $q \equiv 3 \pmod 4$.
     However, $q \neq p_i$ as $p_i \perp P + 2$ for all $i$ (if $p_i \divides P + 2$, then $p_i \divides P + 2 - P = 2$, a contradiction).
@@
 \end{proof}
-For the case of primes $\equiv 1 \mod 4$, I have remembered Fermat's theorem on the sum of two squares and its connection to primes in the ring $\Z[i]$ of Gaussian integers, and somehow my train of thoughts went into Algebraic Number Theory.
+For the case of primes $\equiv 1 \pmod 4$, I have remembered Fermat's theorem on the sum of two squares and its connection to primes in the ring $\Z[i]$ of Gaussian integers, and somehow my train of thoughts went into Algebraic Number Theory.
 After some research, I have found an exercise in \cite[Chapter I, §10]{neukirch} that requires the reader to prove the following proposition.
@@
     Let $q \geq 3$ be an integer.
-    Then there are infinitely many primes $p$ with $p \equiv 1 \mod q$.
+    Then there are infinitely many primes $p$ with $p \equiv 1 \pmod q$.
 \end{proposition}
@@
     Let further $\mathcal{O} \subseteq K$ be the ring of integral elements over $\Z$ in $K$.
-    The prime decomposition law for Dedekind ring extension \cite[Chapter I, Prop 8.3]{neukirch} tells us that for a prime $p$, the ideal $(p)$ is reducible in $\mathcal{O}$ if and only if $\Phi_q \mod p$ is reducible.
-    As $(\Z/p\Z)^\units$ is cyclic of order $p - 1$, this is the case if and only if $q \divides p - 1$, i.e. $p \equiv 1 \mod q$.
+    The prime decomposition law for Dedekind ring extension \cite[Chapter I, Prop 8.3]{neukirch} tells us that for a prime $p$, the ideal $(p)$ is reducible in $\mathcal{O}$ if and only if $\Phi_q$ is reducible modulo $p$.
+    As $(\Z/p\Z)^\units$ is cyclic of order $p - 1$, this is the case if and only if $q \divides p - 1$, i.e. $p \equiv 1 \pmod q$.
 
@@
 \begin{corollary}[Question (iii)]
-    There are infinitely many primes $p$ with $p \equiv 1 \mod 4$.
+    There are infinitely many primes $p$ with $p \equiv 1 \pmod 4$.
 \end{corollary}
@@
 \begin{example}[Question (iii)]
-    Using a computer, we can also study the actual frequency of prime numbers $\equiv 1, 3 \mod 4$ among e.g. the first $10^8$ integers.
+    Using a computer, we can also study the actual frequency of prime numbers $\equiv 1, 3 \pmod 4$ among e.g. the first $10^8$ integers.
     This seems to indicate that both numbers are asymptotically equal, which seems natural, given the result of Example~\ref{ex:dirichlet_sum_over_primes}.
-    For example, there are 332180 primes $\equiv 1 \mod 4$ and 332398 primes $\equiv 3 \mod 4$ smaller than $10^8$.
+    For example, there are 332180 primes $\equiv 1 \pmod 4$ and 332398 primes $\equiv 3$ smaller than $10^8$.
     To find these numbers, the following python code was used.
@@
         \sum_{\chi \in \mathrm{Dir}(q)} \chi(a) &= \begin{cases}
-            q - 1 & \text{if $a \equiv 1 \mod q$} \\
+            q - 1 & \text{if $a \equiv 1 \pmod q$} \\
             0 & \text{otherwise}
@@
         \sum_{\chi \in \mathrm{Dir}(q)} \chi(a)\overline{\chi(b)} = \begin{cases}
-            q - 1 & \text{if $a \equiv b \mod q$} \\
+            q - 1 & \text{if $a \equiv b \pmod q$} \\
             0 & \text{otherwise}
@@
     \end{equation*}
-    By using the earlier results on the structure of $\mathrm{Dir}(q)$ we see that for $a \equiv r^k \not\equiv 1 \mod q$, have
+    By using the earlier results on the structure of $\mathrm{Dir}(q)$ we see that for $a \equiv r^k \not\equiv 1 \pmod q$, have
     \begin{align*}
@@
     \end{equation*}
-    The condition $ab^{-1} = 1$ is equivalent to $a \equiv b \mod q$, so the claim follows.
+    The condition $ab^{-1} = 1$ is equivalent to $a \equiv b \pmod q$, so the claim follows.
 \end{proof}
@@
     \begin{equation*}
-        \sum_{n \equiv a \mod q} \frac {\Lambda(n)} {n^s} = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
+        \sum_{n \equiv a \ (\text{mod} \ q)} \frac {\Lambda(n)} {n^s} = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {\Lambda(n) \chi(n)} {n^s}
     \end{equation*}
@@
         \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \chi(n) = \begin{cases}
-            1 & \text{if $a \equiv n \mod q$} \\
+            1 & \text{if $a \equiv n \pmod q$} \\
             0 & \text{otherwise}
@@
     \begin{align*}
-        \sum_{n \equiv a \mod q} \Lambda(n) n^{-s} =& \sum_{n \geq 1} \Lambda(n) n^{-s} \begin{cases}
-            1 & \text{if $a \equiv n \mod q$} \\
+        \sum_{n \equiv a \ (\text{mod} \ q)} \Lambda(n) n^{-s} =& \sum_{n \geq 1} \Lambda(n) n^{-s} \begin{cases}
+            1 & \text{if $a \equiv n \pmod q$} \\
             0 & \text{otherwise}
@@
     A (primitive) 5-th root of unity $\omega_5 \in \C$ is given by $\omega_5 = \exp(2\pi i/5)$.
-    On the other hand, a primitive root modulo 5 is e.g. given by $r = 2$ since $2^2 \equiv -1 \mod 5$.
+    On the other hand, a primitive root modulo 5 is e.g. given by $r = 2$ since $2^2 \equiv -1 \pmod 5$.
     Thus we have the trivial Dirichlet character $\chi_0$ and $5 - 1 = 4$ nontrivial Dirichlet characters mod 5, namely those given by
@@
     \begin{equation*}
-        \Psi_a(x) := \sum_{n < x, \ n \equiv a \mod q} \Lambda(n)
+        \Psi_a(x) := \sum_{n < x, \ n \equiv a \ (\text{mod} \ q)} \Lambda(n)
     \end{equation*}
@@
     \begin{equation*}
-        \theta_a(x) := \sum_{p < x, \ p \equiv a \mod q} \log(p)
+        \theta_a(x) := \sum_{p < x, \ p \equiv a \ (\text{mod} \ q)} \log(p)
     \end{equation*}
@@
     \begin{align*}
-        \Psi_a(x) - \theta_a(x) =& \sum_{p^k < x, \ p^k \equiv a \mod q} \log(p) - \sum_{p < x, \ p \equiv a \mod q} \log(p) \\
-        =& \sum_{p^k < x, \ k \geq 2, \ p^k \equiv a \mod q} \log(p) \leq \sum_{p^k < x, \ k \geq 2} \log(p) \\
+        \Psi_a(x) - \theta_a(x) =& \sum_{p^k < x, \ p^k \equiv a \ (\text{mod} \ q)} \log(p) - \sum_{p < x, \ p \equiv a \ (\text{mod} \ q)} \log(p) \\
+        =& \sum_{p^k < x, \ k \geq 2, \ p^k \equiv a \ (\text{mod} \ q)} \log(p) \leq \sum_{p^k < x, \ k \geq 2} \log(p) \\
         =& \Psi(x) - \theta(x) = O(x^{1/2}\log(x))
@@
     Assume that $L(1, \chi) \neq 0$ for all $\chi \in \mathrm{Dir}(q) \setminus \{ \chi_0 \}$.
-    Then for all $a \perp q$ there are infinitely many primes $p \equiv a \mod q$.
+    Then for all $a \perp q$ there are infinitely many primes $p \equiv a \pmod q$.
 \end{proposition}
@@
     \begin{equation*}
-        \rho_a(s) = \sum_{n \equiv a \mod q} \Lambda(n) n^{-s}
+        \rho_a(s) = \sum_{n \equiv a \ (\text{mod} \ q)} \Lambda(n) n^{-s}
     \end{equation*}
@@
     \begin{align*}
-        \rho_a(s) =& \sum_{n \equiv a \mod q} \Lambda(n) n^{-s} \\
-        =& \lim_{t \to \infty} \Bigl( \underbrace{ t^{-s} \sum_{n < t, \ n \equiv a \mod q} \Lambda(n) }_{ = t^{-s} \Psi_a(t) = t^{-s} O(t\log t) = o(1)} \Bigr) 
-        + s \int_1^\infty \Bigl( \underbrace{\sum_{n < t, \ n \equiv a \mod q} \Lambda(n) }_{ = \Psi_a(t)} \Bigr) t^{-(s + 1)} dt \\
+        \rho_a(s) =& \sum_{n \equiv a \ (\text{mod} \ q)} \Lambda(n) n^{-s} \\
+        =& \lim_{t \to \infty} \Bigl( \underbrace{ t^{-s} \sum_{n < t, \ n \equiv a \ (\text{mod} \ q)} \Lambda(n) }_{ = t^{-s} \Psi_a(t) = t^{-s} O(t\log t) = o(1)} \Bigr) 
+        + s \int_1^\infty \Bigl( \underbrace{\sum_{n < t, \ n \equiv a \ (\text{mod} \ q)} \Lambda(n) }_{ = \Psi_a(t)} \Bigr) t^{-(s + 1)} dt \\
         =& s \int_1^\infty \Psi_a(t) t^{-s - 1} dt = s \int_1^\infty O(t^{1/2}\log t) t^{-s - 1} dt \\
@@
     \end{equation*}
-    It follows that there are infinitely many primes $\equiv a \mod 5$, for all $a \perp 5$.
+    It follows that there are infinitely many primes $\equiv a \pmod 5$, for all $a \perp 5$.
 \end{example}
@@
         f: \N \to \C, \quad n \mapsto \begin{cases}
-            1 & \text{if $n \equiv a \mod q$} \\
+            1 & \text{if $n \equiv a \pmod q$} \\
             0 & \text{otherwise}
@@
     \end{equation*}
-    Note that we find $n \equiv a \mod q$ such that $n$ has no nontrivial factor $\equiv a \mod q$.
-    E.g. take $n = 9 \equiv 4 \mod 5$, then
+    Note that we find $n \equiv a \pmod q$ such that $n$ has no nontrivial factor $\equiv a \pmod q$.
+    E.g. take $n = 9 \equiv 4 \pmod 5$, then
     \begin{equation*}

### 2021-12-18 Analytic number theory/submission.tex
Added P_k,d proof to combinatorics

@@
     \end{equation*}
-    I will not prove this here, but via partial summation, we can find a meromorphic continuation to $\Re(s) > 0$.
-
     However, here we get stuck.
@@
     \end{equation*}
-    which also has a meromorphic continuation to $\Re(s) > 0$.
+    which has a meromorphic continuation to $\Re(s) > 0$ (I will not prove this here).
     Its derivative is clearly given by

### 2021-12-18 Combinatorics/submission.tex
Added P_k,d proof to combinatorics

@@
 \begin{proof}
-    See e.g. \cite[Theorem 4.2.3]{anderson}.
+    The proof is similar to \cite[Theorem 4.2.3]{anderson}.
+    However, I really like the proof and so we present it here in a somewhat modified form.
+
+    We show condition (2) of Prop.~\ref{prop:characterization_lym}, so consider some pair of consecutive layers $L_{i - 1}, L_i$.
+    Let further $F \subseteq L_i$. 
+    We want to show that
+    \begin{equation*}
+        |L_{i - 1} \times F| \leq |L_i \times \partial F|
+    \end{equation*}
+    Let now $P' := \{ 0, ..., 2k \}^d$ and note that we have the decompositions
+    \begin{align*}
+        L_{i - 1} \times F &= \bigcup_{M \in P', r(M) = 2i - 1} \{ (u, a) \in L_{i - 1} \times F \ | \ u + a = M \} \quad \text{and} \\
+        L_i \times \partial F &= \bigcup_{M \in P', r(M) = 2i - 1} \{ (v, b) \in L_i \times \partial F \ | \ v + b = M \}
+    \end{align*}
+    Hence it suffices to show that
+    \begin{equation*}
+        |\{ (u, a) \in L_{i - 1} \times F \ | \ u + a = M \}| \leq |\{ (v, b) \in L_i \times \partial F \ | \ v + b = M \}|
+    \end{equation*}
+    for each $M \in P', r(M) = 2i - 1$.
+
+    To do so, we show the following, stronger claim by induction.
 \end{proof}
+\begin{lemma}
+    Let $k_1, ..., k_d > 0$ and consider the poset
+    \begin{equation*}
+        P = \bigtimes_{i = 1}^d \{ 0, ..., k_d \}
+    \end{equation*}
+    Let further $M = (M_1, ..., M_d)$ with $M_i \leq 2k_i$ of rank $\sum_i M_i = 2l - 1$ and $F \subseteq L_l$ such that $M$ is an upper bound for $F$.
+    Then
+    \begin{equation*}
+        |\{ (u, a) \in L_{l - 1} \times F \ | \ u + a = M \}| \leq |\{ (v, b) \in L_l \times \partial F \ | \ v + b = M \}|
+    \end{equation*}
+\end{lemma}
+\begin{proof}
+    Use induction on $\sum_i k_i$. 
+    The base case is trivial, so assume $\sum_i k_i > 1$.
+
+    \paragraph{Case 1} If there exists $j$ such that $M_j < k_j$ then clearly
+    \begin{equation*}
+        F, \partial F \in P' := \{ 0, ..., k_1 \} \times ... \times \{ 0, ..., k_j - 1 \} \times ... \times \{ 0, ..., k_d \}
+    \end{equation*}
+    and also $u \in P'$ for all $u \in L_{l - 1}$ with $u + a = M$ for some $a \in F$.
+    Hence the induction hypothesis yields
+    \begin{equation*}
+        |\{ (u, a) \in L_{l - 1} \times F \ | \ u + a = M \}| \leq |\{ (v, b) \in L_l \times \partial F \ | \ v + b = M \}|
+    \end{equation*}
+
+    \paragraph{Case 2} If there exists $j$ such that $M_j > k_j \geq 1$, then consider
+    \begin{align*}
+        F' := &\{ a - e_j \ | \ a \in F, a(j) \neq 0 \} \in \\
+        &P' := \{ 0, ..., k_1 \} \times ... \times \{ 0, ..., k_j - 1 \} \times ... \times \{ 0, ..., k_d \}
+    \end{align*}
+    Clearly $M - 2e_j \geq (k_1, ..., k_j - 1, ..., k_d) \geq a - e_j$ for all $a \in F$, and so $M - 2e_j$ is an upper bound for $F'$.
+    By induction hypothesis, we now get that
+    \begin{equation*}
+        |\{ (u, a) \in L_{l - 2} \times F' \ | \ u + a = M - 2e_j \}| \leq |\{ (v, b) \in L_{l - 1} \times \partial F' \ | \ v + b = M - 2e_j \}|
+    \end{equation*}
+    However, observe that the map
+    \begin{align*}
+        \{ (u, a) \in L_{l - 2} \times F' \ | \ u + a = M - 2e_j \} &\to \{ (u, a) \in L_{l - 1} \times F \ | \ u + a = M \} \\
+        (u, a) &\mapsto (u + e_j, a + e_j)
+    \end{align*}
+    is a bijection.
+    The only nontrivial part is to see that it is surjective, so consider some $(u, a) \in L_{l - 1} \times F$ with $u + a = M$.
+    Then $u(j), a(j) \leq k_j < M(j)$ and so $a(j) = M(j) - u(j) \geq 1$, hence $a - e_j \in F'$.
+    Clearly $u - e_j \in L_{l - 2}$ and $u - e_j + a - e_j = M - 2e_j$.
+    So $(u, a)$ has the preimage $(u - e_j, a - e_j)$.
+
+    Similarly, see that the map
+    \begin{align*}
+        \{ (u, a) \in L_{l - 1} \times \partial F' \ | \ u + a = M - 2e_j \} &\to \{ (u, a) \in L_l \times \partial F \ | \ u + a = M \} \\
+        (u, a) &\mapsto (u + e_j, a + e_j)
+    \end{align*}
+    is a bijection.
+    Thus
+    \begin{equation*}
+        |\{ (u, a) \in L_{l - 1} \times F \ | \ u + a = M \}| \leq |\{ (v, b) \in L_l \times \partial F \ | \ v + b = M \}|
+    \end{equation*}
+
+    \paragraph{Case 3} If $M = (k_1, ..., k_d)$, see that $2l - 1 = \sum_i k_i$ and so the layers $L_{l - 1}, L_l$ must be the two unique middle layers.
+    Now note that $|L_l| = |L_{l - 1}|$ and so it suffices to show that $|\partial F| \geq |F|$.
+    However, this follows directly by the symmetric chain decomposition of the poset $P$.
+    We have proven the symmetric chain decomposition only for $k_1 = ... = k_d$, but the general version can be found in \cite{anderson}.
+\end{proof}
+There are two parts I find interesting in this proof.
+\begin{itemize}
+    \item First of all, the idea to consider all $\bigtimes_i \{ 0, ..., k_i \}$ with possibly distinct $k_i$ makes it easy to use induction, as it suffices to decrease just one coordinate to use the induction hypothesis.
+    \item The decomposition
+    \begin{equation*}
+        L_{i - 1} \times F = \bigcup_{M \in P', r(M) = 2i - 1} \{ (u, a) \in L_{i - 1} \times F \ | \ u + a = M \}
+    \end{equation*}
+    is just very clever, as it really transforms the set of tuples $(u, a)$ into multiple sets that are more or less $\{ a \in F \ | \ a \leq M \}$ and much easier to handle.
+\end{itemize}
 Interestingly, I have also found a variant of the LYM inequality (``pseudo-LYM inequality'') for the poset $\Pi_m$ that we studied earlier.
@@
 \end{equation*}
-is exactly the number of different sequences $n_1 \leq ... \leq n_k$ by the ``stars and bars'' method.
+is exactly the number of different sequences $n_1 \leq ... \leq n_k$ summing to $m$ by the ``stars and bars'' method.
 Then one can see that the expression

### 2021-12-18 Analytic number theory/submission.tex
Final corrections

@@
 In a later chapter, the book also proves the general result \cite[Chapter VII, Theorem 5.14]{neukirch}.
-I am pretty sure that those are exactly the functions $L(\chi, s)$ that we defined above.
+I am pretty sure that those are exactly the functions $L(s, \chi)$ that we defined above.
 \begin{corollary}[Question (iii)]
@@
     \end{equation*}
+    Since the right-hand side converges absolutely for $\Re(s) > 1$, we see that $L(s, \chi)'/L(s, \chi)$ has no pole and so $L(s, \chi)$ is nonzero on $\Re(s) > 1$.
 \end{proposition}
@@
     \end{equation*}
-    defined on $\Re(s) > 1$ has a meromorphic continuation to $\Re(s) > 0$ with a simple poles at $1$ (and possibly other poles on $\Re(s) > 0$), provided that $L(\chi, 1) \neq 0$ for all $\chi \in \mathrm{Dir}(q) \setminus \{ \chi_0 \}$.
+    defined on $\Re(s) > 1$ has a meromorphic continuation to $\Re(s) > 0$ with a simple poles at $1$ (and possibly other poles on $\Re(s) > 0$), provided that $L(1, \chi) \neq 0$ for all $\chi \in \mathrm{Dir}(q) \setminus \{ \chi_0 \}$.
 \end{lemma}
@@
     \begin{equation*}
-        \rho_a(s) = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {L(\chi, s)'} {L(\chi, s)}
+        \rho_a(s) = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \sum_{n \geq 1} \frac {L(s, \chi)'} {L(s, \chi)}
     \end{equation*}

### 2021-12-19 Analytic number theory/submission.tex
Add proof that sum_p f(p)/p is negative to ANT

@@
 \begin{example}[Question (ii)]
+    \label{ex:l_series_mod_4}
     Let $f: \N \to \C$ be the Dirichlet character from Example~\ref{ex:nontrivial_dirichlet_character_mod_4} with corresponding group homomorphism $g: (\Z/4\Z)^\units \to \C$.
@@
     is positive. 
-    Wolfram Alpha \cite{wolfram_alpha} can give an explicit value to this sum, using the digamma function $\psi$. Namely
+    Wolfram Alpha \cite{wolfram_alpha} can give an explicit value to this sum. Namely
     \begin{equation*}
-        \sum_{x \in (\Z/4\Z)^\units} f(n) n^{-1} = \frac 1 4 (\psi(\frac 7 4) - \psi(\frac 5 4))
+        \sum_{n \geq 1} f(n) n^{-1} = \frac 2 3 + \frac 1 3 + \frac \pi 4 - 1 = \frac \pi 4
     \end{equation*}
-    which seems to be $\frac 1 4$.
 \end{example}
@@
     \begin{equation*}
-        \sum_p \frac {f(p)} {p^s} = \log( L(f, s) ) + O( \zeta(2\Re(s)) )
+        \sum_p \frac {f(p)} {p^s} = \log( L(s, f) ) + O( \zeta(2\Re(s)) )
     \end{equation*}
-    In particular, we see that
+    and so
     \begin{equation*}
@@
     \end{equation*}
-    exists.
+    exists. Furthermore, this value is negative.
 \end{example}
 \begin{proof}
-    By Taylor series expansion, see that
+    By Taylor series expansion, see
     \begin{equation*}
-        \log(1 - x) = -x + O(|x|^2)
+        \log(1 - x) = -x + O(x^2)
     \end{equation*}
@@
     \begin{align*}
-        \log( L(f, s) ) =& \log\Bigl( \prod_p \sum_{k \geq 0} \frac {f(p^k)} {p^{ks}} \Bigr) = \log\Bigl( \prod_p \frac 1 {1 - f(p)/p^s} \Bigr) \\
+        \log( L(s, f) ) =& \log\Bigl( \prod_p \sum_{k \geq 0} \frac {f(p^k)} {p^{ks}} \Bigr) = \log\Bigl( \prod_p \frac 1 {1 - f(p)/p^s} \Bigr) \\
         =& \sum_p -\log\Bigl( 1 - \frac {f(p)} {p^s} \Bigr) = \sum_p \frac {f(p)} {p^s} + O\Bigl( \frac {f(p)^2} {p^{2\Re(s)}} \Bigr) \\
-        = & \sum_p \frac {f(p)} {p^s} + O\Bigl( \underbrace{\sum_p \frac {f(p)} {p^{2\Re(s)}}}_{\leq \zeta(2\Re(s))} \Bigr) = \sum_p \frac {f(p)} {p^s} + O(\zeta(2\Re(s)))
+        = & \sum_p \frac {f(p)} {p^s} + O\Bigl( \underbrace{\sum_p \frac {f(p)^2} {p^{2\Re(s)}}}_{\leq \zeta(2\Re(s))} \Bigr) = \sum_p \frac {f(p)} {p^s} + O(\zeta(2\Re(s)))
     \end{align*}
+    Note further that for $|x| \leq \frac 1 2$
+    \begin{align*}
+        \Bigl| \log(1 - x) + x + \frac {x^2} 2 \Bigr| \leq \Bigl| \frac {2x^3} 3 \Bigr|
+    \end{align*}
+    as by Taylor series expansion, find
+    \begin{equation*}
+        \log(1 - x) = -\sum_{n \geq 1} \frac {x^n} {n}
+    \end{equation*}
+    Thus
+    \begin{align*}
+        \Bigl| \log(L(s, f)) - \sum_p \frac {f(p)} {p^s} - \frac 1 2 \sum_p \frac {f(p)^2} {p^{2s}} \Bigr| \leq \frac 2 3 \sum_p \Bigl| \frac {f(p)^3} {p^{3s}} \Bigr|
+    \end{align*}
+    and since
+    \begin{equation*}
+        \frac 2 3 \sum_p \Bigl| \frac {f(p)^3} {p^3} \Bigr| \leq \frac 2 3 \sum_{n \geq 2} \frac 1 {n^3} = \frac 2 3 (\zeta(3) - 1) < \frac 1 5
+    \end{equation*}
+    we see that
+    \begin{equation*}
+        \sum_p \frac {f(p)} p < \frac 1 5 - \underbrace{\frac 1 2 \sum_p \frac {f(p)^2} {p^2}}_{\geq 0} + \underbrace{\log(L(1, f))}_{\leq -1/5} \leq 0
+    \end{equation*}
+    is negative.
+    Here I used that $\zeta(3) \leq 13/10$ and $L(1, f) \leq \exp(-1/5)$, both of which can be considered generally known (see e.g.
+the previous example and \cite{wolfram_alpha}) and can be easily checked using a computer.
 \end{proof}

### 2021-12-19 Algebraic geometry/submission.tex
small fixed, mainly to ANT
Final corrections
Finished alg geo

@@
 \title{Miniproject - Algebraic Geometry}
-\author{Simon Pohmann}
-\date{}
+\author{Student Number: 1462479}
+\date{19.02.2021}
 
@@
 
-For this document, let $V$ be a finitely dimensional vector space with basis $B = (b_1, ..., b_n)$.
+\subsection*{Introduction}
+
+In this Miniproject, we want to study the Grassmanian
+\begin{equation*}
+    \Gr(d, V) := \{ U \subseteq V \ | \ U \ \text{$d$-dimensional subspace} \}
+\end{equation*}
+as an object of Algebraic Geometry.
+First of all, this requires finding a ``natural'' embedding of $\Gr(d, V)$ in to projective space, and showing that w.r.t. that embedding, the Grassmanian is a projective variety.
+
+After that is established, we can continue to study its geometric properties, like vanishing ideal, dimension and degree.
+This part will only be considered in the case $d = 2$.
+
+\subsection*{Conventions}
+We use the convention that $\N = \{ n \in \Z \ | \ n \geq 0 \}$.
+Further, we write $a \divides b$ if $a$ divides $b$ and $a \perp b$ if $a$ and $b$ are coprime.
+During this Miniproject, let $V$ be a finitely dimensional vector space with basis $B = (b_1, ..., b_n)$.
 
@@
 
-    Note that by definition, the vectors $b_{i_1} \wedge ... \wedge b_{i_d}$ for any $1 \leq i_1, ..., i_d \leq n$ span $\extpow^d V$.
+    Note that by definition, the vectors $b_{i_1} \wedge ... \wedge b_{i_d}$ for $1 \leq i_1, ..., i_d \leq n$ span $\extpow^d V$.
     By Lemma~\ref{prop:basic_properties_exterior_product}, we can rewrite any of them (that is nonzero) to be of the above form, so clearly the $b_{i_1} \wedge ...
@@
     \label{prop:equations_grassmanian_2}
-    For the embedding $\phi: \Gr(2, V) \to \extpow^2 V$ we have
+    For the embedding $\phi: \Gr(2, V) \to \Proj(\extpow^2 V)$ we have
     \begin{equation*}
@@
 \begin{proof}
-    We show that the set $G = \{ x_{iv} x_{ju} - x_{iu} x_{jv} + x_{ij} x_{uv} \ | \ i < j < u < v \}$ is a Gröbner basis of $I$.
+    We show that the set $G = \{ x_{iv} x_{ju} - x_{iu} x_{jv} + x_{ij} x_{uv} \ | \ i < j < u < v \}$ is a Gröbner basis of $I$
+    \footnote{In this proof, we write $x_{ij} := x_{i, j}$ to somewhat simplify notation.}.
     The claim then follows by the properties of Gröbner basis.
@@
 At first glance, this lemma above seems quite deep, but it really is a repetitive application of the theory of Gröbner basis.
+\begin{corollary}
+    Using the notation of Prop.~\ref{prop:equations_grassmanian_2}, we get that
+    \begin{equation*}
+        \I(\Gr(2, V)) = I
+    \end{equation*}
+\end{corollary}
+\begin{proof}
+    By Hilbert's Nullstellensatz, it is sufficient to show that $I$ is radical, as we know from Prop.~\ref{prop:equations_grassmanian_2} that $\V(I) = \Gr(2, V)$.
+    This follows from a very standard argument in Commutative Algebra, but for completeness, we will present the full proof here.
 
+    Assume that $f^d \in I$ for some $f \in R$.
+    We show that $f \in I$ by using induction on the position of $\mathrm{lt}(f)$ w.r.t. $\preceq$ (note that this is a well-ordering, so we can use induction on it).
+    The base case $f \in k$ is trivial, so assume that $f$ is not constant.
+
+    By Lemma~\ref{prop:leading_term_ideal_grassmanian} we see that
+    \begin{equation*}
+        \mathrm{lt}(f)^d = \mathrm{lt}(f^d) \in J = \langle x_{i, v} x_{j, u} \ | \ i < j < u < v \rangle
+    \end{equation*}
+    Hence
+    \begin{equation*}
+        \mathrm{lt}(f)^d \equiv x_{i, v} x_{j, u}
+    \end{equation*}
+    for some $i < j < u < v$.
+    Clearly $x_{i, v} \perp x_{j, u}$, and it follows that
+    \begin{equation*}
+        x_{i, v} x_{j, u} \divides \mathrm{lt}(f)
+    \end{equation*}
+    Now consider
+    \begin{equation*}
+        f' := f - \frac {\mathrm{lt}(f)} {x_{i, v} x_{j, u}} (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v}) \in R
+    \end{equation*}
+    Clearly $\mathrm{lt}(f') \prec \mathrm{lt}(f)$ as $x_{i, v} x_{j, v}, x_{i, j} x_{u, v} \prec x_{i, v} x_{j, u} \equiv \mathrm{lt}(f)$.
+    Furthermore
+    \begin{equation*}
+        (f')^d = \sum_{l = 0}^d {d \choose i} f^i (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v})^{d - i} \in I
+    \end{equation*}
+    so by induction hypothesis, find that $f' \in I$.
+    It follows that also
+    \begin{equation*}
+        f = f'  - \frac {\mathrm{lt}(f)} {x_{i, v} x_{j, u}} (x_{i, v} x_{j, u} - x_{i, u} x_{j, v} + x_{i, j} x_{u, v}) \in I
+    \end{equation*}
+    and the claim is shown.
+\end{proof}
 Now we have to study the structure of monomials generating $J = \langle x_{i, v} x_{j, u} \ | \ i < j < u < v \rangle$.
@@
 \lstinputlisting[language = python]{./gr26.sage}
+
+\subsection*{Conclusion}
+We have seen that the linear dependency structure between $d$-element subsets of $V$ can be described very well using the external power $\extpow^d V$.
+Therefore, this might look like a good candidate for describing the Grassmanian, and in this Miniproject, we have seen that indeed it is.
+In particular, it can provide a natural projective space in which to embed the Grassmanian, so that it becomes a projective variety.
+
+After this embedding is constructed, we have shown its close connection to the determinant, which is also a good way to describe linear dependency structures.
+Notably, the determinant is linear in each column or row, and the external product $\cdot \wedge ... \wedge \cdot$ is linear in each component.
+After that, we restricted to the case $d = 2$ and looked at the properties of $\Gr(2, d)$ as projective variety.
+Here we could show that the variety is cut out by quadratic equations, and analyse the concrete varieties $\Gr(2, 4), \Gr(2, 5)$ and $\Gr(2, 6)$ in detail.
+
+Finally, we have used some techniques from the theory of Gröbner basis in Commutative Algebra to further study the general case of $\Gr(2, n)$.
+These methods are quite useful to handle many multivariate polynomials, and in particular the cancellations that can occur when considering $R$-combinations of them.
+As a result of this part, we could determine the vanishing ideal of $\Gr(2, n)$.
+Furthermore, we could reduce the question of dimension and degree of $\Gr(2, n)$ to graph-theoretic questions and solve the one corresponding to the dimension.
+
+Continuing this study of the Grassmanian, the most obvious problem is of course how $\Gr(d, n)$ looks like for $d > 2$.
+In the lecture, we have already seen the degree formula
+\begin{equation*}
+    \deg(\Gr(d, n)) = (d(n - d))! \frac {1! \cdot 2! \cdot ... \cdot (d - 1)!} {(n - d)! \cdot (n - d + 1)! \cdot ... \cdot (n - 1)!}
+\end{equation*}
+and it seems possible that it could be proved by extending the techniques considered at the end of this Miniproject.
+However, the combinatorial problem will probably become significantly more complicated.
+Other question the work naturally leads to are about more properties of the Grassmanian.
+For example, one could show that it is an irreducible and nonsingular variety.
+Furthermore, we could consider intersections of subspaces.
+Here it would be interesting if or how one can describe them using external products, and if we maybe have a rational map
+\begin{equation*}
+    \Gr(d, n) \times \Gr(e, n) \to \Gr(d + e - n, n), \quad (U, V) \mapsto U \cap V
+\end{equation*}
+for $d + e \geq n$.
+All in all, Grassmanians are very fascinating objects, with a lot of nice properties.
+There are definitely a lot of interesting questions about them.
+
 \printbibliography

### 2021-12-19 Algebraic geometry/submission.tex
Added introduction & conclusion to ANT

@@
     Let $\preceq$ be a graded monomial ordering on $R = k[x_0, ..., x_n]$.
-    Then for an ideal $I \leq R$ have that the list of all monomials $x_0^{\alpha_0}, ..., x_n^{\alpha_n} \notin \mathrm{lt}(I)$ not contained in $\mathrm{lt}(I)$ are a $k$-vector space basis of $R/I$.
+    Then for an ideal $I \leq R$ have that the list of all monomials $x_0^{\alpha_0}, ..., x_n^{\alpha_n} \notin \mathrm{lt}(I)$ not contained in the leading term ideal $\mathrm{lt}(I)$ are a $k$-vector space basis of $R/I$.
 
@@
 \end{proof}
-To apply this, first of all we have to collect information about the leading term ideal of $\I(\Gr(2, n))$.
+To apply this, first of all we have to collect information about the leading term ideal of $I$.
 This is done in the following lemma.
@@
     \begin{equation*}
-        \mathrm{lt}(f)^d \equiv x_{i, v} x_{j, u}
+        \mathrm{lt}(f)^d \equiv t x_{i, v} x_{j, u}
     \end{equation*}
-    for some $i < j < u < v$.
+    for some $i < j < u < v$ and any monomial $t \in R$.
     Clearly $x_{i, v} \perp x_{j, u}$, and it follows that

### 2021-12-19 Analytic number theory/submission.tex
Added introduction & conclusion to ANT

@@
 \title{Miniproject - Analytic Number Theory}
-\author{Simon Pohmann}
-\date{}
+\author{Student Number: 1462479}
+\date{19.12.2021}
 
@@
 \maketitle
+
+\subsection*{Introduction}
+In this Miniproject, we want to generalize the notion of the Riemannian Zeta function $\zeta(s)$ to investigate the frequency of primes in arithmetic progressions.
+The central notion to do so is to consider Dirichlet characters $\chi: \N \to \C$.
+We define this kind of map and study some of its properties.
+
+After that, we introduce the Dirichlet series corresponding to a Dirichlet character, denoted by $L(s, \chi)$.
+Using this series, we follow a path somewhat similar to what was done in the lecture to show an important part of Dirichlet's prime number theorem.
+
+\subsection*{Conventions}
 We use the convention that $\N = \{ n \in \Z \ | \ n \geq 0 \}$.
@@
 \section{Part I}
-
 For convenience, we include the definition of a Dirichlet character from the task description first.
@@
 
+\subsection*{Conclusion}
+In this work, we have seen the basic structure of Dirichlet characters and their connection to the group $(\Z/q\Z)^\units$.
+Furthermore, we have studied some properties of the series $L(s, \chi)$, in particular its analytic continuation to $\Re(s) > 0$ and an identiy for its logarithmic derivative.
+By using the theory developed before, we could then establish a connection between the latter and the distribution of primes $\equiv a \pmod q$.
+Assuming now a statement on the zeros of $L(s, \chi)$, we were able to prove Dirichlet's prime number theorem, namely that there are infinitely many primes $\equiv a \pmod q$ for all $a \perp q$ in the case of primes $q$.
+
+Finally, we have also seen a very short detour into analyzing primes $\equiv 1 \mod q$ using Algebraic Number theory.
+For this, we used the theory of cyclotomic number fields, which already hints at the strong connection of $L(s, \chi)$ to cyclotomic number fields that I could see in further literature.
+Of course, also the encounter of the group $(\Z/q\Z)^\units$ and the connection of Dirichlet characters to roots of unity go into that direction.
+
+Of course, the most central question when continuing on this path is to proof the fact $L(1, \chi) \neq 0$ for $\chi \neq \chi_0$ and thus complete the proof of Dirichlet's prime number theorem.
+After that, it seems to be possible to use further techniques from the lecture (like Perron's formula) and show some kind of ``modular prime number theorem'', i.e.
+study the asymptotical frequency of primes $\equiv a \mod q$.
+Since we already have a connection between $\Psi_a$ and $L(s, \chi)'/L(s, \chi)$ to which we could apply Perron's formula, we already have some ingredients for this proof.
+To complete this, it would now be necessary to apply theorems like the ones from Chapter 9 in the lecture to $L(s, \chi)$, and then prove some kind of zero-free region for $L(s, \chi)$.
+This would then show that
+\begin{equation*}
+    \rho_a(s) = \sum_{n \equiv a \ (\text{mod $q$})} \Lambda(n) n^{-s} = \frac 1 {q - 1} \sum_{\chi \in \mathrm{Dir}(q)} \overline{\chi(a)} \frac {L(s, \chi)'} {L(s, \chi)}
+\end{equation*}
+has only one simple pole at $1$ in the zero-free region.
+Using Cauchy's Residue theorem and moving the left contour of integration just left of the line $\Re(s) = 1$, we could then show a statement like $|\{ p \in \primes \ | \ p \equiv a \pmod q, p \leq x\}| \sim x / \log(x) / (q - 1)$, or whatever statement holds on the asymptotic frequency of primes in arithmetic progressions.
+
+All in all, we have seen how to study primes in congruence classes modulo $q$ using analytic techniques.
+As in the lecture, the next questions mainly deal with the distribution of zeros of $L(s, \chi)$.
+
 \printbibliography

### 2021-12-19 Combinatorics/submission.tex
Final corrections
added introduction and conclusion to combinatorics

@@
 \maketitle
+
+\subsection*{Introduction}
+In this work, we will look at the LYM inequality
+\begin{equation*}
+    \sum_{i = 0}^n \frac {|A \cap L_i|} {|L_i|} \leq 1 \quad \text{for an antichain $A \subseteq \powerset(n)$}
+\end{equation*}
+and see how it generalizes to other posets than $\powerset(n)$.
+In particular, it will be necessary to study posets that can be decomposed into layers $L_0, ..., L_n$, which we will call graded posets.
+The goal then is to give a characterization of which posets satisfy such an inequality and then apply this to two examples.
+These are the collection of partitions of $[n]$, ordered by refinement, and the collection of multi-subsets of a multiset.
 
@@
 In this part, we show that sufficiently symmetric posets satisfy the conditions introduced in the previous part.
-We even show a slightly stronger stronger statement than required in the task, namely that the implication to the second condition of Prop.\ref{prop:characterization_lym} already holds ``locally'', i.e.
+We even show a slightly stronger stronger statement than required in the task, namely that the implication to the second condition of Prop.~\ref{prop:characterization_lym} already holds ``locally'', i.e.
 for each layer separately.
@@
 \section{Part IV}
+Now we will present the first example of this Miniproject, namely the collection of partitions of $[m]$, ordered by refinement.
 \begin{example}
@@
     \begin{equation*}
-        S(m, 1) = 1 \quad \text{and} \quad S(m, k) = \sum_{n = 1}^{m - 1} {m - 1 \choose n} S(n, k - 1)
+        S(m, 1) = 1 \quad \text{and} \quad S(m, k) = \sum_{n = k - 1}^{m - 1} {m - 1 \choose n} S(n, k - 1)
     \end{equation*}
@@
         =& \sum_{i = 1}^m {m - 1 \choose i - 1} S(m - i, k - 1) = \sum_{i = 0}^{m - 1} {m - 1 \choose m - i - 1} S(i, k - 1) \\
-        =& \sum_{i = 1}^{m - 1} {m - 1 \choose i} S(i, k - 1)
+        =& \sum_{i = 1}^{m - 1} {m - 1 \choose i} S(i, k - 1) = \sum_{n = k - 1}^{m - 1} {m - 1 \choose n} S(n, k - 1)
     \end{align*}
-    as for $k > 1$ have that $S(0, k) = 0$.
+    as for $k > 1$ have that $S(0, k) = 0$ and $S(m, k) = 0$ if $m < k$.
 \end{proof}
@@
 \section{Part V}
+Now we come to the second example, namely multi-subsets of a $d$-element multiset, ordered by containment.
+Note that we can characterize multisets in different ways, e.g. as vectors $\N^d$ ordered elementwise, or as natural numbers ordered by divisibility.
+In this section, we will focus on the former perspective, but in the last part, we will have a short remark on the latter view.
 \begin{example}
@@
 \begin{proposition}
+    \label{prop:lym_variant_partitions}
     Let $\mathcal{A} \subseteq \Pi_m$ be a nonempty antichain. Then define
@@
 
+\subsection*{Conclusion}
+In this work, we have seen how to generalize the decomposition into layers of $\powerset(n)$ to other posets, which we call graded.
+Based on this, we could state an analogue of the LYM inequality for those posets, and give a characterization of it.
+Further, we found that indeed, the inequality does not hold for arbitrary graded posets, so the posets with LYM-inequality form a proper subclass of all graded posets.
+We have both seen an example of a graded poset with LYM-inequality (that is not $\powerset(n)$) and an example of a graded poset without LYM-inequality.
+
+Additionally, during the attempts to prove the first of those statements, we discovered a polynomial time algorithm (in the size of the poset) that can check whether a given graded poset has an LYM inequality.
+By considering the situation modulo symmetry, we could improve the algorithm such that its running time is polynomial in the count of orbits of the poset under its automorphism group.
+Of course, this improvement requires knowledge of the automorphism group, but in many cases (like for partitions or multisets), the elements of the poset consist of many ``parts'' and the automorphism group is given by all the permutations of those parts.
+We have implemented an ran this algorithm for the case of multisets.
+
+Finally, we had a short look at the literature, and included the proof that the collection of multisets indeed has an LYM-inequality.
+Interestingly, this topic of LYM generalizations seems to have been an important research topic in the last century.
+
+There are some questions that arise naturally from this work.
+Primarily, it might be the case that there are inequalities similar to the LYM inequality, as e.g. in Prop.~\ref{prop:lym_variant_partitions}.
+To me, it looks like one could at least provide an LYM-variant for arbitrary graded posets by weighting elements in each orbit of the automorphism group differently.
+The idea would then be similar to Prop.~\ref{prop:core_of_multisets}, but yield another result, without requiring the relatively complicated assumption.
+
+Of course, there are quite a lot of common graded posets, and it is an interesting question which of those satisfy the LYM inequality.
+I have seen quite a lot of literature about that, so it would certainly be a promising way to continue this work.
+
+In the end, this Miniproject generalized some aspects of the first section of the lecture to a wider class of posets.
+
 \section{Appendix (Code described in Part VI)}

### 2021-12-19 Algebraic geometry/submission.tex
Done last proofreading of alg geo

@@
 as an object of Algebraic Geometry.
-First of all, this requires finding a ``natural'' embedding of $\Gr(d, V)$ in to projective space, and showing that w.r.t. that embedding, the Grassmanian is a projective variety.
+First of all, this requires finding a ``natural'' embedding of $\Gr(d, V)$ into projective space, and showing that w.r.t. that embedding, the Grassmanian is a projective variety.
 
 After that is established, we can continue to study its geometric properties, like vanishing ideal, dimension and degree.
-This part will only be considered in the case $d = 2$.
+In this part, we will restrict to $d = 2$.
 
@@
     \begin{align*}
-        &(u \wedge v \wedge v' \wedge w) + (u \wedge v' \wedge v \wedge w) = \sum_{i_1, ..., i_{j - 1}, i_{j + 2}, ..., i_d} \quad \sum_{0 \leq i, i' \leq n} \lambda_{i_1, ..., i_{j - 1}} \mu_{i_{j + 2}, ..., i_d} \tau_i \tau'_{i'} \\
+        &(u \wedge v \wedge v' \wedge w) + (u \wedge v' \wedge v \wedge w) = \sum_{i_1, ..., i_{j - 1}, i_{j + 2}, ..., i_d} \ \sum_{0 \leq i_j, i_{j + 1} \leq n} \lambda_{i_1, ..., i_{j - 1}} \mu_{i_{j + 2}, ..., i_d} \tau_{i_j} \tau'_{i_{j + 1}} \\
         &\Bigl(\underbrace{\bigl( b_{i_1} \wedge ...
@@
     \end{align*}
-    for all $u \in \extpow^{i - 1}(V), w \in \extpow^{(d - i - 1)}(V)$.
     Hence
@@
     \begin{align*}
-        u_1 \wedge u_2 =& \sum_{i, j} \ \lambda_i \mu_j (\underbrace{v_i \wedge v_j}_{\mathclap{\text{$= 0$ if $i = j$}}}) = \sum_{i < j} \lambda_i \mu_j (v_i \wedge v_j) - \sum_{i > j} \lambda_i \mu_j (v_i \wedge v_j) \\
+        u_1 \wedge u_2 =& \sum_{i, j} \ \lambda_i \mu_j (\underbrace{v_i \wedge v_j}_{\mathclap{\text{$= 0$ if $i = j$}}}) = \sum_{i < j} \lambda_i \mu_j (v_i \wedge v_j) + \sum_{i > j} \lambda_i \mu_j (v_i \wedge v_j) \\
         =& \sum_{i < j} (\lambda_i \mu_j - \lambda_j \mu_i)(v_i \wedge v_j) = \alpha (v_1 \wedge v_2) + \beta (v_1 \wedge v_3) + \gamma (v_2 \wedge v_3) \\
         =& \begin{cases}
-            \beta v_1 + \gamma v_2 \wedge \frac \alpha \beta v_2 + v_3 & \text{if $\beta \neq 0$} \\
-            \alpha v_1 - \gamma v_3 \wedge v_2 & \text{otherwise}
+            (\beta v_1 + \gamma v_2) \wedge (\frac \alpha \beta v_2 + v_3) & \text{if $\beta \neq 0$} \\
+            (\alpha v_1 - \gamma v_3) \wedge v_2 & \text{otherwise}
         \end{cases}
@@
     In other words
+    \footnote{Strictly speaking, we require here that $e_i \wedge e_j, i < j$ are linearly independent. However, we will prove this very soon anyway.}
     \begin{equation*}
@@
     \end{equation*}
-    due to the properties of the free product (the spaces share now basis vectors).
+    due to the properties of the free product (the spaces share no basis vectors).
 
@@
         \sum_{i_1 < ...
-< i_d} \lambda_{i_1, ..., i_d} \underbrace{\bigl( b_{i_1}, ..., b_{i_d} \bigr)}_{\sgn(\sigma_i) = 1 \ \text{as} \ \sigma_i = \mathrm{id}} = &\sum_{\substack{j, \ i_1, ..., i_d\\\sgn(\sigma_i) = 1}} \underbrace{\sgn(\sigma_i) \bigl( \mu_{j, i_1, ..., i_d} - \mu_{j, i_1, ..., i_{j + 1}, i_j, ..., i_d} \bigr)}_{=: \mu'_{j, i_1, ..., i_d}} \\
+< i_d} \lambda_{i_1, ..., i_d} \underbrace{\bigl( b_{i_1}, ..., b_{i_d} \bigr)}_{\sgn(\sigma_i) = 1 \ \text{as} \ \sigma_i = \mathrm{id}} = &\sum_{\substack{j, \ i_1, ..., i_d\\\sgn(\sigma_i) = 1}} \underbrace{\bigl( \mu_{j, i_1, ..., i_d} + \mu_{j, i_1, ..., i_{j + 1}, i_j, ..., i_d} \bigr)}_{=: \mu'_{j, i_1, ..., i_d}} \\
         &\Bigl( \bigl( b_{i_1}, ..., b_{i_d} \bigr) + \bigl( b_{i_1}, ..., b_{i_{j - 1}}, b_{i_{j + 1}}, b_{i_j}, b_{i_{j + 2}}, ..., b_{i_d} \bigr) \Bigr)
@@
         &-\sum_{\substack{j, \ i_1, ..., i_d\\\sgn(\sigma_i) = 1}} \Bigl( \mu'_{j, i_1, ..., i_d} - \begin{cases}
-            \lambda_{i_1, ..., i_d} & \text{if $i_1 < ... < i_d, j = 0$} \\
+            \lambda_{i_1, ..., i_d} & \text{if $i_1 < ... < i_d, j = 1$} \\
             0 & \text{otherwise}
@@
 \begin{proof}
-    wlog assume that $b_1, ..., b_m$ are a basis of $U$.
+    wlog assume that $b_1, ..., b_m$ are a basis of $W$.
     Then
     \begin{equation*}
-        w = \sum_{i_1 < ... < i_{d - 1} < m} \lambda_{i_1, ..., i_{d - 1} \leq m} (b_{i_1} \wedge ... \wedge b_{i_{d - 1}})
+        w = \sum_{i_1 < ... < i_{d - 1} \leq m} \lambda_{i_1, ..., i_{d - 1}} (b_{i_1} \wedge ... \wedge b_{i_{d - 1}})
     \end{equation*}
@@
         v \wedge w =& \sum_{i_1 < ... < i_{d - 1} \leq m} \lambda_{i_1, ..., i_{d - 1}} (v \wedge b_{i_1} \wedge ... \wedge b_{i_{d - 1}}) \\
-        =& \sum_{i_1 \leq n, \ i_1 < ... < i_{d - 1} \leq m} \mu_{i_1} \lambda_{i_2, ..., i_d} (b_{i_1} \wedge ... \wedge b_{i_d})
+        =& \sum_{i_1 \leq n, \ i_2 < ... < i_d \leq m} \mu_{i_1} \lambda_{i_2, ..., i_d} (b_{i_1} \wedge ... \wedge b_{i_d})
     \end{align*}
@@
         \sum_{i_1 \leq n, \ i_2 < ... < i_d \leq m} \Bigl( \mu_{i_1}\lambda_{i_2, ..., i_d} - \begin{cases}
-            \tau_{i_1, ..., i_d} & \text{if $i_1 \leq m$} \\
+            \tau_{i_1, ..., i_d} & \text{if $i_1 < i_2$} \\
             0 & \text{otherwise}
@@
     Hence by the previous Lemma~\ref{prop:basis_product_independence}, we see that for all $i_2 < ... < i_d \leq m < i_1 \leq n$ have
-    \begin{equation*}
-        0 = \mu_{i_1}\lambda_{i_2, ..., i_d} - \begin{cases}
-            \tau_{i_1, ..., i_d} & \text{if $i_1 \leq m$} \\
-            0 & \text{otherwise}
-        \end{cases}
-    \end{equation*}
-    So in particular find for all $i_2 < ... < i_d \leq m < i_1 \leq n$ that
     \begin{equation*}
@@
     \end{equation*}
-    So clearly $v_1 \wedge ... \wedge v_d \neq 0$ as $0 \wedge (v_{d + 1} \wedge ... \wedge v_n) = 0$ for all $v_{d + 1}, ..., v_n \in V$.
 \end{proof}
@@
 
-    Let $\omega = v_1 + ... + v_t$ for linearly independent decomposable vectors $v_i \in \extpow^2 V$.
+    Let $\omega = v_1 + ... + v_t$ for linearly independent decomposable vectors $v_i \in \extpow^d V$.
     Then
@@
         0 =& \omega \wedge \omega = \sum_{i, j} v_i \wedge v_j = \sum_{i < j} (v_i \wedge v_j) + (v_j \wedge v_i) \\
-        =& \sum_{i < j} 2(v_i \wedge v_j) = 2\sum_i v_i \wedge \Bigl( \sum_{j > i} v_j \Bigr)
+        \overset{*}{=}& \sum_{i < j} 2(v_i \wedge v_j) = 2\sum_i v_i \wedge \Bigl( \sum_{j > i} v_j \Bigr)
     \end{align*}
-    Here we used that the reversing permutation $\bigl(1 \ 2d\bigr)\bigl(2 \ (2d - 1)\bigr)...\bigl(d \ (d + 1)\bigr) \in S_{2d}$ has even parity, i.e. $\sgn(\cdot) = 1$ (since $d$ is even).
+    Here we used for $*$ that the reversing permutation $\bigl(1 \ 2d\bigr)\bigl(2 \ (2d - 1)\bigr)...\bigl(d \ (d + 1)\bigr) \in S_{2d}$ has even parity, i.e. $\sgn(\cdot) = 1$ (since $d$ is even).
 
@@
     It is clear by definition that $f$ is linear, so it is left to show that it is bijective. 
-    To show surjectivity, note that the $\pm e_I, I \in \{1, ..., n\}^{(d)}$ form a basis of $k^{\{1, ..., n\}^{(d)}}$.
+    To show surjectivity, note that the unit vectors $\pm e_I, I \in \{1, ..., n\}^{(d)}$ form a basis of $k^{\{1, ..., n\}^{(d)}}$.
     Clearly for $I = \{i_1, ..., i_d\}, J \in \{1, ..., n\}^{(d)}$ we have that
@@
     for $i_1 < ... < i_d$ form a basis of $\extpow^d k^n$ by Lemma~\ref{prop:basis_product_independence}.
-    It follows that $\dim(\extpow^d k^n) = \dim(\Proj^{\{1, ..., n\}^{(d)}})$ and we find that $f$ is also injective.
+    It follows that $\dim(\extpow^d k^n) = \dim(k^{\{1, ..., n\}^{(d)}})$ and we find that $f$ is also injective.
 \end{proof}
@@
     \begin{equation*}
-        x_{i, j} \leq x_{u, v} \ :\Leftrightarrow \ (i, j) \leq_{\text{lex}} (u, v)
+        x_{i, j} \leq x_{u, v} \ :\Leftrightarrow \ (i, j) \leq_{\text{lex}} (u, v) \ \Leftrightarrow \ i < u \ \text{or} \ i = u, j < v
     \end{equation*}
@@
     \end{equation*}
-    for some $i < j < u < v$ and any monomial $t \in R$.
+    for some $i < j < u < v$ and some monomial $t \in R$.
     Clearly $x_{i, v} \perp x_{j, u}$, and it follows that

### 2021-12-20 Analytic number theory/submission.tex
Use candidate number instead of student number
Finalized ANT

@@
 \title{Miniproject - Analytic Number Theory}
-\author{Student Number: 1462479}
+\author{Candidate Number: 1059926}
 \date{19.12.2021}
@@
     \begin{equation*}
-        \chi_f(a)\chi_f(b) = \chi([a])\chi([b]) = \chi([ab]) = \chi_f(ab)
+        \chi_f(a)\chi_f(b) = f([a])f([b]) = f([ab]) = \chi_f(ab)
     \end{equation*}
@@
     \begin{equation*}
-        \sum_{1 \leq n \leq X} \left| \chi(n) n^{-s} \right| \leq \sum_{1 \leq n \leq X} C \left| n^{-s} \right| \leq C \sum_{1 \leq n \leq X} \left| n^{-s} \right|
+        \sum_{X \leq n \leq Y} \left| \chi(n) n^{-s} \right| \leq \sum_{X \leq n \leq Y} C \left| n^{-s} \right| \leq C \sum_{X \leq n \leq Y} \left| n^{-s} \right|
     \end{equation*}
@@
         \sgn(c) \sum_{n \geq 1} \chi(n) n^{-s} &= \sum_{n \geq 0} \ \sum_{0 < k \leq q} \sgn(c) \chi(qn + k) (qn + k)^{-s} \\
-        &\geq \sum_{n \geq 0} \ \sum_{0 < k \leq q}\sgn(c) \chi(qn + k) (qn + n)^{-s} \\
-        &= \sum_{n \geq 0} \sgn(c) (qn + n)^{-s} \underbrace{\sum_{0 < k \leq q} \chi(qn + k)}_{= c} \\
-        &\geq \frac {|c|} {(q + 1)^s} \sum_{n \geq 1} n^{-s} = \frac {|c|} {(q + 1)^s} \zeta(s)
+        &\geq \sum_{n \geq 0} \ \sum_{0 < k \leq q}\sgn(c) \chi(qn + k) (qn + q)^{-s} \\
+        &= \sum_{n \geq 0} \sgn(c) (qn + q)^{-s} \underbrace{\sum_{0 < k \leq q} \chi(qn + k)}_{= c} \\
+        &= \frac {|c|} {q^s} \sum_{n \geq 1} n^{-s} = \frac {|c|} {(q + 1)^s} \zeta(s)
     \end{align*}
@@
         (qn)^{-s} - (qn + k)^{-s} &= \frac {(qn + k)^s - (qn)^s} {(q^2n^2 + qnk)^s} = (qn)^{s} \frac {(1 + k(qn)^{-1})^s - 1} {(q^2n^2 + qnk)^s} \\
-        &\leq (qn)^s \frac {sk(qn)^{-1}} {(q^2n^2 + qnk)^s} = \frac {sk} {qn(qn + k)^s} = O(sn^{-s - 1})
+        &\leq (qn)^s \frac {sk(qn)^{-1}} {(q^2n^2 + qnk)^s} = \frac {sk} {qn(qn + k)^s} = O(s(qn)^{-s - 1})
     \end{align*}
-    If $s > 1$ and $k \leq q$, then also $(qn)^{-s} - (qn + k)^{-s} = O(sn^{-(1 + \epsilon)})$ for some small enough $0 < \epsilon < 1$.
+    If $s > 1$ and $k \leq q$, then also $(qn)^{-s} - (qn + k)^{-s} = O(s(qn)^{-(1 + \epsilon)})$ for some small enough $0 < \epsilon < 1$.
     As $\chi((\Z/q\Z)^\units) \subseteq \C$ is finite, find $C > 0$ with $|\chi_f(n)| \leq C$ for all $n \in \N$. 
@@
         &\sum_{X \leq n \leq Y} \chi(n) n^{-s} \\
-        =& \ O(qCX^{-s} + qCY^{-s}) + \sum_{X/q \leq n \leq Y/q} \ \sum_{0 < k \leq q} \chi(qn + k) \Bigl( (qn)^{-s} + \underbrace{(qn + k)^{-s} - (qn)^{-s}}_{= O(sn^{-(1 + \epsilon)})} \Bigr) \\
-        =& \ O(qCX^{-s}) + \sum_{X/q \leq n \leq Y/q} \Bigl( (qn)^{-s} c + \sum_{0 < k \leq q} O(Csn^{-(1 + \epsilon)}) \Bigr) = \\
-        =& \ O(qCX^{-s}) + 0 + O\Bigl( Cqs \sum_{X/q \leq n \leq Y/q} n^{-(1 + \epsilon)} \Bigr) \\
-        =& \ O(qCX^{-s}) + O\Bigl( Cqs \sum_{n \geq X/q} n^{-(1 + \epsilon)} \Bigr)
+        =& \ O(qCX^{-s} + qCY^{-s}) + \sum_{X/q \leq n \leq Y/q} \ \sum_{0 < k \leq q} \chi(qn + k) \Bigl( (qn)^{-s} + \underbrace{(qn + k)^{-s} - (qn)^{-s}}_{= O(s(qn)^{-(1 + \epsilon)})} \Bigr) \\
+        =& \ O(qCX^{-s}) + \sum_{X/q \leq n \leq Y/q} \Bigl( (qn)^{-s} c + \sum_{0 < k \leq q} O(Cs(qn)^{-(1 + \epsilon)}) \Bigr) = \\
+        =& \ O(qCX^{-s}) + 0 + O\Bigl( Cqs \sum_{X/q \leq n \leq Y/q} (qn)^{-(1 + \epsilon)} \Bigr) \\
+        =& \ O(qCX^{-s}) + O\Bigl( Cq^{-\epsilon}s \sum_{n \geq X/q} n^{-(1 + \epsilon)} \Bigr)
     \end{align*}
@@
     as $X \to \infty$ (on $[\epsilon, \infty[$). 
-    Thus the limit is continuous and extends $L(s, \chi_f)$ defined on $]1, \infty[$.
-    It follows that $\lim_{t \to s^+} L(t, \chi_f)$ exists and is equal to $\sum_{n \geq 1} \chi(n) n^{-s}$.
+    Thus the limit is continuous and extends $L(s, \chi)$ defined on $]1, \infty[$.
+    It follows that $\lim_{t \to s^+} L(t, \chi)$ exists and is equal to $\sum_{n \geq 1} \chi(n) n^{-s}$.
 \end{proof}
@@
     \begin{equation*}
-        \log(1 - x) = -x + O(x^2)
+        \log(1 - x) = -x + O(|x|^2)
     \end{equation*}
@@
     \end{align*}
-    as by Taylor series expansion, find
+    as by Taylor series expansion, find for $|x| < 1$
     \begin{equation*}
@@
 In a later chapter, the book also proves the general result \cite[Chapter VII, Theorem 5.14]{neukirch}.
-I am pretty sure that those are exactly the functions $L(s, \chi)$ that we defined above.
+For this, it uses again the functions $L(s, \chi)$ as introduced here.
 \begin{corollary}[Question (iii)]
@@
         g: \N \to \C, \quad n \mapsto \begin{cases}
-            \omega^{\log_r n} & \text{if $n \perp q$} \\
+            \omega^{\log_{[r]} [n]} & \text{if $n \perp q$} \\
             0 & \text{otherwise}
@@
     Let $\chi: \N \to \C$ be a Dirichlet character with group homomorphism $f: (\Z/q\Z)^\units \to \C^\units$.
-    Then $\mathrm{im}f \leq S$ is a subgroup where $S_q := \{ \omega_q^k \ | \ k \in \Z \}$ is the group of $q$-th roots of unity.
+    Then $\mathrm{im}f \leq S_q$ is a subgroup where $S_q := \{ \omega_q^k \ | \ k \in \Z \}$ is the group of $q$-th roots of unity.
 
@@
     \begin{equation*}
-        \sum_{a \in (\Z/q\Z)^\units} \chi(a) = \sum_{k = 0}^{q - 2} \chi(r^k) = \sum_{k = 0}^{q - 2} \xi^k = \frac {1 - \xi^{q - 1}} {q - \xi} = 0 
+        \sum_{a \in (\Z/q\Z)^\units} \chi(a) = \sum_{k = 1}^{q - 1} \chi(r^k) = \sum_{k = 1}^{q - 1} \xi^k = \xi \frac {1 - \xi^{q - 1}} {q - \xi} = 0 
     \end{equation*}
@@
         \sum_{\chi \in \mathrm{Dir}(q)} \chi(a) &= \sum_{\chi \in \mathrm{Dir}(q)} \chi(r)^k \\
-        &= \sum_{\xi \ \text{$q$-th root of unity}} \xi^k = \sum_{l = 0}^{q - 2} \omega^{kl} = \frac {1 - (\omega^{q - 1})^k} {1 - \omega^k} = 0 
+        &= \sum_{\xi \ \text{$q$-th root of unity}} \xi^k = \sum_{l = 1}^{q - 1} \omega^{kl} = \omega^{k} \frac {1 - (\omega^{q - 1})^k} {1 - \omega^k} = 0 
     \end{align*}
@@
     \end{equation*}
-    The condition $ab^{-1} = 1$ is equivalent to $a \equiv b \pmod q$, so the claim follows.
+    The condition $[a][b]^{-1} = 1$ is equivalent to $a \equiv b \pmod q$, so the claim follows.
 \end{proof}
@@
     \label{prop:logarithmic_derivative_L_bounded}
-    The function $L(s, \chi)'/L(s, \chi)$ is bounded on a neighborhood of $1$, provided that $L(1, \chi) \neq 0$.
+    Let $\chi \neq \chi_0$ be a Dirichlet character modulo $q$.
+    Then the function $L(s, \chi)'/L(s, \chi)$ is bounded on a neighborhood of $1$, provided that $L(1, \chi) \neq 0$.
 \end{corollary}
@@
 
-    However, the derivative of a holomorphic function is again holomorphic, so $L(s, \chi)'$ has no pole at $s = 1$.
+    However, the derivative of a holomorphic function is again holomorphic, so $L(s, \chi)'$ has no pole at $s = 1$ (since we know that $L(s, \chi)$ has not pole at $s = 1$ for $\chi \neq \chi_0$).
     Provided that $L(1, \chi) \neq 0$, it follows that $L(s, \chi)'/L(s, \chi)$ is holomorphic on a compact neighborhood of $1$, so bounded.

### 2021-12-20 Combinatorics/submission.tex
Use candidate number instead of student number
Finalized combinatorics

@@
 \title{Miniproject - Combinatorics}
-\author{Simon Pohmann}
-\date{}
+\author{Candidate Number: 1059926}
+\date{19.12.2021}
 
@@
     \begin{equation*}
-        W \subseteq [t] \times F \ \Rightarrow \ |W| \leq t|F|
+        W \subseteq \{1\} \times [t] \times F \ \Rightarrow \ |W| \leq t|F|
     \end{equation*}
@@
     So Hall's theorem yields a matching $M \subseteq E$ from $V_1$ to $V_2$.
-    As $|V_1| = |V_2|$, this is already a 1-to-one correspondence.
+    As $|V_1| = |V_2|$, this is already a 1-to-1 correspondence.
 
@@
         \begin{align*}
-            S(m, 3) =& \sum_{n = 1}^{m - 1} {m - 1 \choose n} (2^{n - 1} - 1) = \frac 1 2 \sum_{n = 1}^{m - 1} {m - 1 \choose n} 2^n - \sum_{n = 1}^{m - 1} {m - 1 \choose n} 1 \\
+            S(m, 3) =& \sum_{n = 2}^{m - 1} {m - 1 \choose n} (2^{n - 1} - 1) = \frac 1 2 \sum_{n = 1}^{m - 1} {m - 1 \choose n} 2^n - \sum_{n = 1}^{m - 1} {m - 1 \choose n} 1 \\
             =&\frac 1 2 \sum_{n = 0}^{m - 1} {m - 1 \choose n} 2^n - \frac 1 2 - \sum_{n = 0}^{m - 1} {m - 1 \choose n} 1 + 1 \\
@@
 First of all, in Example~\ref{ex:partitions_have_no_lym} we have already shown that the poset $\Pi_m$ does not satisfy the conditions from Prop.~\ref{prop:characterization_lym}.
+Indeed, they do not satisfy (2) of Prop.~\ref{prop:characterization_lym} in a very strong sense:
+There is no constant $\epsilon > 0$ such that
+\begin{equation*}
+    \frac {|\partial F|} {|L_{i - 1}|} \geq \epsilon \frac {|F|} {|L_i|}
+\end{equation*}
+for all $F \subseteq L_i$.
+
 Now we want to investigate whether $\mathcal{P}_{k, d}$ does. 
@@
 
-    Assume there exists a matrix $A = (a_{ij}) \in \Q_{\geq 0}^{m \times n}$ such that
+    Assume there exists a matrix $A = (a_{ij}) \in \Q_{\geq 0}^{m \times n}$ such that for all $i, j$
     \footnote{We use $1 = (1, ..., 1)^T$ as the vector consisting of $1$ only here.}
     \begin{equation*}
-        1^T A 1 = 1
-    \end{equation*}
-    and for all $i, j$
-    \begin{equation*}
-        e_i^T A 1 = \frac 1 {|L_0|} \quad \text{and} \quad 1^T A e_j = \frac 1 {|L_1|}
+        e_i^T A 1 = \frac 1 {|L_{l - 1}|} \quad \text{and} \quad 1^T A e_j = \frac 1 {|L_l|}
     \end{equation*}
@@
 
-    Now consider a (finite) sequence of maximal chains $(C_k)_{k \in I}$ such that the chain corresponding to $u_i < v_j$ occurs $a_{ij} |I|$ times.
+    Now consider a (finite) sequence of maximal chains $(C_k)_{k \in I}$ such that the chain corresponding to $u_i < v_j$ occurs $a_{ij} |I|$ times (this exists as all the $a_{ij}$ are rational).
     By the assumption, we know that for each $i$ have
     \begin{equation*}
-        |\{k \ | \ u_i \in C_k\}| = \sum_{u_i < v_j} a_{ij}|I| = \frac 1 {|L_0|} |I|
+        |\{k \ | \ u_i \in C_k\}| = \sum_{u_i < v_j} a_{ij}|I| = \frac 1 {|L_{l - 1}|} |I|
     \end{equation*}
-    and so each element $u_i \in L_{l - 1}$ is contained in the same number $|I| / |L_0|$ of chains $C_k$.
+    and so each element $u_i \in L_{l - 1}$ is contained in the same number $|I| / |L_{l - 1}|$ of chains $C_k$.
 
@@
     \begin{equation*}
-        |\{k \ | \ v_j \in C_k\}| = \sum_{v_j > u_i} a_{ij}|I| = \frac 1 {|L_1|} |I|
+        |\{k \ | \ v_j \in C_k\}| = \sum_{v_j > u_i} a_{ij}|I| = \frac 1 {|L_l|} |I|
     \end{equation*}
@@
     Let $L_{l - 1} = \{u_1, ..., u_m\}$ and $L_l = \{v_1, ..., v_n\}$ be two consecutive layers of $\mathcal{C}_{k, d}$.
-    Assume there exists a matrix $A = (a_{ij}) \in \Q_{\geq 0}^{m \times n}$ such that 
-    \begin{equation*}
-        1^T A 1 = 1
-    \end{equation*}
-    and for all $i, j$
+    Assume there exists a matrix $A = (a_{ij}) \in \Q_{\geq 0}^{m \times n}$ such that for all $i, j$
     \begin{equation*}
@@
     \begin{equation*}
-        a(n_1, ..., n_k) := |\bigl\{ A \in \mathcal{A} \ \bigm| \ |A| = k, \ |\{ S \in A \ | \ |S| = j \}| = n_j \bigr\}|
+        a(n_1, ..., n_k) := |\bigl\{ A \in \mathcal{A} \ \bigm| \ |A| = k, \ |\{ S \in A \ | \ |S| = j \}| = |\{ i \ | \ n_i = j \}| \bigr\}|
     \end{equation*}
@@
 Note that the total number of partitions $\pi$ such that the classes in $\pi$ have sizes $n_1, ..., n_k$ is given by an expression involving the multinomial coefficient, namely
-\begin{equation*}
-    |\bigl\{ \pi \in \Pi_m \ \bigm| \ |\pi| = k, |\{ S \in \pi \ | \ |S| = j\}| = n_j \bigr\}| = {m \choose n_1, ..., n_k} \underbrace{ \prod_i \frac 1 {|\{ j \ | \ n_j = i\}|!} }_{=: \gamma(n_1, ..., n_k)}
-\end{equation*}
+\begin{align*}
+    &|\bigl\{ \pi \in \Pi_m \ \bigm| \ |\pi| = k, |\{ S \in \pi \ | \ |S| = j\}| \\
+    = &|\{ i \ | \ n_i = j \}| \bigr\}| = {m \choose n_1, ..., n_k} \underbrace{ \prod_i \frac 1 {|\{ j \ | \ n_j = i\}|!} }_{=: \gamma(n_1, ..., n_k)}
+\end{align*}
 Intuitively, the reason is that there are $m!$ ways to order the elements $[m]$, and after splitting such a sequence in chunks of sizes $n_1, ..., n_k$, there are $n_1!
@@
 \begin{equation*}
-    \Pi_m = \bigcup_{k \geq 1, \ n_1 \leq ... \leq n_k} \{ \pi \in \Pi_m \ | \ |\pi| = k, |\{ S \in \pi \ | \ |S| = j \}| = n_j \}
+    \Pi_m = \bigcup_{k \geq 1, \ n_1 \leq ... \leq n_k} \bigl\{ \pi \in \Pi_m \ | \ |\pi| = k, |\{ S \in \pi \ | \ |S| = j \}| = |\{ i \ | \ n_i = j \}| \bigr\}
 \end{equation*}

### 2022-01-19 Algebraic geometry/submission.tex
Finalized alg geo
Added note above the mistake I made

@@
 \usepackage{listings}
-\usepackage{stmaryrd}
-\usepackage[style=english]{csquotes}
+\usepackage[normalem]{ulem}
 \usepackage[language=english, backend=biber, style=alphabetic, sorting=nyt]{biblatex}
@@
 \title{Miniproject - Algebraic Geometry}
-\author{Student Number: 1462479}
+\author{Candidate Number: 1059926}
 \date{19.02.2021}
@@
     \begin{align*}
-        &(u \wedge v \wedge v' \wedge w) + (u \wedge v' \wedge v \wedge w) = \sum_{i_1, ..., i_{j - 1}, i_{j + 2}, ..., i_d} \ \sum_{0 \leq i_j, i_{j + 1} \leq n} \lambda_{i_1, ..., i_{j - 1}} \mu_{i_{j + 2}, ..., i_d} \tau_{i_j} \tau'_{i_{j + 1}} \\
+        &(u \wedge v \wedge v' \wedge w) + (u \wedge v' \wedge v \wedge w) = \sum_{i_1, ..., i_{j - 1}, i_{j + 2}, ..., i_d} \sum_{0 \leq i_j, i_{j + 1} \leq n} \lambda_{i_1, ..., i_{j - 1}} \mu_{i_{j + 2}, ..., i_d} \tau_{i_j} \tau'_{i_{j + 1}} \\
         &\Bigl(\underbrace{\bigl( b_{i_1} \wedge ...
@@
 \end{lemma}
-\begin{proof}
-    Now let $v_1, v_2, v_3$ be a set of generators of $V$.
-    Consider $u_1 = \sum \lambda_i v_i, u_2 = \sum_i \mu_i v_i, u_3 = \sum_i \rho_i v_i$.
-    Then by applying Lemma~\ref{prop:basic_properties_exterior_product}, we see that 
-    \begin{align*}
-        u_1 \wedge u_2 =& \sum_{i, j} \ \lambda_i \mu_j (\underbrace{v_i \wedge v_j}_{\mathclap{\text{$= 0$ if $i = j$}}}) = \sum_{i < j} \lambda_i \mu_j (v_i \wedge v_j) + \sum_{i > j} \lambda_i \mu_j (v_i \wedge v_j) \\
-        =& \sum_{i < j} (\lambda_i \mu_j - \lambda_j \mu_i)(v_i \wedge v_j) = \alpha (v_1 \wedge v_2) + \beta (v_1 \wedge v_3) + \gamma (v_2 \wedge v_3) \\
-        =& \begin{cases}
-            (\beta v_1 + \gamma v_2) \wedge (\frac \alpha \beta v_2 + v_3) & \text{if $\beta \neq 0$} \\
-            (\alpha v_1 - \gamma v_3) \wedge v_2 & \text{otherwise}
-        \end{cases}
-    \end{align*}
-    and
-    \begin{align*}
-        u_1 \wedge u_2 \wedge u_3 =& \sum_{i, j, l} \ \lambda_i \mu_j \rho_l (\underbrace{v_i \wedge v_j \wedge v_l}_{\mathclap{\text{$= 0$ unless $i, j, l$ pairwise distinct}}}) \\
-        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} (v_{\pi(1)} \wedge v_{\pi(2)} \wedge v_{\pi(3)}) \\
-        =& \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi) (v_1 \wedge v_2 \wedge v_3) \\
-        =& (v_1 \wedge v_2 \wedge v_3) \sum_{\pi \in S_3} \lambda_{\pi(1)} \mu_{\pi(2)} \rho_{\pi(3)} \sgn(\pi)
-    \end{align*}
-    are decomposable.
-    Further, it is easy to see from Lemma~\ref{prop:basic_properties_exterior_product} that $\extpow^k(V) = \{ 0 \}$ for $k \geq 4$, which is trivially decomposable.
-\end{proof}
+I did not include the proof here, as it contained a slight mistake.
 
@@
 \end{proof}
-Now we can see that in general, the exterior product contains not decomposable elements.
+Sadly, I have made a crucial mistake in my solution to the next question.
+This mistake boils down to the fact that in general
+\begin{equation*}
+    \extpow^{2d} V \not\cong \extpow^2 \extpow^d V
+\end{equation*}
+Observe e.g. that $\dim \extpow^4 k^3 = 0$ but $\dim \extpow^2 \extpow^2 k^3 = 3$.
+In fact, the next lemma only holds for $d = 2$.
 \begin{lemma}[Question (c)]
     \label{prop:characterization_decomposable_d_even}
-    Let $d$ be even.
+    Let $d$ be \sout{even} two.
     An element $\omega \in \extpow^d V$ is decomposable if and only if $\omega \wedge \omega \in \extpow^{2d} V$ is zero.
@@
     \end{align*}
-    Here we used for $*$ that the reversing permutation $\bigl(1 \ 2d\bigr)\bigl(2 \ (2d - 1)\bigr)...\bigl(d \ (d + 1)\bigr) \in S_{2d}$ has even parity, i.e. $\sgn(\cdot) = 1$ (since $d$ is even).
+    Here we used for $*$ that the reversing permutation $\bigl(1 \ 2d\bigr)\bigl(2 \ (2d - 1)\bigr)...\bigl(d \ (d + 1)\bigr) \in S_{2d}$ has even parity, i.e. $\sgn(\cdot) = 1$ (since $d$ is even)
+    \footnote{Here is the mistake: Here and further down, we consider $v_i \wedge v_j \in \extpow^2 \extpow^d V$, and so the permutation is just $(1 \ 2)$, which clearly has odd parity.
+    If we would consider $v_i \wedge v_j \in \extpow^{2d} V$, this step seems to work out, but below, we then cannot apply Lemma~\ref{prop:extpow_zero_iff_independent} and Lemma~\ref{prop:subspace_closed}}.
 
@@
 \begin{proof}
-    The idea is to apply Macaulay's basis theorem to get information about the Hilbert function of $\Gr(2, n)$.
+    The idea is to apply Macaulay's basis theorem to get information about the Hilbert function of the Grassmanian.
     To this end, observe that all the monomials generating $\mathrm{lt}(\I(\Gr(2, n)))$ are square-free.
